### 2010-06-07 ms/main.tex
Add a template for MS

\documentclass{report}
\usepackage{graphicx}
%\usepackage{fullpage}

\begin{document}

\input{titelblatt}

\tableofcontents
\chapter{Introduction}
\label{sec:intro}
To test bibliography~\cite{Monaghan2005}

\chapter{Method}
\label{sec:method}

\chapter{Results}
\label{sec:results}

\chapter{Conclusion}
\label{sec:conclusion}

\bibliography{bibdata}
\bibliographystyle{plain}

\end{document}

### 2010-06-07 ms/titelblatt.tex
Add a template for MS

% \documentclass[12pt]{article}

% \usepackage{ngerman}
% \selectlanguage{ngerman}
% \usepackage[latin1]{inputenc}

% \usepackage{graphicx}

% \begin{document}

\pagestyle{empty}

\begin{center}

\vspace*{-2.8cm}
\begin{minipage}[c]{.30\textwidth}
  \begin{flushleft}
    \includegraphics[width=3cm,clip=]{LOGO/new-aerlogo.eps}%
  \end{flushleft}
\end{minipage}
\begin{minipage}[c]{.43\textwidth}
    { ~\\ Lehrstuhl f\"{u}r Aerodynamik \\ Prof.~Dr.-Ing. N.~A.~Adams}%
\end{minipage}
\begin{minipage}[c]{.25\textwidth}
  \begin{flushright}
    \vspace*{1em}
    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB.eps}%
  \end{flushright}
\end{minipage}

\vspace*{3.3cm}
\begin{minipage}[c]{11cm}
{\LARGE\bf 
A Riemann solver }
\end{minipage}

\vspace*{0.8cm}
Mark F\"{o}rster\\

\vspace*{2.8cm}
{\bfseries Diplomarbeit}

\vspace*{1.2cm}
%\large
\normalsize
\vfill
\begin{tabular}{ll}
Betreuer: &  Dr.-Ing. Christian Stemmer \\
\ & \ \\
Ausgabe: & 1.\ Oktober 2008\\
Abgabe: & 31.\ M\"{a}rz 2009\\
\end{tabular}

\vspace*{1.6cm}
%\large
Lehrstuhl f\"{u}r Aerodynamik an der Technischen Universit\"{a}t M\"{u}nchen\\
2009
\end{center}

\pagebreak
\pagestyle{plain}

%\end{document}

### 2010-06-07 ms/formulas.tex
Add forumlas.tex: automaticly exported from openoffice (a lot of garbage)

% This file was converted to LaTeX by Writer2LaTeX ver. 1.0.2
% see http://writer2latex.sourceforge.net for more info
\documentclass[letterpaper]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=, pdfsubject=, pdfkeywords=}
% Page layout (geometry)
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{2cm}
\setlength\oddsidemargin{2cm}
\setlength\textheight{23.94cm}
\setlength\textwidth{17.59cm}
\setlength\footskip{0.0cm}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.119cm}
\renewcommand\footnoterule{\vspace*{-0.018cm}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.018cm}}\vspace*{0.101cm}}
% Pages styles
\makeatletter
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\title{}
\author{}
\date{2010-05-29}
\begin{document}
{\bfseries
Formulas used in 1D SPH Code:}

\bigskip

The equations employed are Euler Equation (without physical viscosity)

\bigskip

SPH Form of \textbf{continuity equation}:

\bigskip

For Sum Density mode:

\ \ \ \  $\rho _{a}=\sum {m_{b}W_{b}}$ which corresponds to (2.9)

\bigskip

For integrating density mode:

\ \ \ \  $\frac{d\rho _{a}}{\mathit{dt}}=\sum
{m_{b}v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}$ which corresponds to
(2.18)

\bigskip

\bigskip

SPH Form of \textbf{Momentum equation:}

\bigskip

as this is shock simulation a formulation including an artificial
viscosity is used:

\bigskip

\ \ \ \  $\frac{dv_{a}}{\mathit{dt}}=-\sum {m_{b}(\frac{P_{a}}{\rho
_{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi _{\mathit{ab}})\nabla
_{a}W_{\mathit{ab}}}$(8.2)

\bigskip

\ \ \ \  $\Pi _{\mathit{ab}}=-\nu
(\frac{v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
h_{\mathit{ab}}^{2}})$(8.3)

\bigskip

\ \ \ \  $\nu =\frac{h_{\mathit{ab}}}{\rho _{\mathit{ab}}}(\alpha
c_{\mathit{ab}}-\beta
\frac{h_{\mathit{ab}}v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
h_{\mathit{ab}}^{2}})$(8.10)

\bigskip

\bigskip

SPH Form of \textbf{Energy Equation}

\bigskip

including the artificial viscosity term (to be consistent, we have to
take into account the artificial viscosity in the energy equation as
well. For viscosity leads to a heating of the fluid)

\bigskip

\begin{equation*}
\frac{de_{a}}{\mathit{dt}}=-\mathit{}\frac{1}{2}\sum
{m_{b}(\frac{P_{a}}{\rho _{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi
_{\mathit{ab}})v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
\end{equation*}

\bigskip

This equation in the above form can not directly be found in the
Monaghan 2005 paper, but as (4.78) in the book smoothed particle
hydrodynamics (Liu).
\end{document}

### 2010-06-17 src/latex/annotated.tex
compressible branch

\section{Class List}
Here are the classes, structs, unions and interfaces with brief descriptions:\begin{CompactList}
\item\contentsline{section}{\hyperlink{classBetaSpline}{BetaSpline} (A concrete kernel class )}{\pageref{classBetaSpline}}{}
\item\contentsline{section}{\hyperlink{classBoundary}{Boundary} (\hyperlink{classBoundary}{Boundary} conditions )}{\pageref{classBoundary}}{}
\item\contentsline{section}{\hyperlink{classDiagnose}{Diagnose} (\hyperlink{classOutput}{Output} diagnosal )}{\pageref{classDiagnose}}{}
\item\contentsline{section}{\hyperlink{classForce}{Force} (The class defining force on or between particles )}{\pageref{classForce}}{}
\item\contentsline{section}{\hyperlink{classHydrodynamics}{Hydrodynamics} (Definition of materials and their hydrodynamical interactions )}{\pageref{classHydrodynamics}}{}
\item\contentsline{section}{\hyperlink{classInitiation}{Initiation} (Initiates the simulation )}{\pageref{classInitiation}}{}
\item\contentsline{section}{\hyperlink{classInteraction}{Interaction} (Defines interaction between particles )}{\pageref{classInteraction}}{}
\item\contentsline{section}{\hyperlink{classKernel}{Kernel} (\hyperlink{classKernel}{Kernel} abstract base )}{\pageref{classKernel}}{}
\item\contentsline{section}{\hyperlink{classLlist}{Llist$<$ Ldata $>$} (Double linked list implementation )}{\pageref{classLlist}}{}
\item\contentsline{section}{\hyperlink{classLlistNode}{LlistNode$<$ Ldata $>$} (A template node in the linked list )}{\pageref{classLlistNode}}{}
\item\contentsline{section}{\hyperlink{classMaterial}{Material} (\hyperlink{classMaterial}{Material} )}{\pageref{classMaterial}}{}
\item\contentsline{section}{\hyperlink{classMLS}{MLS} (Moving Least Squares (\hyperlink{classMLS}{MLS}) class )}{\pageref{classMLS}}{}
\item\contentsline{section}{\hyperlink{classOutput}{Output} (\hyperlink{classOutput}{Output} class )}{\pageref{classOutput}}{}
\item\contentsline{section}{\hyperlink{classParticle}{Particle} (\hyperlink{classParticle}{Particle} class )}{\pageref{classParticle}}{}
\item\contentsline{section}{\hyperlink{classParticleManager}{ParticleManager} (\hyperlink{classParticle}{Particle} manager class )}{\pageref{classParticleManager}}{}
\item\contentsline{section}{\hyperlink{classQuinticSpline}{QuinticSpline} (Quintic spline class )}{\pageref{classQuinticSpline}}{}
\item\contentsline{section}{\hyperlink{classTimeSolver}{TimeSolver} (Time solver class )}{\pageref{classTimeSolver}}{}
\item\contentsline{section}{\hyperlink{classWiener}{Wiener} (\hyperlink{classWiener}{Wiener} process )}{\pageref{classWiener}}{}
\end{CompactList}

### 2010-06-17 src/latex/betaspline_8h.tex
compressible branch

\hypertarget{betaspline_8h}{
\section{betaspline.h File Reference}
\label{betaspline_8h}\index{betaspline.h@{betaspline.h}}
}
Beta spline kernel function.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{betaspline_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classBetaSpline}{BetaSpline}
\begin{CompactList}\small\item\em A concrete kernel class. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Beta spline kernel function.

### 2010-06-17 src/latex/boundary_8cpp.tex
compressible branch

\hypertarget{boundary_8cpp}{
\section{boundary.cpp File Reference}
\label{boundary_8cpp}\index{boundary.cpp@{boundary.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for boundary.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{boundary_8cpp__incl}
\end{center}
\end{figure}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
\begin{Desc}
\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$

changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$, \end{Desc}

### 2010-06-17 src/latex/bskernel_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/boundary_8cpp.tex
@@
-\hypertarget{boundary_8cpp}{
-\section{boundary.cpp File Reference}
-\label{boundary_8cpp}\index{boundary.cpp@{boundary.cpp}}
+\hypertarget{bskernel_8cpp}{
+\section{bskernel.cpp File Reference}
+\label{bskernel_8cpp}\index{bskernel.cpp@{bskernel.cpp}}
 }
@@
 
-Include dependency graph for boundary.cpp:\nopagebreak
+Include dependency graph for bskernel.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{boundary_8cpp__incl}
+\includegraphics[width=420pt]{bskernel_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/classBetaSpline.tex
compressible branch

\hypertarget{classBetaSpline}{
\section{BetaSpline Class Reference}
\label{classBetaSpline}\index{BetaSpline@{BetaSpline}}
}
A concrete kernel class.

{\tt \#include $<$betaspline.h$>$}

Inheritance diagram for BetaSpline:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=106pt]{classBetaSpline__inherit__graph}
\end{center}
\end{figure}
Collaboration diagram for BetaSpline:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=106pt]{classBetaSpline__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classBetaSpline_00e744e584e6e7291813ab5e59d801ec}{BetaSpline} (double \hyperlink{classKernel_f088821dba4a00d1d320b27ebcb71258}{smoothingLength})
\begin{CompactList}\small\item\em constructor to initialize the data members and \item\end{CompactList}\item 
virtual double \hyperlink{classBetaSpline_797016b36239b0be98c3aa0715bb045a}{w} (double distance) const 
\begin{CompactList}\small\item\em Calculates the kernel value for the given distance of two particles. \item\end{CompactList}\item 
virtual Vec2d \hyperlink{classBetaSpline_409d22f7b4165a612ffbb62400e55db7}{gradW} (double distance, const Vec2d \&distanceVector) const 
\begin{CompactList}\small\item\em Calculates the kernel derivation for the given distance of two particles. \item\end{CompactList}\item 
\hypertarget{classBetaSpline_5b01a3303b3d45e74cdbff21419a07ff}{
double \hyperlink{classBetaSpline_5b01a3303b3d45e74cdbff21419a07ff}{F} (double distance) const }
\label{classBetaSpline_5b01a3303b3d45e74cdbff21419a07ff}

\begin{CompactList}\small\item\em Calculates the kernel derivation to distance. \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classBetaSpline_3cc93fb702c723e280f4c55aa7422def}{
double \hyperlink{classBetaSpline_3cc93fb702c723e280f4c55aa7422def}{norm}}
\label{classBetaSpline_3cc93fb702c723e280f4c55aa7422def}

\begin{CompactList}\small\item\em Normalization factor. \item\end{CompactList}\item 
\hypertarget{classBetaSpline_ca1e84910928d93dc2b7f4586f1102ac}{
double \hyperlink{classBetaSpline_ca1e84910928d93dc2b7f4586f1102ac}{reciprocH}}
\label{classBetaSpline_ca1e84910928d93dc2b7f4586f1102ac}

\begin{CompactList}\small\item\em Auxiliary factors for intermediate results: The inverse smoothing length $\ast$/. \item\end{CompactList}\item 
\hypertarget{classBetaSpline_06df50a142cacc03bfd3168cc6ae1f57}{
double \hyperlink{classBetaSpline_06df50a142cacc03bfd3168cc6ae1f57}{factorW}}
\label{classBetaSpline_06df50a142cacc03bfd3168cc6ae1f57}

\begin{CompactList}\small\item\em Auxiliary factors for intermediate results: A pre-factor for w $\ast$/. \item\end{CompactList}\item 
\hypertarget{classBetaSpline_0b285867c4f1d4b9fced5847650a47f8}{
double \hyperlink{classBetaSpline_0b285867c4f1d4b9fced5847650a47f8}{factorGradW}}
\label{classBetaSpline_0b285867c4f1d4b9fced5847650a47f8}

\begin{CompactList}\small\item\em Auxiliary factors for intermediate results: A pre-factor for grad w $\ast$/. \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
A concrete kernel class.

see Monaghan \& Lattanzio (1985) most often used kernel implemented in \hyperlink{bskernel_8cpp}{bskernel.cpp}

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classBetaSpline_00e744e584e6e7291813ab5e59d801ec}{
\index{BetaSpline@{BetaSpline}!BetaSpline@{BetaSpline}}
\index{BetaSpline@{BetaSpline}!BetaSpline@{BetaSpline}}
\subsubsection[{BetaSpline}]{\setlength{\rightskip}{0pt plus 5cm}BetaSpline::BetaSpline (double {\em smoothingLength})}}
\label{classBetaSpline_00e744e584e6e7291813ab5e59d801ec}

constructor to initialize the data members and

\begin{itemize}
\item initialize the auxiliary factors\end{itemize}

\begin{itemize}
\item normalize to 1.0 \end{itemize}

\subsection{Member Function Documentation}
\hypertarget{classBetaSpline_409d22f7b4165a612ffbb62400e55db7}{
\index{BetaSpline@{BetaSpline}!gradW@{gradW}}
\index{gradW@{gradW}!BetaSpline@{BetaSpline}}
\subsubsection[{gradW}]{\setlength{\rightskip}{0pt plus 5cm}Vec2d BetaSpline::gradW (double {\em distance}, \/  const Vec2d \& {\em distanceVector}) const\hspace{0.3cm}{\tt  \mbox{[}virtual\mbox{]}}}}
\label{classBetaSpline_409d22f7b4165a612ffbb62400e55db7}

Calculates the kernel derivation for the given distance of two particles.

We take this from Monaghan \& Lattenzio (1985) but used a doubled smoothing length for the definition of the interaction radius.

Implements \hyperlink{classKernel_545e61b98db05db6dd02b88e2ad3da23}{Kernel}.\hypertarget{classBetaSpline_797016b36239b0be98c3aa0715bb045a}{
\index{BetaSpline@{BetaSpline}!w@{w}}
\index{w@{w}!BetaSpline@{BetaSpline}}
\subsubsection[{w}]{\setlength{\rightskip}{0pt plus 5cm}double BetaSpline::w (double {\em distance}) const\hspace{0.3cm}{\tt  \mbox{[}virtual\mbox{]}}}}
\label{classBetaSpline_797016b36239b0be98c3aa0715bb045a}

Calculates the kernel value for the given distance of two particles.

We take this from Monaghan \& Lattenzio (1985) but used a doubled smoothing length for the definition of the interaction radius.

Implements \hyperlink{classKernel_6b4d26ba99457a4acbbbca1454dbdc8a}{Kernel}.

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{betaspline_8h}{betaspline.h}\item 
\hyperlink{bskernel_8cpp}{bskernel.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classBoundary.tex
compressible branch

\hypertarget{classBoundary}{
\section{Boundary Class Reference}
\label{classBoundary}\index{Boundary@{Boundary}}
}
\hyperlink{classBoundary}{Boundary} conditions.

{\tt \#include $<$boundary.h$>$}

Collaboration diagram for Boundary:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=192pt]{classBoundary__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classBoundary_8fe88473063d74e67a5932f2e4d2e517}{Boundary} (\hyperlink{classInitiation}{Initiation} \&ini, \hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classParticleManager}{ParticleManager} \&particles)
\begin{CompactList}\small\item\em boundary particle list for all boundray particles \item\end{CompactList}\item 
void \hyperlink{classBoundary_8a40f99b73f3622cd5f1387fcbbdb824}{BuildBoundaryParticles} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro)
\begin{CompactList}\small\item\em build boundary particles \item\end{CompactList}\item 
void \hyperlink{classBoundary_bedd190ee91482e4e59b2a613ab25d57}{BoundaryCondition} (\hyperlink{classParticleManager}{ParticleManager} \&particles)
\begin{CompactList}\small\item\em boundary conditions \item\end{CompactList}\item 
void \hyperlink{classBoundary_ac37e18aaf60503a66173d9428ed9e54}{RunAwayCheck} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro)
\begin{CompactList}\small\item\em check particle if particle run out of the computational domain \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
int \hyperlink{classBoundary_10dd58ba0715412968c4902fe80b1318}{xBl}
\begin{CompactList}\small\item\em boundary condition indicator left hand side \item\end{CompactList}\item 
int \hyperlink{classBoundary_4a582b489cb580b8a6f3a7123f411a53}{xBr}
\begin{CompactList}\small\item\em boundary condition indicator right hand side \item\end{CompactList}\item 
int \hyperlink{classBoundary_0329bf6b954b3001418391cc16a9194e}{yBd}
\begin{CompactList}\small\item\em boundary condition indicator bottom side \item\end{CompactList}\item 
int \hyperlink{classBoundary_6ccff2a8c5a10104d202504034af9e84}{yBu}
\begin{CompactList}\small\item\em boundary condition indicator upper side \item\end{CompactList}\item 
\hypertarget{classBoundary_238a4e6e7358e1f9a2375d8df08a5c7a}{
Vec2d \hyperlink{classBoundary_238a4e6e7358e1f9a2375d8df08a5c7a}{UxBl}}
\label{classBoundary_238a4e6e7358e1f9a2375d8df08a5c7a}

\begin{CompactList}\small\item\em left hand side boundary velocity \item\end{CompactList}\item 
\hypertarget{classBoundary_375a949ddac9f633af007daa7d323099}{
Vec2d \hyperlink{classBoundary_375a949ddac9f633af007daa7d323099}{UxBr}}
\label{classBoundary_375a949ddac9f633af007daa7d323099}

\begin{CompactList}\small\item\em right hand side boundary velocity \item\end{CompactList}\item 
\hypertarget{classBoundary_cf4a2665428f1516626bf683d1eeb4ba}{
Vec2d \hyperlink{classBoundary_cf4a2665428f1516626bf683d1eeb4ba}{UyBd}}
\label{classBoundary_cf4a2665428f1516626bf683d1eeb4ba}

\begin{CompactList}\small\item\em bottom side boundary velocity \item\end{CompactList}\item 
\hypertarget{classBoundary_47eeae29ae83c1ec9ed3a0fdd96bec23}{
Vec2d \hyperlink{classBoundary_47eeae29ae83c1ec9ed3a0fdd96bec23}{UyBu}}
\label{classBoundary_47eeae29ae83c1ec9ed3a0fdd96bec23}

\begin{CompactList}\small\item\em upper side boundary velocity \item\end{CompactList}\item 
\hypertarget{classBoundary_03c656384691f3575170447ab267b8a5}{
\hyperlink{classLlist}{Llist}$<$ \hyperlink{classParticle}{Particle} $>$ \hyperlink{classBoundary_03c656384691f3575170447ab267b8a5}{boundary\_\-particle\_\-list}}
\label{classBoundary_03c656384691f3575170447ab267b8a5}

\begin{CompactList}\small\item\em boundary particle lists \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classBoundary_bdce0051ff1e2651413242877a4fc507}{
void \hyperlink{classBoundary_bdce0051ff1e2651413242877a4fc507}{non\_\-dimensionalize} (\hyperlink{classInitiation}{Initiation} \&ini)}
\label{classBoundary_bdce0051ff1e2651413242877a4fc507}

\begin{CompactList}\small\item\em non-dimensionalize \item\end{CompactList}\item 
void \hyperlink{classBoundary_116df4b717184d962f40bdc88de26763}{show\_\-information} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em show information on screen \item\end{CompactList}\item 
\hypertarget{classBoundary_8879fae60c663d0bdf55acf44516cd42}{
void \hyperlink{classBoundary_8879fae60c663d0bdf55acf44516cd42}{Boundary\_\-W} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_8879fae60c663d0bdf55acf44516cd42}

\begin{CompactList}\small\item\em implement west side boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_e721f2c23112698b3cee9a3848f3deb1}{
void \hyperlink{classBoundary_e721f2c23112698b3cee9a3848f3deb1}{Boundary\_\-E} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_e721f2c23112698b3cee9a3848f3deb1}

\begin{CompactList}\small\item\em implement east side boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_50c82df28f8e11186b2f3e6f0bd971b0}{
void \hyperlink{classBoundary_50c82df28f8e11186b2f3e6f0bd971b0}{Boundary\_\-S} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_50c82df28f8e11186b2f3e6f0bd971b0}

\begin{CompactList}\small\item\em implement south side boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_ec89b3e4212c60f0b6a42199a844d032}{
void \hyperlink{classBoundary_ec89b3e4212c60f0b6a42199a844d032}{Boundary\_\-N} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_ec89b3e4212c60f0b6a42199a844d032}

\begin{CompactList}\small\item\em implement north side boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_5ec3b43fbe487290b3b3c584ffdfbd54}{
void \hyperlink{classBoundary_5ec3b43fbe487290b3b3c584ffdfbd54}{Boundary\_\-SW} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_5ec3b43fbe487290b3b3c584ffdfbd54}

\begin{CompactList}\small\item\em implement south-west corner boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_8a334d5f6950a17261504751a706ec78}{
void \hyperlink{classBoundary_8a334d5f6950a17261504751a706ec78}{Boundary\_\-SE} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_8a334d5f6950a17261504751a706ec78}

\begin{CompactList}\small\item\em implement south-east corner boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_75bfad6f3ef080a83ca3c0746f94ca4e}{
void \hyperlink{classBoundary_75bfad6f3ef080a83ca3c0746f94ca4e}{Boundary\_\-NW} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_75bfad6f3ef080a83ca3c0746f94ca4e}

\begin{CompactList}\small\item\em implement north-west corner boundary by modifying particle states \item\end{CompactList}\item 
\hypertarget{classBoundary_7ce0aad430a89265e89b76c79ab09dc9}{
void \hyperlink{classBoundary_7ce0aad430a89265e89b76c79ab09dc9}{Boundary\_\-NE} (\hyperlink{classParticle}{Particle} $\ast$prtl)}
\label{classBoundary_7ce0aad430a89265e89b76c79ab09dc9}

\begin{CompactList}\small\item\em implement north-east corner boundary by modifying particle states \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classBoundary_0033d4ccb76b4fa29d2addda930dd572}{
int \hyperlink{classBoundary_0033d4ccb76b4fa29d2addda930dd572}{wall\_\-file}}
\label{classBoundary_0033d4ccb76b4fa29d2addda930dd572}

\begin{CompactList}\small\item\em if read wall particle from file .wll \item\end{CompactList}\item 
\hypertarget{classBoundary_e9c27eae4f9ac0853a089aa4d0c76904}{
Vec2d \hyperlink{classBoundary_e9c27eae4f9ac0853a089aa4d0c76904}{box\_\-size}}
\label{classBoundary_e9c27eae4f9ac0853a089aa4d0c76904}

\begin{CompactList}\small\item\em computational domain size \item\end{CompactList}\item 
\hypertarget{classBoundary_d6bdf67458e91f78f5679f450eee8e29}{
int \hyperlink{classBoundary_d6bdf67458e91f78f5679f450eee8e29}{x\_\-clls}}
\label{classBoundary_d6bdf67458e91f78f5679f450eee8e29}

\begin{CompactList}\small\item\em cell matrix size \item\end{CompactList}\item 
\hypertarget{classBoundary_9066d15cdf92a6d522344e037ed51503}{
int \textbf{y\_\-clls}}
\label{classBoundary_9066d15cdf92a6d522344e037ed51503}

\item 
\hypertarget{classBoundary_ad5dca4ff83933fafee8a858011ab56a}{
int \textbf{number\_\-of\_\-materials}}
\label{classBoundary_ad5dca4ff83933fafee8a858011ab56a}

\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classBoundary}{Boundary} conditions.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classBoundary_8fe88473063d74e67a5932f2e4d2e517}{
\index{Boundary@{Boundary}!Boundary@{Boundary}}
\index{Boundary@{Boundary}!Boundary@{Boundary}}
\subsubsection[{Boundary}]{\setlength{\rightskip}{0pt plus 5cm}Boundary::Boundary ({\bf Initiation} \& {\em ini}, \/  {\bf Hydrodynamics} \& {\em hydro}, \/  {\bf ParticleManager} \& {\em particles})}}
\label{classBoundary_8fe88473063d74e67a5932f2e4d2e517}

boundary particle list for all boundray particles

constructor

copy global properties from initiation class

\begin{itemize}
\item reading key words and configuration data from input file\end{itemize}

\begin{itemize}
\item compare the key words for left, right, upper and lower boundary condition type and their velocities\end{itemize}

\begin{itemize}
\item build boundary particles \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=262pt]{classBoundary_8fe88473063d74e67a5932f2e4d2e517_cgraph}
\end{center}
\end{figure}

\subsection{Member Function Documentation}
\hypertarget{classBoundary_bedd190ee91482e4e59b2a613ab25d57}{
\index{Boundary@{Boundary}!BoundaryCondition@{BoundaryCondition}}
\index{BoundaryCondition@{BoundaryCondition}!Boundary@{Boundary}}
\subsubsection[{BoundaryCondition}]{\setlength{\rightskip}{0pt plus 5cm}void Boundary::BoundaryCondition ({\bf ParticleManager} \& {\em particles})}}
\label{classBoundary_bedd190ee91482e4e59b2a613ab25d57}

boundary conditions

\begin{itemize}
\item west side

\begin{itemize}
\item the rigid wall conditions\end{itemize}

\begin{itemize}
\item the perodic or symmetry conditions \end{itemize}

\item east side \begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}

\item south side

\begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}

\item north side

\begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}
\end{itemize}

considering the coner cells

\begin{itemize}
\item south-west corner \begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}

\item north-west corner \begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}

\item north-east corner \begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}

\item south-east corner \begin{itemize}
\item the rigid wall conditions

\item the perodic or symmetry conditions\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=176pt]{classBoundary_bedd190ee91482e4e59b2a613ab25d57_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=238pt]{classBoundary_bedd190ee91482e4e59b2a613ab25d57_icgraph}
\end{center}
\end{figure}
\hypertarget{classBoundary_8a40f99b73f3622cd5f1387fcbbdb824}{
\index{Boundary@{Boundary}!BuildBoundaryParticles@{BuildBoundaryParticles}}
\index{BuildBoundaryParticles@{BuildBoundaryParticles}!Boundary@{Boundary}}
\subsubsection[{BuildBoundaryParticles}]{\setlength{\rightskip}{0pt plus 5cm}void Boundary::BuildBoundaryParticles ({\bf ParticleManager} \& {\em particles}, \/  {\bf Hydrodynamics} \& {\em hydro})}}
\label{classBoundary_8a40f99b73f3622cd5f1387fcbbdb824}

build boundary particles

\begin{itemize}
\item clear boundary particles list

\item boundary condition for each side

\begin{itemize}
\item west side: test boundary parameter for one of the following cases and then build the appropriate boundary particles

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions \end{itemize}

\item east side

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions\end{itemize}

\item south side

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions\end{itemize}

\item north side

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions\end{itemize}
\end{itemize}

\item considering the coner cells

\begin{itemize}
\item south-west corner \begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions \end{itemize}

\item north-west corner

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions\end{itemize}

\item north-east corner

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions\end{itemize}

\item south-east corner

\begin{itemize}
\item the rigid wall conditions

\item the symmetry conditions

\item the perodic conditions\end{itemize}
\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=186pt]{classBoundary_8a40f99b73f3622cd5f1387fcbbdb824_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=248pt]{classBoundary_8a40f99b73f3622cd5f1387fcbbdb824_icgraph}
\end{center}
\end{figure}
\hypertarget{classBoundary_ac37e18aaf60503a66173d9428ed9e54}{
\index{Boundary@{Boundary}!RunAwayCheck@{RunAwayCheck}}
\index{RunAwayCheck@{RunAwayCheck}!Boundary@{Boundary}}
\subsubsection[{RunAwayCheck}]{\setlength{\rightskip}{0pt plus 5cm}void Boundary::RunAwayCheck ({\bf Hydrodynamics} \& {\em hydro})}}
\label{classBoundary_ac37e18aaf60503a66173d9428ed9e54}

check particle if particle run out of the computational domain

\begin{itemize}
\item iterate the partilce list\end{itemize}

\begin{itemize}
\item only checking real particles (for all boundaries) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=142pt]{classBoundary_ac37e18aaf60503a66173d9428ed9e54_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=231pt]{classBoundary_ac37e18aaf60503a66173d9428ed9e54_icgraph}
\end{center}
\end{figure}
\hypertarget{classBoundary_116df4b717184d962f40bdc88de26763}{
\index{Boundary@{Boundary}!show\_\-information@{show\_\-information}}
\index{show\_\-information@{show\_\-information}!Boundary@{Boundary}}
\subsubsection[{show\_\-information}]{\setlength{\rightskip}{0pt plus 5cm}void Boundary::show\_\-information ({\bf Initiation} \& {\em ini})\hspace{0.3cm}{\tt  \mbox{[}private\mbox{]}}}}
\label{classBoundary_116df4b717184d962f40bdc88de26763}

show information on screen

\begin{itemize}
\item output the property parameters to the screen \end{itemize}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=162pt]{classBoundary_116df4b717184d962f40bdc88de26763_icgraph}
\end{center}
\end{figure}

\subsection{Member Data Documentation}
\hypertarget{classBoundary_10dd58ba0715412968c4902fe80b1318}{
\index{Boundary@{Boundary}!xBl@{xBl}}
\index{xBl@{xBl}!Boundary@{Boundary}}
\subsubsection[{xBl}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Boundary::xBl}}}
\label{classBoundary_10dd58ba0715412968c4902fe80b1318}

boundary condition indicator left hand side

\begin{itemize}
\item 0: wall boundary condition\item 1: perodic boundary condition\item 2: free slip wall boundary condition\item 3: symmetry boundary condition \end{itemize}
\hypertarget{classBoundary_4a582b489cb580b8a6f3a7123f411a53}{
\index{Boundary@{Boundary}!xBr@{xBr}}
\index{xBr@{xBr}!Boundary@{Boundary}}
\subsubsection[{xBr}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Boundary::xBr}}}
\label{classBoundary_4a582b489cb580b8a6f3a7123f411a53}

boundary condition indicator right hand side

\begin{itemize}
\item 0: wall boundary condition\item 1: perodic boundary condition\item 2: free slip wall boundary condition\item 3: symmetry boundary condition \end{itemize}
\hypertarget{classBoundary_0329bf6b954b3001418391cc16a9194e}{
\index{Boundary@{Boundary}!yBd@{yBd}}
\index{yBd@{yBd}!Boundary@{Boundary}}
\subsubsection[{yBd}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Boundary::yBd}}}
\label{classBoundary_0329bf6b954b3001418391cc16a9194e}

boundary condition indicator bottom side

\begin{itemize}
\item 0: wall boundary condition\item 1: perodic boundary condition\item 2: free slip wall boundary condition\item 3: symmetry boundary condition \end{itemize}
\hypertarget{classBoundary_6ccff2a8c5a10104d202504034af9e84}{
\index{Boundary@{Boundary}!yBu@{yBu}}
\index{yBu@{yBu}!Boundary@{Boundary}}
\subsubsection[{yBu}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Boundary::yBu}}}
\label{classBoundary_6ccff2a8c5a10104d202504034af9e84}

boundary condition indicator upper side

\begin{itemize}
\item 0: wall boundary condition\item 1: perodic boundary condition\item 2: free slip wall boundary condition\item 3: symmetry boundary condition \end{itemize}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{boundary_8h}{boundary.h}\item 
\hyperlink{boundary_8cpp}{boundary.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classDiagnose.tex
compressible branch

\hypertarget{classDiagnose}{
\section{Diagnose Class Reference}
\label{classDiagnose}\index{Diagnose@{Diagnose}}
}
\hyperlink{classOutput}{Output} diagnosal.

{\tt \#include $<$diagnose.h$>$}

Collaboration diagram for Diagnose:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=183pt]{classDiagnose__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classDiagnose_915a3d571504c843748bf5e9a9ec801c}{Diagnose} (\hyperlink{classInitiation}{Initiation} \&ini, \hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
void \hyperlink{classDiagnose_bf6d65f3716a9d637186f97c62f7218b}{SaveStates} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro)
\begin{CompactList}\small\item\em save the states of a particle in particle states vectors (vx\_\-list, vy\_\-list, rho\_\-list) \item\end{CompactList}\item 
void \hyperlink{classDiagnose_db2f9991031fb8c301f44518c1d851ea}{OutputProfile} (double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em output distribution up to the time \item\end{CompactList}\item 
void \hyperlink{classDiagnose_8c14b3fa58083f64be2018bd0462604d}{Average} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classMLS}{MLS} \&mls, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em calculate the average values \item\end{CompactList}\item 
void \hyperlink{classDiagnose_dc46dd26362f94e09b956b3affa247c9}{OutputAverage} (double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em output the average values \item\end{CompactList}\item 
void \hyperlink{classDiagnose_9c73b32dc8facce488617780250c14bf}{KineticInformation} (double Time, \hyperlink{classInitiation}{Initiation} \&ini, \hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro)
\begin{CompactList}\small\item\em track the globle average kinetic energy, weight center position and velocity \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classDiagnose_ef3922caa185f5d587edad0eaaf655d3}{
void \hyperlink{classDiagnose_ef3922caa185f5d587edad0eaaf655d3}{BuildDistribution} (\hyperlink{classLlist}{Llist}$<$ double $>$ \&list, double dstrb\mbox{[}2\mbox{]}\mbox{[}101\mbox{]})}
\label{classDiagnose_ef3922caa185f5d587edad0eaaf655d3}

\begin{CompactList}\small\item\em build distribution \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classDiagnose_ff5505506d498c9a3d41a15b848f4fed}{
double \hyperlink{classDiagnose_ff5505506d498c9a3d41a15b848f4fed}{delta}}
\label{classDiagnose_ff5505506d498c9a3d41a15b848f4fed}

\begin{CompactList}\small\item\em the inital particle distance \item\end{CompactList}\item 
\hypertarget{classDiagnose_392e23f84c8d6c19a62ff729dabc4b08}{
int \hyperlink{classDiagnose_392e23f84c8d6c19a62ff729dabc4b08}{x\_\-cells}}
\label{classDiagnose_392e23f84c8d6c19a62ff729dabc4b08}

\begin{CompactList}\small\item\em cells matrix for real particles \item\end{CompactList}\item 
\hypertarget{classDiagnose_b99ebe8786c68b5ef9477c49e32227ad}{
int \textbf{y\_\-cells}}
\label{classDiagnose_b99ebe8786c68b5ef9477c49e32227ad}

\item 
\hypertarget{classDiagnose_85b126f2b079c38847e1b8a42fe39604}{
int \hyperlink{classDiagnose_85b126f2b079c38847e1b8a42fe39604}{hdelta}}
\label{classDiagnose_85b126f2b079c38847e1b8a42fe39604}

\begin{CompactList}\small\item\em the ration between smoothing length and inital particle distance \item\end{CompactList}\item 
\hypertarget{classDiagnose_ea27d34fbb662ee394b81802ddeca495}{
char \hyperlink{classDiagnose_ea27d34fbb662ee394b81802ddeca495}{Project\_\-name} \mbox{[}25\mbox{]}}
\label{classDiagnose_ea27d34fbb662ee394b81802ddeca495}

\begin{CompactList}\small\item\em the project name \item\end{CompactList}\item 
\hypertarget{classDiagnose_e91dcce776e5182100a0d813c7a490c9}{
int \textbf{number\_\-of\_\-materials}}
\label{classDiagnose_e91dcce776e5182100a0d813c7a490c9}

\item 
\hypertarget{classDiagnose_f67fdb70cb79df3d31d151630c63cef8}{
double \hyperlink{classDiagnose_f67fdb70cb79df3d31d151630c63cef8}{vx\_\-dstrb} \mbox{[}2\mbox{]}\mbox{[}101\mbox{]}}
\label{classDiagnose_f67fdb70cb79df3d31d151630c63cef8}

\begin{CompactList}\small\item\em x-velocity distribution \item\end{CompactList}\item 
\hypertarget{classDiagnose_0ec20a8f26b147df7f6dd74f054518fb}{
double \hyperlink{classDiagnose_0ec20a8f26b147df7f6dd74f054518fb}{vy\_\-dstrb} \mbox{[}2\mbox{]}\mbox{[}101\mbox{]}}
\label{classDiagnose_0ec20a8f26b147df7f6dd74f054518fb}

\begin{CompactList}\small\item\em y-velocity distribution \item\end{CompactList}\item 
\hypertarget{classDiagnose_c3b8eb576691e06bc18f30e1e23b053c}{
double \hyperlink{classDiagnose_c3b8eb576691e06bc18f30e1e23b053c}{rho\_\-dstrb} \mbox{[}2\mbox{]}\mbox{[}101\mbox{]}}
\label{classDiagnose_c3b8eb576691e06bc18f30e1e23b053c}

\begin{CompactList}\small\item\em density distribution \item\end{CompactList}\item 
\hypertarget{classDiagnose_145722f84ce6e10d9e6fc08104824996}{
\hyperlink{classLlist}{Llist}$<$ double $>$ \hyperlink{classDiagnose_145722f84ce6e10d9e6fc08104824996}{vx\_\-list}}
\label{classDiagnose_145722f84ce6e10d9e6fc08104824996}

\begin{CompactList}\small\item\em list for vx states of a given particle \item\end{CompactList}\item 
\hypertarget{classDiagnose_7b7a236d8ac6f9b7a901670a8f7703e0}{
\hyperlink{classLlist}{Llist}$<$ double $>$ \hyperlink{classDiagnose_7b7a236d8ac6f9b7a901670a8f7703e0}{vy\_\-list}}
\label{classDiagnose_7b7a236d8ac6f9b7a901670a8f7703e0}

\begin{CompactList}\small\item\em list for vy states of a given particle \item\end{CompactList}\item 
\hypertarget{classDiagnose_d10e7325edc977979a7db9fdcd34d8fd}{
\hyperlink{classLlist}{Llist}$<$ double $>$ \hyperlink{classDiagnose_d10e7325edc977979a7db9fdcd34d8fd}{rho\_\-list}}
\label{classDiagnose_d10e7325edc977979a7db9fdcd34d8fd}

\begin{CompactList}\small\item\em list for rho states of a given particle \item\end{CompactList}\item 
\hypertarget{classDiagnose_63dce0bdefd95c49730ab011321ad984}{
int \hyperlink{classDiagnose_63dce0bdefd95c49730ab011321ad984}{gridx}}
\label{classDiagnose_63dce0bdefd95c49730ab011321ad984}

\begin{CompactList}\small\item\em average profile mesh size in x-direction \item\end{CompactList}\item 
\hypertarget{classDiagnose_3cda015218278477cbbe85b6e55b4398}{
int \hyperlink{classDiagnose_3cda015218278477cbbe85b6e55b4398}{gridy}}
\label{classDiagnose_3cda015218278477cbbe85b6e55b4398}

\begin{CompactList}\small\item\em average profile mesh size in y-direction \item\end{CompactList}\item 
\hypertarget{classDiagnose_8fbc4859156ad72a70b471edd8326552}{
double $\ast$$\ast$$\ast$ \textbf{U}}
\label{classDiagnose_8fbc4859156ad72a70b471edd8326552}

\item 
\hypertarget{classDiagnose_a08ef64241663163214a68507d578e27}{
int \hyperlink{classDiagnose_a08ef64241663163214a68507d578e27}{n\_\-average}}
\label{classDiagnose_a08ef64241663163214a68507d578e27}

\begin{CompactList}\small\item\em the times of average \item\end{CompactList}\item 
double \hyperlink{classDiagnose_31e87c9b084b73a78c1e2758149800ed}{ttl\_\-m}
\begin{CompactList}\small\item\em total mass, global average kinetic energy, \item\end{CompactList}\item 
\hypertarget{classDiagnose_fb8a8b1acd170da00404455ee0e674df}{
double $\ast$ \hyperlink{classDiagnose_fb8a8b1acd170da00404455ee0e674df}{mtl\_\-m}}
\label{classDiagnose_fb8a8b1acd170da00404455ee0e674df}

\begin{CompactList}\small\item\em ??????{\bf (\hyperlink{diagnose_8h}{diagnose.h}, line 36)} \item\end{CompactList}\item 
\hypertarget{classDiagnose_1784f6a7677b271e8968147df019e8b0}{
double \hyperlink{classDiagnose_1784f6a7677b271e8968147df019e8b0}{glb\_\-ave\_\-Ek}}
\label{classDiagnose_1784f6a7677b271e8968147df019e8b0}

\begin{CompactList}\small\item\em global average kinetic energy \item\end{CompactList}\item 
\hypertarget{classDiagnose_52f9cc1859fecd569c05de78243e45bd}{
Vec2d $\ast$ \hyperlink{classDiagnose_52f9cc1859fecd569c05de78243e45bd}{wght\_\-cntr}}
\label{classDiagnose_52f9cc1859fecd569c05de78243e45bd}

\begin{CompactList}\small\item\em material weight center position \item\end{CompactList}\item 
\hypertarget{classDiagnose_8b02748469646274034f793aab57193b}{
Vec2d $\ast$ \hyperlink{classDiagnose_8b02748469646274034f793aab57193b}{wght\_\-v}}
\label{classDiagnose_8b02748469646274034f793aab57193b}

\begin{CompactList}\small\item\em material weight center velocity \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classOutput}{Output} diagnosal.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classDiagnose_915a3d571504c843748bf5e9a9ec801c}{
\index{Diagnose@{Diagnose}!Diagnose@{Diagnose}}
\index{Diagnose@{Diagnose}!Diagnose@{Diagnose}}
\subsubsection[{Diagnose}]{\setlength{\rightskip}{0pt plus 5cm}Diagnose::Diagnose ({\bf Initiation} \& {\em ini}, \/  {\bf Hydrodynamics} \& {\em hydro})}}
\label{classDiagnose_915a3d571504c843748bf5e9a9ec801c}

constructor

\begin{itemize}
\item copy parameters from \hyperlink{classInitiation}{Initiation} class

\item copy boundary properties from initiation class

\item calculate total mass

\item produce output file name (\char`\"{}kinetic\_\-info.dat\char`\"{})and file header \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=128pt]{classDiagnose_915a3d571504c843748bf5e9a9ec801c_cgraph}
\end{center}
\end{figure}

\subsection{Member Function Documentation}
\hypertarget{classDiagnose_8c14b3fa58083f64be2018bd0462604d}{
\index{Diagnose@{Diagnose}!Average@{Average}}
\index{Average@{Average}!Diagnose@{Diagnose}}
\subsubsection[{Average}]{\setlength{\rightskip}{0pt plus 5cm}void Diagnose::Average ({\bf ParticleManager} \& {\em particles}, \/  {\bf MLS} \& {\em mls}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  {\bf Initiation} \& {\em ini})}}
\label{classDiagnose_8c14b3fa58083f64be2018bd0462604d}

calculate the average values

\begin{itemize}
\item loop the grid points

\begin{itemize}
\item build the NNP\_\-list

\item if the NNP list is not empty run \hyperlink{classMLS}{MLS} approximation

\item iterate this Nearest Neighbor \hyperlink{classParticle}{Particle} list

\begin{itemize}
\item get particle data \end{itemize}

\item clear the NNP\_\-list

\item calculating the averages \end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=331pt]{classDiagnose_8c14b3fa58083f64be2018bd0462604d_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=214pt]{classDiagnose_8c14b3fa58083f64be2018bd0462604d_icgraph}
\end{center}
\end{figure}
\hypertarget{classDiagnose_9c73b32dc8facce488617780250c14bf}{
\index{Diagnose@{Diagnose}!KineticInformation@{KineticInformation}}
\index{KineticInformation@{KineticInformation}!Diagnose@{Diagnose}}
\subsubsection[{KineticInformation}]{\setlength{\rightskip}{0pt plus 5cm}void Diagnose::KineticInformation (double {\em Time}, \/  {\bf Initiation} \& {\em ini}, \/  {\bf Hydrodynamics} \& {\em hydro})}}
\label{classDiagnose_9c73b32dc8facce488617780250c14bf}

track the globle average kinetic energy, weight center position and velocity

\begin{itemize}
\item produce output file name

\item iterate the partilce list and calculate data

\item output calculated data in \char`\"{}kinetic\_\-info.dat\char`\"{} \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=166pt]{classDiagnose_9c73b32dc8facce488617780250c14bf_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=235pt]{classDiagnose_9c73b32dc8facce488617780250c14bf_icgraph}
\end{center}
\end{figure}
\hypertarget{classDiagnose_dc46dd26362f94e09b956b3affa247c9}{
\index{Diagnose@{Diagnose}!OutputAverage@{OutputAverage}}
\index{OutputAverage@{OutputAverage}!Diagnose@{Diagnose}}
\subsubsection[{OutputAverage}]{\setlength{\rightskip}{0pt plus 5cm}void Diagnose::OutputAverage (double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classDiagnose_dc46dd26362f94e09b956b3affa247c9}

output the average values

\begin{itemize}
\item produce output file name\end{itemize}

\begin{itemize}
\item defining header for tecplot(plot software)\end{itemize}

\begin{itemize}
\item loop the grid points and output data \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=160pt]{classDiagnose_dc46dd26362f94e09b956b3affa247c9_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=122pt]{classDiagnose_dc46dd26362f94e09b956b3affa247c9_icgraph}
\end{center}
\end{figure}
\hypertarget{classDiagnose_db2f9991031fb8c301f44518c1d851ea}{
\index{Diagnose@{Diagnose}!OutputProfile@{OutputProfile}}
\index{OutputProfile@{OutputProfile}!Diagnose@{Diagnose}}
\subsubsection[{OutputProfile}]{\setlength{\rightskip}{0pt plus 5cm}void Diagnose::OutputProfile (double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classDiagnose_db2f9991031fb8c301f44518c1d851ea}

output distribution up to the time

\begin{itemize}
\item produce output file name \char`\"{}dstrXXXX.dat\char`\"{}\end{itemize}

\begin{itemize}
\item defining file header for tecplot(plot software)\end{itemize}

-build the distribution

\begin{itemize}
\item normalize to unit\end{itemize}

\begin{itemize}
\item output distribution in file \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=221pt]{classDiagnose_db2f9991031fb8c301f44518c1d851ea_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=119pt]{classDiagnose_db2f9991031fb8c301f44518c1d851ea_icgraph}
\end{center}
\end{figure}
\hypertarget{classDiagnose_bf6d65f3716a9d637186f97c62f7218b}{
\index{Diagnose@{Diagnose}!SaveStates@{SaveStates}}
\index{SaveStates@{SaveStates}!Diagnose@{Diagnose}}
\subsubsection[{SaveStates}]{\setlength{\rightskip}{0pt plus 5cm}void Diagnose::SaveStates ({\bf Hydrodynamics} \& {\em hydro})}}
\label{classDiagnose_bf6d65f3716a9d637186f97c62f7218b}

save the states of a particle in particle states vectors (vx\_\-list, vy\_\-list, rho\_\-list)

\begin{itemize}
\item select a given node on the particle list\end{itemize}

\begin{itemize}
\item Insert the states of the particles in the states vectores (vx\_\-list, vy\_\-list, rho\_\-list) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=132pt]{classDiagnose_bf6d65f3716a9d637186f97c62f7218b_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=221pt]{classDiagnose_bf6d65f3716a9d637186f97c62f7218b_icgraph}
\end{center}
\end{figure}

\subsection{Member Data Documentation}
\hypertarget{classDiagnose_31e87c9b084b73a78c1e2758149800ed}{
\index{Diagnose@{Diagnose}!ttl\_\-m@{ttl\_\-m}}
\index{ttl\_\-m@{ttl\_\-m}!Diagnose@{Diagnose}}
\subsubsection[{ttl\_\-m}]{\setlength{\rightskip}{0pt plus 5cm}double {\bf Diagnose::ttl\_\-m}\hspace{0.3cm}{\tt  \mbox{[}private\mbox{]}}}}
\label{classDiagnose_31e87c9b084b73a78c1e2758149800ed}

total mass, global average kinetic energy,

total mass

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{diagnose_8h}{diagnose.h}\item 
\hyperlink{diagose_8cpp}{diagose.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classForce.tex
compressible branch

\hypertarget{classForce}{
\section{Force Class Reference}
\label{classForce}\index{Force@{Force}}
}
The class defining force on or between particles.

{\tt \#include $<$force.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classForce_00983e3bbc206a00bb9253deafc4e424}{Force} ()
\begin{CompactList}\small\item\em shear and bulk slip length \item\end{CompactList}\item 
\hypertarget{classForce_6ce6bddb4bbe52af88b12827324a818d}{
\textbf{Force} (\hyperlink{classInitiation}{Initiation} \&ini)}
\label{classForce_6ce6bddb4bbe52af88b12827324a818d}

\item 
\hypertarget{classForce_75f2e675a6d57e08127d47b6bc31d3d9}{
void \hyperlink{classForce_75f2e675a6d57e08127d47b6bc31d3d9}{non\_\-dimensionalize} (\hyperlink{classInitiation}{Initiation} \&ini)}
\label{classForce_75f2e675a6d57e08127d47b6bc31d3d9}

\begin{CompactList}\small\item\em non-dimensionalize \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classForce_7142842359bf1e78499b5f59cff7a600}{
double \hyperlink{classForce_7142842359bf1e78499b5f59cff7a600}{sigma}}
\label{classForce_7142842359bf1e78499b5f59cff7a600}

\begin{CompactList}\small\item\em heat conduction slip length \item\end{CompactList}\item 
\hypertarget{classForce_5b371059110b1baee895f30c24e209f3}{
double \hyperlink{classForce_5b371059110b1baee895f30c24e209f3}{shear\_\-slip}}
\label{classForce_5b371059110b1baee895f30c24e209f3}

\begin{CompactList}\small\item\em surface tension parameters, its dimension is rho$\ast$u$^\wedge$2$\ast$L \item\end{CompactList}\item 
\hypertarget{classForce_707dd63d90d41bd1c0b345f5ba27a047}{
double \textbf{bulk\_\-slip}}
\label{classForce_707dd63d90d41bd1c0b345f5ba27a047}

\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classForce_ff0b02789964024867fd633fd0e5722a}{
double \hyperlink{classForce_ff0b02789964024867fd633fd0e5722a}{epsilon}}
\label{classForce_ff0b02789964024867fd633fd0e5722a}

\begin{CompactList}\small\item\em interactive force parameters \item\end{CompactList}\item 
\hypertarget{classForce_499d60a627ddd2b9a2909891cd45b78f}{
double \textbf{heat\_\-slip}}
\label{classForce_499d60a627ddd2b9a2909891cd45b78f}

\end{CompactItemize}
\subsection*{Static Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classForce_84055a493186144b98ab363bd958095f}{
static int \hyperlink{classForce_84055a493186144b98ab363bd958095f}{number\_\-of\_\-materials} = 0}
\label{classForce_84055a493186144b98ab363bd958095f}

\begin{CompactList}\small\item\em total number of materials \item\end{CompactList}\item 
\hypertarget{classForce_bcab616ac69fe78d87567506dedd8a56}{
static double \hyperlink{classForce_bcab616ac69fe78d87567506dedd8a56}{smoothinglength} = 0.0}
\label{classForce_bcab616ac69fe78d87567506dedd8a56}

\begin{CompactList}\small\item\em smoothinglenth \item\end{CompactList}\end{CompactItemize}
\subsection*{Friends}
\begin{CompactItemize}
\item 
\hypertarget{classForce_652e6d35f07e2091db6c1d01e86e2286}{
class \hyperlink{classForce_652e6d35f07e2091db6c1d01e86e2286}{Hydrodynamics}}
\label{classForce_652e6d35f07e2091db6c1d01e86e2286}

\end{CompactItemize}

\subsection{Detailed Description}
The class defining force on or between particles.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classForce_00983e3bbc206a00bb9253deafc4e424}{
\index{Force@{Force}!Force@{Force}}
\index{Force@{Force}!Force@{Force}}
\subsubsection[{Force}]{\setlength{\rightskip}{0pt plus 5cm}Force::Force ()}}
\label{classForce_00983e3bbc206a00bb9253deafc4e424}

shear and bulk slip length

constructor

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{force_8h}{force.h}\item 
force.cpp\end{CompactItemize}

### 2010-06-17 src/latex/classHydrodynamics.tex
compressible branch

\hypertarget{classHydrodynamics}{
\section{Hydrodynamics Class Reference}
\label{classHydrodynamics}\index{Hydrodynamics@{Hydrodynamics}}
}
Definition of materials and their hydrodynamical interactions.

{\tt \#include $<$hydrodynamics.h$>$}

Collaboration diagram for Hydrodynamics:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=400pt]{classHydrodynamics__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classHydrodynamics_837d2adb43e7d4ea4fa5a1c89bb59313}{Hydrodynamics} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_281acddb6d4dd1efa9970f24a6bf57cd}{
double \hyperlink{classHydrodynamics_281acddb6d4dd1efa9970f24a6bf57cd}{GetTimestep} ()}
\label{classHydrodynamics_281acddb6d4dd1efa9970f24a6bf57cd}

\begin{CompactList}\small\item\em get the time step \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_41e1527e65d6f93d81c30467871021f5}{BuildPair} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em build new pairs \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_cf0d749b11e8b8474dd204c6ea080235}{UpdatePair} (\hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em update new parameters in pairs \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_67e2d72d69156a086d43168f5cd58bf7}{ZeroChangeRate} ()
\begin{CompactList}\small\item\em initiate particle change rate \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_abdebac769f07f2500c21689fafa2981}{AddGravity} ()
\begin{CompactList}\small\item\em add the gravity effects \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_22df8569d81c4c363029efac143ddb26}{UpdateChangeRate} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em calculate interaction with updating interaction list \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_f744ee07f3f3b511d0db18949160c20a}{UpdateChangeRate} ()
\begin{CompactList}\small\item\em calculate interaction without updating interaction list \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_13810b3b4110a2b931bf7426af2f9bcf}{Zero\_\-density} ()
\begin{CompactList}\small\item\em initiate particle density to zero \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_049f88c2f97863edae4489618dc9e853}{Zero\_\-ShearRate} ()
\item 
void \hyperlink{classHydrodynamics_1818eb1f9044ae980e92c70146e51c5b}{UpdateDensity} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em summation for particles density (with updating interaction list) \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_7ae4f1005699f13414ec6c487bac0ee0}{UpdateShearRate} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em summation for shear rates (with updating interaction list) \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_b6cab35a4d7adf70657ef16b9ec4dafd}{UpdateDensity} ()
\begin{CompactList}\small\item\em currently no shear rate calculated without updating interaction list \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_49570aaeedea32d7a2baf0532880b2e8}{UpdateShearRate} ()
\begin{CompactList}\small\item\em ??? \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_939e9b2ec26b3e4a2eaf2683e5f0343d}{UpdatePhaseGradient} (\hyperlink{classBoundary}{Boundary} \&boundary)
\begin{CompactList}\small\item\em not independant with UpdateDensity \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_3c9019f19ccac5370b7b0ccda343b5d2}{Zero\_\-PhaseGradient} (\hyperlink{classBoundary}{Boundary} \&boundary)
\item 
void \hyperlink{classHydrodynamics_c87ff6437d540454ed7de2f726858f4a}{UpdatePhaseField} (\hyperlink{classBoundary}{Boundary} \&boundary)
\item 
void \hyperlink{classHydrodynamics_dedab91b9a62eb7e26931cbbe73f79cc}{Zero\_\-PhaseField} (\hyperlink{classBoundary}{Boundary} \&boundary)
\item 
void \hyperlink{classHydrodynamics_f5b2c4ad14824e4b6192faa6f60f4014}{UpdateSurfaceStress} (\hyperlink{classBoundary}{Boundary} \&boundary)
\item 
void \hyperlink{classHydrodynamics_dbbe86fd4eac49912a9ffb5e284883ee}{UpdatePhaseLaplacian} (\hyperlink{classBoundary}{Boundary} \&boundary)
\item 
void \hyperlink{classHydrodynamics_d1c5fd5b500eacb886a72f2dab13e91b}{Zero\_\-PhaseLaplacian} (\hyperlink{classBoundary}{Boundary} \&boundary)
\item 
double \hyperlink{classHydrodynamics_e6983cf4d86bf7b33b88c8f089caf3a8}{SurfaceTensionCoefficient} ()
\begin{CompactList}\small\item\em calculate surface tension coefficient \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_a755853b07cbbc5b484d78a3e787d1ef}{UpdatePahseMatrix} (\hyperlink{classBoundary}{Boundary} \&boundary)
\begin{CompactList}\small\item\em this method currently does {\bf NOTHING} \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891}{UpdateState} ()
\begin{CompactList}\small\item\em calculate states from conservatives \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_09a3f5a5c055e0efc822fdf80f40cd7d}{UpdateVolume} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em calculate partilce volume \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_316a6079bf22102d9b911e2632cd2680}{Predictor} (double dt)
\begin{CompactList}\small\item\em predictor method, density evaluated directly \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_928a3fb7752d458026ed06dca1fbf137}{Corrector} (double dt)
\begin{CompactList}\small\item\em corrector method, density evaluated directly:{\bf  corrector advances p, rho, U} \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_911fe25b94fec398fad1f2def036d755}{Predictor\_\-summation} (double dt)
\begin{CompactList}\small\item\em for predictor method, density evaluated with summation (that means: no density update within this method) \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_6a62dad5b8c33b504481a8e4e5b023cb}{Corrector\_\-summation} (double dt)
\begin{CompactList}\small\item\em for corrector method, density evaluated with summation (that means: no density update within this method) \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_f67579320cbdccaf49bbdf3dfb13f23c}{Zero\_\-Random} ()
\begin{CompactList}\small\item\em initiate random force (DPD simulation) \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_2ea6824bef3da552942cbf0c0653a4c0}{
void \hyperlink{classHydrodynamics_2ea6824bef3da552942cbf0c0653a4c0}{UpdateRandom} (double sqrtdt)}
\label{classHydrodynamics_2ea6824bef3da552942cbf0c0653a4c0}

\begin{CompactList}\small\item\em calculate random interaction without updating interaction list (DPD simulation) \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_8f826d2003ca7a4782b028b761a26421}{RandomEffects} ()
\begin{CompactList}\small\item\em including random effects (DPD simulation) \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_a737dcae7a8b53a7829da52a6eee593d}{
void \textbf{MovingTest} (\hyperlink{classInitiation}{Initiation} \&ini)}
\label{classHydrodynamics_a737dcae7a8b53a7829da52a6eee593d}

\item 
\hypertarget{classHydrodynamics_1baf3a0ed4c17a3758b50c223b321f8a}{
double \hyperlink{classHydrodynamics_1baf3a0ed4c17a3758b50c223b321f8a}{ConservationTest} ()}
\label{classHydrodynamics_1baf3a0ed4c17a3758b50c223b321f8a}

\begin{CompactList}\small\item\em test for debug \item\end{CompactList}\item 
void \hyperlink{classHydrodynamics_4f65196eb3002238371d0e04dd76c02a}{Zero\_\-Velocity} ()
\begin{CompactList}\small\item\em special uitilities \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classHydrodynamics_fddd4c6d09a8be4c90fd914913303331}{
\hyperlink{classMaterial}{Material} $\ast$ \hyperlink{classHydrodynamics_fddd4c6d09a8be4c90fd914913303331}{materials}}
\label{classHydrodynamics_fddd4c6d09a8be4c90fd914913303331}

\begin{CompactList}\small\item\em the materials used \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_7a478cfc3248a8ea35d1819f3169c46f}{
\hyperlink{classForce}{Force} $\ast$$\ast$ \hyperlink{classHydrodynamics_7a478cfc3248a8ea35d1819f3169c46f}{forces}}
\label{classHydrodynamics_7a478cfc3248a8ea35d1819f3169c46f}

\begin{CompactList}\small\item\em the interaction force used \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_75c09c83c42e2af4521db7685b4bfdf6}{
\hyperlink{classLlist}{Llist}$<$ \hyperlink{classParticle}{Particle} $>$ \hyperlink{classHydrodynamics_75c09c83c42e2af4521db7685b4bfdf6}{particle\_\-list}}
\label{classHydrodynamics_75c09c83c42e2af4521db7685b4bfdf6}

\begin{CompactList}\small\item\em particle list for all particles \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_01480327db244d4bd8b5ce7f109f7884}{
\hyperlink{classWiener}{Wiener} \hyperlink{classHydrodynamics_01480327db244d4bd8b5ce7f109f7884}{wiener}}
\label{classHydrodynamics_01480327db244d4bd8b5ce7f109f7884}

\begin{CompactList}\small\item\em \hyperlink{classWiener}{Wiener} process. \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classHydrodynamics_74497f44758886505ffdea8972919a6b}{
int \textbf{number\_\-of\_\-materials}}
\label{classHydrodynamics_74497f44758886505ffdea8972919a6b}

\item 
\hypertarget{classHydrodynamics_6f7660b8e3c861315c421a7baac8e81e}{
Vec2d \textbf{gravity}}
\label{classHydrodynamics_6f7660b8e3c861315c421a7baac8e81e}

\item 
\hypertarget{classHydrodynamics_5d05d80cca5039ade949fd272261ed57}{
double \textbf{smoothinglength}}
\label{classHydrodynamics_5d05d80cca5039ade949fd272261ed57}

\item 
\hypertarget{classHydrodynamics_d70d17be4ff45e1b01aaa779771a27e0}{
double \textbf{delta}}
\label{classHydrodynamics_d70d17be4ff45e1b01aaa779771a27e0}

\item 
\hypertarget{classHydrodynamics_74ed6f3fd3d1a615fceea4aa926add37}{
double \textbf{delta2}}
\label{classHydrodynamics_74ed6f3fd3d1a615fceea4aa926add37}

\item 
\hypertarget{classHydrodynamics_d39804d0ef02e7bbced89f22f6980867}{
double \textbf{delta3}}
\label{classHydrodynamics_d39804d0ef02e7bbced89f22f6980867}

\item 
\hypertarget{classHydrodynamics_50784f838fa0e34eca594e9eb99a2bb0}{
double \textbf{dt\_\-g\_\-vis}}
\label{classHydrodynamics_50784f838fa0e34eca594e9eb99a2bb0}

\item 
\hypertarget{classHydrodynamics_666c0e9c93f1b3fbc0d6b8dd0e697f3e}{
double \textbf{dt\_\-surf}}
\label{classHydrodynamics_666c0e9c93f1b3fbc0d6b8dd0e697f3e}

\item 
\hypertarget{classHydrodynamics_5b155497d0ab985266f7dcf4448c2253}{
\hyperlink{classLlist}{Llist}$<$ \hyperlink{classInteraction}{Interaction} $>$ \hyperlink{classHydrodynamics_5b155497d0ab985266f7dcf4448c2253}{interaction\_\-list}}
\label{classHydrodynamics_5b155497d0ab985266f7dcf4448c2253}

\begin{CompactList}\small\item\em the interaction (particle pair) list \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_9f6ba4a1659ccd79a80b5a0291c7c5a0}{
double \hyperlink{classHydrodynamics_9f6ba4a1659ccd79a80b5a0291c7c5a0}{viscosity\_\-max}}
\label{classHydrodynamics_9f6ba4a1659ccd79a80b5a0291c7c5a0}

\begin{CompactList}\small\item\em for first time step \item\end{CompactList}\item 
\hypertarget{classHydrodynamics_a1ead264a05af3f201e712d5d17abccb}{
double \hyperlink{classHydrodynamics_a1ead264a05af3f201e712d5d17abccb}{surface\_\-max}}
\label{classHydrodynamics_a1ead264a05af3f201e712d5d17abccb}

\begin{CompactList}\small\item\em for first time step \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
Definition of materials and their hydrodynamical interactions.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classHydrodynamics_837d2adb43e7d4ea4fa5a1c89bb59313}{
\index{Hydrodynamics@{Hydrodynamics}!Hydrodynamics@{Hydrodynamics}}
\index{Hydrodynamics@{Hydrodynamics}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Hydrodynamics}]{\setlength{\rightskip}{0pt plus 5cm}Hydrodynamics::Hydrodynamics ({\bf ParticleManager} \& {\em particles}, \/  {\bf Initiation} \& {\em ini})}}
\label{classHydrodynamics_837d2adb43e7d4ea4fa5a1c89bb59313}

constructor

\begin{itemize}
\item copy properties from initiation class

\item create material matrix

\item create the force matrix

\item check if inputfile exists

\item reading all key words and configuration data

\item if key word material: read all materials (from .cfg file)

\begin{itemize}
\item save each one of them in materials matrix

\item output the material property parameters to the screen

\item non-dimensionalize\end{itemize}

\item if key word forces: read all forces for all materials (from .cfg file)

\begin{itemize}
\item save eahc one of them in forces matrix

\item copy smoothing length fro initiation

\item and non-dimensionalize\end{itemize}

\item initialize parameters for time step and the artificial compressiblity

\item determine the artificial compressiblity

\item biuld the real particles \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=310pt]{classHydrodynamics_837d2adb43e7d4ea4fa5a1c89bb59313_cgraph}
\end{center}
\end{figure}

\subsection{Member Function Documentation}
\hypertarget{classHydrodynamics_abdebac769f07f2500c21689fafa2981}{
\index{Hydrodynamics@{Hydrodynamics}!AddGravity@{AddGravity}}
\index{AddGravity@{AddGravity}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{AddGravity}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::AddGravity ()}}
\label{classHydrodynamics_abdebac769f07f2500c21689fafa2981}

add the gravity effects

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item to each particles dUdt: add the gravity effects \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=145pt]{classHydrodynamics_abdebac769f07f2500c21689fafa2981_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=339pt]{classHydrodynamics_abdebac769f07f2500c21689fafa2981_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_41e1527e65d6f93d81c30467871021f5}{
\index{Hydrodynamics@{Hydrodynamics}!BuildPair@{BuildPair}}
\index{BuildPair@{BuildPair}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{BuildPair}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::BuildPair ({\bf ParticleManager} \& {\em particles}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classHydrodynamics_41e1527e65d6f93d81c30467871021f5}

build new pairs

\begin{itemize}
\item obtain the interaction pairs by just calling the particles BuildInteraction method \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=340pt]{classHydrodynamics_41e1527e65d6f93d81c30467871021f5_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=230pt]{classHydrodynamics_41e1527e65d6f93d81c30467871021f5_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_928a3fb7752d458026ed06dca1fbf137}{
\index{Hydrodynamics@{Hydrodynamics}!Corrector@{Corrector}}
\index{Corrector@{Corrector}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Corrector}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Corrector (double {\em dt})}}
\label{classHydrodynamics_928a3fb7752d458026ed06dca1fbf137}

corrector method, density evaluated directly:{\bf  corrector advances p, rho, U}

\begin{itemize}
\item iterate the real partilce list\end{itemize}

\begin{itemize}
\item for each particle: correction based on values on n step and change rate at n+1/2 \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=141pt]{classHydrodynamics_928a3fb7752d458026ed06dca1fbf137_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=166pt]{classHydrodynamics_928a3fb7752d458026ed06dca1fbf137_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_6a62dad5b8c33b504481a8e4e5b023cb}{
\index{Hydrodynamics@{Hydrodynamics}!Corrector\_\-summation@{Corrector\_\-summation}}
\index{Corrector\_\-summation@{Corrector\_\-summation}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Corrector\_\-summation}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Corrector\_\-summation (double {\em dt})}}
\label{classHydrodynamics_6a62dad5b8c33b504481a8e4e5b023cb}

for corrector method, density evaluated with summation (that means: no density update within this method)

\begin{itemize}
\item iterate the real partilce list\end{itemize}

\begin{itemize}
\item for each particle: correction (advances R,U) based on values on n step and change rate at n+1/2 \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=168pt]{classHydrodynamics_6a62dad5b8c33b504481a8e4e5b023cb_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=257pt]{classHydrodynamics_6a62dad5b8c33b504481a8e4e5b023cb_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_316a6079bf22102d9b911e2632cd2680}{
\index{Hydrodynamics@{Hydrodynamics}!Predictor@{Predictor}}
\index{Predictor@{Predictor}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Predictor}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Predictor (double {\em dt})}}
\label{classHydrodynamics_316a6079bf22102d9b911e2632cd2680}

predictor method, density evaluated directly

\begin{itemize}
\item iterate the real partilce list

\begin{itemize}
\item save values at step n

\item predict values at step n+1

\item calculate the middle values at step n+1/2\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=141pt]{classHydrodynamics_316a6079bf22102d9b911e2632cd2680_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=166pt]{classHydrodynamics_316a6079bf22102d9b911e2632cd2680_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_911fe25b94fec398fad1f2def036d755}{
\index{Hydrodynamics@{Hydrodynamics}!Predictor\_\-summation@{Predictor\_\-summation}}
\index{Predictor\_\-summation@{Predictor\_\-summation}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Predictor\_\-summation}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Predictor\_\-summation (double {\em dt})}}
\label{classHydrodynamics_911fe25b94fec398fad1f2def036d755}

for predictor method, density evaluated with summation (that means: no density update within this method)

\begin{itemize}
\item iterate the real partilce list

\begin{itemize}
\item save values (R,U) at step n in intermediate variables .\_\-I

\item predict values at step n+1

\item calculate the middle values at step n+1/2 and save them in \hyperlink{classParticle}{Particle} objects prtl\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=167pt]{classHydrodynamics_911fe25b94fec398fad1f2def036d755_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=256pt]{classHydrodynamics_911fe25b94fec398fad1f2def036d755_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_8f826d2003ca7a4782b028b761a26421}{
\index{Hydrodynamics@{Hydrodynamics}!RandomEffects@{RandomEffects}}
\index{RandomEffects@{RandomEffects}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{RandomEffects}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::RandomEffects ()}}
\label{classHydrodynamics_8f826d2003ca7a4782b028b761a26421}

including random effects (DPD simulation)

\begin{itemize}
\item iterate the real partilce list\end{itemize}

\begin{itemize}
\item for each particle: add random velocity \_\-dU \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=154pt]{classHydrodynamics_8f826d2003ca7a4782b028b761a26421_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=179pt]{classHydrodynamics_8f826d2003ca7a4782b028b761a26421_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_e6983cf4d86bf7b33b88c8f089caf3a8}{
\index{Hydrodynamics@{Hydrodynamics}!SurfaceTensionCoefficient@{SurfaceTensionCoefficient}}
\index{SurfaceTensionCoefficient@{SurfaceTensionCoefficient}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{SurfaceTensionCoefficient}]{\setlength{\rightskip}{0pt plus 5cm}double Hydrodynamics::SurfaceTensionCoefficient ()}}
\label{classHydrodynamics_e6983cf4d86bf7b33b88c8f089caf3a8}

calculate surface tension coefficient

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item calculate phase surface stress for all particles \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=177pt]{classHydrodynamics_e6983cf4d86bf7b33b88c8f089caf3a8_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_f744ee07f3f3b511d0db18949160c20a}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateChangeRate@{UpdateChangeRate}}
\index{UpdateChangeRate@{UpdateChangeRate}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateChangeRate}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateChangeRate ()}}
\label{classHydrodynamics_f744ee07f3f3b511d0db18949160c20a}

calculate interaction without updating interaction list

\begin{itemize}
\item initiate the change rate of each real particle by calling \hyperlink{classHydrodynamics_67e2d72d69156a086d43168f5cd58bf7}{ZeroChangeRate()}\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate\end{itemize}

\begin{itemize}
\item include the gravity effects \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=262pt]{classHydrodynamics_f744ee07f3f3b511d0db18949160c20a_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_22df8569d81c4c363029efac143ddb26}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateChangeRate@{UpdateChangeRate}}
\index{UpdateChangeRate@{UpdateChangeRate}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateChangeRate}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateChangeRate ({\bf ParticleManager} \& {\em particles}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classHydrodynamics_22df8569d81c4c363029efac143ddb26}

calculate interaction with updating interaction list

\begin{itemize}
\item initiate change rate of each real particle by calling ZerpChangeRate()\end{itemize}

\begin{itemize}
\item obtain the interaction pairs\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for eahc pair the pair forces or change rate\end{itemize}

\begin{itemize}
\item include the gravity effects by calling \hyperlink{classHydrodynamics_abdebac769f07f2500c21689fafa2981}{AddGravity()} \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=363pt]{classHydrodynamics_22df8569d81c4c363029efac143ddb26_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=252pt]{classHydrodynamics_22df8569d81c4c363029efac143ddb26_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_b6cab35a4d7adf70657ef16b9ec4dafd}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateDensity@{UpdateDensity}}
\index{UpdateDensity@{UpdateDensity}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateDensity}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateDensity ()}}
\label{classHydrodynamics_b6cab35a4d7adf70657ef16b9ec4dafd}

currently no shear rate calculated without updating interaction list

\begin{itemize}
\item initiate zero density\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate\end{itemize}

\begin{itemize}
\item calulate new pressure by calling \hyperlink{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891}{UpdateState()} \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=251pt]{classHydrodynamics_b6cab35a4d7adf70657ef16b9ec4dafd_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_1818eb1f9044ae980e92c70146e51c5b}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateDensity@{UpdateDensity}}
\index{UpdateDensity@{UpdateDensity}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateDensity}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateDensity ({\bf ParticleManager} \& {\em particles}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classHydrodynamics_1818eb1f9044ae980e92c70146e51c5b}

summation for particles density (with updating interaction list)

\begin{itemize}
\item obtain the interaction pairs\end{itemize}

\begin{itemize}
\item initiate by calling Zero\_\-density method\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate by calling SummationDensity() method\end{itemize}

\begin{itemize}
\item calulate new pressure by calling \hyperlink{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891}{UpdateState()} Method \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=352pt]{classHydrodynamics_1818eb1f9044ae980e92c70146e51c5b_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=242pt]{classHydrodynamics_1818eb1f9044ae980e92c70146e51c5b_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_a755853b07cbbc5b484d78a3e787d1ef}{
\index{Hydrodynamics@{Hydrodynamics}!UpdatePahseMatrix@{UpdatePahseMatrix}}
\index{UpdatePahseMatrix@{UpdatePahseMatrix}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdatePahseMatrix}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdatePahseMatrix ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_a755853b07cbbc5b484d78a3e787d1ef}

this method currently does {\bf NOTHING}

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item all phase surface stress (currently no action is performed)\end{itemize}

\begin{itemize}
\item iterate particles on the boundary particle list\end{itemize}

\begin{itemize}
\item all phase surface stress (currently no action is perforemd) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=164pt]{classHydrodynamics_a755853b07cbbc5b484d78a3e787d1ef_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_cf0d749b11e8b8474dd204c6ea080235}{
\index{Hydrodynamics@{Hydrodynamics}!UpdatePair@{UpdatePair}}
\index{UpdatePair@{UpdatePair}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdatePair}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdatePair ({\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classHydrodynamics_cf0d749b11e8b8474dd204c6ea080235}

update new parameters in pairs

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item and for each interactionpair call RenewInteraction method \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=251pt]{classHydrodynamics_cf0d749b11e8b8474dd204c6ea080235_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=234pt]{classHydrodynamics_cf0d749b11e8b8474dd204c6ea080235_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_c87ff6437d540454ed7de2f726858f4a}{
\index{Hydrodynamics@{Hydrodynamics}!UpdatePhaseField@{UpdatePhaseField}}
\index{UpdatePhaseField@{UpdatePhaseField}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdatePhaseField}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdatePhaseField ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_c87ff6437d540454ed7de2f726858f4a}

\begin{itemize}
\item initiate by calling \hyperlink{classHydrodynamics_dedab91b9a62eb7e26931cbbe73f79cc}{Zero\_\-PhaseField()}\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=262pt]{classHydrodynamics_c87ff6437d540454ed7de2f726858f4a_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_939e9b2ec26b3e4a2eaf2683e5f0343d}{
\index{Hydrodynamics@{Hydrodynamics}!UpdatePhaseGradient@{UpdatePhaseGradient}}
\index{UpdatePhaseGradient@{UpdatePhaseGradient}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdatePhaseGradient}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdatePhaseGradient ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_939e9b2ec26b3e4a2eaf2683e5f0343d}

not independant with UpdateDensity

\begin{itemize}
\item initiate by callingZer\_\-PhaseGradient()\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=278pt]{classHydrodynamics_939e9b2ec26b3e4a2eaf2683e5f0343d_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=258pt]{classHydrodynamics_939e9b2ec26b3e4a2eaf2683e5f0343d_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_dbbe86fd4eac49912a9ffb5e284883ee}{
\index{Hydrodynamics@{Hydrodynamics}!UpdatePhaseLaplacian@{UpdatePhaseLaplacian}}
\index{UpdatePhaseLaplacian@{UpdatePhaseLaplacian}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdatePhaseLaplacian}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdatePhaseLaplacian ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_dbbe86fd4eac49912a9ffb5e284883ee}

\begin{itemize}
\item initiate zero shear rateby calling \hyperlink{classHydrodynamics_d1c5fd5b500eacb886a72f2dab13e91b}{Zero\_\-PhaseLaplacian()}\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=281pt]{classHydrodynamics_dbbe86fd4eac49912a9ffb5e284883ee_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_49570aaeedea32d7a2baf0532880b2e8}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateShearRate@{UpdateShearRate}}
\index{UpdateShearRate@{UpdateShearRate}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateShearRate}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateShearRate ()}}
\label{classHydrodynamics_49570aaeedea32d7a2baf0532880b2e8}

???

\begin{itemize}
\item initiate by calling Zero\_\-ShearRate(\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=258pt]{classHydrodynamics_49570aaeedea32d7a2baf0532880b2e8_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_7ae4f1005699f13414ec6c487bac0ee0}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateShearRate@{UpdateShearRate}}
\index{UpdateShearRate@{UpdateShearRate}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateShearRate}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateShearRate ({\bf ParticleManager} \& {\em particles}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classHydrodynamics_7ae4f1005699f13414ec6c487bac0ee0}

summation for shear rates (with updating interaction list)

\begin{itemize}
\item obtain the interaction pairs\end{itemize}

\begin{itemize}
\item initiate by calling Zero\_\-ShearRate Method\end{itemize}

\begin{itemize}
\item iterate the interaction list\end{itemize}

\begin{itemize}
\item calculate for each pair the pair forces or change rate \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=359pt]{classHydrodynamics_7ae4f1005699f13414ec6c487bac0ee0_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateState@{UpdateState}}
\index{UpdateState@{UpdateState}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateState}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateState ()}}
\label{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891}

calculate states from conservatives

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item calculate pressure for each particle \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=153pt]{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=332pt]{classHydrodynamics_1698dbe8ecc0e730319de5d7eca7a891_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_f5b2c4ad14824e4b6192faa6f60f4014}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateSurfaceStress@{UpdateSurfaceStress}}
\index{UpdateSurfaceStress@{UpdateSurfaceStress}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateSurfaceStress}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateSurfaceStress ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_f5b2c4ad14824e4b6192faa6f60f4014}

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item update phase surface stress for all particles on this list\end{itemize}

\begin{itemize}
\item iterate particles on the boundary particle list\end{itemize}

\begin{itemize}
\item update phase surface stress for all particles on this list \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=167pt]{classHydrodynamics_f5b2c4ad14824e4b6192faa6f60f4014_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=256pt]{classHydrodynamics_f5b2c4ad14824e4b6192faa6f60f4014_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_09a3f5a5c055e0efc822fdf80f40cd7d}{
\index{Hydrodynamics@{Hydrodynamics}!UpdateVolume@{UpdateVolume}}
\index{UpdateVolume@{UpdateVolume}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{UpdateVolume}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::UpdateVolume ({\bf ParticleManager} \& {\em particles}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classHydrodynamics_09a3f5a5c055e0efc822fdf80f40cd7d}

calculate partilce volume

\begin{itemize}
\item iterate particles on the particle list

\begin{itemize}
\item take origin particle

\begin{itemize}
\item sum the weights for all of these particles (because they are the inverse of a volume!?!)\end{itemize}

\item clear the NNP\_\-list\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=246pt]{classHydrodynamics_09a3f5a5c055e0efc822fdf80f40cd7d_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_13810b3b4110a2b931bf7426af2f9bcf}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-density@{Zero\_\-density}}
\index{Zero\_\-density@{Zero\_\-density}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-density}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-density ()}}
\label{classHydrodynamics_13810b3b4110a2b931bf7426af2f9bcf}

initiate particle density to zero

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item set for each particle density to zero \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=149pt]{classHydrodynamics_13810b3b4110a2b931bf7426af2f9bcf_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=333pt]{classHydrodynamics_13810b3b4110a2b931bf7426af2f9bcf_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_dedab91b9a62eb7e26931cbbe73f79cc}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-PhaseField@{Zero\_\-PhaseField}}
\index{Zero\_\-PhaseField@{Zero\_\-PhaseField}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-PhaseField}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-PhaseField ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_dedab91b9a62eb7e26931cbbe73f79cc}

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item set all phases for all of these particles to zero\end{itemize}

\begin{itemize}
\item iterate particles on the boundary particle list\end{itemize}

\begin{itemize}
\item set all phases for all of these particles to zero \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=157pt]{classHydrodynamics_dedab91b9a62eb7e26931cbbe73f79cc_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=206pt]{classHydrodynamics_dedab91b9a62eb7e26931cbbe73f79cc_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_3c9019f19ccac5370b7b0ccda343b5d2}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-PhaseGradient@{Zero\_\-PhaseGradient}}
\index{Zero\_\-PhaseGradient@{Zero\_\-PhaseGradient}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-PhaseGradient}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-PhaseGradient ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_3c9019f19ccac5370b7b0ccda343b5d2}

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item set phase gradient to zeo for each of these particles\end{itemize}

\begin{itemize}
\item iterate particles on the boundary particle list\end{itemize}

\begin{itemize}
\item set phase gradient to zeo for each of these particle \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=165pt]{classHydrodynamics_3c9019f19ccac5370b7b0ccda343b5d2_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=365pt]{classHydrodynamics_3c9019f19ccac5370b7b0ccda343b5d2_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_d1c5fd5b500eacb886a72f2dab13e91b}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-PhaseLaplacian@{Zero\_\-PhaseLaplacian}}
\index{Zero\_\-PhaseLaplacian@{Zero\_\-PhaseLaplacian}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-PhaseLaplacian}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-PhaseLaplacian ({\bf Boundary} \& {\em boundary})}}
\label{classHydrodynamics_d1c5fd5b500eacb886a72f2dab13e91b}

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item set to zero all phase Laplacians for these particles\end{itemize}

\begin{itemize}
\item iterate particles on the boundary particle list\end{itemize}

\begin{itemize}
\item set to zero all phase Laplacians for these particles \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=168pt]{classHydrodynamics_d1c5fd5b500eacb886a72f2dab13e91b_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=227pt]{classHydrodynamics_d1c5fd5b500eacb886a72f2dab13e91b_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_f67579320cbdccaf49bbdf3dfb13f23c}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-Random@{Zero\_\-Random}}
\index{Zero\_\-Random@{Zero\_\-Random}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-Random}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-Random ()}}
\label{classHydrodynamics_f67579320cbdccaf49bbdf3dfb13f23c}

initiate random force (DPD simulation)

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item all random values to zero (so, \_\-dU is random value???) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=151pt]{classHydrodynamics_f67579320cbdccaf49bbdf3dfb13f23c_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=272pt]{classHydrodynamics_f67579320cbdccaf49bbdf3dfb13f23c_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_049f88c2f97863edae4489618dc9e853}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-ShearRate@{Zero\_\-ShearRate}}
\index{Zero\_\-ShearRate@{Zero\_\-ShearRate}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-ShearRate}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-ShearRate ()}}
\label{classHydrodynamics_049f88c2f97863edae4489618dc9e853}

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item set ShearRate to zero for each particle \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=156pt]{classHydrodynamics_049f88c2f97863edae4489618dc9e853_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=203pt]{classHydrodynamics_049f88c2f97863edae4489618dc9e853_icgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_4f65196eb3002238371d0e04dd76c02a}{
\index{Hydrodynamics@{Hydrodynamics}!Zero\_\-Velocity@{Zero\_\-Velocity}}
\index{Zero\_\-Velocity@{Zero\_\-Velocity}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{Zero\_\-Velocity}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::Zero\_\-Velocity ()}}
\label{classHydrodynamics_4f65196eb3002238371d0e04dd76c02a}

special uitilities

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item all velocities to zero \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=151pt]{classHydrodynamics_4f65196eb3002238371d0e04dd76c02a_cgraph}
\end{center}
\end{figure}
\hypertarget{classHydrodynamics_67e2d72d69156a086d43168f5cd58bf7}{
\index{Hydrodynamics@{Hydrodynamics}!ZeroChangeRate@{ZeroChangeRate}}
\index{ZeroChangeRate@{ZeroChangeRate}!Hydrodynamics@{Hydrodynamics}}
\subsubsection[{ZeroChangeRate}]{\setlength{\rightskip}{0pt plus 5cm}void Hydrodynamics::ZeroChangeRate ()}}
\label{classHydrodynamics_67e2d72d69156a086d43168f5cd58bf7}

initiate particle change rate

\begin{itemize}
\item iterate particles on the real particle list\end{itemize}

\begin{itemize}
\item set for each particle change rates to zero \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=157pt]{classHydrodynamics_67e2d72d69156a086d43168f5cd58bf7_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=351pt]{classHydrodynamics_67e2d72d69156a086d43168f5cd58bf7_icgraph}
\end{center}
\end{figure}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{hydrodynamics_8h}{hydrodynamics.h}\item 
\hyperlink{hydrodynamics_8cpp}{hydrodynamics.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classInitiation.tex
compressible branch

\hypertarget{classInitiation}{
\section{Initiation Class Reference}
\label{classInitiation}\index{Initiation@{Initiation}}
}
Initiates the simulation.

{\tt \#include $<$initiation.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classInitiation_4db3b8c45d38cf4e188de6aa672e8c0d}{Initiation} (const char $\ast$project\_\-name)
\item 
void \hyperlink{classInitiation_916e5b3e316dad1f524a1327b9e4aeb4}{non\_\-dimensionalize} ()
\begin{CompactList}\small\item\em non-dimensionalize initial condition and parameters \item\end{CompactList}\item 
void \hyperlink{classInitiation_cdbf1374b9b0f0b50a0bb1d9abf76293}{show\_\-information} ()
\begin{CompactList}\small\item\em show information on screen \item\end{CompactList}\item 
void \hyperlink{classInitiation_e80adc7d2105ad67b766fd1127966df3}{VolumeMass} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em predict the particle volume and mass \item\end{CompactList}\item 
\hypertarget{classInitiation_689c73dd7149dc11207eca5c3109a7cd}{
double \hyperlink{classInitiation_689c73dd7149dc11207eca5c3109a7cd}{non\_\-dms\_\-p} (double p)}
\label{classInitiation_689c73dd7149dc11207eca5c3109a7cd}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_deddac317c4755623e4fcef187b3f07a}{
double \hyperlink{classInitiation_deddac317c4755623e4fcef187b3f07a}{non\_\-dms\_\-T} (double T)}
\label{classInitiation_deddac317c4755623e4fcef187b3f07a}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_29245385c400c4f0de40707cb07dc0dd}{
double \hyperlink{classInitiation_29245385c400c4f0de40707cb07dc0dd}{non\_\-dms\_\-rho} (double rho)}
\label{classInitiation_29245385c400c4f0de40707cb07dc0dd}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_e39448af30a53dd8f4354492be9883fc}{
double \hyperlink{classInitiation_e39448af30a53dd8f4354492be9883fc}{non\_\-dms\_\-mass} (double mass)}
\label{classInitiation_e39448af30a53dd8f4354492be9883fc}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_2ec28f27a197bfaeb3937733dbb47b03}{
double \hyperlink{classInitiation_2ec28f27a197bfaeb3937733dbb47b03}{non\_\-dms\_\-time} (double time)}
\label{classInitiation_2ec28f27a197bfaeb3937733dbb47b03}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_921fe74dff7653520c5e72cc5c11b353}{
double \hyperlink{classInitiation_921fe74dff7653520c5e72cc5c11b353}{non\_\-dms\_\-length} (double length)}
\label{classInitiation_921fe74dff7653520c5e72cc5c11b353}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_1b13c381a36c5d841bf9b4dc108a03f6}{
Vec2d \hyperlink{classInitiation_1b13c381a36c5d841bf9b4dc108a03f6}{non\_\-dms\_\-box\_\-size} (Vec2d \hyperlink{classInitiation_c4ab38f327f64513f4c21cd5781f508a}{box\_\-size})}
\label{classInitiation_1b13c381a36c5d841bf9b4dc108a03f6}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_7e4fbcccd66df50f14970074038c2988}{
double \hyperlink{classInitiation_7e4fbcccd66df50f14970074038c2988}{non\_\-dms\_\-velocity} (double velocity)}
\label{classInitiation_7e4fbcccd66df50f14970074038c2988}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_f48f16aceb256dd582f8697f21408322}{
double \hyperlink{classInitiation_f48f16aceb256dd582f8697f21408322}{non\_\-dms\_\-kinetic\_\-viscosity} (double nu)}
\label{classInitiation_f48f16aceb256dd582f8697f21408322}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_32f485a6951b34ce75bac6422419ebce}{
Vec2d \hyperlink{classInitiation_32f485a6951b34ce75bac6422419ebce}{non\_\-dms\_\-velocity} (Vec2d velocity)}
\label{classInitiation_32f485a6951b34ce75bac6422419ebce}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_cc810254f426d6f2ed61ef6edee27d89}{
double \hyperlink{classInitiation_cc810254f426d6f2ed61ef6edee27d89}{non\_\-dms\_\-acceleration} (double acceleration)}
\label{classInitiation_cc810254f426d6f2ed61ef6edee27d89}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_68c764e4253f4cc5b66c8e978ef37fc8}{
Vec2d \hyperlink{classInitiation_68c764e4253f4cc5b66c8e978ef37fc8}{non\_\-dms\_\-acceleration} (Vec2d acceleration)}
\label{classInitiation_68c764e4253f4cc5b66c8e978ef37fc8}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_0d433208c495509df2e2270804b9c2ef}{
double \hyperlink{classInitiation_0d433208c495509df2e2270804b9c2ef}{non\_\-dms\_\-viscosity} (double mu)}
\label{classInitiation_0d433208c495509df2e2270804b9c2ef}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_98ded96b747a9ee7512fcc95702b2580}{
double \hyperlink{classInitiation_98ded96b747a9ee7512fcc95702b2580}{non\_\-dms\_\-heat\_\-ratio} (double cv)}
\label{classInitiation_98ded96b747a9ee7512fcc95702b2580}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_7d54bcdd903f0d9a0b602008bf9cd10d}{
double \hyperlink{classInitiation_7d54bcdd903f0d9a0b602008bf9cd10d}{non\_\-dms\_\-heat\_\-conduction} (double kappa)}
\label{classInitiation_7d54bcdd903f0d9a0b602008bf9cd10d}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_5e09a2250d66d54ef63def3cb9419eae}{
double \hyperlink{classInitiation_5e09a2250d66d54ef63def3cb9419eae}{non\_\-dms\_\-Boltzmann} (double \hyperlink{sph_8cpp_a50583a118c0a3e801d3e48a45b6a259}{k\_\-bltz})}
\label{classInitiation_5e09a2250d66d54ef63def3cb9419eae}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_190a357cdd44440885bd5081cc4236a5}{
double \hyperlink{classInitiation_190a357cdd44440885bd5081cc4236a5}{non\_\-dms\_\-surface} (double sigma)}
\label{classInitiation_190a357cdd44440885bd5081cc4236a5}

\begin{CompactList}\small\item\em a non dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_282fa06b6cb9769ceb01a2b22976126f}{
double \hyperlink{classInitiation_282fa06b6cb9769ceb01a2b22976126f}{dms\_\-p} (double p\_\-non)}
\label{classInitiation_282fa06b6cb9769ceb01a2b22976126f}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_f769934489a9293b6059072bf0e26ae7}{
double \hyperlink{classInitiation_f769934489a9293b6059072bf0e26ae7}{dms\_\-T} (double T\_\-non)}
\label{classInitiation_f769934489a9293b6059072bf0e26ae7}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_4d77129052a63bf33ad36638aaa47972}{
double \hyperlink{classInitiation_4d77129052a63bf33ad36638aaa47972}{dms\_\-rho} (double rho\_\-non)}
\label{classInitiation_4d77129052a63bf33ad36638aaa47972}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_e28be0f6a53920bdab379301eb414990}{
double \hyperlink{classInitiation_e28be0f6a53920bdab379301eb414990}{dms\_\-mass} (double mass\_\-non)}
\label{classInitiation_e28be0f6a53920bdab379301eb414990}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_0e76e3a9e585398854689d151b4af2d8}{
double \hyperlink{classInitiation_0e76e3a9e585398854689d151b4af2d8}{dms\_\-time} (double time\_\-non)}
\label{classInitiation_0e76e3a9e585398854689d151b4af2d8}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_d6747d9cbd12e6327249606b021a87f1}{
double \hyperlink{classInitiation_d6747d9cbd12e6327249606b021a87f1}{dms\_\-length} (double length\_\-non)}
\label{classInitiation_d6747d9cbd12e6327249606b021a87f1}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_8b5815911256da330c686c9e84e3ccbc}{
Vec2d \hyperlink{classInitiation_8b5815911256da330c686c9e84e3ccbc}{dms\_\-box\_\-size} (Vec2d box\_\-size\_\-non)}
\label{classInitiation_8b5815911256da330c686c9e84e3ccbc}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_1bbabaf118b739c082d9db6e5a0d1021}{
double \hyperlink{classInitiation_1bbabaf118b739c082d9db6e5a0d1021}{dms\_\-velocity} (double velocity\_\-non)}
\label{classInitiation_1bbabaf118b739c082d9db6e5a0d1021}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_ff3a9cd4918e5d823b4a1413b805c056}{
Vec2d \hyperlink{classInitiation_ff3a9cd4918e5d823b4a1413b805c056}{dms\_\-velocity} (Vec2d velocity\_\-non)}
\label{classInitiation_ff3a9cd4918e5d823b4a1413b805c056}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_d08c20a915f7c4878a8e382d54874fb1}{
double \hyperlink{classInitiation_d08c20a915f7c4878a8e382d54874fb1}{dms\_\-energy} (double energy\_\-non)}
\label{classInitiation_d08c20a915f7c4878a8e382d54874fb1}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_7746aa0e130fbfdd4ef72d662eaf4fe5}{
double \hyperlink{classInitiation_7746aa0e130fbfdd4ef72d662eaf4fe5}{dms\_\-acceleration} (double acceleration\_\-non)}
\label{classInitiation_7746aa0e130fbfdd4ef72d662eaf4fe5}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_c82bd7ac7f359587868b80b4498c4220}{
Vec2d \hyperlink{classInitiation_c82bd7ac7f359587868b80b4498c4220}{dms\_\-acceleration} (Vec2d acceleration\_\-non)}
\label{classInitiation_c82bd7ac7f359587868b80b4498c4220}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_f867793b42e943a473d1132d0bbb721a}{
double \hyperlink{classInitiation_f867793b42e943a473d1132d0bbb721a}{dms\_\-viscosity} (double mu\_\-non)}
\label{classInitiation_f867793b42e943a473d1132d0bbb721a}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\item 
\hypertarget{classInitiation_cbd8852ba19297b3278e96f6fb9ecb60}{
double \hyperlink{classInitiation_cbd8852ba19297b3278e96f6fb9ecb60}{dms\_\-surface} (double sigma\_\-non)}
\label{classInitiation_cbd8852ba19297b3278e96f6fb9ecb60}

\begin{CompactList}\small\item\em a re-dimensionalize method \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classInitiation_d011ce1385a1cd46fb500d9a62de6883}{
char \hyperlink{classInitiation_d011ce1385a1cd46fb500d9a62de6883}{Project\_\-name} \mbox{[}25\mbox{]}}
\label{classInitiation_d011ce1385a1cd46fb500d9a62de6883}

\begin{CompactList}\small\item\em the project name \item\end{CompactList}\item 
int \hyperlink{classInitiation_ac12d75613f51d4a10a3f28887be0821}{number\_\-of\_\-materials}
\begin{CompactList}\small\item\em number of materials \item\end{CompactList}\item 
\hypertarget{classInitiation_3f9f020a489c9179885c02c867e77ef0}{
char \hyperlink{classInitiation_3f9f020a489c9179885c02c867e77ef0}{inputfile} \mbox{[}25\mbox{]}}
\label{classInitiation_3f9f020a489c9179885c02c867e77ef0}

\begin{CompactList}\small\item\em the global inputfile name: a $\ast$.cfg file \item\end{CompactList}\item 
int \hyperlink{classInitiation_1bbced7f2136569c065e0f5c874c6cff}{initial\_\-condition}
\begin{CompactList}\small\item\em initial condition marker: \item\end{CompactList}\item 
\hypertarget{classInitiation_b9979da1d25141fa58f79393232b0a9c}{
int \hyperlink{classInitiation_b9979da1d25141fa58f79393232b0a9c}{diagnose}}
\label{classInitiation_b9979da1d25141fa58f79393232b0a9c}

\begin{CompactList}\small\item\em diagnose information maker: 1 output diagnose information \item\end{CompactList}\item 
\hypertarget{classInitiation_115596cc83b34b6f75031c5e5b0c3fe7}{
double \hyperlink{classInitiation_115596cc83b34b6f75031c5e5b0c3fe7}{art\_\-vis}}
\label{classInitiation_115596cc83b34b6f75031c5e5b0c3fe7}

\begin{CompactList}\small\item\em artificial viscosity \item\end{CompactList}\item 
\hypertarget{classInitiation_db9ebb73d2d6e17bb8e0179d29abaf7b}{
int \hyperlink{classInitiation_db9ebb73d2d6e17bb8e0179d29abaf7b}{simu\_\-mode}}
\label{classInitiation_db9ebb73d2d6e17bb8e0179d29abaf7b}

\begin{CompactList}\small\item\em simulation mode (1:liquids, 2: gas dynamics) \item\end{CompactList}\item 
\hypertarget{classInitiation_7053a11a810568d6beb69ed19bc7fa59}{
double \hyperlink{classInitiation_7053a11a810568d6beb69ed19bc7fa59}{smoothinglength}}
\label{classInitiation_7053a11a810568d6beb69ed19bc7fa59}

\begin{CompactList}\small\item\em smoothinglength \item\end{CompactList}\item 
\hypertarget{classInitiation_c4ab38f327f64513f4c21cd5781f508a}{
Vec2d \hyperlink{classInitiation_c4ab38f327f64513f4c21cd5781f508a}{box\_\-size}}
\label{classInitiation_c4ab38f327f64513f4c21cd5781f508a}

\begin{CompactList}\small\item\em the compuational domain size \item\end{CompactList}\item 
\hypertarget{classInitiation_ed9ecf2c5296af4ac243b1a089966c86}{
double \hyperlink{classInitiation_ed9ecf2c5296af4ac243b1a089966c86}{cell\_\-size}}
\label{classInitiation_ed9ecf2c5296af4ac243b1a089966c86}

\begin{CompactList}\small\item\em cell size \item\end{CompactList}\item 
\hypertarget{classInitiation_300dc1f911e95df0ecf34179bf1931fa}{
double \hyperlink{classInitiation_300dc1f911e95df0ecf34179bf1931fa}{delta}}
\label{classInitiation_300dc1f911e95df0ecf34179bf1931fa}

\begin{CompactList}\small\item\em the inital particle distance \item\end{CompactList}\item 
\hypertarget{classInitiation_c0d2d3c34bb4831258ce646b05a35981}{
int \hyperlink{classInitiation_c0d2d3c34bb4831258ce646b05a35981}{hdelta}}
\label{classInitiation_c0d2d3c34bb4831258ce646b05a35981}

\begin{CompactList}\small\item\em the ration between smoothing length and inital particle distance \item\end{CompactList}\item 
\hypertarget{classInitiation_8bc245d0b81987fc9fb8443713ebe6df}{
int \hyperlink{classInitiation_8bc245d0b81987fc9fb8443713ebe6df}{x\_\-cells}}
\label{classInitiation_8bc245d0b81987fc9fb8443713ebe6df}

\begin{CompactList}\small\item\em cells matrix for real particles \item\end{CompactList}\item 
\hypertarget{classInitiation_4741b9c5dfa95aadd6b103f091456f72}{
int \textbf{y\_\-cells}}
\label{classInitiation_4741b9c5dfa95aadd6b103f091456f72}

\item 
\hypertarget{classInitiation_cf2bd144db5215805966ccd40a5abaed}{
Vec2d \hyperlink{classInitiation_cf2bd144db5215805966ccd40a5abaed}{g\_\-force}}
\label{classInitiation_cf2bd144db5215805966ccd40a5abaed}

\begin{CompactList}\small\item\em g force on particles \item\end{CompactList}\item 
\hypertarget{classInitiation_802c22e6b71f5d2cfe68309685bf423b}{
double \hyperlink{classInitiation_802c22e6b71f5d2cfe68309685bf423b}{Start\_\-time}}
\label{classInitiation_802c22e6b71f5d2cfe68309685bf423b}

\begin{CompactList}\small\item\em Simulation start time. \item\end{CompactList}\item 
\hypertarget{classInitiation_0d3e0f13a25c1bbbc7b319ef59838012}{
double \hyperlink{classInitiation_0d3e0f13a25c1bbbc7b319ef59838012}{End\_\-time}}
\label{classInitiation_0d3e0f13a25c1bbbc7b319ef59838012}

\begin{CompactList}\small\item\em Simulation end time. \item\end{CompactList}\item 
\hypertarget{classInitiation_e6599efb2ef3de1c552d39ba6ce5fe5e}{
double \hyperlink{classInitiation_e6599efb2ef3de1c552d39ba6ce5fe5e}{D\_\-time}}
\label{classInitiation_e6599efb2ef3de1c552d39ba6ce5fe5e}

\begin{CompactList}\small\item\em time interval for output (every D\_\-time: output) \item\end{CompactList}\item 
\hypertarget{classInitiation_8f3749288efc593efb8c6b2e5da2dce2}{
Vec2d \hyperlink{classInitiation_8f3749288efc593efb8c6b2e5da2dce2}{U0}}
\label{classInitiation_8f3749288efc593efb8c6b2e5da2dce2}

\begin{CompactList}\small\item\em inital flow speed (if initial condition is defined here)w \item\end{CompactList}\item 
\hypertarget{classInitiation_a426f5569c652979800af92d6d4dd033}{
double \hyperlink{classInitiation_a426f5569c652979800af92d6d4dd033}{rho0}}
\label{classInitiation_a426f5569c652979800af92d6d4dd033}

\begin{CompactList}\small\item\em initial particle density(if initial condition is defined here) \item\end{CompactList}\item 
\hypertarget{classInitiation_d108934b865ac8267f61d1e04339fea0}{
double \hyperlink{classInitiation_d108934b865ac8267f61d1e04339fea0}{p0}}
\label{classInitiation_d108934b865ac8267f61d1e04339fea0}

\begin{CompactList}\small\item\em initial pressure(if initial condition is defined here) \item\end{CompactList}\item 
\hypertarget{classInitiation_b8db429b0356e54c88d8769191e6f550}{
double \hyperlink{classInitiation_b8db429b0356e54c88d8769191e6f550}{T0}}
\label{classInitiation_b8db429b0356e54c88d8769191e6f550}

\begin{CompactList}\small\item\em initial temperature(if initial condition is defined here) \item\end{CompactList}\item 
\hypertarget{classInitiation_4a7f19654a3c5fc2c703796150ab7de5}{
int \hyperlink{classInitiation_4a7f19654a3c5fc2c703796150ab7de5}{MLS\_\-MAX}}
\label{classInitiation_4a7f19654a3c5fc2c703796150ab7de5}

\begin{CompactList}\small\item\em Moving Least Squarr. \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classInitiation_18480401f4b40c2830a764cc56085167}{
double \hyperlink{classInitiation_18480401f4b40c2830a764cc56085167}{\_\-length}}
\label{classInitiation_18480401f4b40c2830a764cc56085167}

\begin{CompactList}\small\item\em reference length for non dimensional value \item\end{CompactList}\item 
\hypertarget{classInitiation_0e7baf9e9f15d03c957db7bc1df9e5f0}{
double \hyperlink{classInitiation_0e7baf9e9f15d03c957db7bc1df9e5f0}{\_\-v}}
\label{classInitiation_0e7baf9e9f15d03c957db7bc1df9e5f0}

\begin{CompactList}\small\item\em reference speed for non dimensional value \item\end{CompactList}\item 
\hypertarget{classInitiation_a20ec3ff1ccfd3aaf9505a86c2d629a1}{
double \hyperlink{classInitiation_a20ec3ff1ccfd3aaf9505a86c2d629a1}{\_\-rho}}
\label{classInitiation_a20ec3ff1ccfd3aaf9505a86c2d629a1}

\begin{CompactList}\small\item\em reference density for non dimensional value \item\end{CompactList}\item 
\hypertarget{classInitiation_8dc68dc47e54d0e3bf9ab4a222513c51}{
double \hyperlink{classInitiation_8dc68dc47e54d0e3bf9ab4a222513c51}{\_\-T}}
\label{classInitiation_8dc68dc47e54d0e3bf9ab4a222513c51}

\begin{CompactList}\small\item\em reference temperature for non dimensional value \item\end{CompactList}\end{CompactItemize}
\subsection*{Friends}
\begin{CompactItemize}
\item 
\hypertarget{classInitiation_a1212b6e372a0f45d2c01f3cd203af77}{
class \hyperlink{classInitiation_a1212b6e372a0f45d2c01f3cd203af77}{Material}}
\label{classInitiation_a1212b6e372a0f45d2c01f3cd203af77}

\item 
\hypertarget{classInitiation_652e6d35f07e2091db6c1d01e86e2286}{
class \hyperlink{classInitiation_652e6d35f07e2091db6c1d01e86e2286}{Hydrodynamics}}
\label{classInitiation_652e6d35f07e2091db6c1d01e86e2286}

\end{CompactItemize}

\subsection{Detailed Description}
Initiates the simulation.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classInitiation_4db3b8c45d38cf4e188de6aa672e8c0d}{
\index{Initiation@{Initiation}!Initiation@{Initiation}}
\index{Initiation@{Initiation}!Initiation@{Initiation}}
\subsubsection[{Initiation}]{\setlength{\rightskip}{0pt plus 5cm}Initiation::Initiation (const char $\ast$ {\em project\_\-name})\hspace{0.3cm}{\tt  \mbox{[}explicit\mbox{]}}}}
\label{classInitiation_4db3b8c45d38cf4e188de6aa672e8c0d}

constructor \begin{Desc}
\item[Parameters:]
\begin{description}
\item[{\em $\ast$project\_\-name,:}]a pointer to the project name array (the project name is defined as a main-function argument and therefore given as an additional command line element when running the progam) \end{description}
\end{Desc}

\begin{itemize}
\item check if inputfile exists (if not exit the program)

\item reading key words and configuration data from configuration file and assign them to the appropriate variable

\item create outdata directory

\item process the data {\bf !!!Question!!!}

(line 104) this is only true if h=cell\_\-size (which is not necessarily given, as h, cell\_\-size can be initiated independently in configuration file)

\item output information to screen

\item non-dimensionalize \par
\par
 \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=255pt]{classInitiation_4db3b8c45d38cf4e188de6aa672e8c0d_cgraph}
\end{center}
\end{figure}

\subsection{Member Function Documentation}
\hypertarget{classInitiation_916e5b3e316dad1f524a1327b9e4aeb4}{
\index{Initiation@{Initiation}!non\_\-dimensionalize@{non\_\-dimensionalize}}
\index{non\_\-dimensionalize@{non\_\-dimensionalize}!Initiation@{Initiation}}
\subsubsection[{non\_\-dimensionalize}]{\setlength{\rightskip}{0pt plus 5cm}void Initiation::non\_\-dimensionalize ()}}
\label{classInitiation_916e5b3e316dad1f524a1327b9e4aeb4}

non-dimensionalize initial condition and parameters

method calls the individual non\_\-dms\_\-methods vor each variable\par
 remark:to avoid confusion: the non dimensional variables have the same identifiers like the dimensional ones!!!\par
\par

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=190pt]{classInitiation_916e5b3e316dad1f524a1327b9e4aeb4_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=159pt]{classInitiation_916e5b3e316dad1f524a1327b9e4aeb4_icgraph}
\end{center}
\end{figure}
\hypertarget{classInitiation_cdbf1374b9b0f0b50a0bb1d9abf76293}{
\index{Initiation@{Initiation}!show\_\-information@{show\_\-information}}
\index{show\_\-information@{show\_\-information}!Initiation@{Initiation}}
\subsubsection[{show\_\-information}]{\setlength{\rightskip}{0pt plus 5cm}void Initiation::show\_\-information ()}}
\label{classInitiation_cdbf1374b9b0f0b50a0bb1d9abf76293}

show information on screen

\begin{itemize}
\item output general information on screen\end{itemize}

\begin{itemize}
\item output the timing information on screen\end{itemize}

\begin{itemize}
\item output iniformation on initialization mode (.cfg file or .rst file) \end{itemize}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=154pt]{classInitiation_cdbf1374b9b0f0b50a0bb1d9abf76293_icgraph}
\end{center}
\end{figure}
\hypertarget{classInitiation_e80adc7d2105ad67b766fd1127966df3}{
\index{Initiation@{Initiation}!VolumeMass@{VolumeMass}}
\index{VolumeMass@{VolumeMass}!Initiation@{Initiation}}
\subsubsection[{VolumeMass}]{\setlength{\rightskip}{0pt plus 5cm}void Initiation::VolumeMass ({\bf Hydrodynamics} \& {\em hydro}, \/  {\bf ParticleManager} \& {\em particles}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classInitiation_e80adc7d2105ad67b766fd1127966df3}

predict the particle volume and mass

\begin{itemize}
\item iterate particles on the particle list

\begin{itemize}
\item pick an origin particle

\item build the nearest neighbor particle list for chosen origin particle

\item iterate this Nearest Neighbor \hyperlink{classParticle}{Particle} list

\begin{itemize}
\item get a particle

\item calculate distance (origin$<$-$>$ neighbor)

\item calculate weight function for given distance (w=0, if dist$>$supportlengtg) an summ it up \end{itemize}

\item calculate volume as reciprocal value of weight function

\item save volume and mass in the respective particle list node (whih is each a \hyperlink{classParticle}{Particle} object with all the particle properties)

\item clear the NNP\_\-list\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=227pt]{classInitiation_e80adc7d2105ad67b766fd1127966df3_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=117pt]{classInitiation_e80adc7d2105ad67b766fd1127966df3_icgraph}
\end{center}
\end{figure}

\subsection{Member Data Documentation}
\hypertarget{classInitiation_1bbced7f2136569c065e0f5c874c6cff}{
\index{Initiation@{Initiation}!initial\_\-condition@{initial\_\-condition}}
\index{initial\_\-condition@{initial\_\-condition}!Initiation@{Initiation}}
\subsubsection[{initial\_\-condition}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Initiation::initial\_\-condition}}}
\label{classInitiation_1bbced7f2136569c065e0f5c874c6cff}

initial condition marker:

\begin{itemize}
\item 0 initialize from the .cfg file;\item 1 read from the .rst file particle by particle with non-dimensional data \end{itemize}
\hypertarget{classInitiation_ac12d75613f51d4a10a3f28887be0821}{
\index{Initiation@{Initiation}!number\_\-of\_\-materials@{number\_\-of\_\-materials}}
\index{number\_\-of\_\-materials@{number\_\-of\_\-materials}!Initiation@{Initiation}}
\subsubsection[{number\_\-of\_\-materials}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Initiation::number\_\-of\_\-materials}}}
\label{classInitiation_ac12d75613f51d4a10a3f28887be0821}

number of materials

\begin{itemize}
\item the no. zero material is always the wall\item therefore at least 2 materials should be included \end{itemize}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{initiation_8h}{initiation.h}\item 
\hyperlink{initiation_8cpp}{initiation.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classInteraction.tex
compressible branch

\hypertarget{classInteraction}{
\section{Interaction Class Reference}
\label{classInteraction}\index{Interaction@{Interaction}}
}
Defines interaction between particles.

{\tt \#include $<$interaction.h$>$}

Collaboration diagram for Interaction:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=192pt]{classInteraction__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classInteraction_76755da7b86df4bd62c2761d0bed095a}{Interaction} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
\hyperlink{classInteraction_9c72b648e00a7bafabc6c96a10492801}{Interaction} (\hyperlink{classParticle}{Particle} $\ast$prtl\_\-org, \hyperlink{classParticle}{Particle} $\ast$prtl\_\-dest, \hyperlink{classForce}{Force} $\ast$$\ast$forces, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, double dstc)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
void \hyperlink{classInteraction_cba2f76f1316695e948c07d31dfadea9}{NewInteraction} (\hyperlink{classParticle}{Particle} $\ast$prtl\_\-org, \hyperlink{classParticle}{Particle} $\ast$prtl\_\-dest, \hyperlink{classForce}{Force} $\ast$$\ast$forces, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, double dstc)
\begin{CompactList}\small\item\em use old interaction object for new interaction \item\end{CompactList}\item 
void \hyperlink{classInteraction_1adb37756172d95124e56556c9008120}{RenewInteraction} (\hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em renew pair parameters and changing pair values \item\end{CompactList}\item 
void \hyperlink{classInteraction_8151e605eb5d7695e0203e2f126c7b4c}{SummationDensity} ()
\begin{CompactList}\small\item\em summation of the density \item\end{CompactList}\item 
void \hyperlink{classInteraction_98a1dd36fd34e7646aec02e21426562d}{SummationShearRate} ()
\begin{CompactList}\small\item\em summation of the shear rates \item\end{CompactList}\item 
void \hyperlink{classInteraction_6c0000b8eaede20c1d3576013195d71f}{SummationPhaseField} ()
\begin{CompactList}\small\item\em sum phase field contribution of interaction pair \item\end{CompactList}\item 
\hypertarget{classInteraction_e12db5ebc1b5b49de8024073062c7d2d}{
void \textbf{SummationCurvature} ()}
\label{classInteraction_e12db5ebc1b5b49de8024073062c7d2d}

\item 
void \hyperlink{classInteraction_28d4a91b7bbf8a430474ff0659d61d2d}{SummationPhaseGradient} ()
\begin{CompactList}\small\item\em sum phase gradient contribution of interaction pair \item\end{CompactList}\item 
\hypertarget{classInteraction_30a4bcf8e6ba5372a5ccfa2eb5f0c599}{
void \textbf{SummationPhaseGradient\_\-old} ()}
\label{classInteraction_30a4bcf8e6ba5372a5ccfa2eb5f0c599}

\item 
\hypertarget{classInteraction_f0fbe6eae076e7416deebbfce35e2652}{
void \textbf{SummationPhaseLaplacian} ()}
\label{classInteraction_f0fbe6eae076e7416deebbfce35e2652}

\item 
void \hyperlink{classInteraction_7d1b68aea03829678cfbe8c5ec3acc2a}{UpdateForces} ()
\begin{CompactList}\small\item\em update forces \item\end{CompactList}\item 
void \hyperlink{classInteraction_4cfd21ed44349e4295fd70e98bdae381}{UpdateForces\_\-vis} ()
\begin{CompactList}\small\item\em update forces with summation of viscosity \item\end{CompactList}\item 
\hypertarget{classInteraction_25763a827f24b2b073c564f274b0ae47}{
void \hyperlink{classInteraction_25763a827f24b2b073c564f274b0ae47}{RandomForces} (\hyperlink{classWiener}{Wiener} \&wiener, double sqrtdt)}
\label{classInteraction_25763a827f24b2b073c564f274b0ae47}

\begin{CompactList}\small\item\em update random forces \item\end{CompactList}\item 
\hypertarget{classInteraction_90f82e85aeec6d1d2ee4229f18049bd8}{
void \hyperlink{classInteraction_90f82e85aeec6d1d2ee4229f18049bd8}{RandomForces\_\-Espanol} (\hyperlink{classWiener}{Wiener} \&wiener, double sqrtdt)}
\label{classInteraction_90f82e85aeec6d1d2ee4229f18049bd8}

\begin{CompactList}\small\item\em update random forces with Espanol's method \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classInteraction_b68efe982297a5b6e71ec85e37a60bfb}{
\hyperlink{classParticle}{Particle} $\ast$ \hyperlink{classInteraction_b68efe982297a5b6e71ec85e37a60bfb}{Org}}
\label{classInteraction_b68efe982297a5b6e71ec85e37a60bfb}

\begin{CompactList}\small\item\em pointer to particle with larger ID (of particle pair) \item\end{CompactList}\item 
\hypertarget{classInteraction_61023db08855158f1d188044251a412d}{
\hyperlink{classParticle}{Particle} $\ast$ \hyperlink{classInteraction_61023db08855158f1d188044251a412d}{Dest}}
\label{classInteraction_61023db08855158f1d188044251a412d}

\begin{CompactList}\small\item\em pointer to particle with smaller ID (of particle pair) \item\end{CompactList}\item 
\hypertarget{classInteraction_d9eed70414bdb5e371b096a7671c7a20}{
\hyperlink{classForce}{Force} $\ast$$\ast$ \hyperlink{classInteraction_d9eed70414bdb5e371b096a7671c7a20}{frc\_\-ij}}
\label{classInteraction_d9eed70414bdb5e371b096a7671c7a20}

\begin{CompactList}\small\item\em force from particle i to particle j \item\end{CompactList}\item 
\hypertarget{classInteraction_3e9360ca4d40c2e68bdf383fdd24ccce}{
int \hyperlink{classInteraction_3e9360ca4d40c2e68bdf383fdd24ccce}{noi}}
\label{classInteraction_3e9360ca4d40c2e68bdf383fdd24ccce}

\begin{CompactList}\small\item\em material NO. of the partilce i \item\end{CompactList}\item 
\hypertarget{classInteraction_0bad561d2bd56d468e48e1c2436978fc}{
int \hyperlink{classInteraction_0bad561d2bd56d468e48e1c2436978fc}{noj}}
\label{classInteraction_0bad561d2bd56d468e48e1c2436978fc}

\begin{CompactList}\small\item\em material NO. of the partilce j \item\end{CompactList}\item 
\hypertarget{classInteraction_784e1559dae549bcfd16d610e0f0afc1}{
double \hyperlink{classInteraction_784e1559dae549bcfd16d610e0f0afc1}{mi}}
\label{classInteraction_784e1559dae549bcfd16d610e0f0afc1}

\begin{CompactList}\small\item\em mass particle i \item\end{CompactList}\item 
\hypertarget{classInteraction_4210c5eab19bbba749d449c62cd32dbf}{
double \hyperlink{classInteraction_4210c5eab19bbba749d449c62cd32dbf}{rmi}}
\label{classInteraction_4210c5eab19bbba749d449c62cd32dbf}

\begin{CompactList}\small\item\em reciprocal value of mass particle i \item\end{CompactList}\item 
\hypertarget{classInteraction_9d05f9f756cc060e83df36e6f4a91916}{
double \hyperlink{classInteraction_9d05f9f756cc060e83df36e6f4a91916}{etai}}
\label{classInteraction_9d05f9f756cc060e83df36e6f4a91916}

\begin{CompactList}\small\item\em viscosity for particle i \item\end{CompactList}\item 
\hypertarget{classInteraction_5894b29fda10089be87da2c66e600843}{
double \hyperlink{classInteraction_5894b29fda10089be87da2c66e600843}{zetai}}
\label{classInteraction_5894b29fda10089be87da2c66e600843}

\begin{CompactList}\small\item\em {\bf !!!question!!!{\bf other viscosity for particle??? }}\item\end{CompactList}\item 
\hypertarget{classInteraction_0c96b05bcc1f55aa3c095dd483478159}{
double \hyperlink{classInteraction_0c96b05bcc1f55aa3c095dd483478159}{mj}}
\label{classInteraction_0c96b05bcc1f55aa3c095dd483478159}

\begin{CompactList}\small\item\em mass particle j \item\end{CompactList}\item 
\hypertarget{classInteraction_fbdcead1ee80174b4d98952a12763e31}{
double \hyperlink{classInteraction_fbdcead1ee80174b4d98952a12763e31}{rmj}}
\label{classInteraction_fbdcead1ee80174b4d98952a12763e31}

\begin{CompactList}\small\item\em reciprocal value of mass particle j \item\end{CompactList}\item 
\hypertarget{classInteraction_af810b6d29f848738dc472d0bf1dd5f5}{
double \hyperlink{classInteraction_af810b6d29f848738dc472d0bf1dd5f5}{etaj}}
\label{classInteraction_af810b6d29f848738dc472d0bf1dd5f5}

\begin{CompactList}\small\item\em viscosity for particle j \item\end{CompactList}\item 
\hypertarget{classInteraction_fec2d2babd85fff5f6e54e41aa65a862}{
double \hyperlink{classInteraction_fec2d2babd85fff5f6e54e41aa65a862}{zetaj}}
\label{classInteraction_fec2d2babd85fff5f6e54e41aa65a862}

\begin{CompactList}\small\item\em {\bf !!!question!!!{\bf other viscosity for particle??? }}\item\end{CompactList}\item 
\hypertarget{classInteraction_d2a06f46206fe80c305c39320ec693f3}{
double \hyperlink{classInteraction_d2a06f46206fe80c305c39320ec693f3}{rij}}
\label{classInteraction_d2a06f46206fe80c305c39320ec693f3}

\begin{CompactList}\small\item\em distance between 2 particles \item\end{CompactList}\item 
\hypertarget{classInteraction_85655b8499e012ca1abfbe441b9cd877}{
double \hyperlink{classInteraction_85655b8499e012ca1abfbe441b9cd877}{rrij}}
\label{classInteraction_85655b8499e012ca1abfbe441b9cd877}

\begin{CompactList}\small\item\em reciprocal value of distance between 2 particles \item\end{CompactList}\item 
\hypertarget{classInteraction_eba240d2ffdb54061f81731aa71899c5}{
double \hyperlink{classInteraction_eba240d2ffdb54061f81731aa71899c5}{Wij}}
\label{classInteraction_eba240d2ffdb54061f81731aa71899c5}

\begin{CompactList}\small\item\em {\bf !!!question!!!{\bf  }}\item\end{CompactList}\item 
\hypertarget{classInteraction_852d78e817e68e1b993728fbd82be282}{
double \hyperlink{classInteraction_852d78e817e68e1b993728fbd82be282}{Fij}}
\label{classInteraction_852d78e817e68e1b993728fbd82be282}

\begin{CompactList}\small\item\em {\bf !!!question!!!{\bf  }}\item\end{CompactList}\item 
\hypertarget{classInteraction_7c35fdb7203d62ee603c98cd85bae892}{
double \hyperlink{classInteraction_7c35fdb7203d62ee603c98cd85bae892}{LapWij}}
\label{classInteraction_7c35fdb7203d62ee603c98cd85bae892}

\begin{CompactList}\small\item\em {\bf !!!question!!!{\bf  }}\item\end{CompactList}\item 
\hypertarget{classInteraction_ab5f36ffa814690f70e996687babc39e}{
double \hyperlink{classInteraction_ab5f36ffa814690f70e996687babc39e}{Wij2}}
\label{classInteraction_ab5f36ffa814690f70e996687babc39e}

\begin{CompactList}\small\item\em {\bf !!!question!!!{\bf  }}\item\end{CompactList}\item 
\hypertarget{classInteraction_7c283bad9c22a17c44d3566eacd02705}{
Vec2d \hyperlink{classInteraction_7c283bad9c22a17c44d3566eacd02705}{eij}}
\label{classInteraction_7c283bad9c22a17c44d3566eacd02705}

\begin{CompactList}\small\item\em pair direction from orginal particle to destination particle \item\end{CompactList}\item 
\hypertarget{classInteraction_cb951c6ab7ba28c54b6c03f9dcda6d2b}{
double \hyperlink{classInteraction_cb951c6ab7ba28c54b6c03f9dcda6d2b}{shear\_\-rij}}
\label{classInteraction_cb951c6ab7ba28c54b6c03f9dcda6d2b}

\begin{CompactList}\small\item\em particle length to implement slip boundary$<${\bf !!!question!!!{\bf  }}\item\end{CompactList}\item 
\hypertarget{classInteraction_6e7625bfb7180e7ca9e9d113b16ac64e}{
double \hyperlink{classInteraction_6e7625bfb7180e7ca9e9d113b16ac64e}{bulk\_\-rij}}
\label{classInteraction_6e7625bfb7180e7ca9e9d113b16ac64e}

\begin{CompactList}\small\item\em particle length to implement slip boundary$<${\bf !!!question!!!{\bf  }}\item\end{CompactList}\end{CompactItemize}
\subsection*{Static Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classInteraction_aeeeca2f8dcc8cd22803b2ef6633319f}{
static int \hyperlink{classInteraction_aeeeca2f8dcc8cd22803b2ef6633319f}{number\_\-of\_\-materials} = 0}
\label{classInteraction_aeeeca2f8dcc8cd22803b2ef6633319f}

\begin{CompactList}\small\item\em total number of materials \item\end{CompactList}\item 
\hypertarget{classInteraction_7d9addfe3a9f9c69357d900cd9495c94}{
static double \textbf{smoothinglength} = 0.0}
\label{classInteraction_7d9addfe3a9f9c69357d900cd9495c94}

\item 
\hypertarget{classInteraction_4480c9589b1406bed453fcb0f72bc215}{
static double \hyperlink{classInteraction_4480c9589b1406bed453fcb0f72bc215}{delta} = 0.0}
\label{classInteraction_4480c9589b1406bed453fcb0f72bc215}

\begin{CompactList}\small\item\em particle distance \item\end{CompactList}\item 
\hypertarget{classInteraction_e39ad193f42e2a0d3579e6b59fca3d72}{
static double \hyperlink{classInteraction_e39ad193f42e2a0d3579e6b59fca3d72}{art\_\-vis} = 0.0}
\label{classInteraction_e39ad193f42e2a0d3579e6b59fca3d72}

\begin{CompactList}\small\item\em artificial viscosity \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
Defines interaction between particles.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classInteraction_76755da7b86df4bd62c2761d0bed095a}{
\index{Interaction@{Interaction}!Interaction@{Interaction}}
\index{Interaction@{Interaction}!Interaction@{Interaction}}
\subsubsection[{Interaction}]{\setlength{\rightskip}{0pt plus 5cm}Interaction::Interaction ({\bf Initiation} \& {\em ini})}}
\label{classInteraction_76755da7b86df4bd62c2761d0bed095a}

constructor

\begin{itemize}
\item copy properties from initiation \end{itemize}
\hypertarget{classInteraction_9c72b648e00a7bafabc6c96a10492801}{
\index{Interaction@{Interaction}!Interaction@{Interaction}}
\index{Interaction@{Interaction}!Interaction@{Interaction}}
\subsubsection[{Interaction}]{\setlength{\rightskip}{0pt plus 5cm}Interaction::Interaction ({\bf Particle} $\ast$ {\em prtl\_\-org}, \/  {\bf Particle} $\ast$ {\em prtl\_\-dest}, \/  {\bf Force} $\ast$$\ast$ {\em forces}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  double {\em dstc})}}
\label{classInteraction_9c72b648e00a7bafabc6c96a10492801}

constructor

\begin{itemize}
\item assign the original and the destinate particle in the reaction pair\end{itemize}

\begin{itemize}
\item determine interaction parameters\end{itemize}

\begin{itemize}
\item define pair values (mass, viscosity), do not change in sub time steps\end{itemize}

\begin{itemize}
\item calculate pair parameters (weight functions, shear- and bulk-) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=149pt]{classInteraction_9c72b648e00a7bafabc6c96a10492801_cgraph}
\end{center}
\end{figure}

\subsection{Member Function Documentation}
\hypertarget{classInteraction_cba2f76f1316695e948c07d31dfadea9}{
\index{Interaction@{Interaction}!NewInteraction@{NewInteraction}}
\index{NewInteraction@{NewInteraction}!Interaction@{Interaction}}
\subsubsection[{NewInteraction}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::NewInteraction ({\bf Particle} $\ast$ {\em prtl\_\-org}, \/  {\bf Particle} $\ast$ {\em prtl\_\-dest}, \/  {\bf Force} $\ast$$\ast$ {\em forces}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  double {\em dstc})}}
\label{classInteraction_cba2f76f1316695e948c07d31dfadea9}

use old interaction object for new interaction

\begin{itemize}
\item assign the original and the destinate particle in the reaction pair\end{itemize}

\begin{itemize}
\item determine interaction parameters\end{itemize}

\begin{itemize}
\item define pair values(mass, viscosity), do not change in sub time steps\end{itemize}

\begin{itemize}
\item calculate pair parameters (weight functions, shear- and bulk-) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=159pt]{classInteraction_cba2f76f1316695e948c07d31dfadea9_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{classInteraction_cba2f76f1316695e948c07d31dfadea9_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_1adb37756172d95124e56556c9008120}{
\index{Interaction@{Interaction}!RenewInteraction@{RenewInteraction}}
\index{RenewInteraction@{RenewInteraction}!Interaction@{Interaction}}
\subsubsection[{RenewInteraction}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::RenewInteraction ({\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classInteraction_1adb37756172d95124e56556c9008120}

renew pair parameters and changing pair values

Changes: \hyperlink{classInteraction}{Interaction} object\par
 Depends on: \hyperlink{classInteraction}{Interaction} Object, Org, Dest

\begin{itemize}
\item calculate pair parameters (weight functions, shear- and bulk-) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=164pt]{classInteraction_1adb37756172d95124e56556c9008120_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=323pt]{classInteraction_1adb37756172d95124e56556c9008120_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_8151e605eb5d7695e0203e2f126c7b4c}{
\index{Interaction@{Interaction}!SummationDensity@{SummationDensity}}
\index{SummationDensity@{SummationDensity}!Interaction@{Interaction}}
\subsubsection[{SummationDensity}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::SummationDensity ()}}
\label{classInteraction_8151e605eb5d7695e0203e2f126c7b4c}

summation of the density

Changes: Org(rho:summation), Dest(rho:summation)\par
 Depends on: \hyperlink{classInteraction}{Interaction} Object, Org(rho), Dest(rho) Remark: the idea is different from the original sph method

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=335pt]{classInteraction_8151e605eb5d7695e0203e2f126c7b4c_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_6c0000b8eaede20c1d3576013195d71f}{
\index{Interaction@{Interaction}!SummationPhaseField@{SummationPhaseField}}
\index{SummationPhaseField@{SummationPhaseField}!Interaction@{Interaction}}
\subsubsection[{SummationPhaseField}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::SummationPhaseField ()}}
\label{classInteraction_6c0000b8eaede20c1d3576013195d71f}

sum phase field contribution of interaction pair

Changes: Org(phi:summation), Dest(phi:summation)\par
 Depends on: \hyperlink{classInteraction}{Interaction} Object, Org(phi, rho), Dest(phi, rho)

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=208pt]{classInteraction_6c0000b8eaede20c1d3576013195d71f_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_28d4a91b7bbf8a430474ff0659d61d2d}{
\index{Interaction@{Interaction}!SummationPhaseGradient@{SummationPhaseGradient}}
\index{SummationPhaseGradient@{SummationPhaseGradient}!Interaction@{Interaction}}
\subsubsection[{SummationPhaseGradient}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::SummationPhaseGradient ()}}
\label{classInteraction_28d4a91b7bbf8a430474ff0659d61d2d}

sum phase gradient contribution of interaction pair

Changes: Org(del\_\-phi:summation), Dest(del\_\-phi:summation)\par
 Depends on: \hyperlink{classInteraction}{Interaction} Object, Org(del\_\-phi,rho), Dest(del\_\-phi,rho)

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=367pt]{classInteraction_28d4a91b7bbf8a430474ff0659d61d2d_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_98a1dd36fd34e7646aec02e21426562d}{
\index{Interaction@{Interaction}!SummationShearRate@{SummationShearRate}}
\index{SummationShearRate@{SummationShearRate}!Interaction@{Interaction}}
\subsubsection[{SummationShearRate}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::SummationShearRate ()}}
\label{classInteraction_98a1dd36fd34e7646aec02e21426562d}

summation of the shear rates

Changes: Org(ShearRate\_\-x, ShearRate\_\-y:summation), Dest(ShearRate\_\-x, ShearRate\_\-y:summation)\par
 Depends on: \hyperlink{classInteraction}{Interaction} Object, Org(ShearRate\_\-x, ShearRate\_\-y, U, rho), Dest(ShearRate\_\-x, ShearRate\_\-y, U, rho)

\begin{itemize}
\item define particle state values\end{itemize}

\begin{itemize}
\item summation of shear rates \end{itemize}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=204pt]{classInteraction_98a1dd36fd34e7646aec02e21426562d_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_7d1b68aea03829678cfbe8c5ec3acc2a}{
\index{Interaction@{Interaction}!UpdateForces@{UpdateForces}}
\index{UpdateForces@{UpdateForces}!Interaction@{Interaction}}
\subsubsection[{UpdateForces}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::UpdateForces ()}}
\label{classInteraction_7d1b68aea03829678cfbe8c5ec3acc2a}

update forces

\begin{itemize}
\item calculate artificial viscosity or Neumann\_\-Richtmyer viscosity\end{itemize}

\begin{itemize}
\item calculate density change rate\end{itemize}

\begin{itemize}
\item calculate momentum change rate\end{itemize}

\begin{itemize}
\item calculate additional momentum change rate contribution due to surface tension (with simplified model) \end{itemize}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=334pt]{classInteraction_7d1b68aea03829678cfbe8c5ec3acc2a_icgraph}
\end{center}
\end{figure}
\hypertarget{classInteraction_4cfd21ed44349e4295fd70e98bdae381}{
\index{Interaction@{Interaction}!UpdateForces\_\-vis@{UpdateForces\_\-vis}}
\index{UpdateForces\_\-vis@{UpdateForces\_\-vis}!Interaction@{Interaction}}
\subsubsection[{UpdateForces\_\-vis}]{\setlength{\rightskip}{0pt plus 5cm}void Interaction::UpdateForces\_\-vis ()}}
\label{classInteraction_4cfd21ed44349e4295fd70e98bdae381}

update forces with summation of viscosity

\begin{itemize}
\item calculate shear force\end{itemize}

\begin{itemize}
\item define pair force or momentum change rate\end{itemize}

summation (acceleration (=velovity change rate)=force (=momentum change rate)$\ast$ mass

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{interaction_8h}{interaction.h}\item 
\hyperlink{interaction_8cpp}{interaction.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classKernel.tex
compressible branch

\hypertarget{classKernel}{
\section{Kernel Class Reference}
\label{classKernel}\index{Kernel@{Kernel}}
}
\hyperlink{classKernel}{Kernel} abstract base.

{\tt \#include $<$kernel.h$>$}

Inheritance diagram for Kernel:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=198pt]{classKernel__inherit__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classKernel_7ff93426a5df552fdb40f0600dbfe314}{
\hyperlink{classKernel_7ff93426a5df552fdb40f0600dbfe314}{Kernel} (double \hyperlink{classKernel_f088821dba4a00d1d320b27ebcb71258}{smoothingLength})}
\label{classKernel_7ff93426a5df552fdb40f0600dbfe314}

\begin{CompactList}\small\item\em Constructor to initialize data members. \item\end{CompactList}\item 
virtual \hyperlink{classKernel_9c7407e3a0b1cb9b2f96e9a030187064}{$\sim$Kernel} ()
\begin{CompactList}\small\item\em Base classes with virtual member functions should have a virtual destructor. \item\end{CompactList}\item 
\hypertarget{classKernel_6b4d26ba99457a4acbbbca1454dbdc8a}{
virtual double \hyperlink{classKernel_6b4d26ba99457a4acbbbca1454dbdc8a}{w} (double distance) const =0}
\label{classKernel_6b4d26ba99457a4acbbbca1454dbdc8a}

\begin{CompactList}\small\item\em Calculates the kernel value for the given distance of two particles. \item\end{CompactList}\item 
\hypertarget{classKernel_545e61b98db05db6dd02b88e2ad3da23}{
virtual Vec2d \hyperlink{classKernel_545e61b98db05db6dd02b88e2ad3da23}{gradW} (double distance, const Vec2d \&distanceVector) const =0}
\label{classKernel_545e61b98db05db6dd02b88e2ad3da23}

\begin{CompactList}\small\item\em Calculates the kernel derivation for the given distance of two particles. \item\end{CompactList}\end{CompactItemize}
\subsection*{Protected Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classKernel_f088821dba4a00d1d320b27ebcb71258}{
const double \hyperlink{classKernel_f088821dba4a00d1d320b27ebcb71258}{smoothingLength}}
\label{classKernel_f088821dba4a00d1d320b27ebcb71258}

\begin{CompactList}\small\item\em A local copy of the smoothing length. \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classKernel}{Kernel} abstract base.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classKernel_9c7407e3a0b1cb9b2f96e9a030187064}{
\index{Kernel@{Kernel}!$\sim$Kernel@{$\sim$Kernel}}
\index{$\sim$Kernel@{$\sim$Kernel}!Kernel@{Kernel}}
\subsubsection[{$\sim$Kernel}]{\setlength{\rightskip}{0pt plus 5cm}Kernel::$\sim$Kernel ()\hspace{0.3cm}{\tt  \mbox{[}virtual\mbox{]}}}}
\label{classKernel_9c7407e3a0b1cb9b2f96e9a030187064}

Base classes with virtual member functions should have a virtual destructor.

deconstructor

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{kernel_8h}{kernel.h}\item 
\hyperlink{kernel_8cpp}{kernel.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classLlist.tex
compressible branch

\hypertarget{classLlist}{
\section{Llist$<$ Ldata $>$ Class Template Reference}
\label{classLlist}\index{Llist@{Llist}}
}
Double linked list implementation.

{\tt \#include $<$dllist.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classLlist_80be9511479463e949f442a22e48c064}{
\hyperlink{classLlist_80be9511479463e949f442a22e48c064}{Llist} ()}
\label{classLlist_80be9511479463e949f442a22e48c064}

\begin{CompactList}\small\item\em creates a list with an empty head node (no data in the head, but the node exists) \item\end{CompactList}\item 
\hypertarget{classLlist_6a139c360a8687527ebd74a27ff77ec2}{
bool \hyperlink{classLlist_6a139c360a8687527ebd74a27ff77ec2}{empty} () const }
\label{classLlist_6a139c360a8687527ebd74a27ff77ec2}

\begin{CompactList}\small\item\em Check if the list is empty (the first node is the last). \item\end{CompactList}\item 
\hypertarget{classLlist_a02016d71082697d45b3d0dcd5ce1343}{
bool \hyperlink{classLlist_a02016d71082697d45b3d0dcd5ce1343}{isEnd} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p) const }
\label{classLlist_a02016d71082697d45b3d0dcd5ce1343}

\begin{CompactList}\small\item\em Check if the node is the last node. \item\end{CompactList}\item 
\hypertarget{classLlist_91f735ef2924ff78864157c2434c81e3}{
\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$ \hyperlink{classLlist_91f735ef2924ff78864157c2434c81e3}{first} () const }
\label{classLlist_91f735ef2924ff78864157c2434c81e3}

\begin{CompactList}\small\item\em Get the first node. \item\end{CompactList}\item 
\hypertarget{classLlist_db32667fa0f00bd82d0c1c08c5998fc9}{
\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$ \hyperlink{classLlist_db32667fa0f00bd82d0c1c08c5998fc9}{next} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p) const }
\label{classLlist_db32667fa0f00bd82d0c1c08c5998fc9}

\begin{CompactList}\small\item\em Get the next node. \item\end{CompactList}\item 
\hypertarget{classLlist_367d32016c163108d10064afafd52029}{
\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$ \hyperlink{classLlist_367d32016c163108d10064afafd52029}{prev} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p) const }
\label{classLlist_367d32016c163108d10064afafd52029}

\begin{CompactList}\small\item\em Get the previous node. \item\end{CompactList}\item 
\hypertarget{classLlist_67608f0f66a3def622134d074294585d}{
Ldata $\ast$ \hyperlink{classLlist_67608f0f66a3def622134d074294585d}{retrieve} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p) const }
\label{classLlist_67608f0f66a3def622134d074294585d}

\begin{CompactList}\small\item\em Get the node data. \item\end{CompactList}\item 
\hypertarget{classLlist_99cb4c4f9cbf48a6b1c2cdae4f366097}{
void \hyperlink{classLlist_99cb4c4f9cbf48a6b1c2cdae4f366097}{store} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p, Ldata $\ast$d)}
\label{classLlist_99cb4c4f9cbf48a6b1c2cdae4f366097}

\begin{CompactList}\small\item\em set the particle \item\end{CompactList}\item 
\hypertarget{classLlist_52e0c9e8af720fc20a70fcd159bae5c6}{
int \hyperlink{classLlist_52e0c9e8af720fc20a70fcd159bae5c6}{length} () const }
\label{classLlist_52e0c9e8af720fc20a70fcd159bae5c6}

\begin{CompactList}\small\item\em get the list length \item\end{CompactList}\item 
\hypertarget{classLlist_62d2c41eb7e240d74de37f15fb31717a}{
void \hyperlink{classLlist_62d2c41eb7e240d74de37f15fb31717a}{insert} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p, Ldata $\ast$d)}
\label{classLlist_62d2c41eb7e240d74de37f15fb31717a}

\begin{CompactList}\small\item\em insert a node with node data \item\end{CompactList}\item 
\hypertarget{classLlist_978a0ea9a47f2b809d8626a6261eb5f6}{
void \hyperlink{classLlist_978a0ea9a47f2b809d8626a6261eb5f6}{remove} (\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$p)}
\label{classLlist_978a0ea9a47f2b809d8626a6261eb5f6}

\begin{CompactList}\small\item\em delete a node \item\end{CompactList}\item 
\hypertarget{classLlist_27c7c4149e117b782289c2d5bc965635}{
void \hyperlink{classLlist_27c7c4149e117b782289c2d5bc965635}{clear} ()}
\label{classLlist_27c7c4149e117b782289c2d5bc965635}

\begin{CompactList}\small\item\em re-initialize to empty list \item\end{CompactList}\item 
\hypertarget{classLlist_09061ffe39434195d24e86dc1c53a047}{
void \hyperlink{classLlist_09061ffe39434195d24e86dc1c53a047}{clear\_\-data} ()}
\label{classLlist_09061ffe39434195d24e86dc1c53a047}

\begin{CompactList}\small\item\em re-initialize to empty list \item\end{CompactList}\item 
\hypertarget{classLlist_f9d773bb9b844be5ff4a4bfb449cd0c9}{
\hyperlink{classLlist_f9d773bb9b844be5ff4a4bfb449cd0c9}{$\sim$Llist} ()}
\label{classLlist_f9d773bb9b844be5ff4a4bfb449cd0c9}

\begin{CompactList}\small\item\em deconstructor \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classLlist_15efb1e209596ba50b865a7809f72783}{
int \hyperlink{classLlist_15efb1e209596ba50b865a7809f72783}{len}}
\label{classLlist_15efb1e209596ba50b865a7809f72783}

\begin{CompactList}\small\item\em list length \item\end{CompactList}\item 
\hypertarget{classLlist_3c383a2a2ed152eb6cbf451c6ca24198}{
\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$ \hyperlink{classLlist_3c383a2a2ed152eb6cbf451c6ca24198}{node}}
\label{classLlist_3c383a2a2ed152eb6cbf451c6ca24198}

\begin{CompactList}\small\item\em the list head \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$class Ldata$>$ class Llist$<$ Ldata $>$}

Double linked list implementation.

----------------------------------------------------------------------- the template linked list ----------------------------------------------------------------------- This class implements a double linked list with generic data. The next pointer of the last node points to the first node and the prev pointer of the first node point to the node itself

The documentation for this class was generated from the following file:\begin{CompactItemize}
\item 
\hyperlink{dllist_8h}{dllist.h}\end{CompactItemize}

### 2010-06-17 src/latex/classLlistNode.tex
compressible branch

\hypertarget{classLlistNode}{
\section{LlistNode$<$ Ldata $>$ Class Template Reference}
\label{classLlistNode}\index{LlistNode@{LlistNode}}
}
A template node in the linked list.

{\tt \#include $<$dllist.h$>$}

Collaboration diagram for LlistNode$<$ Ldata $>$:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=142pt]{classLlistNode__coll__graph}
\end{center}
\end{figure}
\subsection*{Private Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classLlistNode_9e537419faf945c1be64fb8a994773f3}{LlistNode} ()
\begin{CompactList}\small\item\em constructors \item\end{CompactList}\item 
\hyperlink{classLlistNode_0257863d0b35acbdac9e297cadf90a04}{LlistNode} (Ldata $\ast$d, \hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$n)
\begin{CompactList}\small\item\em Creates a new node and inserts it before n. \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classLlistNode_f6147c63bdee0e7d19323ee2c8390755}{
Ldata $\ast$ \hyperlink{classLlistNode_f6147c63bdee0e7d19323ee2c8390755}{data}}
\label{classLlistNode_f6147c63bdee0e7d19323ee2c8390755}

\begin{CompactList}\small\item\em The data of this node. \item\end{CompactList}\item 
\hypertarget{classLlistNode_06cabe26723b810e801708ef9660f556}{
\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$ \hyperlink{classLlistNode_06cabe26723b810e801708ef9660f556}{next}}
\label{classLlistNode_06cabe26723b810e801708ef9660f556}

\begin{CompactList}\small\item\em The next and the previous nodes. \item\end{CompactList}\item 
\hypertarget{classLlistNode_445540ddfb7fe610b13ebe59312b8545}{
\hyperlink{classLlistNode}{LlistNode}$<$ Ldata $>$ $\ast$ \textbf{prev}}
\label{classLlistNode_445540ddfb7fe610b13ebe59312b8545}

\end{CompactItemize}
\subsection*{Friends}
\begin{CompactItemize}
\item 
\hypertarget{classLlistNode_59c8480ff68562e8cfa2bc1285d79b77}{
class \hyperlink{classLlistNode_59c8480ff68562e8cfa2bc1285d79b77}{Llist$<$ Ldata $>$}}
\label{classLlistNode_59c8480ff68562e8cfa2bc1285d79b77}

\begin{CompactList}\small\item\em the list class which manipulates the nodes \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
\subsubsection*{template$<$class Ldata$>$ class LlistNode$<$ Ldata $>$}

A template node in the linked list.

----------------------------------------------------------------------- a template node on the list ----------------------------------------------------------------------- This class represents a node of the generic double linked list \hyperlink{classLlist}{Llist}

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classLlistNode_9e537419faf945c1be64fb8a994773f3}{
\index{LlistNode@{LlistNode}!LlistNode@{LlistNode}}
\index{LlistNode@{LlistNode}!LlistNode@{LlistNode}}
\subsubsection[{LlistNode}]{\setlength{\rightskip}{0pt plus 5cm}template$<$class Ldata$>$ {\bf LlistNode}$<$ Ldata $>$::{\bf LlistNode} ()\hspace{0.3cm}{\tt  \mbox{[}inline, private\mbox{]}}}}
\label{classLlistNode_9e537419faf945c1be64fb8a994773f3}

constructors

An empty node, used for the head node \hypertarget{classLlistNode_0257863d0b35acbdac9e297cadf90a04}{
\index{LlistNode@{LlistNode}!LlistNode@{LlistNode}}
\index{LlistNode@{LlistNode}!LlistNode@{LlistNode}}
\subsubsection[{LlistNode}]{\setlength{\rightskip}{0pt plus 5cm}template$<$class Ldata$>$ {\bf LlistNode}$<$ Ldata $>$::{\bf LlistNode} (Ldata $\ast$ {\em d}, \/  {\bf LlistNode}$<$ Ldata $>$ $\ast$ {\em n})\hspace{0.3cm}{\tt  \mbox{[}inline, private\mbox{]}}}}
\label{classLlistNode_0257863d0b35acbdac9e297cadf90a04}

Creates a new node and inserts it before n.

\begin{Desc}
\item[Parameters:]
\begin{description}
\item[{\em d}]The data for the new node \item[{\em n}]The node before which the new node is to be inserted \end{description}
\end{Desc}

The documentation for this class was generated from the following file:\begin{CompactItemize}
\item 
\hyperlink{dllist_8h}{dllist.h}\end{CompactItemize}

### 2010-06-17 src/latex/classMLS.tex
compressible branch

\hypertarget{classMLS}{
\section{MLS Class Reference}
\label{classMLS}\index{MLS@{MLS}}
}
Moving Least Squares (\hyperlink{classMLS}{MLS}) class.

{\tt \#include $<$mls.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classMLS_69c81b7b81631bb306259deaf925cac3}{MLS} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
void \hyperlink{classMLS_70f00e273459e8fe02baa5a0c06d6f24}{MLSMapping} (Vec2d \&point, \hyperlink{classLlist}{Llist}$<$ \hyperlink{classParticle}{Particle} $>$ \&NNP\_\-list, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, int order)
\begin{CompactList}\small\item\em \hyperlink{classMLS}{MLS} Mapping to grid points. \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classMLS_8e02a81746ff6002015a7325b871282c}{
double $\ast$ \hyperlink{classMLS_8e02a81746ff6002015a7325b871282c}{phi}}
\label{classMLS_8e02a81746ff6002015a7325b871282c}

\begin{CompactList}\small\item\em shape function (pointer to) \item\end{CompactList}\item 
\hypertarget{classMLS_328f8049ce8b237bdc42f89a8b5dde07}{
Vec2d $\ast$ \hyperlink{classMLS_328f8049ce8b237bdc42f89a8b5dde07}{dphi}}
\label{classMLS_328f8049ce8b237bdc42f89a8b5dde07}

\begin{CompactList}\small\item\em derivatives (pointer to): have not been implemented! \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classMLS_7c7baa105805cd17714d35e351283bf7}{
void \hyperlink{classMLS_7c7baa105805cd17714d35e351283bf7}{MLS\_\-Solver} (int order)}
\label{classMLS_7c7baa105805cd17714d35e351283bf7}

\begin{CompactList}\small\item\em calculate the shape function and its derivative \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classMLS_2a4087a4494f44c3876144093a355b5f}{
int \hyperlink{classMLS_2a4087a4494f44c3876144093a355b5f}{N}}
\label{classMLS_2a4087a4494f44c3876144093a355b5f}

\begin{CompactList}\small\item\em numbers of points \item\end{CompactList}\item 
\hypertarget{classMLS_b610a9eb7b7df89432454f08ad98c9b0}{
int \hyperlink{classMLS_b610a9eb7b7df89432454f08ad98c9b0}{MLS\_\-MAX}}
\label{classMLS_b610a9eb7b7df89432454f08ad98c9b0}

\begin{CompactList}\small\item\em maximum number of reference points \item\end{CompactList}\item 
\hypertarget{classMLS_9499afde579c88688a27973bde8b4183}{
double \textbf{A} \mbox{[}3\mbox{]}\mbox{[}3\mbox{]}}
\label{classMLS_9499afde579c88688a27973bde8b4183}

\item 
\hypertarget{classMLS_ecdcd478c6683a0a865ef4db7385d77a}{
double $\ast$$\ast$ \hyperlink{classMLS_ecdcd478c6683a0a865ef4db7385d77a}{B}}
\label{classMLS_ecdcd478c6683a0a865ef4db7385d77a}

\begin{CompactList}\small\item\em weighted moment matrix (pointer to pointer) \item\end{CompactList}\item 
\hypertarget{classMLS_871ec34ef81919130fa552b982324a40}{
double \textbf{p} \mbox{[}3\mbox{]}}
\label{classMLS_871ec34ef81919130fa552b982324a40}

\item 
\hypertarget{classMLS_71607b0dededb152f2c75a767b84ffb8}{
double $\ast$$\ast$ \hyperlink{classMLS_71607b0dededb152f2c75a767b84ffb8}{pi}}
\label{classMLS_71607b0dededb152f2c75a767b84ffb8}

\begin{CompactList}\small\item\em ploynomial basis matrix (pointer to pointer) \item\end{CompactList}\item 
\hypertarget{classMLS_78d2e05f618cac0c7a8ca0ddef8c21c8}{
double $\ast$ \hyperlink{classMLS_78d2e05f618cac0c7a8ca0ddef8c21c8}{Wi}}
\label{classMLS_78d2e05f618cac0c7a8ca0ddef8c21c8}

\begin{CompactList}\small\item\em weights (pointer to) \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
Moving Least Squares (\hyperlink{classMLS}{MLS}) class.

Using Moving Least Squares Approximation 2D and linear aproximation based on (Liu GR, Mesh Free Methods-$>$Moving beyond the finite element method, CRC press, London, 2003, p79-87)

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classMLS_69c81b7b81631bb306259deaf925cac3}{
\index{MLS@{MLS}!MLS@{MLS}}
\index{MLS@{MLS}!MLS@{MLS}}
\subsubsection[{MLS}]{\setlength{\rightskip}{0pt plus 5cm}MLS::MLS ({\bf Initiation} \& {\em ini})}}
\label{classMLS_69c81b7b81631bb306259deaf925cac3}

constructor

\begin{itemize}
\item declares the weighted moment matrix and assigns it to corresponding pointer\end{itemize}

\begin{itemize}
\item declares the ploynomial basis matrix and assigns it to corresponding pointer\end{itemize}

\begin{itemize}
\item declares the weights and assigns it to corresponding pointer\end{itemize}

\begin{itemize}
\item declares shape function matrix and assigns it to corresponding pointer\end{itemize}

\begin{itemize}
\item declares derivatives matrix (HAS NOT BEEN IMPLEMENTED!!!) and assigns it to corresponding pointer \end{itemize}

\subsection{Member Function Documentation}
\hypertarget{classMLS_70f00e273459e8fe02baa5a0c06d6f24}{
\index{MLS@{MLS}!MLSMapping@{MLSMapping}}
\index{MLSMapping@{MLSMapping}!MLS@{MLS}}
\subsubsection[{MLSMapping}]{\setlength{\rightskip}{0pt plus 5cm}void MLS::MLSMapping (Vec2d \& {\em point}, \/  {\bf Llist}$<$ {\bf Particle} $>$ \& {\em NNP\_\-list}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  int {\em order})}}
\label{classMLS_70f00e273459e8fe02baa5a0c06d6f24}

\hyperlink{classMLS}{MLS} Mapping to grid points.

set up the enviroment for \hyperlink{classMLS}{MLS} calculation and run \hyperlink{classMLS}{MLS} solver

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=246pt]{classMLS_70f00e273459e8fe02baa5a0c06d6f24_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=284pt]{classMLS_70f00e273459e8fe02baa5a0c06d6f24_icgraph}
\end{center}
\end{figure}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{mls_8h}{mls.h}\item 
\hyperlink{mls_8cpp}{mls.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classMaterial.tex
compressible branch

\hypertarget{classMaterial}{
\section{Material Class Reference}
\label{classMaterial}\index{Material@{Material}}
}
\hyperlink{classMaterial}{Material}.

{\tt \#include $<$material.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classMaterial_137e987401b63eb7c6c27c3e38bc74b5}{
\hyperlink{classMaterial_137e987401b63eb7c6c27c3e38bc74b5}{Material} ()}
\label{classMaterial_137e987401b63eb7c6c27c3e38bc74b5}

\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
\hypertarget{classMaterial_8232db4572229d207a6438cf37b0c548}{
\hyperlink{classMaterial_8232db4572229d207a6438cf37b0c548}{Material} (\hyperlink{classInitiation}{Initiation} \&ini)}
\label{classMaterial_8232db4572229d207a6438cf37b0c548}

\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
\hyperlink{classMaterial_16e68aae88c0ecd98a88654e4648aa75}{Material} (char $\ast$\hyperlink{classMaterial_d7d10964971b23171efeac3c801371cf}{material\_\-name}, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
\hypertarget{classMaterial_7319953e9448604807d6e9301eea6986}{
void \hyperlink{classMaterial_7319953e9448604807d6e9301eea6986}{non\_\-dimensionalize} (\hyperlink{classInitiation}{Initiation} \&ini)}
\label{classMaterial_7319953e9448604807d6e9301eea6986}

\begin{CompactList}\small\item\em non-dimensionalize \item\end{CompactList}\item 
\hypertarget{classMaterial_1c79d7b457fd73587612d34c687f4286}{
void \hyperlink{classMaterial_1c79d7b457fd73587612d34c687f4286}{show\_\-properties} ()}
\label{classMaterial_1c79d7b457fd73587612d34c687f4286}

\begin{CompactList}\small\item\em show properties \item\end{CompactList}\item 
\hypertarget{classMaterial_fb5f537d2e8476debf2228ce8db4e8cf}{
void \hyperlink{classMaterial_fb5f537d2e8476debf2228ce8db4e8cf}{Get\_\-b0} (double sound)}
\label{classMaterial_fb5f537d2e8476debf2228ce8db4e8cf}

\begin{CompactList}\small\item\em obtain parameter b0 \item\end{CompactList}\item 
\hypertarget{classMaterial_be327be4e21bff9a227d0152c0db3f97}{
double \hyperlink{classMaterial_be327be4e21bff9a227d0152c0db3f97}{get\_\-p} (double rho)}
\label{classMaterial_be327be4e21bff9a227d0152c0db3f97}

\begin{CompactList}\small\item\em get pressure \item\end{CompactList}\item 
\hypertarget{classMaterial_6d61301ba97502c9acb2987afc0a8f5e}{
double \hyperlink{classMaterial_6d61301ba97502c9acb2987afc0a8f5e}{get\_\-rho} (double p)}
\label{classMaterial_6d61301ba97502c9acb2987afc0a8f5e}

\begin{CompactList}\small\item\em get rho from pressure \item\end{CompactList}\item 
\hypertarget{classMaterial_e3c05673e9e43b1d16340b95ebaf64b0}{
double \hyperlink{classMaterial_e3c05673e9e43b1d16340b95ebaf64b0}{get\_\-e} (double T)}
\label{classMaterial_e3c05673e9e43b1d16340b95ebaf64b0}

\begin{CompactList}\small\item\em get interal energy \item\end{CompactList}\item 
\hypertarget{classMaterial_8f02587e88f4e307bd7952f0d47a6737}{
double \hyperlink{classMaterial_8f02587e88f4e307bd7952f0d47a6737}{get\_\-T} (double e)}
\label{classMaterial_8f02587e88f4e307bd7952f0d47a6737}

\begin{CompactList}\small\item\em get temperature (function is defined nowhere) \item\end{CompactList}\item 
\hypertarget{classMaterial_ad32f778be3001bd9d359beb8c071106}{
double \hyperlink{classMaterial_ad32f778be3001bd9d359beb8c071106}{get\_\-Cs} (double p, double rho)}
\label{classMaterial_ad32f778be3001bd9d359beb8c071106}

\begin{CompactList}\small\item\em get sound speed \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classMaterial_d7d10964971b23171efeac3c801371cf}{
char \hyperlink{classMaterial_d7d10964971b23171efeac3c801371cf}{material\_\-name} \mbox{[}25\mbox{]}}
\label{classMaterial_d7d10964971b23171efeac3c801371cf}

\begin{CompactList}\small\item\em material name string \item\end{CompactList}\item 
\hypertarget{classMaterial_e773333eded6b2af56382fb5c405310f}{
int \hyperlink{classMaterial_e773333eded6b2af56382fb5c405310f}{number}}
\label{classMaterial_e773333eded6b2af56382fb5c405310f}

\begin{CompactList}\small\item\em the material NO. \item\end{CompactList}\item 
int \hyperlink{classMaterial_4eaab2babdbe6e6338cf094bfefb6b2e}{material\_\-type}
\begin{CompactList}\small\item\em material type \item\end{CompactList}\item 
\hypertarget{classMaterial_994575fad2f67950eb32dad7fbd63e5e}{
double \hyperlink{classMaterial_994575fad2f67950eb32dad7fbd63e5e}{cv}}
\label{classMaterial_994575fad2f67950eb32dad7fbd63e5e}

\begin{CompactList}\small\item\em heat capacity \item\end{CompactList}\item 
\hypertarget{classMaterial_62e8368c76c975790315b16d97558c26}{
double \hyperlink{classMaterial_62e8368c76c975790315b16d97558c26}{eta}}
\label{classMaterial_62e8368c76c975790315b16d97558c26}

\begin{CompactList}\small\item\em viscosity \item\end{CompactList}\item 
\hypertarget{classMaterial_a9a05f29e651c0ca772a50f5dbbfda2a}{
double \hyperlink{classMaterial_a9a05f29e651c0ca772a50f5dbbfda2a}{zeta}}
\label{classMaterial_a9a05f29e651c0ca772a50f5dbbfda2a}

\begin{CompactList}\small\item\em heat conduction rate \item\end{CompactList}\item 
\hypertarget{classMaterial_2444df069ed1e68eea1aead044e47847}{
double \hyperlink{classMaterial_2444df069ed1e68eea1aead044e47847}{kappa}}
\label{classMaterial_2444df069ed1e68eea1aead044e47847}

\begin{CompactList}\small\item\em ??? \item\end{CompactList}\item 
\hypertarget{classMaterial_fcbe6b9bc1cffe3105bdfbf593834e37}{
double \hyperlink{classMaterial_fcbe6b9bc1cffe3105bdfbf593834e37}{gamma}}
\label{classMaterial_fcbe6b9bc1cffe3105bdfbf593834e37}

\begin{CompactList}\small\item\em ??? \item\end{CompactList}\item 
\hypertarget{classMaterial_3da7d0218fcd6369d0bdbb7f91280664}{
double \hyperlink{classMaterial_3da7d0218fcd6369d0bdbb7f91280664}{nu}}
\label{classMaterial_3da7d0218fcd6369d0bdbb7f91280664}

\begin{CompactList}\small\item\em kinetice viscosity \item\end{CompactList}\item 
\hypertarget{classMaterial_9ead67ba9a2882dabf61b6a5e501c8a9}{
double \hyperlink{classMaterial_9ead67ba9a2882dabf61b6a5e501c8a9}{b0}}
\label{classMaterial_9ead67ba9a2882dabf61b6a5e501c8a9}

\begin{CompactList}\small\item\em reference pressure \item\end{CompactList}\item 
\hypertarget{classMaterial_80c74d0a402e1150466fb3d350c81e61}{
double \hyperlink{classMaterial_80c74d0a402e1150466fb3d350c81e61}{rho0}}
\label{classMaterial_80c74d0a402e1150466fb3d350c81e61}

\begin{CompactList}\small\item\em reference density \item\end{CompactList}\item 
\hypertarget{classMaterial_c6109a2fded5aa9c518b2d5271fc7d76}{
double \hyperlink{classMaterial_c6109a2fded5aa9c518b2d5271fc7d76}{a0}}
\label{classMaterial_c6109a2fded5aa9c518b2d5271fc7d76}

\begin{CompactList}\small\item\em reference {\bf sound speed??? was not commented} \item\end{CompactList}\end{CompactItemize}
\subsection*{Static Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classMaterial_d8ce370248325165c1c2505895cc9658}{
static int \hyperlink{classMaterial_d8ce370248325165c1c2505895cc9658}{number\_\-of\_\-materials} = 0}
\label{classMaterial_d8ce370248325165c1c2505895cc9658}

\begin{CompactList}\small\item\em total number of materials \item\end{CompactList}\item 
\hypertarget{classMaterial_623d1eecd8b673ffbfb5934df209c5a7}{
static double \hyperlink{classMaterial_623d1eecd8b673ffbfb5934df209c5a7}{smoothinglength} = 0.0}
\label{classMaterial_623d1eecd8b673ffbfb5934df209c5a7}

\begin{CompactList}\small\item\em smoothinglenth \item\end{CompactList}\item 
\hypertarget{classMaterial_31f7c32c96eae2d91b5988d1945e9c18}{
static double \textbf{delta} = 0.0}
\label{classMaterial_31f7c32c96eae2d91b5988d1945e9c18}

\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classMaterial}{Material}.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classMaterial_16e68aae88c0ecd98a88654e4648aa75}{
\index{Material@{Material}!Material@{Material}}
\index{Material@{Material}!Material@{Material}}
\subsubsection[{Material}]{\setlength{\rightskip}{0pt plus 5cm}Material::Material (char $\ast$ {\em material\_\-name}, \/  {\bf Initiation} \& {\em ini})}}
\label{classMaterial_16e68aae88c0ecd98a88654e4648aa75}

constructor

-check if inputfile exist

-read material properties from .cfg file

\begin{itemize}
\item output the property parameters to the screen \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=262pt]{classMaterial_16e68aae88c0ecd98a88654e4648aa75_cgraph}
\end{center}
\end{figure}

\subsection{Member Data Documentation}
\hypertarget{classMaterial_4eaab2babdbe6e6338cf094bfefb6b2e}{
\index{Material@{Material}!material\_\-type@{material\_\-type}}
\index{material\_\-type@{material\_\-type}!Material@{Material}}
\subsubsection[{material\_\-type}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Material::material\_\-type}}}
\label{classMaterial_4eaab2babdbe6e6338cf094bfefb6b2e}

material type

\begin{itemize}
\item 0: solid;\item 1: liquid;\item 2: gas \end{itemize}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{material_8h}{material.h}\item 
\hyperlink{material_8cpp}{material.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classOutput.tex
compressible branch

\hypertarget{classOutput}{
\section{Output Class Reference}
\label{classOutput}\index{Output@{Output}}
}
\hyperlink{classOutput}{Output} class.

{\tt \#include $<$output.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classOutput_2bd84635e13bedd1b8417fd39062a767}{Output} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
void \hyperlink{classOutput_f9e8b1a0aa456c01c69f7b3c7ee2649a}{OutputParticles} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classBoundary}{Boundary} \&boundary, double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em output particle positions respected different materials \item\end{CompactList}\item 
void \hyperlink{classOutput_2b41cacb61eecf10cbaca6bebb3e6316}{OutputStates} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classMLS}{MLS} \&mls, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em output material states on uniform grid \item\end{CompactList}\item 
void \hyperlink{classOutput_a96aad43762590fc7779d24050c0a151}{OutRestart} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em \hyperlink{classOutput}{Output} real particle data for restart the computation. \item\end{CompactList}\item 
\hypertarget{classOutput_16c4f8bae53fec90a812e5d479ae822d}{
void \hyperlink{classOutput_16c4f8bae53fec90a812e5d479ae822d}{CreatParticleMovie} ()}
\label{classOutput_16c4f8bae53fec90a812e5d479ae822d}

\begin{CompactList}\small\item\em create a head file for a movie of particle motion \item\end{CompactList}\item 
void \hyperlink{classOutput_3ff4c5c04d9f7e89eb3f36b299256f10}{WriteParticleMovie} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em write the data for a movie of particle motion (output real and wall particles) \item\end{CompactList}\item 
void \hyperlink{classOutput_13b9be49d851806b4ab40d60624095ad}{OutAverage} (\hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classMLS}{MLS} \&mls, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, double Time, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em avergaed values for Poiseuille and Couette flows (average is taken in horizontal direction) \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classOutput_b52dd1cb165a9270cc45610b0bc8cc43}{
char \hyperlink{classOutput_b52dd1cb165a9270cc45610b0bc8cc43}{Project\_\-name} \mbox{[}25\mbox{]}}
\label{classOutput_b52dd1cb165a9270cc45610b0bc8cc43}

\begin{CompactList}\small\item\em the project name \item\end{CompactList}\item 
\hypertarget{classOutput_c2696f9c30e4840eab5b7ab3901bbf6b}{
int \textbf{number\_\-of\_\-materials}}
\label{classOutput_c2696f9c30e4840eab5b7ab3901bbf6b}

\item 
\hypertarget{classOutput_b3283271fd00c93268f9af19879a2fc6}{
double \hyperlink{classOutput_b3283271fd00c93268f9af19879a2fc6}{delta}}
\label{classOutput_b3283271fd00c93268f9af19879a2fc6}

\begin{CompactList}\small\item\em the inital particle distance \item\end{CompactList}\item 
\hypertarget{classOutput_8222be56a91be9ffd805ae2f87d68ec5}{
int \hyperlink{classOutput_8222be56a91be9ffd805ae2f87d68ec5}{x\_\-cells}}
\label{classOutput_8222be56a91be9ffd805ae2f87d68ec5}

\begin{CompactList}\small\item\em cells matrix for real particles \item\end{CompactList}\item 
\hypertarget{classOutput_d9bb2a18d020f12343b75eb5844fa79b}{
int \textbf{y\_\-cells}}
\label{classOutput_d9bb2a18d020f12343b75eb5844fa79b}

\item 
\hypertarget{classOutput_b2ba6673b6ca7b7ad7d952015c6dbfb7}{
int \hyperlink{classOutput_b2ba6673b6ca7b7ad7d952015c6dbfb7}{hdelta}}
\label{classOutput_b2ba6673b6ca7b7ad7d952015c6dbfb7}

\begin{CompactList}\small\item\em the ratio between smoothing length and inital particle distance \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classOutput}{Output} class.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classOutput_2bd84635e13bedd1b8417fd39062a767}{
\index{Output@{Output}!Output@{Output}}
\index{Output@{Output}!Output@{Output}}
\subsubsection[{Output}]{\setlength{\rightskip}{0pt plus 5cm}Output::Output ({\bf Initiation} \& {\em ini})}}
\label{classOutput_2bd84635e13bedd1b8417fd39062a767}

constructor

copy boundary properties from initiation class

\subsection{Member Function Documentation}
\hypertarget{classOutput_13b9be49d851806b4ab40d60624095ad}{
\index{Output@{Output}!OutAverage@{OutAverage}}
\index{OutAverage@{OutAverage}!Output@{Output}}
\subsubsection[{OutAverage}]{\setlength{\rightskip}{0pt plus 5cm}void Output::OutAverage ({\bf ParticleManager} \& {\em particles}, \/  {\bf MLS} \& {\em mls}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classOutput_13b9be49d851806b4ab40d60624095ad}

avergaed values for Poiseuille and Couette flows (average is taken in horizontal direction)

\begin{itemize}
\item produce output file name\end{itemize}

\begin{itemize}
\item defining header for tecplot(plot software)\end{itemize}

\begin{itemize}
\item loop the grid points \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=333pt]{classOutput_13b9be49d851806b4ab40d60624095ad_cgraph}
\end{center}
\end{figure}
\hypertarget{classOutput_f9e8b1a0aa456c01c69f7b3c7ee2649a}{
\index{Output@{Output}!OutputParticles@{OutputParticles}}
\index{OutputParticles@{OutputParticles}!Output@{Output}}
\subsubsection[{OutputParticles}]{\setlength{\rightskip}{0pt plus 5cm}void Output::OutputParticles ({\bf Hydrodynamics} \& {\em hydro}, \/  {\bf Boundary} \& {\em boundary}, \/  double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classOutput_f9e8b1a0aa456c01c69f7b3c7ee2649a}

output particle positions respected different materials

\begin{itemize}
\item produce output file name

\item defining header for tecplot(plot software)

\item output real and soild particles

\begin{itemize}
\item iterate the real partilce list

\item iterate the boundary partilce list \end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=157pt]{classOutput_f9e8b1a0aa456c01c69f7b3c7ee2649a_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=119pt]{classOutput_f9e8b1a0aa456c01c69f7b3c7ee2649a_icgraph}
\end{center}
\end{figure}
\hypertarget{classOutput_2b41cacb61eecf10cbaca6bebb3e6316}{
\index{Output@{Output}!OutputStates@{OutputStates}}
\index{OutputStates@{OutputStates}!Output@{Output}}
\subsubsection[{OutputStates}]{\setlength{\rightskip}{0pt plus 5cm}void Output::OutputStates ({\bf ParticleManager} \& {\em particles}, \/  {\bf MLS} \& {\em mls}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classOutput_2b41cacb61eecf10cbaca6bebb3e6316}

output material states on uniform grid

\begin{itemize}
\item produce output file name\end{itemize}

\begin{itemize}
\item defining header for tecplot(plot software)\end{itemize}

\begin{itemize}
\item loop the grid points \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=337pt]{classOutput_2b41cacb61eecf10cbaca6bebb3e6316_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=114pt]{classOutput_2b41cacb61eecf10cbaca6bebb3e6316_icgraph}
\end{center}
\end{figure}
\hypertarget{classOutput_a96aad43762590fc7779d24050c0a151}{
\index{Output@{Output}!OutRestart@{OutRestart}}
\index{OutRestart@{OutRestart}!Output@{Output}}
\subsubsection[{OutRestart}]{\setlength{\rightskip}{0pt plus 5cm}void Output::OutRestart ({\bf Hydrodynamics} \& {\em hydro}, \/  double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classOutput_a96aad43762590fc7779d24050c0a151}

\hyperlink{classOutput}{Output} real particle data for restart the computation.

\begin{itemize}
\item output non-dimensional data\end{itemize}

\begin{itemize}
\item out reinitiation Time\end{itemize}

\begin{itemize}
\item output real particles (by iterating the particle list) \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=126pt]{classOutput_a96aad43762590fc7779d24050c0a151_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=109pt]{classOutput_a96aad43762590fc7779d24050c0a151_icgraph}
\end{center}
\end{figure}
\hypertarget{classOutput_3ff4c5c04d9f7e89eb3f36b299256f10}{
\index{Output@{Output}!WriteParticleMovie@{WriteParticleMovie}}
\index{WriteParticleMovie@{WriteParticleMovie}!Output@{Output}}
\subsubsection[{WriteParticleMovie}]{\setlength{\rightskip}{0pt plus 5cm}void Output::WriteParticleMovie ({\bf Hydrodynamics} \& {\em hydro}, \/  double {\em Time}, \/  {\bf Initiation} \& {\em ini})}}
\label{classOutput_3ff4c5c04d9f7e89eb3f36b299256f10}

write the data for a movie of particle motion (output real and wall particles)

\begin{itemize}
\item produce output file name\end{itemize}

\begin{itemize}
\item iterate the partilce list \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=160pt]{classOutput_3ff4c5c04d9f7e89eb3f36b299256f10_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=125pt]{classOutput_3ff4c5c04d9f7e89eb3f36b299256f10_icgraph}
\end{center}
\end{figure}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{output_8h}{output.h}\item 
\hyperlink{output_8cpp}{output.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classParticle.tex
compressible branch

\hypertarget{classParticle}{
\section{Particle Class Reference}
\label{classParticle}\index{Particle@{Particle}}
}
\hyperlink{classParticle}{Particle} class.

{\tt \#include $<$particle.h$>$}

Collaboration diagram for Particle:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=135pt]{classParticle__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classParticle_91ea71cca6b4c538391fc881bc8da59a}{Particle} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em a particle constructur for empty particles \item\end{CompactList}\item 
\hyperlink{classParticle_5cf658952a598524638d789db59b4249}{Particle} (Vec2d position, Vec2d velocity, double density, double pressure, double temperature, \hyperlink{classMaterial}{Material} \&material)
\begin{CompactList}\small\item\em construct a real particle NOTE the particle mass and volume will be specified in initiation::VolumeMass(w) \item\end{CompactList}\item 
\hyperlink{classParticle_141d53920868e51381f83b6a5d5973d2}{Particle} (double x, double y, double u, double v, double distance, double normal\_\-x, double normal\_\-y, \hyperlink{classMaterial}{Material} \&material)
\begin{CompactList}\small\item\em construct a wall particle \item\end{CompactList}\item 
\hyperlink{classParticle_0c88a1f547bae9946678288ff371acb2}{Particle} (\hyperlink{classParticle}{Particle} \&RealParticle)
\begin{CompactList}\small\item\em ghost particle creator \item\end{CompactList}\item 
\hyperlink{classParticle_4f3ed6cdbd582d85e39622038205f0e1}{Particle} (\hyperlink{classParticle}{Particle} \&RealParticle, \hyperlink{classMaterial}{Material} \&material)
\begin{CompactList}\small\item\em Mirror image particle creator. \item\end{CompactList}\item 
\hyperlink{classParticle_d030d0fe7b88cf81744b127c99244ff4}{$\sim$Particle} ()
\begin{CompactList}\small\item\em deconstructor particle \item\end{CompactList}\item 
void \hyperlink{classParticle_d202d28edab1253eb51be75ea0cbdbfd}{StatesCopier} (\hyperlink{classParticle}{Particle} \&RealParticle, int type)
\begin{CompactList}\small\item\em particle states copier for boundary particles \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classParticle_5dd341dff09126775ee3f94b9386345f}{
int \hyperlink{classParticle_5dd341dff09126775ee3f94b9386345f}{cell\_\-i}}
\label{classParticle_5dd341dff09126775ee3f94b9386345f}

\begin{CompactList}\small\item\em i-position in cells \item\end{CompactList}\item 
\hypertarget{classParticle_eea0c9b28b244318e2f0b8d4bb2a47b3}{
int \hyperlink{classParticle_eea0c9b28b244318e2f0b8d4bb2a47b3}{cell\_\-j}}
\label{classParticle_eea0c9b28b244318e2f0b8d4bb2a47b3}

\begin{CompactList}\small\item\em j-position in cells \item\end{CompactList}\item 
\hypertarget{classParticle_26fec1228a429d36a7e7fbbd5da13cc5}{
\hyperlink{classMaterial}{Material} $\ast$ \hyperlink{classParticle_26fec1228a429d36a7e7fbbd5da13cc5}{mtl}}
\label{classParticle_26fec1228a429d36a7e7fbbd5da13cc5}

\begin{CompactList}\small\item\em pointer to the material \item\end{CompactList}\item 
\hypertarget{classParticle_6baadd44a1051798d0e248757c450234}{
\hyperlink{classParticle}{Particle} $\ast$ \hyperlink{classParticle_6baadd44a1051798d0e248757c450234}{rl\_\-prtl}}
\label{classParticle_6baadd44a1051798d0e248757c450234}

\begin{CompactList}\small\item\em pointer to a real particle \item\end{CompactList}\item 
\hypertarget{classParticle_eef75ee5a8289086612542c3c1619e0e}{
Vec2d \hyperlink{classParticle_eef75ee5a8289086612542c3c1619e0e}{R}}
\label{classParticle_eef75ee5a8289086612542c3c1619e0e}

\begin{CompactList}\small\item\em position \item\end{CompactList}\item 
\hypertarget{classParticle_3fbc48c56ba3d5d7c9c1fd848f9f8dfa}{
Vec2d \hyperlink{classParticle_3fbc48c56ba3d5d7c9c1fd848f9f8dfa}{P}}
\label{classParticle_3fbc48c56ba3d5d7c9c1fd848f9f8dfa}

\begin{CompactList}\small\item\em momentum \item\end{CompactList}\item 
\hypertarget{classParticle_f931f3625b557b51cca6b199dc1f3e95}{
Vec2d \hyperlink{classParticle_f931f3625b557b51cca6b199dc1f3e95}{U}}
\label{classParticle_f931f3625b557b51cca6b199dc1f3e95}

\begin{CompactList}\small\item\em velocityy \item\end{CompactList}\item 
\hypertarget{classParticle_4a4fc6e753e74eac9d7725c431e94205}{
double \hyperlink{classParticle_4a4fc6e753e74eac9d7725c431e94205}{rho}}
\label{classParticle_4a4fc6e753e74eac9d7725c431e94205}

\begin{CompactList}\small\item\em density \item\end{CompactList}\item 
\hypertarget{classParticle_9ef797ea4feb5eed21755d5d8e99508e}{
double \hyperlink{classParticle_9ef797ea4feb5eed21755d5d8e99508e}{p}}
\label{classParticle_9ef797ea4feb5eed21755d5d8e99508e}

\begin{CompactList}\small\item\em pressure \item\end{CompactList}\item 
\hypertarget{classParticle_b07ac93118d84bc548e0dc837a5c31f5}{
double \hyperlink{classParticle_b07ac93118d84bc548e0dc837a5c31f5}{T}}
\label{classParticle_b07ac93118d84bc548e0dc837a5c31f5}

\begin{CompactList}\small\item\em Temperature. \item\end{CompactList}\item 
\hypertarget{classParticle_04aaaa78c93a52103d092923287d79ae}{
double \hyperlink{classParticle_04aaaa78c93a52103d092923287d79ae}{Cs}}
\label{classParticle_04aaaa78c93a52103d092923287d79ae}

\begin{CompactList}\small\item\em do not know what this is {\bf !!!Question!!!} \item\end{CompactList}\item 
\hypertarget{classParticle_c9af22c35c1bf1c33ae8145b0ec3a631}{
double \hyperlink{classParticle_c9af22c35c1bf1c33ae8145b0ec3a631}{rho\_\-I}}
\label{classParticle_c9af22c35c1bf1c33ae8145b0ec3a631}

\begin{CompactList}\small\item\em intermediate value for density (needed for integration) \item\end{CompactList}\item 
\hypertarget{classParticle_4a7dfc727da093aeb484b9e3a699f3b0}{
double \textbf{rho\_\-n}}
\label{classParticle_4a7dfc727da093aeb484b9e3a699f3b0}

\item 
\hypertarget{classParticle_edcc7e1bc53b0e2b1a4a07c9a1b47563}{
double \hyperlink{classParticle_edcc7e1bc53b0e2b1a4a07c9a1b47563}{m}}
\label{classParticle_edcc7e1bc53b0e2b1a4a07c9a1b47563}

\begin{CompactList}\small\item\em mass \item\end{CompactList}\item 
\hypertarget{classParticle_941e43f9d9b080269a58bc98847ea7ab}{
double \hyperlink{classParticle_941e43f9d9b080269a58bc98847ea7ab}{V}}
\label{classParticle_941e43f9d9b080269a58bc98847ea7ab}

\begin{CompactList}\small\item\em volume \item\end{CompactList}\item 
\hypertarget{classParticle_00a04c82ccc76272a9b4ae779c7583e1}{
double \hyperlink{classParticle_00a04c82ccc76272a9b4ae779c7583e1}{e}}
\label{classParticle_00a04c82ccc76272a9b4ae779c7583e1}

\begin{CompactList}\small\item\em internal energy \item\end{CompactList}\item 
\hypertarget{classParticle_ad1dfedaf6bb2f6ccd639d0a38322cca}{
Vec2d \hyperlink{classParticle_ad1dfedaf6bb2f6ccd639d0a38322cca}{R\_\-I}}
\label{classParticle_ad1dfedaf6bb2f6ccd639d0a38322cca}

\begin{CompactList}\small\item\em intermediate position \item\end{CompactList}\item 
\hypertarget{classParticle_4b83fe9f80ff112a9ef19ca0fe22d07d}{
Vec2d \hyperlink{classParticle_4b83fe9f80ff112a9ef19ca0fe22d07d}{P\_\-I}}
\label{classParticle_4b83fe9f80ff112a9ef19ca0fe22d07d}

\begin{CompactList}\small\item\em intermediate momentim \item\end{CompactList}\item 
\hypertarget{classParticle_346aeb99054a013436d225c9df535002}{
Vec2d \hyperlink{classParticle_346aeb99054a013436d225c9df535002}{U\_\-I}}
\label{classParticle_346aeb99054a013436d225c9df535002}

\begin{CompactList}\small\item\em intermediate velocity \item\end{CompactList}\item 
\hypertarget{classParticle_d5c24e7c813bcd558aa40acb8fd84de7}{
Vec2d \hyperlink{classParticle_d5c24e7c813bcd558aa40acb8fd84de7}{P\_\-n}}
\label{classParticle_d5c24e7c813bcd558aa40acb8fd84de7}

\begin{CompactList}\small\item\em do not knwo what this is n=?conservative???{\bf !!!Question!!!} \item\end{CompactList}\item 
\hypertarget{classParticle_9a4a7631b4f39ea1dbfdf9b426ad2e1a}{
Vec2d \hyperlink{classParticle_9a4a7631b4f39ea1dbfdf9b426ad2e1a}{U\_\-n}}
\label{classParticle_9a4a7631b4f39ea1dbfdf9b426ad2e1a}

\begin{CompactList}\small\item\em do not knwo what this is n=?conservative???{\bf !!!Question!!!} \item\end{CompactList}\item 
\hypertarget{classParticle_2a993ea8900f2f84595599fb18224bde}{
double \hyperlink{classParticle_2a993ea8900f2f84595599fb18224bde}{e\_\-I}}
\label{classParticle_2a993ea8900f2f84595599fb18224bde}

\begin{CompactList}\small\item\em intermediate value of internal enegry (used in the integrator) \item\end{CompactList}\item 
\hypertarget{classParticle_79b451e92d70e0b029820c528a346499}{
double \textbf{e\_\-n}}
\label{classParticle_79b451e92d70e0b029820c528a346499}

\item 
\hypertarget{classParticle_7a60f30c44da2e6cfb2c17d3199d65f2}{
Vec2d \hyperlink{classParticle_7a60f30c44da2e6cfb2c17d3199d65f2}{ShearRate\_\-x}}
\label{classParticle_7a60f30c44da2e6cfb2c17d3199d65f2}

\begin{CompactList}\small\item\em intermediate volume, internal energy used in integrator \item\end{CompactList}\item 
\hypertarget{classParticle_02f0b4442dc26c724d3bca383f542683}{
Vec2d \textbf{ShearRate\_\-y}}
\label{classParticle_02f0b4442dc26c724d3bca383f542683}

\item 
\hypertarget{classParticle_2d0c5ad7aa3ed6f2a18822020cfc5fa4}{
double \textbf{eta}}
\label{classParticle_2d0c5ad7aa3ed6f2a18822020cfc5fa4}

\item 
\hypertarget{classParticle_5d070e879a5fd02b62f822c5a21c1747}{
double \textbf{zeta}}
\label{classParticle_5d070e879a5fd02b62f822c5a21c1747}

\item 
\hypertarget{classParticle_acc4d2cb20aafcb510b648e8f0ccadac}{
double $\ast$$\ast$ \hyperlink{classParticle_acc4d2cb20aafcb510b648e8f0ccadac}{phi}}
\label{classParticle_acc4d2cb20aafcb510b648e8f0ccadac}

\begin{CompactList}\small\item\em \hyperlink{particle_8h_source}{particle.h}(line 69-74) viscosity of each particle{\bf !!!Question!!!} \item\end{CompactList}\item 
Vec2d \hyperlink{classParticle_0461d98d796ba0e2dc72edb5b2fb093a}{del\_\-phi}
\item 
\hypertarget{classParticle_5b6d8725dbd06dfeb73692f6a91776db}{
double $\ast$$\ast$ \textbf{lap\_\-phi}}
\label{classParticle_5b6d8725dbd06dfeb73692f6a91776db}

\item 
\hypertarget{classParticle_b8ed5fa9fede49e38ef74e955e1179ee}{
double \hyperlink{classParticle_b8ed5fa9fede49e38ef74e955e1179ee}{drhodt}}
\label{classParticle_b8ed5fa9fede49e38ef74e955e1179ee}

\begin{CompactList}\small\item\em density change rate for real particles \item\end{CompactList}\item 
\hypertarget{classParticle_114e4e1b158cff18b44a881981cba71a}{
double \hyperlink{classParticle_114e4e1b158cff18b44a881981cba71a}{dedt}}
\label{classParticle_114e4e1b158cff18b44a881981cba71a}

\begin{CompactList}\small\item\em internal energy change rate for real particles \item\end{CompactList}\item 
\hypertarget{classParticle_b3039ea91cdab042862b80f8ecd97c3e}{
Vec2d \hyperlink{classParticle_b3039ea91cdab042862b80f8ecd97c3e}{dUdt}}
\label{classParticle_b3039ea91cdab042862b80f8ecd97c3e}

\begin{CompactList}\small\item\em acceleration change for real particles {\bf or is it the other wa round} \item\end{CompactList}\item 
\hypertarget{classParticle_da30e275fe7bb7855bf968ed7bd3adbf}{
Vec2d \hyperlink{classParticle_da30e275fe7bb7855bf968ed7bd3adbf}{\_\-dU}}
\label{classParticle_da30e275fe7bb7855bf968ed7bd3adbf}

\begin{CompactList}\small\item\em random velocity change for real particles {\bf or is it the other wa round} \item\end{CompactList}\item 
int \hyperlink{classParticle_873301ecb921ab815ef7b693033e8c88}{bd}
\begin{CompactList}\small\item\em boundary particle or not \item\end{CompactList}\item 
int \hyperlink{classParticle_73728c6443f6ade479e960ef9d070221}{bd\_\-type}
\item 
long \hyperlink{classParticle_1072ca8f2323417f321cc333d37ff1a3}{ID}
\begin{CompactList}\small\item\em ID number. \item\end{CompactList}\item 
\hypertarget{classParticle_1ef8cc0c391f174490a54ba1bb4d712f}{
double \hyperlink{classParticle_1ef8cc0c391f174490a54ba1bb4d712f}{bd\_\-dst}}
\label{classParticle_1ef8cc0c391f174490a54ba1bb4d712f}

\begin{CompactList}\small\item\em for wall boundary particles \item\end{CompactList}\item 
\hypertarget{classParticle_8397ab51179bf583b6eded2f3d2004a9}{
Vec2d \hyperlink{classParticle_8397ab51179bf583b6eded2f3d2004a9}{nrml}}
\label{classParticle_8397ab51179bf583b6eded2f3d2004a9}

\begin{CompactList}\small\item\em for wall boundary particles \item\end{CompactList}\end{CompactItemize}
\subsection*{Static Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classParticle_c8d46625d0bcafc38564f213b9668580}{
static long \hyperlink{classParticle_c8d46625d0bcafc38564f213b9668580}{ID\_\-max} = 0}
\label{classParticle_c8d46625d0bcafc38564f213b9668580}

\begin{CompactList}\small\item\em maximum ID number for non-ghost particles (real or wall particles) in the simulation \item\end{CompactList}\end{CompactItemize}
\subsection*{Static Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classParticle_cbf60684ef8e09fb20fcd2e9aacf723f}{
static int \textbf{number\_\-of\_\-materials} = 0}
\label{classParticle_cbf60684ef8e09fb20fcd2e9aacf723f}

\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classParticle}{Particle} class.

note: reference a particle by pointer or adress never reference a particle directly!

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classParticle_91ea71cca6b4c538391fc881bc8da59a}{
\index{Particle@{Particle}!Particle@{Particle}}
\index{Particle@{Particle}!Particle@{Particle}}
\subsubsection[{Particle}]{\setlength{\rightskip}{0pt plus 5cm}Particle::Particle ({\bf Initiation} \& {\em ini})}}
\label{classParticle_91ea71cca6b4c538391fc881bc8da59a}

a particle constructur for empty particles

\begin{itemize}
\item copy properties from initiation\end{itemize}

\begin{itemize}
\item set up phase field \end{itemize}
\hypertarget{classParticle_5cf658952a598524638d789db59b4249}{
\index{Particle@{Particle}!Particle@{Particle}}
\index{Particle@{Particle}!Particle@{Particle}}
\subsubsection[{Particle}]{\setlength{\rightskip}{0pt plus 5cm}Particle::Particle (Vec2d {\em position}, \/  Vec2d {\em velocity}, \/  double {\em density}, \/  double {\em pressure}, \/  double {\em temperature}, \/  {\bf Material} \& {\em material})}}
\label{classParticle_5cf658952a598524638d789db59b4249}

construct a real particle NOTE the particle mass and volume will be specified in initiation::VolumeMass(w)

\begin{itemize}
\item increase the total particle number\end{itemize}

\begin{itemize}
\item give a new ID number\end{itemize}

\begin{itemize}
\item point to the material properties\end{itemize}

\begin{itemize}
\item set viscosity\end{itemize}

\begin{itemize}
\item set particle position\end{itemize}

\begin{itemize}
\item set states\end{itemize}

\begin{itemize}
\item set conservative values and their intermediate values\end{itemize}

\begin{itemize}
\item set up phase field \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=128pt]{classParticle_5cf658952a598524638d789db59b4249_cgraph}
\end{center}
\end{figure}
\hypertarget{classParticle_141d53920868e51381f83b6a5d5973d2}{
\index{Particle@{Particle}!Particle@{Particle}}
\index{Particle@{Particle}!Particle@{Particle}}
\subsubsection[{Particle}]{\setlength{\rightskip}{0pt plus 5cm}Particle::Particle (double {\em x}, \/  double {\em y}, \/  double {\em u}, \/  double {\em v}, \/  double {\em distance}, \/  double {\em normal\_\-x}, \/  double {\em normal\_\-y}, \/  {\bf Material} \& {\em material})}}
\label{classParticle_141d53920868e51381f83b6a5d5973d2}

construct a wall particle

\begin{itemize}
\item give a new ID number\end{itemize}

\begin{itemize}
\item point to the material properties\end{itemize}

\begin{itemize}
\item set particle position\end{itemize}

\begin{itemize}
\item set states\end{itemize}

\begin{itemize}
\item set distance and normal directions to boundary\end{itemize}

\begin{itemize}
\item set states value to avoid error \end{itemize}
\hypertarget{classParticle_0c88a1f547bae9946678288ff371acb2}{
\index{Particle@{Particle}!Particle@{Particle}}
\index{Particle@{Particle}!Particle@{Particle}}
\subsubsection[{Particle}]{\setlength{\rightskip}{0pt plus 5cm}Particle::Particle ({\bf Particle} \& {\em RealParticle})}}
\label{classParticle_0c88a1f547bae9946678288ff371acb2}

ghost particle creator

\begin{itemize}
\item give a new ID number\end{itemize}

\begin{itemize}
\item point to its real particle\end{itemize}

\begin{itemize}
\item point to the material properties\end{itemize}

\begin{itemize}
\item set viscosity\end{itemize}

\begin{itemize}
\item set states\end{itemize}

\begin{itemize}
\item set conservative values and their intermediate values\end{itemize}

\begin{itemize}
\item set up phase field \end{itemize}
\hypertarget{classParticle_4f3ed6cdbd582d85e39622038205f0e1}{
\index{Particle@{Particle}!Particle@{Particle}}
\index{Particle@{Particle}!Particle@{Particle}}
\subsubsection[{Particle}]{\setlength{\rightskip}{0pt plus 5cm}Particle::Particle ({\bf Particle} \& {\em RealParticle}, \/  {\bf Material} \& {\em material})}}
\label{classParticle_4f3ed6cdbd582d85e39622038205f0e1}

Mirror image particle creator.

\begin{itemize}
\item give a new ID number\end{itemize}

\begin{itemize}
\item point to its real particle\end{itemize}

\begin{itemize}
\item point to the material properties\end{itemize}

\begin{itemize}
\item set viscosity\end{itemize}

\begin{itemize}
\item set states\end{itemize}

\begin{itemize}
\item set conservative values and their intermediate values\end{itemize}

\begin{itemize}
\item set up phase field \end{itemize}
\hypertarget{classParticle_d030d0fe7b88cf81744b127c99244ff4}{
\index{Particle@{Particle}!$\sim$Particle@{$\sim$Particle}}
\index{$\sim$Particle@{$\sim$Particle}!Particle@{Particle}}
\subsubsection[{$\sim$Particle}]{\setlength{\rightskip}{0pt plus 5cm}Particle::$\sim$Particle ()}}
\label{classParticle_d030d0fe7b88cf81744b127c99244ff4}

deconstructor particle

\begin{itemize}
\item delete phase field\end{itemize}

\begin{itemize}
\item delete pahse field gradient matrix \end{itemize}

\subsection{Member Function Documentation}
\hypertarget{classParticle_d202d28edab1253eb51be75ea0cbdbfd}{
\index{Particle@{Particle}!StatesCopier@{StatesCopier}}
\index{StatesCopier@{StatesCopier}!Particle@{Particle}}
\subsubsection[{StatesCopier}]{\setlength{\rightskip}{0pt plus 5cm}void Particle::StatesCopier ({\bf Particle} \& {\em RealParticle}, \/  int {\em type})}}
\label{classParticle_d202d28edab1253eb51be75ea0cbdbfd}

particle states copier for boundary particles

\begin{itemize}
\item copy states\end{itemize}

\begin{itemize}
\item set phase field (depending on boundary type: periodic/wall) \end{itemize}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=312pt]{classParticle_d202d28edab1253eb51be75ea0cbdbfd_icgraph}
\end{center}
\end{figure}

\subsection{Member Data Documentation}
\hypertarget{classParticle_873301ecb921ab815ef7b693033e8c88}{
\index{Particle@{Particle}!bd@{bd}}
\index{bd@{bd}!Particle@{Particle}}
\subsubsection[{bd}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Particle::bd}}}
\label{classParticle_873301ecb921ab815ef7b693033e8c88}

boundary particle or not

\begin{itemize}
\item 0: inside the boundary\item 1: on the boundary \end{itemize}
\hypertarget{classParticle_73728c6443f6ade479e960ef9d070221}{
\index{Particle@{Particle}!bd\_\-type@{bd\_\-type}}
\index{bd\_\-type@{bd\_\-type}!Particle@{Particle}}
\subsubsection[{bd\_\-type}]{\setlength{\rightskip}{0pt plus 5cm}int {\bf Particle::bd\_\-type}}}
\label{classParticle_73728c6443f6ade479e960ef9d070221}

boundary type if bd = 1\begin{itemize}
\item 0 wall particle with zero or constant velocity but never move its position\item 1 ghost particle for perodic boundary \end{itemize}
\hypertarget{classParticle_0461d98d796ba0e2dc72edb5b2fb093a}{
\index{Particle@{Particle}!del\_\-phi@{del\_\-phi}}
\index{del\_\-phi@{del\_\-phi}!Particle@{Particle}}
\subsubsection[{del\_\-phi}]{\setlength{\rightskip}{0pt plus 5cm}Vec2d {\bf Particle::del\_\-phi}}}
\label{classParticle_0461d98d796ba0e2dc72edb5b2fb093a}

phase field matrix{\bf !!!Question!!!} first as phase field gradient matrix {\bf !!!Question!!!} then the independent values (\mbox{[}0\mbox{]}\mbox{[}0\mbox{]} and \mbox{[}0\mbox{]}\mbox{[}1\mbox{]}) of suface stress matrix {\bf !!!Question!!!} \hypertarget{classParticle_1072ca8f2323417f321cc333d37ff1a3}{
\index{Particle@{Particle}!ID@{ID}}
\index{ID@{ID}!Particle@{Particle}}
\subsubsection[{ID}]{\setlength{\rightskip}{0pt plus 5cm}long {\bf Particle::ID}}}
\label{classParticle_1072ca8f2323417f321cc333d37ff1a3}

ID number.

\begin{itemize}
\item a real particle has a unique positive ID\item a wall particle has zero ID\item an ghost particle (for perodic boundary condition) has a negtive ID of its corresponding real particle \end{itemize}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
particle.h\item 
\hyperlink{particle_8cpp}{particle.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classParticleManager.tex
compressible branch

\hypertarget{classParticleManager}{
\section{ParticleManager Class Reference}
\label{classParticleManager}\index{ParticleManager@{ParticleManager}}
}
\hyperlink{classParticle}{Particle} manager class.

{\tt \#include $<$particlemanager.h$>$}

Collaboration diagram for ParticleManager:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=189pt]{classParticleManager__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classParticleManager_36f2371b06ef7bd96fc1e0cb1fcebd66}{
\hyperlink{classParticleManager_36f2371b06ef7bd96fc1e0cb1fcebd66}{ParticleManager} ()}
\label{classParticleManager_36f2371b06ef7bd96fc1e0cb1fcebd66}

\begin{CompactList}\small\item\em \char`\"{}empty\char`\"{} constructor \item\end{CompactList}\item 
\hyperlink{classParticleManager_11a8f14c20f087713172d230de468166}{ParticleManager} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
\hypertarget{classParticleManager_7e835509b041635805a127cbedc194bd}{
\textbf{ParticleManager} (double cell\_\-size, int x\_\-cells, int y\_\-cells)}
\label{classParticleManager_7e835509b041635805a127cbedc194bd}

\item 
void \hyperlink{classParticleManager_6ee12c3925f371782800a50b17ac0941}{BiuldRealParticles} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em buid the initial particles and the linked lists \item\end{CompactList}\item 
\hypertarget{classParticleManager_04ed35d52cf918b98006a0def713dc89}{
void \textbf{BiuldRealParticles} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro)}
\label{classParticleManager_04ed35d52cf918b98006a0def713dc89}

\item 
void \hyperlink{classParticleManager_740244439672f753735abc5a6a7cc3bc}{UpdateCellLinkedLists} ()
\begin{CompactList}\small\item\em update the cell linked lists for real particles \item\end{CompactList}\item 
void \hyperlink{classParticleManager_4e0f9e5cb222739a83f0f80ee4ba265b}{BuildNNP} (Vec2d \&point)
\begin{CompactList}\small\item\em do NNP search around a point and build the NNP list \item\end{CompactList}\item 
void \hyperlink{classParticleManager_b68ab55a9429ac8d32368b531487dcec}{BuildNNP\_\-MLSMapping} (Vec2d \&point)
\begin{CompactList}\small\item\em do NNP search around a point and build the NNP list for \hyperlink{classMLS}{MLS} approximation \item\end{CompactList}\item 
void \hyperlink{classParticleManager_8cc6658324694ad28d3c50bfc0cbd0f7}{BuildInteraction} (\hyperlink{classLlist}{Llist}$<$ \hyperlink{classInteraction}{Interaction} $>$ \&interactions, \hyperlink{classLlist}{Llist}$<$ \hyperlink{classParticle}{Particle} $>$ \&particle\_\-list, \hyperlink{classForce}{Force} $\ast$$\ast$forces, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function)
\begin{CompactList}\small\item\em build the interaction (particle pair) list \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classParticleManager_26e6109376eb2a1dc37f7fe623aaf528}{
int \hyperlink{classParticleManager_26e6109376eb2a1dc37f7fe623aaf528}{x\_\-clls}}
\label{classParticleManager_26e6109376eb2a1dc37f7fe623aaf528}

\begin{CompactList}\small\item\em linked cell matrix size x-direction \item\end{CompactList}\item 
\hypertarget{classParticleManager_09eae89d0d9e56d988e40cdebf13825b}{
int \hyperlink{classParticleManager_09eae89d0d9e56d988e40cdebf13825b}{y\_\-clls}}
\label{classParticleManager_09eae89d0d9e56d988e40cdebf13825b}

\begin{CompactList}\small\item\em linked cell matrix size y-direction \item\end{CompactList}\item 
\hypertarget{classParticleManager_0b7d522a4ecc14073c1adbb42c23fc84}{
\hyperlink{classLlist}{Llist}$<$ \hyperlink{classParticle}{Particle} $>$ $\ast$$\ast$ \hyperlink{classParticleManager_0b7d522a4ecc14073c1adbb42c23fc84}{cell\_\-lists}}
\label{classParticleManager_0b7d522a4ecc14073c1adbb42c23fc84}

\begin{CompactList}\small\item\em cell linked list in 2-d array \item\end{CompactList}\item 
\hypertarget{classParticleManager_8f47c372d7ea5ff68657defd7a492e85}{
\hyperlink{classLlist}{Llist}$<$ \hyperlink{classParticle}{Particle} $>$ \hyperlink{classParticleManager_8f47c372d7ea5ff68657defd7a492e85}{NNP\_\-list}}
\label{classParticleManager_8f47c372d7ea5ff68657defd7a492e85}

\begin{CompactList}\small\item\em list for the nearest neighbor particles \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Member Functions}
\begin{CompactItemize}
\item 
void \hyperlink{classParticleManager_edebb3e37b06426f6509b35c0926bd59}{BiuldWallParticles} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classInitiation}{Initiation} \&ini, \hyperlink{classBoundary}{Boundary} \&boundary)
\begin{CompactList}\small\item\em buid the initial wall particles and the linked lists \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classParticleManager_85dd6a84aa88a5e873ea6c23f65f9358}{
char \hyperlink{classParticleManager_85dd6a84aa88a5e873ea6c23f65f9358}{Project\_\-name} \mbox{[}25\mbox{]}}
\label{classParticleManager_85dd6a84aa88a5e873ea6c23f65f9358}

\begin{CompactList}\small\item\em the project name \item\end{CompactList}\item 
\hypertarget{classParticleManager_4585baa6023df69c39f277ee05cd21c8}{
int \textbf{number\_\-of\_\-materials}}
\label{classParticleManager_4585baa6023df69c39f277ee05cd21c8}

\item 
\hypertarget{classParticleManager_ed08b546912db6b921a172fe93dec0ab}{
double \hyperlink{classParticleManager_ed08b546912db6b921a172fe93dec0ab}{smoothinglength}}
\label{classParticleManager_ed08b546912db6b921a172fe93dec0ab}

\begin{CompactList}\small\item\em smoothinglenth \item\end{CompactList}\item 
\hypertarget{classParticleManager_43a0ada795094f76ae26db96c10e7955}{
double \hyperlink{classParticleManager_43a0ada795094f76ae26db96c10e7955}{smoothinglengthsquare}}
\label{classParticleManager_43a0ada795094f76ae26db96c10e7955}

\begin{CompactList}\small\item\em smoothinglenth \item\end{CompactList}\item 
\hypertarget{classParticleManager_585655101c829ec78e9abe6d849210fe}{
double \hyperlink{classParticleManager_585655101c829ec78e9abe6d849210fe}{cll\_\-sz}}
\label{classParticleManager_585655101c829ec78e9abe6d849210fe}

\begin{CompactList}\small\item\em cell size \item\end{CompactList}\item 
\hypertarget{classParticleManager_5e9cc4e55e0af75b59849f83a63bbec6}{
Vec2d \hyperlink{classParticleManager_5e9cc4e55e0af75b59849f83a63bbec6}{box\_\-size}}
\label{classParticleManager_5e9cc4e55e0af75b59849f83a63bbec6}

\begin{CompactList}\small\item\em computational domain size \item\end{CompactList}\item 
\hypertarget{classParticleManager_f91681a876131de64a0e2f6209d9bd89}{
int \hyperlink{classParticleManager_f91681a876131de64a0e2f6209d9bd89}{initial\_\-condition}}
\label{classParticleManager_f91681a876131de64a0e2f6209d9bd89}

\begin{CompactList}\small\item\em initial condition marker \item\end{CompactList}\item 
\hypertarget{classParticleManager_186eaba52a3b1a3ed7f098d1f2a56d9c}{
double \hyperlink{classParticleManager_186eaba52a3b1a3ed7f098d1f2a56d9c}{delta}}
\label{classParticleManager_186eaba52a3b1a3ed7f098d1f2a56d9c}

\begin{CompactList}\small\item\em the inital particle distance \item\end{CompactList}\item 
\hypertarget{classParticleManager_d77df8bc47beefcd049c4277c53d095a}{
int \hyperlink{classParticleManager_d77df8bc47beefcd049c4277c53d095a}{hdelta}}
\label{classParticleManager_d77df8bc47beefcd049c4277c53d095a}

\begin{CompactList}\small\item\em the ration between smoothing length and inital particle distance \item\end{CompactList}\item 
\hypertarget{classParticleManager_cb03c536574d333e0d733158aae652a1}{
Vec2d \hyperlink{classParticleManager_cb03c536574d333e0d733158aae652a1}{U0}}
\label{classParticleManager_cb03c536574d333e0d733158aae652a1}

\begin{CompactList}\small\item\em inital flow speed \item\end{CompactList}\item 
\hypertarget{classParticleManager_f19707700ab5014b13c1f623438d6b2f}{
double \textbf{rho0}}
\label{classParticleManager_f19707700ab5014b13c1f623438d6b2f}

\item 
\hypertarget{classParticleManager_729e474fe73f5d59f5448023798aee66}{
double \textbf{p0}}
\label{classParticleManager_729e474fe73f5d59f5448023798aee66}

\item 
\hypertarget{classParticleManager_edabda5cb1b485cd2ddaf10dad18f896}{
double \hyperlink{classParticleManager_edabda5cb1b485cd2ddaf10dad18f896}{T0}}
\label{classParticleManager_edabda5cb1b485cd2ddaf10dad18f896}

\begin{CompactList}\small\item\em initial particle mass and density, pressure and temperature \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classParticle}{Particle} manager class.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classParticleManager_11a8f14c20f087713172d230de468166}{
\index{ParticleManager@{ParticleManager}!ParticleManager@{ParticleManager}}
\index{ParticleManager@{ParticleManager}!ParticleManager@{ParticleManager}}
\subsubsection[{ParticleManager}]{\setlength{\rightskip}{0pt plus 5cm}ParticleManager::ParticleManager ({\bf Initiation} \& {\em ini})}}
\label{classParticleManager_11a8f14c20f087713172d230de468166}

constructor

\begin{itemize}
\item copy properties from class \hyperlink{classInitiation}{Initiation}\end{itemize}

\begin{itemize}
\item strore the cell linked lists in a 2-d array \end{itemize}

\subsection{Member Function Documentation}
\hypertarget{classParticleManager_6ee12c3925f371782800a50b17ac0941}{
\index{ParticleManager@{ParticleManager}!BiuldRealParticles@{BiuldRealParticles}}
\index{BiuldRealParticles@{BiuldRealParticles}!ParticleManager@{ParticleManager}}
\subsubsection[{BiuldRealParticles}]{\setlength{\rightskip}{0pt plus 5cm}void ParticleManager::BiuldRealParticles ({\bf Hydrodynamics} \& {\em hydro}, \/  {\bf Initiation} \& {\em ini})}}
\label{classParticleManager_6ee12c3925f371782800a50b17ac0941}

buid the initial particles and the linked lists

initial particles either from .cfg file or from .rst file

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=171pt]{classParticleManager_6ee12c3925f371782800a50b17ac0941_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=205pt]{classParticleManager_6ee12c3925f371782800a50b17ac0941_icgraph}
\end{center}
\end{figure}
\hypertarget{classParticleManager_edebb3e37b06426f6509b35c0926bd59}{
\index{ParticleManager@{ParticleManager}!BiuldWallParticles@{BiuldWallParticles}}
\index{BiuldWallParticles@{BiuldWallParticles}!ParticleManager@{ParticleManager}}
\subsubsection[{BiuldWallParticles}]{\setlength{\rightskip}{0pt plus 5cm}void ParticleManager::BiuldWallParticles ({\bf Hydrodynamics} \& {\em hydro}, \/  {\bf Initiation} \& {\em ini}, \/  {\bf Boundary} \& {\em boundary})\hspace{0.3cm}{\tt  \mbox{[}private\mbox{]}}}}
\label{classParticleManager_edebb3e37b06426f6509b35c0926bd59}

buid the initial wall particles and the linked lists

left hand border (corresponds to the first column)

\begin{itemize}
\item iterate over the first colums of all cells that constitute this boundary

\begin{itemize}
\item create a new wall particle

\item insert its position on the particle list

\item insert the position into corresponding cell list\end{itemize}
\end{itemize}

right hand border(corresponds to the last column)

\begin{itemize}
\item iterate over the last colums of all cells that constitute this boundary

\begin{itemize}
\item create a new wall particle

\item insert its poistion on the particle list

\item insert the position into corresponding cell list\end{itemize}
\end{itemize}

lower border(corresponds to the lowest row)

\begin{itemize}
\item iterate over the lowest row of all cells that constitute this boundary

\begin{itemize}
\item creat a new wall particle

\item insert its poistion on the particle list

\item insert the position into corresponding cell list\end{itemize}
\end{itemize}

upper border (corresponds to the last row)

\begin{itemize}
\item iterate over the last rows of all cells that constitute this boundary

\begin{itemize}
\item create a new wall particle

\item insert its poistion on the particle list

\item insert the position into corresponding cell list\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=158pt]{classParticleManager_edebb3e37b06426f6509b35c0926bd59_cgraph}
\end{center}
\end{figure}
\hypertarget{classParticleManager_8cc6658324694ad28d3c50bfc0cbd0f7}{
\index{ParticleManager@{ParticleManager}!BuildInteraction@{BuildInteraction}}
\index{BuildInteraction@{BuildInteraction}!ParticleManager@{ParticleManager}}
\subsubsection[{BuildInteraction}]{\setlength{\rightskip}{0pt plus 5cm}void ParticleManager::BuildInteraction ({\bf Llist}$<$ {\bf Interaction} $>$ \& {\em interactions}, \/  {\bf Llist}$<$ {\bf Particle} $>$ \& {\em particle\_\-list}, \/  {\bf Force} $\ast$$\ast$ {\em forces}, \/  {\bf QuinticSpline} \& {\em weight\_\-function})}}
\label{classParticleManager_8cc6658324694ad28d3c50bfc0cbd0f7}

build the interaction (particle pair) list

\begin{itemize}
\item iterate particles on the particle list

\begin{itemize}
\item choose origin particle

\item find out where(in which cell) the particle is

\item loop on this and all surrounding cells

\begin{itemize}
\item iterate this cell list

\begin{itemize}
\item calculate distance between particle in question and destination particle (which is iterated)and if interaction takes place: add pair to inetraction list ({\bf question: why is dst compared to h$^\wedge$2 and not support length to determine if there is interaction or not??} \end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=257pt]{classParticleManager_8cc6658324694ad28d3c50bfc0cbd0f7_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=350pt]{classParticleManager_8cc6658324694ad28d3c50bfc0cbd0f7_icgraph}
\end{center}
\end{figure}
\hypertarget{classParticleManager_4e0f9e5cb222739a83f0f80ee4ba265b}{
\index{ParticleManager@{ParticleManager}!BuildNNP@{BuildNNP}}
\index{BuildNNP@{BuildNNP}!ParticleManager@{ParticleManager}}
\subsubsection[{BuildNNP}]{\setlength{\rightskip}{0pt plus 5cm}void ParticleManager::BuildNNP (Vec2d \& {\em point})}}
\label{classParticleManager_4e0f9e5cb222739a83f0f80ee4ba265b}

do NNP search around a point and build the NNP list

\begin{itemize}
\item clear the list first

\item loop on this and all surrounding cells

\begin{itemize}
\item iterate this cell list

\begin{itemize}
\item check the position of the particle and (if particle is NNP) insert the nearest particle to the list

\item (line 137){\bf Question: WHY SMOOTHINGLENGTH AND NOT SUPPORT LENGT???} \end{itemize}
\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=151pt]{classParticleManager_4e0f9e5cb222739a83f0f80ee4ba265b_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=328pt]{classParticleManager_4e0f9e5cb222739a83f0f80ee4ba265b_icgraph}
\end{center}
\end{figure}
\hypertarget{classParticleManager_b68ab55a9429ac8d32368b531487dcec}{
\index{ParticleManager@{ParticleManager}!BuildNNP\_\-MLSMapping@{BuildNNP\_\-MLSMapping}}
\index{BuildNNP\_\-MLSMapping@{BuildNNP\_\-MLSMapping}!ParticleManager@{ParticleManager}}
\subsubsection[{BuildNNP\_\-MLSMapping}]{\setlength{\rightskip}{0pt plus 5cm}void ParticleManager::BuildNNP\_\-MLSMapping (Vec2d \& {\em point})}}
\label{classParticleManager_b68ab55a9429ac8d32368b531487dcec}

do NNP search around a point and build the NNP list for \hyperlink{classMLS}{MLS} approximation

\begin{itemize}
\item loop on this and all surrounding cells

\begin{itemize}
\item iterate this cell list

\begin{itemize}
\item check the position of the real particle and (if particle is NNP) insert it to the list \end{itemize}
\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=175pt]{classParticleManager_b68ab55a9429ac8d32368b531487dcec_cgraph}
\end{center}
\end{figure}
\hypertarget{classParticleManager_740244439672f753735abc5a6a7cc3bc}{
\index{ParticleManager@{ParticleManager}!UpdateCellLinkedLists@{UpdateCellLinkedLists}}
\index{UpdateCellLinkedLists@{UpdateCellLinkedLists}!ParticleManager@{ParticleManager}}
\subsubsection[{UpdateCellLinkedLists}]{\setlength{\rightskip}{0pt plus 5cm}void ParticleManager::UpdateCellLinkedLists ()}}
\label{classParticleManager_740244439672f753735abc5a6a7cc3bc}

update the cell linked lists for real particles

\begin{itemize}
\item (double) loop (as indices i, j) on all cells

\begin{itemize}
\item iterate this cell list

\item if the list is empty or the node position is at the end {\bf !!!Question!!! is this comment right? would it not rather be...if list NOT empty and NOT at the end }

\begin{itemize}
\item check the position of the real particle

\begin{itemize}
\item if the partilce runs out of the current cell

\begin{itemize}
\item delete the current node

\item insert it to the new cell linked list\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=171pt]{classParticleManager_740244439672f753735abc5a6a7cc3bc_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=260pt]{classParticleManager_740244439672f753735abc5a6a7cc3bc_icgraph}
\end{center}
\end{figure}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{particlemanager_8h}{particlemanager.h}\item 
particlemanager.cpp\end{CompactItemize}

### 2010-06-17 src/latex/classQuinticSpline.tex
compressible branch

\hypertarget{classQuinticSpline}{
\section{QuinticSpline Class Reference}
\label{classQuinticSpline}\index{QuinticSpline@{QuinticSpline}}
}
Quintic spline class.

{\tt \#include $<$quinticspline.h$>$}

Inheritance diagram for QuinticSpline:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=118pt]{classQuinticSpline__inherit__graph}
\end{center}
\end{figure}
Collaboration diagram for QuinticSpline:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=118pt]{classQuinticSpline__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classQuinticSpline_e2d0a39985327a020d2794516f895f27}{
\hyperlink{classQuinticSpline_e2d0a39985327a020d2794516f895f27}{QuinticSpline} (const double \hyperlink{classKernel_f088821dba4a00d1d320b27ebcb71258}{smoothingLength})}
\label{classQuinticSpline_e2d0a39985327a020d2794516f895f27}

\begin{CompactList}\small\item\em constructor to initialize the data members (auxiliary factors for kernel calculation) \item\end{CompactList}\item 
virtual double \hyperlink{classQuinticSpline_021acaeb55230bf10cf3a2c634381088}{w} (const double distance) const 
\begin{CompactList}\small\item\em Calculates the kernel value for the given distance of two particles. \item\end{CompactList}\item 
virtual Vec2d \hyperlink{classQuinticSpline_00a31074e58e60a4721144e4935c56b2}{gradW} (const double distance, const Vec2d \&distanceVector) const 
\begin{CompactList}\small\item\em Calculates the kernel derivation for the given distance of two particles. \item\end{CompactList}\item 
\hypertarget{classQuinticSpline_67fa50759531bbbbef728d28282788e7}{
double \hyperlink{classQuinticSpline_67fa50759531bbbbef728d28282788e7}{F} (const double distance) const }
\label{classQuinticSpline_67fa50759531bbbbef728d28282788e7}

\begin{CompactList}\small\item\em Calculates the kernel derivation (a double, not a vector) to distance. \item\end{CompactList}\item 
\hypertarget{classQuinticSpline_adc23e95cd346c434b423b3276156e8c}{
double \hyperlink{classQuinticSpline_adc23e95cd346c434b423b3276156e8c}{LapW} (const double distance) const }
\label{classQuinticSpline_adc23e95cd346c434b423b3276156e8c}

\begin{CompactList}\small\item\em Calculates the kernel Laplacian. \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classQuinticSpline_bd65ef2de82ce850ec80393582726532}{
const double \hyperlink{classQuinticSpline_bd65ef2de82ce850ec80393582726532}{norm}}
\label{classQuinticSpline_bd65ef2de82ce850ec80393582726532}

\begin{CompactList}\small\item\em Normalization factor. \item\end{CompactList}\item 
\hypertarget{classQuinticSpline_743bd6fe1beb6049f5bdcf76beba04e2}{
double \hyperlink{classQuinticSpline_743bd6fe1beb6049f5bdcf76beba04e2}{reciprocH}}
\label{classQuinticSpline_743bd6fe1beb6049f5bdcf76beba04e2}

\begin{CompactList}\small\item\em Auxiliary factors for intermediate results: The inverse smoothing length. \item\end{CompactList}\item 
\hypertarget{classQuinticSpline_e260195cb042866d86a822f469a1277f}{
double \hyperlink{classQuinticSpline_e260195cb042866d86a822f469a1277f}{factorW}}
\label{classQuinticSpline_e260195cb042866d86a822f469a1277f}

\begin{CompactList}\small\item\em Auxiliary factors for intermediate results: A pre-factor for w. \item\end{CompactList}\item 
\hypertarget{classQuinticSpline_fda98a6d7b9feda4e30871111ece88b3}{
double \hyperlink{classQuinticSpline_fda98a6d7b9feda4e30871111ece88b3}{factorGradW}}
\label{classQuinticSpline_fda98a6d7b9feda4e30871111ece88b3}

\begin{CompactList}\small\item\em Auxiliary factors for intermediate results: A pre-factor for grad w. \item\end{CompactList}\item 
\hypertarget{classQuinticSpline_5cf5d05e9069c965ffc315770a1206ec}{
double \hyperlink{classQuinticSpline_5cf5d05e9069c965ffc315770a1206ec}{factorLapW}}
\label{classQuinticSpline_5cf5d05e9069c965ffc315770a1206ec}

\begin{CompactList}\small\item\em Auxiliary factors for Laplacian. \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
Quintic spline class.

\subsection{Member Function Documentation}
\hypertarget{classQuinticSpline_00a31074e58e60a4721144e4935c56b2}{
\index{QuinticSpline@{QuinticSpline}!gradW@{gradW}}
\index{gradW@{gradW}!QuinticSpline@{QuinticSpline}}
\subsubsection[{gradW}]{\setlength{\rightskip}{0pt plus 5cm}Vec2d QuinticSpline::gradW (const double {\em distance}, \/  const Vec2d \& {\em distanceVector}) const\hspace{0.3cm}{\tt  \mbox{[}virtual\mbox{]}}}}
\label{classQuinticSpline_00a31074e58e60a4721144e4935c56b2}

Calculates the kernel derivation for the given distance of two particles.

We take this from Morris, Fox and Zhu (1997) but used a tripled smoothing length for the definition of the interaction radius.

Implements \hyperlink{classKernel_545e61b98db05db6dd02b88e2ad3da23}{Kernel}.\hypertarget{classQuinticSpline_021acaeb55230bf10cf3a2c634381088}{
\index{QuinticSpline@{QuinticSpline}!w@{w}}
\index{w@{w}!QuinticSpline@{QuinticSpline}}
\subsubsection[{w}]{\setlength{\rightskip}{0pt plus 5cm}double QuinticSpline::w (const double {\em distance}) const\hspace{0.3cm}{\tt  \mbox{[}virtual\mbox{]}}}}
\label{classQuinticSpline_021acaeb55230bf10cf3a2c634381088}

Calculates the kernel value for the given distance of two particles.

We take this from Morris, Fox and Zhu (1997) but used a tripled smoothing length for the definition of the interaction radius.

Implements \hyperlink{classKernel_6b4d26ba99457a4acbbbca1454dbdc8a}{Kernel}.

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{classQuinticSpline_021acaeb55230bf10cf3a2c634381088_icgraph}
\end{center}
\end{figure}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{quinticspline_8h}{quinticspline.h}\item 
\hyperlink{quinticspline_8cpp}{quinticspline.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classTimeSolver.tex
compressible branch

\hypertarget{classTimeSolver}{
\section{TimeSolver Class Reference}
\label{classTimeSolver}\index{TimeSolver@{TimeSolver}}
}
Time solver class.

{\tt \#include $<$timesolver.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hyperlink{classTimeSolver_c5ed4d99be532dd9c3e77424b3e7a60a}{TimeSolver} (\hyperlink{classInitiation}{Initiation} \&ini)
\begin{CompactList}\small\item\em constructor \item\end{CompactList}\item 
void \hyperlink{classTimeSolver_edd74b3f1e292277b972b938787f4a3c}{TimeIntegral} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classBoundary}{Boundary} \&boundary, double \&Time, double D\_\-time, \hyperlink{classDiagnose}{Diagnose} \&diagnose, \hyperlink{classInitiation}{Initiation} \&ini, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, \hyperlink{classMLS}{MLS} \&mls)
\begin{CompactList}\small\item\em advance time interval D\_\-time (=output time interval) \item\end{CompactList}\item 
void \hyperlink{classTimeSolver_2cbbdd8eecbd3aae12c153f8b9da1402}{TimeIntegral\_\-summation} (\hyperlink{classHydrodynamics}{Hydrodynamics} \&hydro, \hyperlink{classParticleManager}{ParticleManager} \&particles, \hyperlink{classBoundary}{Boundary} \&boundary, double \&Time, double D\_\-time, \hyperlink{classDiagnose}{Diagnose} \&diagnose, \hyperlink{classInitiation}{Initiation} \&ini, \hyperlink{classQuinticSpline}{QuinticSpline} \&weight\_\-function, \hyperlink{classMLS}{MLS} \&mls)
\begin{CompactList}\small\item\em advance time interval D\_\-time with summation for density \item\end{CompactList}\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classTimeSolver_6650fefd2ce17fe4b84c21d2cf84b3c0}{
double \hyperlink{classTimeSolver_6650fefd2ce17fe4b84c21d2cf84b3c0}{cell\_\-size}}
\label{classTimeSolver_6650fefd2ce17fe4b84c21d2cf84b3c0}

\begin{CompactList}\small\item\em will be copied from initiation \item\end{CompactList}\item 
\hypertarget{classTimeSolver_091ff25ed4144106f86ec1b0043a2b00}{
Vec2d \hyperlink{classTimeSolver_091ff25ed4144106f86ec1b0043a2b00}{box\_\-size}}
\label{classTimeSolver_091ff25ed4144106f86ec1b0043a2b00}

\begin{CompactList}\small\item\em will be copied from initiation \item\end{CompactList}\item 
\hypertarget{classTimeSolver_8a435c6de2503a8cd74868e19a9ed099}{
double \hyperlink{classTimeSolver_8a435c6de2503a8cd74868e19a9ed099}{smoothinglength}}
\label{classTimeSolver_8a435c6de2503a8cd74868e19a9ed099}

\begin{CompactList}\small\item\em will be copied from initiation \item\end{CompactList}\item 
\hypertarget{classTimeSolver_059eae3a0771b4d3201aea0aef1aaee4}{
int \hyperlink{classTimeSolver_059eae3a0771b4d3201aea0aef1aaee4}{ite}}
\label{classTimeSolver_059eae3a0771b4d3201aea0aef1aaee4}

\begin{CompactList}\small\item\em number of iteration \item\end{CompactList}\item 
\hypertarget{classTimeSolver_66c0a9afc7f8fbc205e4ce4de9435aed}{
double \hyperlink{classTimeSolver_66c0a9afc7f8fbc205e4ce4de9435aed}{dt}}
\label{classTimeSolver_66c0a9afc7f8fbc205e4ce4de9435aed}

\begin{CompactList}\small\item\em time step \item\end{CompactList}\end{CompactItemize}

\subsection{Detailed Description}
Time solver class.

\subsection{Constructor \& Destructor Documentation}
\hypertarget{classTimeSolver_c5ed4d99be532dd9c3e77424b3e7a60a}{
\index{TimeSolver@{TimeSolver}!TimeSolver@{TimeSolver}}
\index{TimeSolver@{TimeSolver}!TimeSolver@{TimeSolver}}
\subsubsection[{TimeSolver}]{\setlength{\rightskip}{0pt plus 5cm}TimeSolver::TimeSolver ({\bf Initiation} \& {\em ini})}}
\label{classTimeSolver_c5ed4d99be532dd9c3e77424b3e7a60a}

constructor

\begin{itemize}
\item copy properties from class \hyperlink{classInitiation}{Initiation}\end{itemize}

\begin{itemize}
\item initialize the iteration \end{itemize}

\subsection{Member Function Documentation}
\hypertarget{classTimeSolver_edd74b3f1e292277b972b938787f4a3c}{
\index{TimeSolver@{TimeSolver}!TimeIntegral@{TimeIntegral}}
\index{TimeIntegral@{TimeIntegral}!TimeSolver@{TimeSolver}}
\subsubsection[{TimeIntegral}]{\setlength{\rightskip}{0pt plus 5cm}void TimeSolver::TimeIntegral ({\bf Hydrodynamics} \& {\em hydro}, \/  {\bf ParticleManager} \& {\em particles}, \/  {\bf Boundary} \& {\em boundary}, \/  double \& {\em Time}, \/  double {\em D\_\-time}, \/  {\bf Diagnose} \& {\em diagnose}, \/  {\bf Initiation} \& {\em ini}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  {\bf MLS} \& {\em mls})}}
\label{classTimeSolver_edd74b3f1e292277b972b938787f4a3c}

advance time interval D\_\-time (=output time interval)

\begin{itemize}
\item print out screen information for the iteration

\item calculating diagonse information

\item the prediction step

\begin{enumerate}
\item hydro.BuildPair

\item hydro.UpdateChangeRate

\item hydro.Predictor

\item hydro.UpdateState\end{enumerate}

\item the correction step without update the interaction list

\begin{enumerate}
\item hydro.UpdatePair

\item boundary.BoundaryCondition

\item hydro.UpdateChangeRate

\item hydro.UpdateRandom

\item hydro.Corrector

\item hydro.RandomEffects

\item hydro.UpdateState\end{enumerate}

\item renew boundary particles

\begin{enumerate}
\item boundary.RunAwayCheck

\item particles.UpdateCellLinkedLists

\item boundary.BuildBoundaryParticles\end{enumerate}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{classTimeSolver_edd74b3f1e292277b972b938787f4a3c_cgraph}
\end{center}
\end{figure}
\hypertarget{classTimeSolver_2cbbdd8eecbd3aae12c153f8b9da1402}{
\index{TimeSolver@{TimeSolver}!TimeIntegral\_\-summation@{TimeIntegral\_\-summation}}
\index{TimeIntegral\_\-summation@{TimeIntegral\_\-summation}!TimeSolver@{TimeSolver}}
\subsubsection[{TimeIntegral\_\-summation}]{\setlength{\rightskip}{0pt plus 5cm}void TimeSolver::TimeIntegral\_\-summation ({\bf Hydrodynamics} \& {\em hydro}, \/  {\bf ParticleManager} \& {\em particles}, \/  {\bf Boundary} \& {\em boundary}, \/  double \& {\em Time}, \/  double {\em D\_\-time}, \/  {\bf Diagnose} \& {\em diagnose}, \/  {\bf Initiation} \& {\em ini}, \/  {\bf QuinticSpline} \& {\em weight\_\-function}, \/  {\bf MLS} \& {\em mls})}}
\label{classTimeSolver_2cbbdd8eecbd3aae12c153f8b9da1402}

advance time interval D\_\-time with summation for density

\begin{itemize}
\item screen information for the iteration

\item calculating diagnose information

\item the prediction step

\begin{enumerate}
\item hydro.buildPair

\item hydro.UpdateDensity

\item boundary.BoundaryCondition

\item hydro.UpdatePhaseGradient

\item boundary.BoundaryCondition

\item hydro.UpdateSurfaceStress

\item hydro.UpdateChangeRate

\item hydro.Predictor\_\-summation\end{enumerate}

\item the correction step without update the interaction list

\begin{enumerate}
\item boundary.BoundaryCondition

\item hydro.UpdatePair

\item hydro.UpdateDensity

\item boundary.BoundaryCondition

\item hydro.UpdatePhaseGradient

\item boundary.BoundaryCondition

\item hydro.UpdateSurfaceStress

\item hydro.UpdateChangeRate

\item hydro.Corrector\_\-summation\end{enumerate}

\item renew boundary particles

\begin{enumerate}
\item boundary.RunAwayCheck

\item particles.UpdateCellLinkedLists

\item boundary.BuildBoundaryParticles\end{enumerate}
\end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=409pt]{classTimeSolver_2cbbdd8eecbd3aae12c153f8b9da1402_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=147pt]{classTimeSolver_2cbbdd8eecbd3aae12c153f8b9da1402_icgraph}
\end{center}
\end{figure}

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{timesolver_8h}{timesolver.h}\item 
\hyperlink{timesolver_8cpp}{timesolver.cpp}\end{CompactItemize}

### 2010-06-17 src/latex/classWiener.tex
compressible branch

\hypertarget{classWiener}{
\section{Wiener Class Reference}
\label{classWiener}\index{Wiener@{Wiener}}
}
\hyperlink{classWiener}{Wiener} process.

{\tt \#include $<$wiener.h$>$}

\subsection*{Public Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classWiener_9b2daa0e357c11b963463e6c2a510ad1}{
\hyperlink{classWiener_9b2daa0e357c11b963463e6c2a510ad1}{Wiener} ()}
\label{classWiener_9b2daa0e357c11b963463e6c2a510ad1}

\begin{CompactList}\small\item\em costructure \item\end{CompactList}\item 
\hypertarget{classWiener_454f6ab52cf050daf682fa6f374504ea}{
\textbf{Wiener} (const int dimension)}
\label{classWiener_454f6ab52cf050daf682fa6f374504ea}

\item 
\hypertarget{classWiener_9bf2a13de68b15f52e6b3ff5a9c485b6}{
void \hyperlink{classWiener_9bf2a13de68b15f52e6b3ff5a9c485b6}{get\_\-wiener\_\-Espanol} (const double sqrtdt)}
\label{classWiener_9bf2a13de68b15f52e6b3ff5a9c485b6}

\begin{CompactList}\small\item\em produce wiener vlaue matrix with symmetric tracless part, and the trace \item\end{CompactList}\item 
\hypertarget{classWiener_be754cfa9c89ec2e405126f26997e0f0}{
void \hyperlink{classWiener_be754cfa9c89ec2e405126f26997e0f0}{get\_\-wiener} (const double sqrtdt)}
\label{classWiener_be754cfa9c89ec2e405126f26997e0f0}

\begin{CompactList}\small\item\em wiener process with Flekkoy's form \item\end{CompactList}\item 
\hypertarget{classWiener_2fb89a7b43c2d6378ff6698614907098}{
void \hyperlink{classWiener_2fb89a7b43c2d6378ff6698614907098}{Ranils} ()}
\label{classWiener_2fb89a7b43c2d6378ff6698614907098}

\begin{CompactList}\small\item\em set the random seed \item\end{CompactList}\end{CompactItemize}
\subsection*{Public Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classWiener_cd79f000952f14b816c3cdd008c34a2a}{
double $\ast$$\ast$ \textbf{sym\_\-trclss}}
\label{classWiener_cd79f000952f14b816c3cdd008c34a2a}

\item 
\hypertarget{classWiener_c24cf9f8fd8385325584c190f93f0abe}{
double \textbf{trace\_\-d}}
\label{classWiener_c24cf9f8fd8385325584c190f93f0abe}

\item 
\hypertarget{classWiener_f47c4ccdb5cc42751beaf9023e64d426}{
double \textbf{Random\_\-p}}
\label{classWiener_f47c4ccdb5cc42751beaf9023e64d426}

\item 
\hypertarget{classWiener_411516a928b7d38aa170c2311af6c26a}{
double \textbf{Random\_\-v}}
\label{classWiener_411516a928b7d38aa170c2311af6c26a}

\end{CompactItemize}
\subsection*{Private Member Functions}
\begin{CompactItemize}
\item 
\hypertarget{classWiener_238e64201f993e2e4fff5c6615b1cf85}{
double \hyperlink{classWiener_238e64201f993e2e4fff5c6615b1cf85}{Ranuls} ()}
\label{classWiener_238e64201f993e2e4fff5c6615b1cf85}

\begin{CompactList}\small\item\em get the random number uniform distributed in \mbox{[}0, 1\mbox{]} \item\end{CompactList}\item 
void \hyperlink{classWiener_afdd7d1aa80e1609edd7bcc7532d56d6}{Gaussian} (double \&y1, double \&y2)
\end{CompactItemize}
\subsection*{Private Attributes}
\begin{CompactItemize}
\item 
\hypertarget{classWiener_4bf535cc91f737b904552f51ae1f0ac6}{
int \textbf{dimension}}
\label{classWiener_4bf535cc91f737b904552f51ae1f0ac6}

\item 
\hypertarget{classWiener_09f6069684c20e3eecdddd17602fcf05}{
double $\ast$$\ast$ \textbf{randoms}}
\label{classWiener_09f6069684c20e3eecdddd17602fcf05}

\item 
long int \hyperlink{classWiener_eb32502c4439ae23e7a6922c5d8cd3ba}{idum}
\item 
\hypertarget{classWiener_b06d8f8b4ff3e2c1c099570a66c1ce84}{
long int \textbf{idum2}}
\label{classWiener_b06d8f8b4ff3e2c1c099570a66c1ce84}

\item 
\hypertarget{classWiener_040aaffc7d7758d597582660a09656d3}{
long int \textbf{iy}}
\label{classWiener_040aaffc7d7758d597582660a09656d3}

\item 
\hypertarget{classWiener_f6aa4a6e172025e1ab3f9150e69f865a}{
long int \textbf{ntab}}
\label{classWiener_f6aa4a6e172025e1ab3f9150e69f865a}

\item 
\hypertarget{classWiener_56f50cb31e458ec78b843809ac4a0101}{
long int \textbf{iseed}}
\label{classWiener_56f50cb31e458ec78b843809ac4a0101}

\item 
\hypertarget{classWiener_353476d32254b68fdedaee29f3ae137d}{
long int $\ast$ \textbf{iv}}
\label{classWiener_353476d32254b68fdedaee29f3ae137d}

\end{CompactItemize}

\subsection{Detailed Description}
\hyperlink{classWiener}{Wiener} process.

----------------------------------------------------------------------- The class defining \hyperlink{classWiener}{Wiener} process in two dimensions -----------------------------------------------------------------------

\subsection{Member Function Documentation}
\hypertarget{classWiener_afdd7d1aa80e1609edd7bcc7532d56d6}{
\index{Wiener@{Wiener}!Gaussian@{Gaussian}}
\index{Gaussian@{Gaussian}!Wiener@{Wiener}}
\subsubsection[{Gaussian}]{\setlength{\rightskip}{0pt plus 5cm}void Wiener::Gaussian (double \& {\em y1}, \/  double \& {\em y2})\hspace{0.3cm}{\tt  \mbox{[}private\mbox{]}}}}
\label{classWiener_afdd7d1aa80e1609edd7bcc7532d56d6}

get two random numbers y1, y2 with guassian distribution with zero mean and variance one from random numbers uniform distributed in \mbox{[}0, 1\mbox{]}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=129pt]{classWiener_afdd7d1aa80e1609edd7bcc7532d56d6_cgraph}
\end{center}
\end{figure}

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{classWiener_afdd7d1aa80e1609edd7bcc7532d56d6_icgraph}
\end{center}
\end{figure}

\subsection{Member Data Documentation}
\hypertarget{classWiener_eb32502c4439ae23e7a6922c5d8cd3ba}{
\index{Wiener@{Wiener}!idum@{idum}}
\index{idum@{idum}!Wiener@{Wiener}}
\subsubsection[{idum}]{\setlength{\rightskip}{0pt plus 5cm}long int {\bf Wiener::idum}\hspace{0.3cm}{\tt  \mbox{[}private\mbox{]}}}}
\label{classWiener_eb32502c4439ae23e7a6922c5d8cd3ba}

for random number generator variables

The documentation for this class was generated from the following files:\begin{CompactItemize}
\item 
\hyperlink{wiener_8h}{wiener.h}\item 
wiener.cpp\end{CompactItemize}

### 2010-06-17 src/latex/diagose_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/bskernel_8cpp.tex
@@
-\hypertarget{bskernel_8cpp}{
-\section{bskernel.cpp File Reference}
-\label{bskernel_8cpp}\index{bskernel.cpp@{bskernel.cpp}}
+\hypertarget{diagose_8cpp}{
+\section{diagose.cpp File Reference}
+\label{diagose_8cpp}\index{diagose.cpp@{diagose.cpp}}
 }
@@
 {\tt \#include $<$cstdlib$>$}\par
-{\tt \#include $<$cmath$>$}\par
 {\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
@@
 
-Include dependency graph for bskernel.cpp:\nopagebreak
+Include dependency graph for diagose.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{bskernel_8cpp__incl}
+\includegraphics[width=420pt]{diagose_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/dllist_8h.tex
compressible branch

\hypertarget{dllist_8h}{
\section{dllist.h File Reference}
\label{dllist_8h}\index{dllist.h@{dllist.h}}
}
Double linked list implementation.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{dllist_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classLlistNode}{LlistNode$<$ Ldata $>$}
\begin{CompactList}\small\item\em A template node in the linked list. \item\end{CompactList}\item 
class \hyperlink{classLlist}{Llist$<$ Ldata $>$}
\begin{CompactList}\small\item\em Double linked list implementation. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Double linked list implementation.

\begin{Desc}
\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$

changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$

changes by: Andreas Mattes Declares and defines a generic double linked list template \end{Desc}

### 2010-06-17 src/latex/files.tex
compressible branch

\section{File List}
Here is a list of all documented files with brief descriptions:\begin{CompactList}
\item\contentsline{section}{\hyperlink{betaspline_8h}{betaspline.h} (Beta spline kernel function )}{\pageref{betaspline_8h}}{}
\item\contentsline{section}{\hyperlink{boundary_8cpp}{boundary.cpp} }{\pageref{boundary_8cpp}}{}
\item\contentsline{section}{\hyperlink{boundary_8h}{boundary.h} (Bonudary conditions )}{\pageref{boundary_8h}}{}
\item\contentsline{section}{\hyperlink{bskernel_8cpp}{bskernel.cpp} }{\pageref{bskernel_8cpp}}{}
\item\contentsline{section}{\hyperlink{diagnose_8h}{diagnose.h} (\hyperlink{classOutput}{Output} the diagnosal results )}{\pageref{diagnose_8h}}{}
\item\contentsline{section}{\hyperlink{diagose_8cpp}{diagose.cpp} }{\pageref{diagose_8cpp}}{}
\item\contentsline{section}{\hyperlink{dllist_8h}{dllist.h} (Double linked list implementation )}{\pageref{dllist_8h}}{}
\item\contentsline{section}{\hyperlink{force_8h}{force.h} (The class defining force on or between particles )}{\pageref{force_8h}}{}
\item\contentsline{section}{\hyperlink{glbcls_8h}{glbcls.h} (Global class declarations )}{\pageref{glbcls_8h}}{}
\item\contentsline{section}{\hyperlink{glbfunc_8cpp}{glbfunc.cpp} }{\pageref{glbfunc_8cpp}}{}
\item\contentsline{section}{\hyperlink{glbfunc_8h}{glbfunc.h} }{\pageref{glbfunc_8h}}{}
\item\contentsline{section}{\hyperlink{hydrodynamics_8cpp}{hydrodynamics.cpp} }{\pageref{hydrodynamics_8cpp}}{}
\item\contentsline{section}{\hyperlink{hydrodynamics_8h}{hydrodynamics.h} (Definition of materials and their hydrodynamical interactions )}{\pageref{hydrodynamics_8h}}{}
\item\contentsline{section}{\hyperlink{initiation_8cpp}{initiation.cpp} }{\pageref{initiation_8cpp}}{}
\item\contentsline{section}{\hyperlink{initiation_8h}{initiation.h} (Initiates the simulation )}{\pageref{initiation_8h}}{}
\item\contentsline{section}{\hyperlink{interaction_8cpp}{interaction.cpp} }{\pageref{interaction_8cpp}}{}
\item\contentsline{section}{\hyperlink{interaction_8h}{interaction.h} (Defines interaction between particles )}{\pageref{interaction_8h}}{}
\item\contentsline{section}{\hyperlink{kernel_8cpp}{kernel.cpp} (Abstract kernel base class )}{\pageref{kernel_8cpp}}{}
\item\contentsline{section}{\hyperlink{kernel_8h}{kernel.h} (\hyperlink{classKernel}{Kernel} abstract base )}{\pageref{kernel_8h}}{}
\item\contentsline{section}{\hyperlink{material_8cpp}{material.cpp} }{\pageref{material_8cpp}}{}
\item\contentsline{section}{\hyperlink{material_8h}{material.h} (\hyperlink{classMaterial}{Material} )}{\pageref{material_8h}}{}
\item\contentsline{section}{\hyperlink{mls_8cpp}{mls.cpp} }{\pageref{mls_8cpp}}{}
\item\contentsline{section}{\hyperlink{mls_8h}{mls.h} }{\pageref{mls_8h}}{}
\item\contentsline{section}{\hyperlink{output_8cpp}{output.cpp} }{\pageref{output_8cpp}}{}
\item\contentsline{section}{\hyperlink{output_8h}{output.h} (\hyperlink{classOutput}{Output} the computational results )}{\pageref{output_8h}}{}
\item\contentsline{section}{\hyperlink{particle_8cpp}{particle.cpp} }{\pageref{particle_8cpp}}{}
\item\contentsline{section}{\textbf{particle.h} }{\pageref{particle_8h}}{}
\item\contentsline{section}{\hyperlink{particlemanager_8h}{particlemanager.h} (\hyperlink{classParticle}{Particle} manager )}{\pageref{particlemanager_8h}}{}
\item\contentsline{section}{\hyperlink{quinticspline_8cpp}{quinticspline.cpp} }{\pageref{quinticspline_8cpp}}{}
\item\contentsline{section}{\hyperlink{quinticspline_8h}{quinticspline.h} (Quintic spline kernel )}{\pageref{quinticspline_8h}}{}
\item\contentsline{section}{\hyperlink{sph_8cpp}{sph.cpp} }{\pageref{sph_8cpp}}{}
\item\contentsline{section}{\hyperlink{timesolver_8cpp}{timesolver.cpp} }{\pageref{timesolver_8cpp}}{}
\item\contentsline{section}{\hyperlink{timesolver_8h}{timesolver.h} (Time solver class )}{\pageref{timesolver_8h}}{}
\item\contentsline{section}{\hyperlink{vec2d_8h}{vec2d.h} (Define 2-d vectors and associated operations )}{\pageref{vec2d_8h}}{}
\item\contentsline{section}{\hyperlink{wiener_8h}{wiener.h} (\hyperlink{classWiener}{Wiener} process )}{\pageref{wiener_8h}}{}
\end{CompactList}

### 2010-06-17 src/latex/force_8h.tex
compressible branch

--- 2010-06-17 src/latex/dllist_8h.tex
@@
-\hypertarget{dllist_8h}{
-\section{dllist.h File Reference}
-\label{dllist_8h}\index{dllist.h@{dllist.h}}
+\hypertarget{force_8h}{
+\section{force.h File Reference}
+\label{force_8h}\index{force.h@{force.h}}
 }
-Double linked list implementation.
+The class defining force on or between particles.
 
@@
 \leavevmode
-\includegraphics[width=420pt]{dllist_8h__dep__incl}
+\includegraphics[width=420pt]{force_8h__dep__incl}
 \end{center}
@@
 \item 
-class \hyperlink{classLlistNode}{LlistNode$<$ Ldata $>$}
-\begin{CompactList}\small\item\em A template node in the linked list. \item\end{CompactList}\item 
-class \hyperlink{classLlist}{Llist$<$ Ldata $>$}
-\begin{CompactList}\small\item\em Double linked list implementation. \item\end{CompactList}\end{CompactItemize}
+class \hyperlink{classForce}{Force}
+\begin{CompactList}\small\item\em The class defining force on or between particles. \item\end{CompactList}\end{CompactItemize}
 
@@
 \subsection{Detailed Description}
-Double linked list implementation.
-
-\begin{Desc}
-\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$
-
-changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$
-
-changes by: Andreas Mattes Declares and defines a generic double linked list template \end{Desc}
+The class defining force on or between particles.

### 2010-06-17 src/latex/glbfunc_8cpp.tex
compressible branch

\hypertarget{glbfunc_8cpp}{
\section{glbfunc.cpp File Reference}
\label{glbfunc_8cpp}\index{glbfunc.cpp@{glbfunc.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for glbfunc.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=238pt]{glbfunc_8cpp__incl}
\end{center}
\end{figure}
\subsection*{Functions}
\begin{CompactItemize}
\item 
\hypertarget{glbfunc_8cpp_78a6c97f8b8f5e0fbb4e52d0aa6110aa}{
double \hyperlink{glbfunc_8cpp_78a6c97f8b8f5e0fbb4e52d0aa6110aa}{AMAX1} (double a, double b)}
\label{glbfunc_8cpp_78a6c97f8b8f5e0fbb4e52d0aa6110aa}

\begin{CompactList}\small\item\em a. Get the maximum \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_70d74bfbfb9d5e299e3effddb147b5ce}{
double \hyperlink{glbfunc_8cpp_70d74bfbfb9d5e299e3effddb147b5ce}{AMIN1} (double a, double b)}
\label{glbfunc_8cpp_70d74bfbfb9d5e299e3effddb147b5ce}

\begin{CompactList}\small\item\em b. Get the minimum \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_4285ca4ceabec63382f74718de72daf0}{
double \hyperlink{glbfunc_8cpp_4285ca4ceabec63382f74718de72daf0}{SIGN} (double a, double b)}
\label{glbfunc_8cpp_4285ca4ceabec63382f74718de72daf0}

\begin{CompactList}\small\item\em d. Sign of the first value is determined by the secomax\_\-species\_\-number value's sign \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_0b49a61653d985585465515587b087ee}{
double \hyperlink{glbfunc_8cpp_0b49a61653d985585465515587b087ee}{AMAX4} (double a, double b, double c, double d)}
\label{glbfunc_8cpp_0b49a61653d985585465515587b087ee}

\begin{CompactList}\small\item\em e. Get the maximum from four \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_7bf26e1cff694aad68df394cb63c1a31}{
int \hyperlink{glbfunc_8cpp_7bf26e1cff694aad68df394cb63c1a31}{SymmetricInverse3x3} (double M\mbox{[}3\mbox{]}\mbox{[}3\mbox{]})}
\label{glbfunc_8cpp_7bf26e1cff694aad68df394cb63c1a31}

\begin{CompactList}\small\item\em f. Get the inverse of symmetric array \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_810e8e13a2409b115ead17fdf00760d1}{
double \hyperlink{glbfunc_8cpp_810e8e13a2409b115ead17fdf00760d1}{Kronecker} (int a, int b)}
\label{glbfunc_8cpp_810e8e13a2409b115ead17fdf00760d1}

\begin{CompactList}\small\item\em g. Kronecker delta \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_3cab9f4eb994d85cb307ef4ca698b923}{
double \hyperlink{glbfunc_8cpp_3cab9f4eb994d85cb307ef4ca698b923}{K\_\-sign} (int a, int b)}
\label{glbfunc_8cpp_3cab9f4eb994d85cb307ef4ca698b923}

\begin{CompactList}\small\item\em h. Sign function \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_3b0843a41bc641e5553d442b94b1f3e1}{
double \hyperlink{glbfunc_8cpp_3b0843a41bc641e5553d442b94b1f3e1}{compare} (int a, int b)}
\label{glbfunc_8cpp_3b0843a41bc641e5553d442b94b1f3e1}

\begin{CompactList}\small\item\em h. comparing \item\end{CompactList}\item 
\hypertarget{glbfunc_8cpp_21546457e67986c8772ab1ce75ab8e7a}{
double \hyperlink{glbfunc_8cpp_21546457e67986c8772ab1ce75ab8e7a}{sq} (double a)}
\label{glbfunc_8cpp_21546457e67986c8772ab1ce75ab8e7a}

\begin{CompactList}\small\item\em i. square \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
$\backslash$ author Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$ \begin{Desc}
\item[Author:]changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$, \end{Desc}

### 2010-06-17 src/latex/glbfunc_8h.tex
compressible branch

\hypertarget{glbfunc_8h}{
\section{glbfunc.h File Reference}
\label{glbfunc_8h}\index{glbfunc.h@{glbfunc.h}}
}

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{glbfunc_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Functions}
\begin{CompactItemize}
\item 
\hypertarget{glbfunc_8h_78a6c97f8b8f5e0fbb4e52d0aa6110aa}{
double \hyperlink{glbfunc_8h_78a6c97f8b8f5e0fbb4e52d0aa6110aa}{AMAX1} (double a, double b)}
\label{glbfunc_8h_78a6c97f8b8f5e0fbb4e52d0aa6110aa}

\begin{CompactList}\small\item\em a. Get the maximum \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_70d74bfbfb9d5e299e3effddb147b5ce}{
double \hyperlink{glbfunc_8h_70d74bfbfb9d5e299e3effddb147b5ce}{AMIN1} (double a, double b)}
\label{glbfunc_8h_70d74bfbfb9d5e299e3effddb147b5ce}

\begin{CompactList}\small\item\em b. Get the minimum \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_ecdd3901ee6e4ecdafd81998cef6cafe}{
double \hyperlink{glbfunc_8h_ecdd3901ee6e4ecdafd81998cef6cafe}{ABS} (double a)}
\label{glbfunc_8h_ecdd3901ee6e4ecdafd81998cef6cafe}

\begin{CompactList}\small\item\em c. Get the absolute \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_4285ca4ceabec63382f74718de72daf0}{
double \hyperlink{glbfunc_8h_4285ca4ceabec63382f74718de72daf0}{SIGN} (double a, double b)}
\label{glbfunc_8h_4285ca4ceabec63382f74718de72daf0}

\begin{CompactList}\small\item\em d. Sign of the first value is determined by the secomax\_\-species\_\-number value's sign \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_0b49a61653d985585465515587b087ee}{
double \hyperlink{glbfunc_8h_0b49a61653d985585465515587b087ee}{AMAX4} (double a, double b, double c, double d)}
\label{glbfunc_8h_0b49a61653d985585465515587b087ee}

\begin{CompactList}\small\item\em e. Get the maximum from four \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_7bf26e1cff694aad68df394cb63c1a31}{
int \hyperlink{glbfunc_8h_7bf26e1cff694aad68df394cb63c1a31}{SymmetricInverse3x3} (double M\mbox{[}3\mbox{]}\mbox{[}3\mbox{]})}
\label{glbfunc_8h_7bf26e1cff694aad68df394cb63c1a31}

\begin{CompactList}\small\item\em f. Get the inverse of symmetric array \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_810e8e13a2409b115ead17fdf00760d1}{
double \hyperlink{glbfunc_8h_810e8e13a2409b115ead17fdf00760d1}{Kronecker} (int a, int b)}
\label{glbfunc_8h_810e8e13a2409b115ead17fdf00760d1}

\begin{CompactList}\small\item\em g. Kronecker delta \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_3cab9f4eb994d85cb307ef4ca698b923}{
double \hyperlink{glbfunc_8h_3cab9f4eb994d85cb307ef4ca698b923}{K\_\-sign} (int a, int b)}
\label{glbfunc_8h_3cab9f4eb994d85cb307ef4ca698b923}

\begin{CompactList}\small\item\em h. Sign function \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_3b0843a41bc641e5553d442b94b1f3e1}{
double \hyperlink{glbfunc_8h_3b0843a41bc641e5553d442b94b1f3e1}{compare} (int a, int b)}
\label{glbfunc_8h_3b0843a41bc641e5553d442b94b1f3e1}

\begin{CompactList}\small\item\em h. comparing \item\end{CompactList}\item 
\hypertarget{glbfunc_8h_21546457e67986c8772ab1ce75ab8e7a}{
double \hyperlink{glbfunc_8h_21546457e67986c8772ab1ce75ab8e7a}{sq} (double a)}
\label{glbfunc_8h_21546457e67986c8772ab1ce75ab8e7a}

\begin{CompactList}\small\item\em i. square \item\end{CompactList}\end{CompactItemize}
\subsection*{Variables}
\begin{CompactItemize}
\item 
const double \hyperlink{glbfunc_8h_43016d873124d39034edb8cd164794db}{pi} = 3.141592653589793
\begin{CompactList}\small\item\em Pi. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
\begin{Desc}
\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$  by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$, \end{Desc}

\subsection{Variable Documentation}
\hypertarget{glbfunc_8h_43016d873124d39034edb8cd164794db}{
\index{glbfunc.h@{glbfunc.h}!pi@{pi}}
\index{pi@{pi}!glbfunc.h@{glbfunc.h}}
\subsubsection[{pi}]{\setlength{\rightskip}{0pt plus 5cm}const double {\bf pi} = 3.141592653589793}}
\label{glbfunc_8h_43016d873124d39034edb8cd164794db}

Pi.

---------------------------------------------------------------------------------------- Define globle paremeters and functions \hyperlink{glbfunc_8h}{glbfunc.h} ----------------------------------------------------------------------------------------

### 2010-06-17 src/latex/hydrodynamics_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/diagose_8cpp.tex
@@
-\hypertarget{diagose_8cpp}{
-\section{diagose.cpp File Reference}
-\label{diagose_8cpp}\index{diagose.cpp@{diagose.cpp}}
+\hypertarget{hydrodynamics_8cpp}{
+\section{hydrodynamics.cpp File Reference}
+\label{hydrodynamics_8cpp}\index{hydrodynamics.cpp@{hydrodynamics.cpp}}
 }
@@
 
-Include dependency graph for diagose.cpp:\nopagebreak
+Include dependency graph for hydrodynamics.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{diagose_8cpp__incl}
+\includegraphics[width=420pt]{hydrodynamics_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/hydrodynamics_8h.tex
compressible branch

\hypertarget{hydrodynamics_8h}{
\section{hydrodynamics.h File Reference}
\label{hydrodynamics_8h}\index{hydrodynamics.h@{hydrodynamics.h}}
}
Definition of materials and their hydrodynamical interactions.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{hydrodynamics_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classHydrodynamics}{Hydrodynamics}
\begin{CompactList}\small\item\em Definition of materials and their hydrodynamical interactions. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Definition of materials and their hydrodynamical interactions.

### 2010-06-17 src/latex/index.tex
compressible branch

\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
SPH and SDPD 2D code\hypertarget{index_install_sec}{}\section{Installation}\label{index_install_sec}
Check the source code from github and compile

\begin{footnotesize}\begin{verbatim}
   git clone git://github.com/slitvinov/sph-blitz
   cd sph-blitz
   ./local-install.sh  \end{verbatim}
\end{footnotesize}
\hypertarget{index_restart_file}{}\section{Restart file format}\label{index_restart_file}
\hypertarget{index_input_file}{}\section{Input file format}\label{index_input_file}
\hypertarget{index_sim}{}\section{Runnig simulations}\label{index_sim}

\begin{footnotesize}\begin{verbatim}
   cd src
   ./sph ../cases/couette \end{verbatim}
\end{footnotesize}
 \hypertarget{index_post}{}\section{Postprocessing}\label{index_post}
To combine all time snapshots in one file

\begin{footnotesize}\begin{verbatim}
   cd outdata/
   ../../scripts/dat2punto.sh > punto.dat
 \end{verbatim}
\end{footnotesize}
\hypertarget{index_vis}{}\section{Visuzalization}\label{index_vis}
\hypertarget{index_vis_gnuplot}{}\subsection{gnuplot}\label{index_vis_gnuplot}
 \hypertarget{index_vis_punto}{}\subsection{punto}\label{index_vis_punto}

\begin{footnotesize}\begin{verbatim}
    punto -D 2 -c 4 -B 0:0:0.04:0.04 -G -0.6:0.6 -s 8 -lc black -bg white  punto.dat \end{verbatim}
\end{footnotesize}

### 2010-06-17 src/latex/initiation_8cpp.tex
compressible branch

\hypertarget{initiation_8cpp}{
\section{initiation.cpp File Reference}
\label{initiation_8cpp}\index{initiation.cpp@{initiation.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par

Include dependency graph for initiation.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{initiation_8cpp__incl}
\end{center}
\end{figure}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
\begin{Desc}
\item[Author:]author Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$ \end{Desc}

### 2010-06-17 src/latex/initiation_8h.tex
compressible branch

--- 2010-06-17 src/latex/hydrodynamics_8h.tex
@@
-\hypertarget{hydrodynamics_8h}{
-\section{hydrodynamics.h File Reference}
-\label{hydrodynamics_8h}\index{hydrodynamics.h@{hydrodynamics.h}}
+\hypertarget{initiation_8h}{
+\section{initiation.h File Reference}
+\label{initiation_8h}\index{initiation.h@{initiation.h}}
 }
-Definition of materials and their hydrodynamical interactions.
+Initiates the simulation.
 
@@
 \leavevmode
-\includegraphics[width=420pt]{hydrodynamics_8h__dep__incl}
+\includegraphics[width=420pt]{initiation_8h__dep__incl}
 \end{center}
@@
 \item 
-class \hyperlink{classHydrodynamics}{Hydrodynamics}
-\begin{CompactList}\small\item\em Definition of materials and their hydrodynamical interactions. \item\end{CompactList}\end{CompactItemize}
+class \hyperlink{classInitiation}{Initiation}
+\begin{CompactList}\small\item\em Initiates the simulation. \item\end{CompactList}\end{CompactItemize}
 
@@
 \subsection{Detailed Description}
-Definition of materials and their hydrodynamical interactions.
+Initiates the simulation.

### 2010-06-17 src/latex/interaction_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/diagose_8cpp.tex
@@
-\hypertarget{diagose_8cpp}{
-\section{diagose.cpp File Reference}
-\label{diagose_8cpp}\index{diagose.cpp@{diagose.cpp}}
+\hypertarget{interaction_8cpp}{
+\section{interaction.cpp File Reference}
+\label{interaction_8cpp}\index{interaction.cpp@{interaction.cpp}}
 }
@@
 
-Include dependency graph for diagose.cpp:\nopagebreak
+Include dependency graph for interaction.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{diagose_8cpp__incl}
+\includegraphics[width=420pt]{interaction_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/interaction_8h.tex
compressible branch

\hypertarget{interaction_8h}{
\section{interaction.h File Reference}
\label{interaction_8h}\index{interaction.h@{interaction.h}}
}
Defines interaction between particles.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{interaction_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classInteraction}{Interaction}
\begin{CompactList}\small\item\em Defines interaction between particles. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Defines interaction between particles.

### 2010-06-17 src/latex/kernel_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/dllist_8h.tex
@@
-\hypertarget{dllist_8h}{
-\section{dllist.h File Reference}
-\label{dllist_8h}\index{dllist.h@{dllist.h}}
+\hypertarget{kernel_8cpp}{
+\section{kernel.cpp File Reference}
+\label{kernel_8cpp}\index{kernel.cpp@{kernel.cpp}}
 }
-Double linked list implementation.
+the abstract kernel base class
 
-This graph shows which files directly or indirectly include this file:\nopagebreak
+{\tt \#include $<$iostream$>$}\par
+{\tt \#include $<$cstdlib$>$}\par
+{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
+{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par
+
+Include dependency graph for kernel.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{dllist_8h__dep__incl}
+\includegraphics[width=420pt]{kernel_8cpp__incl}
 \end{center}
 \end{figure}
-\subsection*{Classes}
-\begin{CompactItemize}
-\item 
-class \hyperlink{classLlistNode}{LlistNode$<$ Ldata $>$}
-\begin{CompactList}\small\item\em A template node in the linked list. \item\end{CompactList}\item 
-class \hyperlink{classLlist}{Llist$<$ Ldata $>$}
-\begin{CompactList}\small\item\em Double linked list implementation. \item\end{CompactList}\end{CompactItemize}
 
@@
 \subsection{Detailed Description}
-Double linked list implementation.
+the abstract kernel base class
 
@@
 
-changes by: Andreas Mattes Declares and defines a generic double linked list template \end{Desc}
+changes by: Andreas Mattes \end{Desc}

### 2010-06-17 src/latex/material_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/diagose_8cpp.tex
@@
-\hypertarget{diagose_8cpp}{
-\section{diagose.cpp File Reference}
-\label{diagose_8cpp}\index{diagose.cpp@{diagose.cpp}}
+\hypertarget{material_8cpp}{
+\section{material.cpp File Reference}
+\label{material_8cpp}\index{material.cpp@{material.cpp}}
 }
@@
 {\tt \#include $<$cstdlib$>$}\par
+{\tt \#include $<$cmath$>$}\par
 {\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
@@
 
-Include dependency graph for diagose.cpp:\nopagebreak
+Include dependency graph for material.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{diagose_8cpp__incl}
+\includegraphics[width=420pt]{material_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/mls_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/interaction_8cpp.tex
@@
-\hypertarget{interaction_8cpp}{
-\section{interaction.cpp File Reference}
-\label{interaction_8cpp}\index{interaction.cpp@{interaction.cpp}}
+\hypertarget{mls_8cpp}{
+\section{mls.cpp File Reference}
+\label{mls_8cpp}\index{mls.cpp@{mls.cpp}}
 }
@@
 
-Include dependency graph for interaction.cpp:\nopagebreak
+Include dependency graph for mls.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{interaction_8cpp__incl}
+\includegraphics[width=420pt]{mls_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/mls_8h.tex
compressible branch

--- 2010-06-17 src/latex/betaspline_8h.tex
@@
-\hypertarget{betaspline_8h}{
-\section{betaspline.h File Reference}
-\label{betaspline_8h}\index{betaspline.h@{betaspline.h}}
+\hypertarget{mls_8h}{
+\section{mls.h File Reference}
+\label{mls_8h}\index{mls.h@{mls.h}}
 }
-Beta spline kernel function.
 
@@
 \leavevmode
-\includegraphics[width=420pt]{betaspline_8h__dep__incl}
+\includegraphics[width=420pt]{mls_8h__dep__incl}
 \end{center}
@@
 \item 
-class \hyperlink{classBetaSpline}{BetaSpline}
-\begin{CompactList}\small\item\em A concrete kernel class. \item\end{CompactList}\end{CompactItemize}
+class \hyperlink{classMLS}{MLS}
+\begin{CompactList}\small\item\em Moving Least Squares (\hyperlink{classMLS}{MLS}) class. \item\end{CompactList}\end{CompactItemize}
 
@@
 \subsection{Detailed Description}
-Beta spline kernel function.
+contains \hyperlink{classMLS}{MLS} class

### 2010-06-17 src/latex/output_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/mls_8cpp.tex
@@
-\hypertarget{mls_8cpp}{
-\section{mls.cpp File Reference}
-\label{mls_8cpp}\index{mls.cpp@{mls.cpp}}
+\hypertarget{output_8cpp}{
+\section{output.cpp File Reference}
+\label{output_8cpp}\index{output.cpp@{output.cpp}}
 }
@@
 
-Include dependency graph for mls.cpp:\nopagebreak
+Include dependency graph for output.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{mls_8cpp__incl}
+\includegraphics[width=420pt]{output_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/particle_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/output_8cpp.tex
@@
-\hypertarget{output_8cpp}{
-\section{output.cpp File Reference}
-\label{output_8cpp}\index{output.cpp@{output.cpp}}
+\hypertarget{particle_8cpp}{
+\section{particle.cpp File Reference}
+\label{particle_8cpp}\index{particle.cpp@{particle.cpp}}
 }
-{\tt \#include $<$iostream$>$}\par
-{\tt \#include $<$fstream$>$}\par
-{\tt \#include $<$string$>$}\par
-{\tt \#include $<$cstdio$>$}\par
-{\tt \#include $<$cstdlib$>$}\par
 {\tt \#include \char`\"{}glbcls.h\char`\"{}}\par
@@
 
-Include dependency graph for output.cpp:\nopagebreak
+Include dependency graph for particle.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{output_8cpp__incl}
+\includegraphics[width=420pt]{particle_8cpp__incl}
 \end{center}
@@
 
-changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$, \end{Desc}
+changes by: \end{Desc}

### 2010-06-17 src/latex/particlemanager_8h.tex
compressible branch

\hypertarget{particlemanager_8h}{
\section{particlemanager.h File Reference}
\label{particlemanager_8h}\index{particlemanager.h@{particlemanager.h}}
}
particle manager

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{particlemanager_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classParticleManager}{ParticleManager}
\begin{CompactList}\small\item\em \hyperlink{classParticle}{Particle} manager class. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
particle manager

### 2010-06-17 src/latex/quinticspline_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/output_8cpp.tex
@@
-\hypertarget{output_8cpp}{
-\section{output.cpp File Reference}
-\label{output_8cpp}\index{output.cpp@{output.cpp}}
+\hypertarget{quinticspline_8cpp}{
+\section{quinticspline.cpp File Reference}
+\label{quinticspline_8cpp}\index{quinticspline.cpp@{quinticspline.cpp}}
 }
@@
 
-Include dependency graph for output.cpp:\nopagebreak
+Include dependency graph for quinticspline.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{output_8cpp__incl}
+\includegraphics[width=420pt]{quinticspline_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/sph_8cpp.tex
compressible branch

\hypertarget{sph_8cpp}{
\section{sph.cpp File Reference}
\label{sph_8cpp}\index{sph.cpp@{sph.cpp}}
}
{\tt \#include $<$iostream$>$}\par
{\tt \#include $<$fstream$>$}\par
{\tt \#include $<$string$>$}\par
{\tt \#include $<$cstdio$>$}\par
{\tt \#include $<$cstdlib$>$}\par
{\tt \#include $<$ctime$>$}\par
{\tt \#include $<$cmath$>$}\par
{\tt \#include \char`\"{}glbfunc.h\char`\"{}}\par
{\tt \#include \char`\"{}glbcls.h\char`\"{}}\par

Include dependency graph for sph.cpp:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{sph_8cpp__incl}
\end{center}
\end{figure}
\subsection*{Functions}
\begin{CompactItemize}
\item 
int \hyperlink{sph_8cpp_0ddf1224851353fc92bfbff6f499fa97}{main} (int argc, char $\ast$argv\mbox{[}$\,$\mbox{]})
\begin{CompactList}\small\item\em The main program. \item\end{CompactList}\end{CompactItemize}
\subsection*{Variables}
\begin{CompactItemize}
\item 
\hypertarget{sph_8cpp_a50583a118c0a3e801d3e48a45b6a259}{
double \hyperlink{sph_8cpp_a50583a118c0a3e801d3e48a45b6a259}{k\_\-bltz} = 1.380662e-023}
\label{sph_8cpp_a50583a118c0a3e801d3e48a45b6a259}

\begin{CompactList}\small\item\em Bltzmann constant, will be non-dimensionalized in the program. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
\begin{Desc}
\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$

changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$

changes by: Andreas Mattes \end{Desc}

\subsection{Function Documentation}
\hypertarget{sph_8cpp_0ddf1224851353fc92bfbff6f499fa97}{
\index{sph.cpp@{sph.cpp}!main@{main}}
\index{main@{main}!sph.cpp@{sph.cpp}}
\subsubsection[{main}]{\setlength{\rightskip}{0pt plus 5cm}int main (int {\em argc}, \/  char $\ast$ {\em argv}\mbox{[}$\,$\mbox{]})}}
\label{sph_8cpp_0ddf1224851353fc92bfbff6f499fa97}

The main program.

Starts the initialization methods and contains the main computation loop \begin{Desc}
\item[Parameters:]
\begin{description}
\item[{\em argc}]The number of command line arguments, should be two: program name (by default) and project name \item[{\em argv}]The command line arguments array: by default program name at first position (index 0), and then the project( which is specified when calling the program name (e.g. s./sph ../cases/couette) at index 1 \end{description}
\end{Desc}

\par
 {\bf below the rough structure of the main function:}

initializations

\begin{itemize}
\item global initialization (by defining an object of class \hyperlink{classInitiation}{Initiation} (initialization \char`\"{}automatically\char`\"{} done at this moment (from .cfg or .rst file) by constructor method of \hyperlink{classInitiation}{Initiation} class. That is by the way the reason why the initiation::initiation method does not figure in the call grapf of the main function (constructors are not shwon there)\end{itemize}

\begin{itemize}
\item initiate the weight function\end{itemize}

\begin{itemize}
\item initiate the Moving Least Squares approximation\end{itemize}

\begin{itemize}
\item initiate the particle manager\end{itemize}

\begin{itemize}
\item create materials, forces and real particles\end{itemize}

\begin{itemize}
\item initiate boundary conditions and boundary particles\end{itemize}

\begin{itemize}
\item initialize the time solver\end{itemize}

\begin{itemize}
\item initialize output class (should be the last to be initialized)\end{itemize}

\par
 computation loop starts

\begin{itemize}
\item call the time slover (who iterates over one output time interval)\end{itemize}

\begin{itemize}
\item output results after a time interval\par
\par
 \end{itemize}

Here is the call graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{sph_8cpp_0ddf1224851353fc92bfbff6f499fa97_cgraph}
\end{center}
\end{figure}

### 2010-06-17 src/latex/timesolver_8cpp.tex
compressible branch

--- 2010-06-17 src/latex/output_8cpp.tex
@@
-\hypertarget{output_8cpp}{
-\section{output.cpp File Reference}
-\label{output_8cpp}\index{output.cpp@{output.cpp}}
+\hypertarget{timesolver_8cpp}{
+\section{timesolver.cpp File Reference}
+\label{timesolver_8cpp}\index{timesolver.cpp@{timesolver.cpp}}
 }
@@
 
-Include dependency graph for output.cpp:\nopagebreak
+Include dependency graph for timesolver.cpp:\nopagebreak
 \begin{figure}[H]
@@
 \leavevmode
-\includegraphics[width=420pt]{output_8cpp__incl}
+\includegraphics[width=420pt]{timesolver_8cpp__incl}
 \end{center}

### 2010-06-17 src/latex/timesolver_8h.tex
compressible branch

\hypertarget{timesolver_8h}{
\section{timesolver.h File Reference}
\label{timesolver_8h}\index{timesolver.h@{timesolver.h}}
}
Time solver class.

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{timesolver_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classTimeSolver}{TimeSolver}
\begin{CompactList}\small\item\em Time solver class. \item\end{CompactList}\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Time solver class.

provides methods that iterate over one output time interval (D\_\-time) either with the summation density approach or with the continuity density approach

### 2010-06-17 src/latex/vec2d_8h.tex
compressible branch

\hypertarget{vec2d_8h}{
\section{vec2d.h File Reference}
\label{vec2d_8h}\index{vec2d.h@{vec2d.h}}
}
Define 2-d vectors and associated operations.

{\tt \#include $<$cmath$>$}\par
{\tt \#include $<$blitz/tinyvec.h$>$}\par
{\tt \#include $<$blitz/tinyvec-et.h$>$}\par

Include dependency graph for vec2d.h:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=141pt]{vec2d_8h__incl}
\end{center}
\end{figure}

This graph shows which files directly or indirectly include this file:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=420pt]{vec2d_8h__dep__incl}
\end{center}
\end{figure}
\subsection*{Typedefs}
\begin{CompactItemize}
\item 
\hypertarget{vec2d_8h_268cbe88997e7b383a3f73ea7b5822aa}{
typedef TinyVector$<$ double, 2 $>$ \textbf{Vec2d}}
\label{vec2d_8h_268cbe88997e7b383a3f73ea7b5822aa}

\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
\hypertarget{vec2d_8h_d4fd110790320d1dd8d63411159b4d9c}{
double \hyperlink{vec2d_8h_d4fd110790320d1dd8d63411159b4d9c}{v\_\-abs} (const Vec2d \&v)}
\label{vec2d_8h_d4fd110790320d1dd8d63411159b4d9c}

\begin{CompactList}\small\item\em Return the absolute value of the vector (the length). \item\end{CompactList}\item 
\hypertarget{vec2d_8h_ce785ede99492e5a2e149d4a9a6521af}{
double \hyperlink{vec2d_8h_ce785ede99492e5a2e149d4a9a6521af}{v\_\-sq} (const Vec2d \&v)}
\label{vec2d_8h_ce785ede99492e5a2e149d4a9a6521af}

\begin{CompactList}\small\item\em Return the square sum of the vector values. \item\end{CompactList}\item 
\hypertarget{vec2d_8h_59971685b370dc9fe915f7d3ae23bf3b}{
double \hyperlink{vec2d_8h_59971685b370dc9fe915f7d3ae23bf3b}{v\_\-sqdiff} (const Vec2d \&v)}
\label{vec2d_8h_59971685b370dc9fe915f7d3ae23bf3b}

\begin{CompactList}\small\item\em Return the square difference of the vector values. \item\end{CompactList}\item 
double \hyperlink{vec2d_8h_977aa48c7b1ffeff460162482c21e2c4}{v\_\-distance} (const Vec2d \&va, const Vec2d \&vb)
\begin{CompactList}\small\item\em Return the distance of two points given as vectors. \item\end{CompactList}\item 
\hypertarget{vec2d_8h_5b8cbe588276a9c63c1fdc5322ec877e}{
void \hyperlink{vec2d_8h_5b8cbe588276a9c63c1fdc5322ec877e}{perodic\_\-position} (Vec2d \&va, const Vec2d \&vb, const Vec2d \&perodic)}
\label{vec2d_8h_5b8cbe588276a9c63c1fdc5322ec877e}

\begin{CompactList}\small\item\em Return the perodic position. \item\end{CompactList}\item 
\hypertarget{vec2d_8h_22f4e97ed7ca9e188dc4e074a1b2e5a7}{
double \textbf{sqr} (double x)}
\label{vec2d_8h_22f4e97ed7ca9e188dc4e074a1b2e5a7}

\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Define 2-d vectors and associated operations.

\begin{Desc}
\item[Author:]Xiangyu Hu $<$\href{mailto:Xiangyu.Hu@aer.mw.tum.de}{\tt Xiangyu.Hu@aer.mw.tum.de}$>$

changes by: Martin Bernreuther $<$\href{mailto:Martin.Bernreuther@ipvs.uni-stuttgart.de}{\tt Martin.Bernreuther@ipvs.uni-stuttgart.de}$>$

changes by: Andreas Mattes \end{Desc}

\subsection{Function Documentation}
\hypertarget{vec2d_8h_977aa48c7b1ffeff460162482c21e2c4}{
\index{vec2d.h@{vec2d.h}!v\_\-distance@{v\_\-distance}}
\index{v\_\-distance@{v\_\-distance}!vec2d.h@{vec2d.h}}
\subsubsection[{v\_\-distance}]{\setlength{\rightskip}{0pt plus 5cm}double v\_\-distance (const Vec2d \& {\em va}, \/  const Vec2d \& {\em vb})\hspace{0.3cm}{\tt  \mbox{[}inline\mbox{]}}}}
\label{vec2d_8h_977aa48c7b1ffeff460162482c21e2c4}

Return the distance of two points given as vectors.

return v\_\-abs(va-vb); double dx=va\mbox{[}0\mbox{]}-vb\mbox{[}0\mbox{]}; double dy=va\mbox{[}1\mbox{]}-vb\mbox{[}1\mbox{]};

Here is the caller graph for this function:\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=408pt]{vec2d_8h_977aa48c7b1ffeff460162482c21e2c4_icgraph}
\end{center}
\end{figure}

### 2010-06-17 src/boundary.h

@@ -1,5 +1,3 @@
-#ifndef BOUNDARY_H
-#define BOUNDARY_H
 /// \file boundary.h
 /// \brief Bonudary conditions
 
@@ -91,5 +89,3 @@ public:
 	///check particle if particle run out of the computational domain
 	void RunAwayCheck(Hydrodynamics &hydro);
 };
-
-#endif //BOUNDARY_H

### 2010-06-17 src/bskernel.cpp

@@ -1,0 +1,129 @@
+/// \file bskernel.cpp
+/// \author Xiangyu Hu <Xiangyu.Hu@aer.mw.tum.de>
+///\author changes by: Martin Bernreuther <Martin.Bernreuther@ipvs.uni-stuttgart.de>, 
+
+//----------------------------------------------------------------------------------------
+//      A concrete kernel class
+//		see Monaghan & Lattanzio (1985).
+//		Most often used kernel.
+//		bskernel.cpp
+//----------------------------------------------------------------------------------------
+
+// ***** system includes *****
+#include <iostream>
+#include <fstream>
+#include <string>
+
+#include <cstdio>
+#include <cstdlib>
+#include <cmath>
+
+//local includes
+#include "glbcls.h"
+#include "glbfunc.h"
+
+using namespace std;
+
+//----------------------------------------------------------------------------------------
+//							constructor
+//----------------------------------------------------------------------------------------
+BetaSpline::BetaSpline(double smoothingLength)
+    : Kernel(smoothingLength)
+{
+    ///-  initialize the auxiliary factors
+    reciprocH = 1.0 / smoothingLength;
+    
+      ///- normalize to 1.0
+	norm = 40.0 / 7.0 / pi;
+      
+    factorW     = norm * pow(reciprocH, 2);
+    factorGradW = - 6.0 * norm * pow(reciprocH, 3);
+    
+    // a comment on the gradW sign:
+    // In Speith (3.21) gradW has a minus in front!
+    // This is the one before the 6.0 * ...
+}
+//----------------------------------------------------------------------------------------
+// Calculates the kernel value for the given distance of two particles
+// We take this from Monaghan & Lattenzio (1985)
+// but used a doubled smoothing length for the definition of the interaction radius.
+//----------------------------------------------------------------------------------------
+double BetaSpline::w(double distance) const
+{
+    // dist/smoothingLength is often needed
+    double normedDist = distance * reciprocH;
+
+    // the beta-spline is composed of three functions, so we must determine, were we are
+    if (normedDist < 0.5) 
+    // we are in the inner region of the kernel
+    {
+        return factorW * (6.0 * normedDist * normedDist * normedDist - 
+                            6.0 * normedDist * normedDist + 1.0);
+    }
+    else if (normedDist < 1.0)
+    // we are in the outer region of the kernel (not outside!)
+    {
+        double aux = 1.0 - normedDist;
+        return factorW * ( 2.0 * aux * aux * aux );
+    }
+    else
[…]

### 2010-06-17 src/cubicspline1D.h

@@ -1,0 +1,47 @@
+/// \file cubicspline1D.h 
+/// \brief  cubic spline kernel 1D
+
+/// cubicspline1D class
+class cubicspline1D : public Kernel
+{
+
+public:
+
+  ///constructor to initialize the data members (auxiliary factors for kernel calculation)
+  cubicspline1D(const double smoothingLength);
+  
+  ///\brief Calculates the kernel value for the given distance of two particles
+  ///
+  /// We take this from Morris, Fox and Zhu (1997)
+  /// but used a tripled smoothing length for the definition of the interaction radius.
 
+  virtual double w(const double distance) const;
+  
+  ///\brief Calculates the kernel derivation  for the given distance of two particles 
+  ///
+  /// We take this from Morris, Fox and Zhu (1997)
+  /// but used a tripled smoothing length for the definition of the interaction radius.
+  virtual Vec2d gradW(const double distance, const Vec2d& distanceVector) const;
+  
+  ///Calculates the kernel derivation (a double, not a vector) to distance
+  double F(const double distance) const;
+
+  ///Calculates the kernel Laplacian
+  double LapW(const double distance) const;
+
+private:
+    ///Normalization factor
+    const double norm;
+
+    ///Auxiliary factors for intermediate results: The inverse smoothing length
+    double reciprocH;
+
+    ///Auxiliary factors for intermediate results: A pre-factor for w 
+    double factorW;
+
+    ///Auxiliary factors for intermediate results: A pre-factor for grad w
+    double factorGradW;
+
+    ///Auxiliary factors for Laplacian
+    double factorLapW;
+
+};

### 2010-06-17 src/initiation.h

@@ -1,5 +1,3 @@
-#ifndef INITIATION_H
-#define INITIATION_H
 /// \file initiation.h 
 /// \brief Initiates the simulation
 
@@ -38,7 +36,8 @@ public:
 	int diagnose;
 	///artificial viscosity
 	double art_vis;
-
+	///simulation mode (1:liquids, 2: gas dynamics)
+	int simu_mode;
 	///smoothinglength
 	double smoothinglength;
 	///the compuational domain size
@@ -113,5 +112,3 @@ public:
 	double dms_surface(double sigma_non);///<a re-dimensionalize method
 
 };
-
-#endif //INITIATION_H

### 2010-06-17 src/interaction.h

@@ -1,5 +1,3 @@
-#ifndef INTERACTION_H
-#define INTERACTION_H
 /// \file interaction.h 
 /// \brief Defines interaction between particles
 
@@ -9,10 +7,16 @@ class Interaction {
 	///total number of materials
 	static int number_of_materials;
 	static double smoothinglength;
-	///particle distance
+        ///particle distance
 	static double delta;
 	///artificial viscosity
 	static double art_vis;
+	///simulation mode
+       static int simu_mode;
+       static double alpha_artVis;///<factor for Monaghan Artificial viscosity
+       static double beta_artVis;///<factor for Monaghan Artificial viscosity
+       static double epsilon_artVis;///<factor for Monaghan Artificial viscosity
+
 
 	//particle pair
 	Particle *Org;	///<pointer to particle with larger ID (of particle pair)
@@ -31,6 +35,12 @@ class Interaction {
 	double etaj;///<viscosity for particle j
 	double zetaj;///<<b>!!!question!!!<b>other viscosity for particle???
 
+	double hij;///averaged smoothing length
+	double cij;///averaged sound speed
+	double rhoij;///averaged density
+	double phiij;///parameter for monaghan artificial viscosity
+	double piij;///Monaghan artificial viscosity
+
 	//distance between the two particles, weight and derivatives
 	double rij;///<distance between 2 particles
         double rrij;///< reciprocal value of distance between 2 particles
@@ -38,6 +48,7 @@ class Interaction {
         double Fij;///<<b>!!!question!!!<b>
         double LapWij;///<<b>!!!question!!!<b>
         double Wij2;///<<b>!!!question!!!<b>
+	Vec2d gradWij;///kernel gradient
 	Vec2d eij; ///<pair direction from orginal particle to destination particle 
 	double shear_rij ;///<particle length to implement slip boundary<<b>!!!question!!!<b>
 	double bulk_rij; ///<particle length to implement slip boundary<<b>!!!question!!!<b>
@@ -113,7 +124,9 @@ public:
 	void RandomForces(Wiener &wiener, double sqrtdt);
 	///update random forces with Espanol's method
 	void RandomForces_Espanol(Wiener &wiener, double sqrtdt);
-	
-};
+	Particle* getOrigin();
+	Particle* getDest();
+	double getWij();
+	Vec2d getGradWij();
 
-#endif //INTERACTION_H
+};

### 2010-06-17 src/kernel.h

@@ -1,5 +1,3 @@
-#ifndef KERNEL_H
-#define KERNEL_H
 /// \file kernel.h 
 /// \brief Kernel abstract base
 
@@ -27,5 +25,3 @@ protected:
     ///A local copy of the smoothing length
     const double smoothingLength;
 };
-
-#endif //KERNEL_H

### 2010-06-17 src/material.h

@@ -1,5 +1,3 @@
-#ifndef MATERIAL_H
-#define MATERIAL_H
 /// \file material.h 
 /// \brief Material 
 
@@ -53,16 +51,17 @@ public:
 	//equation of states
 
 	///get pressure
-	double get_p(double rho);
+	double get_p(double rho);// equation of state for liquids
+	double get_p(double rho, double e);//equation of state for gasdynamics
 	///get rho from pressure
-	double get_rho(double p);
+	double get_rho(double p);// equation of state for liquids
+	double get_rho(double p, double e);//equation of state for gasdynamics
 	///get interal energy
 	double get_e(double T);
-	///get temperature (function is defined nowhere)
-	double get_T(double e);
+	///get temperature 
+	double get_T(double e);//(function is defined nowhere)
+	double get_T(double p, double rho);
 	///get sound speed
 	double get_Cs(double p, double rho);
 
 };
-
-#endif //MATERIAL_H

### 2010-06-17 src/particle.cpp

@@ -81,7 +81,7 @@ Particle::Particle(Vec2d position, Vec2d velocity, double density, double pressu
 	rho = density; p = pressure; T = temperature; Cs = mtl->get_Cs(p, rho);
 	U = velocity; U_I = U;
 	
-	///- set conservative values and their  intermediate values
+	///- set conservative values (mass and volume determined lateron) and their  intermediate values
 	m = 0.0; V = 0.0; e = mtl->get_e(T); e_I = e;
 	R_I = R; P_I = P; rho_I = rho;
 	P_n = P; U_n = U; rho_n = rho; e_n = e; 
@@ -227,6 +227,7 @@ void Particle::StatesCopier(Particle &RealParticle, int type)
 	R = RealParticle.R; m = RealParticle.m;
 	rho = RealParticle.rho; V = RealParticle.V;
 	p = RealParticle.p; T = RealParticle.T;
+	e = RealParticle.e;
 	rho_I = RealParticle.rho_I;
 	Cs =RealParticle.Cs; U = RealParticle.U; U_I = RealParticle.U_I;
 	ShearRate_x = RealParticle.ShearRate_x, ShearRate_y = RealParticle.ShearRate_y;

### 2010-06-17 src/particle.h

@@ -1,5 +1,3 @@
-#ifndef PARTICLE_H
-#define PARTICLE_H
 /// \file partilce.h 
 /// \brief a sph particle
 
@@ -110,5 +108,3 @@ public:
 	Vec2d  nrml;///<for wall boundary particles
 
 };
-
-#endif //PARTICLE_H

### 2010-06-17 src/particlemanager.h

@@ -1,5 +1,3 @@
-#ifndef PARTICLEMANAGER_H
-#define PARTICLEMANAGER_H
 /// \file particlemanager.h 
 /// \brief particle manager
 
@@ -14,6 +12,7 @@ class ParticleManager
 	double cll_sz; ///<cell size
 	Vec2d box_size; ///<computational domain size
 	int initial_condition; ///<initial condition marker
+	int simu_mode;///<simulation mode
 	double delta; ///<the inital particle distance
 	int hdelta; ///<the ration between smoothing length and inital particle distance
 	Vec2d U0; ///<inital flow speed
@@ -59,5 +58,3 @@ public:
 						Force **forces, QuinticSpline &weight_function);
 	
 };
-
-#endif //PARTICLEMANAGER_H

### 2010-06-17 src/quinticspline.cpp

@@ -18,6 +18,8 @@
 #include <cstdlib>
 #include <cmath>
 
+#include <math.h>
+
 //local includes
 #include "glbcls.h"
 #include "glbfunc.h"
@@ -27,16 +29,19 @@ using namespace std;
 //----------------------------------------------------------------------------------------
 //										constructor
 //----------------------------------------------------------------------------------------
+
+/*
+
 QuinticSpline::QuinticSpline(const double smoothingLength)
   : Kernel(smoothingLength), 
-    norm(63.0 / 478.0 / pi)
+    norm(/*63.0 / 478.0 / pi  360)
 {
   // initialize the auxiliary factors
     reciprocH = 1.0 / smoothingLength;
       
-    factorW     = norm * pow(reciprocH, 2);
-    factorGradW = 15.0*norm * pow(reciprocH, 3);
-    factorLapW = 15.0*12.0*norm * pow(reciprocH, 4);
+      factorW     = norm * pow(reciprocH,1/* 2 );
+	factorGradW = 15.0*norm * pow(reciprocH,2/* 3 /);
+	  factorLapW = 15.0*12.0*norm * pow(reciprocH,3/* 4 /);
 
     // a comment on the gradW sign:
     // The gradW has a minus in front!
@@ -188,4 +193,147 @@ double QuinticSpline::LapW(const double distance) const
 
 
 
+
+
+*/
+QuinticSpline::QuinticSpline(const double smoothingLength)
+  : Kernel(smoothingLength), 
+    norm(1)
+{
+  // initialize the auxiliary factors
+
+
+  h =smoothingLength/2;//factor two as the use ofsmoothinglength within this program is not consistent with its actula definition
+	double alphaD=1/h; //coefficient for cubic spline kernel in 1D (see Liu eq(3.6), page 64)
+
+ }
+//----------------------------------------------------------------------------------------
+// Calculates the kernel value for the given distance of two particles
+//----------------------------------------------------------------------------------------
+double QuinticSpline::w(const double distance) const
+{
+	double alphaD=1/h; //coefficient for cubic spline kernel in 1D (see Liu eq(3.6), page 64)
+	double R= distance/h;
+	double W;
+if(R>2)//support of 4h, everything beyond is zero
+	{
+		W=0;
+	}
+	else if(R<1)
+	{
+		W=(double)2/3-pow(R,2)+0.5*pow(R,3); //attention: the "^"symbol does NOT mean "exponent"!!!
+	}
[…]

### 2010-06-17 src/quinticspline.h

@@ -1,5 +1,3 @@
-#ifndef QUINTICSPLINE_H
-#define QUINTICSPLINE_H
 /// \file quinticspline.h 
 /// \brief Quintic spline kernel
 
@@ -37,6 +35,9 @@ private:
     ///Auxiliary factors for intermediate results: The inverse smoothing length
     double reciprocH;
 
+    ///smoothing length
+    double h;
+   
     ///Auxiliary factors for intermediate results: A pre-factor for w 
     double factorW;
 
@@ -47,5 +48,3 @@ private:
     double factorLapW;
 
 };
-
-#endif //QUINTICSPLINE_H

### 2010-06-17 src/vec2d.h

@@ -1,10 +1,11 @@
-#ifndef VEC2D_H
-#define VEC2D_H
 /// \file vec2d.h
 /// \author Xiangyu Hu <Xiangyu.Hu@aer.mw.tum.de>
 /// \author changes by: Martin Bernreuther <Martin.Bernreuther@ipvs.uni-stuttgart.de>
 /// \author changes by: Andreas Mattes
 /// \brief Define 2-d vectors and associated operations
+
+#ifndef VEC2D_H
+#define VEC2D_H
 
 #include <cmath>
 #include <blitz/tinyvec.h>
@@ -195,10 +196,9 @@ inline void perodic_position(Vec2d &va, const Vec2d &vb, const Vec2d &perodic)
 
 }
 
-/// return square of x
-inline double sqr(const double x) {
+inline double sqr(double x) {
 	return x*x;
 }
 
 
-#endif //VEC2D_H
+#endif

### 2010-06-22 ms/main.tex
Add a figure to MS template
Add a program listiong example
including new cfg file

@@
 \usepackage{graphicx}
+\usepackage{listings}
 %\usepackage{fullpage}
@@
 \label{sec:intro}
-To test bibliography~\cite{Monaghan2005}
+
+This work aimes at the numerical simluation of high enthalpy flow in
+porosities. The subject is of interest, as CITATION
+NEEDED (Prof Hornung) has discovered porous surfaces to inhibit/block a
+certain form of instabilities in hypersonic flows over a body/cone. A numerical
+simulation of this configuration is desired to furnish data for a detailed
+analysis of the acting phenomena. The simulation method of choice for the first approach
+to this configuration is called Smoothed Particle Hydrodynamics (SPH).Although
+there has been no known application of SPH to this precise/concrete case yet/before,
+SPH is adopted, as it promises a crucial advantage in the way boundary
+conditions are implemented. And for the treatment of porosities,
+boundaries/walls represent a non negligible part of the problem.
+
+SPH designates a meshfree method for numerical simulation of particle
+ensembles (respectively matter that can be modelled as an ensemble of
+particles as it is the case for fluids).
+Thereby,the term particle ensembles not only refers
+to fluids (as the name of the method would suggest) but also to solids. In
+fact nowadays SPH is employed to simulate problems in different fields,
+such as body elasticity and fracture,liquid flows and gas
+dynamics~\cite{Monaghan2005}.
+The initial developement of the method dates back to 1977, where Gingold and
+Monaghan tempted to compute an astrophysical problem with a new, more
+efficient method~\cite{Gingold1977}. Independently and simultaneously, work in
+this field was also carried out by Lucy who came up with the same
+idea~\cite{Lucy1977}.
+ADVANTAGES???DISADVANTAGES???
+
+PREVIOUS APPLICATIONS IN GAS DYNAMICS (citing different relevant papers)
+
+OTHER APPROACHES FOR CAVITY/POROSITY SIMULATION (look up in literature)
 
@@
 \label{sec:method}
+\section{Basic Idea of SPH}
+\label{sec:BasicsSPH}
+
+To illustrate the basic idea of SPH, it is helpful to first have a look at the
+ruling equations of fluid dynamics, here represented by the SPH equations in
+lagrangian form. The use of the lagrangian form seems logical as SPH is a
+particle method.
+
+\begin {equation}
+NAVIER STOKES IN LAGRANGIAN FORM
+\end {equation}
+
+The above equations have the form~\cite{Monaghan2005}
+
+\begin {equation}
+\label{eq:EFD_form}
+{dA(r)\over dt}=f(A(r),\nabla A(r),r)
+\end {equation}
+where
+\begin {equation}
+{d(.)\over dt}={\partial(.)\over \partial t}+v\nabla(.)
+\end{equation}
+
+Thus the rates of change of  physical quantity depend on its spatial
+derivatives. The goal of any method for numerical simulation is to approximate
+these derivatives by information of a discrete number of points in order for a
+computer to be able to handle it.
+
+The SPH method is based on the idea of approximating a function $A(x)$ by an
+integral interpolant
+\begin{equation}
+\label{eq:int_interpolant}
+A_I(x)=\int A(r')W(r-r',h)dr'
+\end{equation}
+where $W(r-r',h)$ is the so called kernel or smoothing function and $h$ the
+smoothing length. This Interpolation is exact, if $W$ is the delta function,
+otherwise it describes/represents an approximation. As the theoretically
+perfect Kernel, the delta function, is of no practical use, the Kernels
+employed in practice are functions which tend to the delta function, when $h$
+tends to zero. Examples for those kernel functions are a Gaussian Kernel or
+Kernels based on Schoenbergs~\cite{Schoenberg1946} $M_n$ splines~\cite{Monaghan2005}. More details on Kernels are given in the section
+(LINK TO SECTION??) and in the book on SPH published by Liu~\cite{Liu2003}
+
+The fact of using a kernel different from the delta function constitutes/is the
+first of two approximations /approximative assumptions made for the SPH
+method. It is often refered to as kernel approximation~\cite{Liu2003}.
+The second approximation consists of a discretization of the integral
+expression in equation\ref{eq:int_interpolant}, leading to a summation over
+all discretized elements (the particles) of the domain instead
+of an integration when calculating the interpolant value $A_I(x)$, which
+finally allows a treatment of the problem by a numerical machine. In SPH
+literature, this second approximation is commonly called particle
+approximation~\cite{Liu2003}
+
+Applying the particle approximation on \ref{eq:int_interpolant} leads with the
+relation between mass, density and volume for each discretized particle
+\begin{equation}
+m_i=\rho_i V_i
+\end{equation}
+ to the following expression
+
+\begin{equation}
+A_S(r)=\sum_b m_b \frac{A_b}{\rho_b}W(r-r_b,h)
+\end{equation}
+
+In the same way, the derivative of the fieldfunction $frac{dA(x)}{dx}$ can be
+approximated to give\cite{Monaghan2005}or\cite{Liu2003}(in Liu with gradient,
+im Monaghan for 1 direction)
+
+\begin{equation}
+\label{eq:simpleDerivative}
+\nabla A_S(r)=\sum_b m_b \frac{A_b}{\rho_b}\nabla W(r-r_b,h)
+\end{equation}
+
+The disadvantage of the above equation \ref{eq:simpleDerivative} is, that for
+$A(r)=const.$ the approximated derivative does not vanish. By writing (in
+Monaghan the equation figures not with gradient but only in 1 direction!?!)
+\begin{equation}
+\label{eq:derivativeIdentity}
+\nabla A = \frac{1}{\Phi}(\nabla {\Phi A}-A\nabla \Phi)
+\end{equation}
+where $\Phi$ is any differentiable function, this problem can be resolved. In its
+SPH form  equation \ref{eq:derivativeIdentity} reads as follows:
+\begin{equation}
+\nabla_a A = \frac{1}{\Phi_a}\sum_b frac{m_b}{\rho_b}(A_b-A_a)\nabla_a W_{ab}
+\end{equation}
+
+It can be seen, that the (approximation of the) derivative of the
+fieldfunction $A$ is now expressed by a summation over the fieldfunction itself
+and the derivative of the kernel function - which can be determined exactly.
+
+Now the basic formulations are introduced in principle: Both the fieldfunction
+itself and its spacial derivatives can be approximated using only information
+(=the states) of a discrete number of particles. Hence, the change rates of
+the states described by the equations of fluid dynamics, which have a form
+according to \ref{eq:EFD_form} can be rewritten using this information. Doing
+this one obtains the SPH formulation of the equations of fluid dynamics.
+
+The detailed derivation of those equations will not be shown here, as the
+interest  only lies in describing the principle ideas behind the SPH
+method. To resume, this are the following ones: A (field) function can be
+described as an integral interpolation over the function itself and a kernel
+function (which has to be chosen in an appropriate way). A further
+approximation consists in transforming the integral over the domain into a
+summation over the discrete elements constituing this domain (the particles). This allows to express both
+the field function and its spacial derivatives dependent exclusively on discrete values
+of the fieldfunction itself (and the kernel function, which is known as well as
+its derivatvies).By finally choosing an appropriate kernel function with
+compact support, the summation over all particles in the domain can be reduced
+to a summation over those particles within the support domain of the particle
+in question.
+
+As already mentionned above, the SPH formulation of the equations of fluid
+dynamics is obtained by applying the above principles and conducting different
+transformations to the original (exact) equations. Depending on the
+transformations used, the final SPH equations can assume a different form. In
+the following, a common form for the change rates of density, velocity and
+internal energy based on the EULER EQUATIONS (i.e. without viscosity) is
+listed\cite{Monaghan2005}\cite{Liu2003} (perhaps list NSG-form as well, and
+explain why Euler is of interest as well (for 1DSPH code, perhaps later real
+code including viscosity???)
+
+\begin{equation}
+\frac{d\rho _a}{\mathit{dt}}=\sum{m_{b}v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
+\end{equation}
+
+\begin{equation}
+\label{eq:VelChangeRate}
+\frac{dv_{a}}{\mathit{dt}}=-\sum {m_{b}(\frac{P_{a}}{\rho_{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi _{ab})\nabla_{a}W_{ab}}
+\end{equation}
+
+\begin{equation}
+\frac{de_{a}}{\mathit{dt}}=-\mathit{}\frac{1}{2}\sum{m_{b}(\frac{P_{a}}{\rho _{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi_{\mathit{ab}})v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
+\end{equation}
+
+For the detailed procedure of derivation and for alternative formulations of
+these equations refer to \cite{Monaghan2005}\cite{Liu2003}
+
+Artificial Viscosity
+
+Another poit that has to be taken into account for SPH simulations, especially
+such including shock phenomena, is arificial viscosity\cite{Monaghan2005}. It
+prevents particles from penetrating one into an other in zones with high
+compression rates and also generally stabilizes a numerical
+allgorithm.
+Artificial viscosity for numerical simulation of shock phenomena
+in general was first introduced by \cite{vonNeumann1950}. They suggested to
+introduce an artificial dissipation to give the shock a thickness which
+allowed it to be calculated numerically (in the cited example with finite difference
+scheme) without introduction of pre-/after shock boundary conditions.    ...(see article)
+The first use of artificial viscosity specifically for the mesh free SPH goes
+back to Lucy\cite{Lucy1977}.He suggested an artificial bulk viscosity to
+prevent a slow buildup of acoustic energy by integration errors in zones with
+low density respectively low particle presence. 
+Finally, the form of artificial viscosity most commomly used in SPH
+literature\cite{Liu2003} is the one proposed by Monaghan and
+Gingold\cite{Monaghan1983}. They stated that the use of one of the artificial
+viscosities cited above (Neumann Richtmyer (adapted to SPH) or bulk
+viscosity) on shock problems would lead to either excessive particle
+oscillation or excessive smearing of the shock front. The expression for this
+artificial viscosity $\Pi_{ab}$, which is added to the pressure term of
+equation \ref{eq:VelChangeRate}, is:
+
+\begin{equation}
+\Pi _{\mathit{ab}}=-\nu
+(\frac{v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
+h_{\mathit{ab}}^{2}})
+\end{equation}
+where 
+\begin{equation}
+\nu =\frac{h_{\mathit{ab}}}{\rho _{\mathit{ab}}}(\alpha
+c_{\mathit{ab}}-\beta
+\frac{h_{\mathit{ab}}v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
+h_{\mathit{ab}}^{2}})
+\end{equation}
+
+$v_{ab}$ stands for $v_a-v_b$, $r_{ab}$ for $r_a-r_b$, $c_{ab}$ is the
+averaged sound speed of the two particles in question $1/2(c_a+c_b)$. The same
+applies for $\rho_{ab}(=1/2(\rho_a+\rho_b))$ and $h_{ab}=(1/2(h_a+h_b))$. IT
+HAS TO BE MENTIONED SOMEWHERE (but probably not right here) THAT: the use of
+the averaged smoothing length $h_{ab}$ is a way to symmetrize particle
+interactions when h is spatially variable. In this case a particle $a$ could be
+located in the support domain of a particle $b$ but not vice versa. This would
+lead to an assymetric mutual contribution of forces. To avoid this, using the
+averaged smoothing length between two particles is an appropriate remedy\cite{Liu2003}.
+
+mention somewhere that kernel unity is inverse of volume?!?!?
+
+\section{Implementation of an SPH code}
+This section presents some particular features of an SPH code. Emphasis is
+placed on these features which are finally implemented in one of the
+two SPH codes designed and modified during this work.
+Points of interest are the implementation of different boundary conditions in
+SPH, a closer description of the kernel function, as well as different methods/allgorithms
+to perform the search for the interacting particles. Furthermore different
+equations of state are introduced, depending on the nature of the flow problem
+to be considered(compressible/incompressible). Finally some words on numerical
+integration schemes that have proven to be reliable for SPH applications.
+
+\subsection{boundary condition implementation}
+For particles at the edge of the calculation domain, the summation interpolation does not
+give exact results, as the integral (or better the sum) is truncated due to
+the simple fact that outside the domain there are no
+particles.\cite{Liu2003}(find better citation...) This efect is called the
+problem of article deficiencythe particle deficiency
+problem.\cite{Liu2003}. In some cases there is no need to consider this
+problem, as the areas close to the edges are not of interest and due to
+limited simulation time there is no time for the error to propagate into the
+actual zone of interest. The 1D shock tube simulation described further below
+(PERHAPS LINK TO SECTION)is an example for such a case.  
+But for other applications the edges play an important role or the domain has
+to be rendered periodocally. So there is a need to define specific boundary
+conditions. This can be accomplished by a special boundary treatment, which
+often includes so called virtual particles or ghost
+particles\cite{Liu2003}. The first ones to come up with this idea were
+\cite{LIBERSKY1993}. Virtual particles are used to model solid walls by
+placing them inside the solid body, mirrored at the surface. For each real
+particle whose support domain interfres with the wall, one such particle is
+built. Virtual particles have the same properties as their real counterpart
+except for the velocity. Depending on the type of boundary condition they are
+supposed to represent, different velocities are assigned to them.\cite{Hu2006}
+
+non slip velocity boundary condition
+
+\begin{equation}
+v_{virtual}=2v_{wall}-v_{real}
+\end{equation}
+
+free slip velocity boundary condition
+
+\begin{equation}
+v_{virtual}^{tangential}=v_{real}^{tangential}
+\end{equation}
+
+ILLUSTRATION OF VELOCITY ASSIGNMENT FOR VIRTUAL BOUNDARY PARTICLES
+
+For the treatment of periodic boundary conditions, no ghost particles are
+needed. Particles leaving the calculation domain on one side are simple
+reinserted on the opposite side (with the same properties).
+
+\subsection{kernel function}
+???not sure, if its the right place here, but somewhere there should be a
+paragraph with more detailed information on kernels used, compact support,
+perhaps even some properties,...(and perhaps some graphics???)
+
+Some properties of Kernel functions (smoothing functions) and notions related
+to them have allready been mentionned in the section
+\ref{sec:BasicsSPH}. In principal every function can act as Kernel function
+when it respects a set of criteria complsed by \cite{Liu2003}.
+The most important ones are:
+
+The smoothing function should vanish outside of a certain area around its
+center. This property is called compact support and the domain where $W\neq0$
+the support domain of the smoothing function. The smoothing length $\kappa h$ and the
+support length $h$ may not be mixed up.
+\begin{equation}
+W(x-x')=0,\text{for}|x-x'|>\kappa h
+\end{equation}
+
+The smoothing function should be normalized to 1, which ensures that constants
+are interpolated exactly
+\begin{equation}
+\int{W(x-x',h)dx'}=1
+\end{equation}
+
+The smoothing function should tend towards the delta function as the smoothing
+length $h$ tends to zero
+\begin{equation}
+\lim\limits_{h \rightarrow 0}{W(x-x',h)}=\delta(x-x')
+\end{equation}
+This is to ensure consistency of the integral approximation, which means that
+the approximative expression tends to the exact expression of the integral
+interpolant equation.
+
+The full list of SPH kernel properties can be found in  \cite{Liu2003}.
+Based on those properties a variety of Kernels are used in SPH literature. A
+very commonly used Kernel though is the $M_4$ Kernel based on Schoenbergs
+$M_n$-Splines\cite{Schoenberg1946}.
+
+FORMULA M_4 Kernel
+
+In the work of \cite{Fulk1996} a mesure of merit for Kernels is developed and
+they came to the result, that in 1D no kernel performed significantly better
+than the cubic spline.
+This is why for the 1D SPH code described in section (WHATEVER) the cubic
+splime kernel is employed.
+
+\subsection{neighboring particle search methods}
+
+\subsection{equation of state}
+
+\subsection{numerical integration}
+...conservation properties more important than order of scheme\cite{Monaghan2005}
+
+\section{1D SPH code}
+\subsection{short overview}
+\subsection{components}
+\subsection {structure}
+\section{2D SPH code}
+\subsection{short overview}
+\subsection{components}
+
+\subsection{structure}
+
+\lstinputlisting[language=c++,caption=An example of program listing,captionpos=b]{code/hello.cpp}
 
 \chapter{Results}
+\section{1D SPH code}
+...Monaghan05 p.1739... not width important but pre and after shock values...
+
+\section{...}
 \label{sec:results}
+
+In the Figure~\ref{fig:1dshock} one can see \ldots
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.95\textwidth]{img/1dshock.eps}
+  \caption{An example of a figure}
+  \label{fig:1dshock}
+\end{figure}
 
@@
 \label{sec:conclusion}
+
+\listoffigures
 

### 2010-07-10 ms/main.tex
Small changes in main.tex
documentation updated

@@
 \usepackage{listings}
+\usepackage{amsmath}
+\usepackage[pict2e]{struktex}
+\usepackage{parcolumns}
+% \usepackage{multicol}
+%\usepackage[rflt]{floatflt}
+
 %\usepackage{fullpage}
+
+%I've found the following lines in the internet to automatically begin a new line after a paragraph
+\makeatletter
+\renewcommand\paragraph{\@startsection{paragraph}{4}{\z@}%
+  {-3.25ex\@plus -1ex \@minus -.2ex}%
+  {1.5ex \@plus .2ex}%
+  {\normalfont\normalsize\bfseries}}
+\makeatother
+
+%to change section numbering depth to 3 (default 2)
+\setcounter{secnumdepth}{3}
+
+%to change depth for appearence in table of contents to 3 (default 2)
+\setcounter{tocdepth}{3}
 
@@
 
+INTRODUCE THE TWO CODES AND MENTION THAT THEY ARE WRITTEN IN C/C++...
+
 \chapter{Method}
@@
 \label{eq:EFD_form}
-{dA(r)\over dt}=f(A(r),\nabla A(r),r)
+{\frac{dA(r)}{dt}}=f(A(r),\nabla A(r),r)
 \end {equation}
@@
 \begin {equation}
-{d(.)\over dt}={\partial(.)\over \partial t}+v\nabla(.)
+{\frac{d(.)}{dt}}={\frac{\partial(.)}{ \partial t}}+v\nabla(.)
 \end{equation}
@@
 \begin{equation}
+\label{eq:intInter}
 A_S(r)=\sum_b m_b \frac{A_b}{\rho_b}W(r-r_b,h)
@@
 \begin{equation}
-\nabla_a A = \frac{1}{\Phi_a}\sum_b frac{m_b}{\rho_b}(A_b-A_a)\nabla_a W_{ab}
+\nabla_a A = \frac{1}{\Phi_a}\sum_b \frac{m_b}{\rho_b}(A_b-A_a)\nabla_a W_{ab}
 \end{equation}
@@
 It can be seen, that the (approximation of the) derivative of the
-fieldfunction $A$ is now expressed by a summation over the fieldfunction itself
+field function $A$ is now expressed by a summation over the fieldfunction itself
 and the derivative of the kernel function - which can be determined exactly.
@@
 internal energy based on the EULER EQUATIONS (i.e. without viscosity) is
-listed\cite{Monaghan2005}\cite{Liu2003} (perhaps list NSG-form as well, and
+listed\cite{Monaghan2005}\cite{Liu2003} (perhaps also list NSG-form, and
 explain why Euler is of interest as well (for 1DSPH code, perhaps later real
@@
 \begin{equation}
+\label{eq:DCR_Euler}
 \frac{d\rho _a}{\mathit{dt}}=\sum{m_{b}v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
@@
 \begin{equation}
-\label{eq:VelChangeRate}
-\frac{dv_{a}}{\mathit{dt}}=-\sum {m_{b}(\frac{P_{a}}{\rho_{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi _{ab})\nabla_{a}W_{ab}}
+\label{eq:VCR_Euler}
+\frac{dv_{a}}{\mathit{dt}}=-\sum {m_{b}\left(\frac{P_{a}}{\rho_{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}\right)\nabla_{a}W_{ab}}
 \end{equation}
@@
 \begin{equation}
-\frac{de_{a}}{\mathit{dt}}=-\mathit{}\frac{1}{2}\sum{m_{b}(\frac{P_{a}}{\rho _{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi_{\mathit{ab}})v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
+\label{eq:ECR_Euler}
+\frac{de_{a}}{\mathit{dt}}=-\mathit{}\frac{1}{2}\sum{m_{b}\left(\frac{P_{a}}{\rho _{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}\right)v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
 \end{equation}
@@
 For the detailed procedure of derivation and for alternative formulations of
-these equations refer to \cite{Monaghan2005}\cite{Liu2003}
+these equations refer to \cite{Monaghan2005, Liu2003}
 
@@
 
-Another poit that has to be taken into account for SPH simulations, especially
+(perhaps I will move this section and make it a subsection of 'Implementation of SPH' (as artificial viscosity is linked to numerics
+
+Another point that has to be taken into account for SPH simulations, especially
 such including shock phenomena, is arificial viscosity\cite{Monaghan2005}. It
@@
 The first use of artificial viscosity specifically for the mesh free SPH goes
-back to Lucy\cite{Lucy1977}.He suggested an artificial bulk viscosity to
+back to Lucy\cite{Lucy1977}. He suggested an artificial bulk viscosity to
 prevent a slow buildup of acoustic energy by integration errors in zones with
@@
 artificial viscosity $\Pi_{ab}$, which is added to the pressure term of
-equation \ref{eq:VelChangeRate}, is:
+equation \ref{eq:VCR_Euler}, is:
 
 \begin{equation}
+\label{eq:MonArtVis}
 \Pi _{\mathit{ab}}=-\nu
-(\frac{v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
-h_{\mathit{ab}}^{2}})
+\left(\frac{v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
+h_{\mathit{ab}}^{2}}\right)
 \end{equation}
@@
 \begin{equation}
-\nu =\frac{h_{\mathit{ab}}}{\rho _{\mathit{ab}}}(\alpha
+\label{eq:FactArtVis}
+\nu =\frac{h_{\mathit{ab}}}{\rho _{\mathit{ab}}}\left(\alpha
 c_{\mathit{ab}}-\beta
 \frac{h_{\mathit{ab}}v_{\mathit{ab}}r_{\mathit{ab}}}{r_{\mathit{ab}}^{2}+\epsilon
-h_{\mathit{ab}}^{2}})
+h_{\mathit{ab}}^{2}}\right)
 \end{equation}
@@
 averaged smoothing length between two particles is an appropriate remedy\cite{Liu2003}.
+Including artificial viscosity, the SPH form of the Euler momentum equation becomes\cite{Monaghan2005}
+
+\begin{equation}
+\label{eq:VCR_EulerInclArtVis}
+\frac{dv_{a}}{\mathit{dt}}=-\sum {m_{b}\left(\frac{P_{a}}{\rho_{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}+\Pi _{ab}\right)\nabla_{a}W_{ab}}
+\end{equation}
+
+The introduced artificial viscosity must also be reflected in the energy equation, as viscosity transfers energy from kinetic to thermal\cite{Monaghan2005}.
+One formulation of the energy equation which is convenient for implementation in the 1D SPH code (as a big part of the needed expression has already been calculated for \ref{eq:VCR_EulerInclArtVis}) can be found in\cite{Liu2003}
+
+\begin{equation}
+\label{eq:ECR_EulerInclArtVis}
+\frac{de_{a}}{\mathit{dt}}=-\mathit{}\frac{1}{2}\sum{m_{b}\left(\frac{P_{a}}{\rho _{a}^{2}}+\frac{P_{b}}{\rho _{b}^{2}}\right)v_{\mathit{ab}}\nabla _{a}W_{\mathit{ab}}}
+\end{equation}
 
@@
 \subsection{boundary condition implementation}
+\label{sec:boundaryConditionImplementation}
 For particles at the edge of the calculation domain, the summation interpolation does not
@@
 \subsection{kernel function}
+\label{sec:KernelFunction}
 ???not sure, if its the right place here, but somewhere there should be a
@@
 \begin{equation}
-W(x-x')=0,\text{for}|x-x'|>\kappa h
+W(x-x')=0,\textit{for}|x-x'|>\kappa h
 \end{equation}
@@
 
-The smoothing function should tend towards the delta function as the smoothing
+The smoothing function should tend towards the delta function as/when the smoothing
 length $h$ tends to zero
@@
 Based on those properties a variety of Kernels are used in SPH literature. A
-very commonly used Kernel though is the $M_4$ Kernel based on Schoenbergs
+very commonly used Kernel though is the $M_4$ Kernel (Cubic Spline) based on Schoenbergs
 $M_n$-Splines\cite{Schoenberg1946}.
 
-FORMULA M_4 Kernel
+\begin{equation}
+\label{eq:cubicSpline}
+M_{4}(x)=\begin{cases}
+\frac{1}{6}[(2-q)^{3}-4(1-q)^{3}],& \text{for 0 $\leq$ q $\leq$ 1} \\
+\frac{1}{6}(2-q)^{3},&  \text{for 1 $\leq$ q $\leq$ 2} \\
+O,& \text{for q $>$ 2}
+\end{cases}
+\end{equation}
 
@@
 This is why for the 1D SPH code described in section (WHATEVER) the cubic
-splime kernel is employed.
+spline kernel is employed.
 
 \subsection{neighboring particle search methods}
+\label{sec:NNPS}
+To calculate the change rates in \ref{eq:DCR_Euler}-\ref{eq:ECR_Euler} a
+summation over all paricles has to be performed. However, as we defined kernel
+functions with a compact support, only particles within a certain distance from
+the particle in question (within its support domain) contribute to the
+interpolation of its values, and thus interact. Finding the interacting
+particles is one of the key features in an SPH implementation, as an effective
+interaction search method (often also called nearest neighboring particle (NNP)
+search method in SPH literature) can considerably speed up/accelerate
+computation time.
+
+The most basic NNP algorithm is called all pair search, and as its name
+suggests all imaginable particle pairs are tested for interaction. This means
+the calculation process consists of a double loop where the outer loop
+iterates over all particles and defines one of the pair's partners (often
+refered to as origin). For each of the (origin) particles an inner loop is
+performed, which iterates again over all particles thus defining the oterh
+partner (destination) of the pair. Then, the pair is tested for the
+interaction condition, meaning that their distance has to be inferior to the
+support length. In this way, for a calculation domain consisting of $N$
+particles, $N*N$ iteration steps and tests have to be executed. The
+calculation cost of this approach is of the order $O(N^2)$. 
+If the
+interactions are assumed pairwise (i.e. if there is a spacially constant
+smoothing (and therefore support) length; THINK ABOUT THE AVERAGED SMOOTHING
+LENGTH...) there is a simple but efficient way of reducing computation
+time. In this case namely, if the pair $P_{ij}$ is an interaction, the pair
+$P_{ji}$ is an interaction as well. That way half of the $O(N^2)$ iterations
+and tests can be avoided leading to a complexity of $O(N!)$ (LOOK FOR
+REFERENCES). This approach is employed in the 1D SPH code as it is easy to
+implement\cite{Liu2003} and the number of particles in this 1D simulation is
+still reasonably low in order not to have to use more sophisticated algorithms
+like they are introduced below.
+
+A more effective but also more complicated method is the linked list
+algorithm. Its idea is based on the fact, that kernels wit compact suport are
+used and thus interacting particles may only be located in the neighborhood of
+the considered particle. The computation domain is divided into cells (with
+cell size$\ge \kappa h$, ideally $=\kappa h$) and the
+particles are assigned to the cell they are located inc\cite{Monaghan1983}. In this way the cell
+structure serves as a book keeping device and in case of an interaction
+calculation with an origin particle $i$ not all the particles $j,j={1,...,N}$ have
+to be considered but only those particles in the adjoining cells. Hence, the
+complexity of the original problem which is of order $O(N^2)$ can be reduced
+largely and tends even to $O(N)$ if the particles in one cell are few.
+
+DIAGRAM WITH CELLS /PARTICLES /DOMAIN!?!
+
+Technically the cells are managed by the implementation of a linked list
+structure in a computational code. More details on this are given in section
+(SOMEWHERE IN 2D CODE DESCRIPTION), as this algorithm is implemented in the 2D
+SPH code, and in \cite{Monaghan1985, Hockney1988}.
+The method however has a drawback if used with a spacially variable smoothing
+length. In this case the cell size is not ideally adapted to every particle
+and the allgorithm looses efficiency.
+
+Moreover, different other NPP techniques exist which, here, shall not be introduced in
+detail. One of them are tree search algorithms\cite{Hernquist1989}, which are
+especially robust and efficient for problems with variabe smoothing
+length\cite{Liu2003}.
 
@@
 
+The equation of state allows for the computation of the pressure $p$ based on
+information about the density $\rho$ and the internal energy $e$ (or equivalent...).
+For the application of SPH for gas dynamics, the assumption of an ideal gas is appropriate (citation and conditions).
+In this case the (ideal gas) equation of state is
+
+...equation of state in the original form...
+
+...
+transformation steps (or at least realations needed)...
+
+\begin{equation}
+ p=(\gamma-1)\rho e
+\end{equation}
+
+The sound speed, which is needed to calculate the artificial viscisoty (see (\ref{eq:FactArtVis})), can be formulated for an ideal gas as:
+
+\begin{equation}
+ c=\sqrt{\gamma R T}
+\end{equation}
+or with $c_v T=e$, $R=c_p-c_v$ and $\gamma=\frac{c_p}{c_v}$
+
+\begin{equation}
+ c=\sqrt{\gamma(\gamma-1)e}
+\end{equation}
+
+???shold I mention the equation of state applied for liquids (by artificially
+introducing a little compressibility \cite{Monaghan1994,Monaghan2005}???
+
 \subsection{numerical integration}
-...conservation properties more important than order of scheme\cite{Monaghan2005}
+\label{sec:numIntegr}
+
+As far as the time integation of the equations of SPH is concerned, any stable
+time stepping algorithm for ordinary differential equations may be
+used\cite{Monaghan2005}. However for SPH simulations, the conservation properties
+(linear and angular momentum) of the integrator are more important than its
+order\cite{Monaghan2005}.
+
+Thus, a stadard leap frog scheme is one possibility to perform the integration in
+time. The initial time step is done according to the following algorithm where
+$S$ is a substtitute for $\rho,v,e$
+
+For $n=0$:
+\begin{equation}
+S_{\frac{1}{2}}=S_0+\frac{1}{2}dt\left(\frac{dS}{dt}\right)_0
+\end{equation}
+\begin{equation}
+x_1=x_0+dt v_{\frac{1}{2}}
+\end{equation}
+
+for any further time step $n\ge1$:
+
+\begin{equation}
+S_n=S_{n-\frac{1}{2}}+\frac{1}{2}dt\left(\frac{dS}{dt}\right)_{n-1} \rightarrow
+\frac{dS}{dt})_n 
+\end{equation}
+\begin{equation}
+S_{n+\frac{1}{2}}=S_{n-\frac{1}{2}}+dt\left(\frac{dS}{dt}\right)_n 
+\end{equation}
+\begin{equation}
+x_1=x_0+dt v_{\frac{1}{2}}
+\end{equation}
+
+Another possibility for time integration is a predictor corrector scheme, as
+used by \cite{Hu2007}(IS THIS REFERENCE OK?). The 2D SPH code structure being based on their work,
+this integration scheme is implemented in the above mentionned program.
+
+In the predictor step a guess $\hat S$ of the value $s$ at $n+1$ is made by simply
+applying a normal Euler step.
+
+\begin{equation}
+\hat S_{n+1}=S_n+dt\left(\frac{dS}{dt}\right)_n
+\end{equation}
+\begin{equation}
+x_{n+1}=x_n+dt v_{n}
+\end{equation}
+
+This guess is then corrected by a central scheme to update the values at
+$n+1$:
+
+\begin{equation}
+S_{n+1}=S_n+dt\left(\frac{dS}{dt}\right)_{n+\frac{1}{2}}
+\end{equation}
+
+The values at $n+\frac{1}{2}$ needed to calculate
+$\frac{dS}{dt})_{n+\frac{1}{2}}$ are obtained by taking the mean value of
+$S_n$ and $\hat S_{n+1}$:
+
+\begin{equation}
+S_{n+\frac{1}{2}}=\frac{1}{2}(S_n+\hat S_{n+1})
+\end{equation}
+
+\subsection{Summation Density and Continuity Density approach}
+\label{sec:DensCalcMode}
+One way to update/calculate the density with the SPH method is simply to integrate the density change rate \ref{eq:DCR_Euler} for each time step, just like it is done for velocity and internal energy.
+Thanks to the character of the SPH formulation, there is another possibility of obtaining density.
+Taking the interpolation equation \ref{eq:intInter} and supposing $A$ is the density $\rho$ gives an expression for the interpolation (the smoothing) of the density of a particle $a$ by summing over all particles within the support domain\cite{Monaghan2005}.
+
+\begin{equation}
+\label{eq:SumDensity}
+\rho(r)=\sum_b m_b W(r-r_b,h)
+\end{equation}
+
+The first method where density is integrated using \ref{eq:DCR_Euler} is refered to as continuity density approach, the second one where density is obtained by summation/smoothing as summation density approach \cite{Liu2003}.
+Both methods are commonly used in SPH codes, they are often even implemented both in one same code.
+ADVANTAGES/DISADVANTAGES SEE LIU AND REFERENCES...
+
+\subsection{basic structure of an SPH code}
+
+Any implementation of an SPH code possesses a certain basic structure defined by the nature of the SPH equations.
+\ref{fig:BasicSphCode} (adapted from \cite{Liu2003}) together with the description in this paragraph shall show the interdependence of the constituent parts of an SPH code in principle.
+The actual (control) flow of an implememented SPH code may differ in details from \ref{fig:BasicSphCode} and can be seen on/from the more detailed flow diagrams for the specific codes.
+Remark: the structure described in the following paragraph applies to any (serial, not parallel) SPH code (no matter if compressible/incompressible or viscous/inviscous).
+The equations referred to however, are the SPH form of the Euler equations and thus are only valid for invscid problems.
+
+\ref{fig:BasicSphCode} shows that the first essential part of an SPH program is the setting up of the initial conditions includuing the definition of geometrical and other probem specific parameters.
+The choice of the variables/quantities given as initial conditions not being unique, there are several possibilities in defining them.
+(for example giving $m$ and $\rho$ defines the particle spacing (which corresponds to the volume) and giving the spacing and $\rho$ fixes $m$.) Which way is selected for a specific program is precised in the corresonding section.
+Thereafter the program enters the main computation loop and the operations executed therein are repeated for each time step.
+Among those operations is the creation of the virtual boundary particles (\ref{sec:boundaryConditionImplementation}) which are then needed included in the nearest neighbouring particle search (\ref{sec:NNPS}).
+After having determined all the interactions for all particles the smoothing function and its derivative can be computed for each interaction pair.
+Then, depending on the density calculation mode (?see?
+\ref{sec:DensCalcMode}), the program sequence differs slightly.
+For/with the summation density approach, density is obtained by summation (smoothing)\ref{eq:SumDensity} and once density is calculated, the forces on the particles may be determined.
+Those forces allow for the computation of the momentum change rate (remark: the calculation of forces and momentum change rate can be considered as one single step, all included in \ref{eq:VCR_Euler}).
+Also, the energy change rate is determined \ref{eq:ECR_Euler}.
+As for the continuity density approach, the calculation of forces is conducted without smoothing, taking the density value obtained at the previous step (or the initial value for the first time step).
+But the density change rate has to be determined as well \ref{eq:DCR_Euler}, as density will be obtained by integration.
+Once all necessary change rates are known, the values can be updated to the next time step, see \ref{sec:numIntegr} and the loop can be restarted.
+After the actual simulation is finished, an output module is in charge of making data available in a form (that is) exploitable to the user.
+
+\begin{figure}[h]
+  \centering
+      \includegraphics[width=1.0\textwidth]{Graphics/general_structure_SPH}
+  \caption{basic structure of an SPH code}
+  \label{fig:BasicSphCode}
+\end{figure}
 
 \section{1D SPH code}
+
 \subsection{short overview}
-\subsection{components}
-\subsection {structure}
+PERHAPS THIS SUBSECTION TITLE IS REMOVED AND THE FOLLOWING TEXT WILL FIGURE JUST BELOW THE SECTION TITLE!?!
+
+This code has a relatively simple structure, yet it features all the components a more sophisticated SPH computational program would incorporate.
+Both the summation density approach and the continuity density approach are implemented \ref{sec:DensCalcMode} By computing a 1D shock tube problem, the code is used to verify the basic SPH equations which are then implemented in the more complex 2D program.
+As the analytical solution for this problem is well known, the shock tube is a very common test case for 1D compressible codes \cite{Sod1978} (PERHAPS ONE MORE REFERENCE WHICH STATES THAT SHOCK TUBE IS A COMMONLY USED TEST CASE...).
+The problem setup and the obtained results are discussed in the corresponding section.
+
+\subsection{Validation Case}
+As mentionned above, the test case for this 1D compressible SPH code is a 1D shock tube problem. It is introduced already at this stage as it is referred to sometimes in the following section.
+In general a shock tube consists of two initially separated (e.g. by a diaphragm) gas filled areas, one side under higher pressure than the other....
+
+PLUS FIGURE SHOCK TUBE
+
+\subsection{components and structure}
+
+\subsubsection{the data structures}
+
+To facilitate the implementation and the handling of the code, two data structures (have been) are defined.
+
+\paragraph{The parameters data structure}
+
+This data structure is defined in the header file parameters.h(WRITE IN CODE STYLE) and containes all parameters needed to set up the problem.
+Among those parameters are geometrical values, the initial conditions,simulation length and time step (IN AN EARLY VERSION; IN A LATER VERSION TRY TO ADAPT TIME STEP AUTOMATICALLY!!!!?!!!) as well as parameters defining the fluid properties.
+
+\paragraph{The simulation data structure}
+
+Defined in the file simulation.h(WRITE IN CODE STYLE) this structure is made up of all variables that change in the course of the simulation.
+To begin with, these are the values of interest like position, velocity, density, pressure, energy, etc..
+Furthermore there are variables needed as intermediate results (such as the smoothing length and its derivative).
+Most of the variables contained in the simulation data structure are needed one per particle.
+Therefore those variables are defined as vectors with a size that corresponds to the number of particles in the system.
+
+\subsubsection{The Functions}
+
+As the size of the 1D SPH program is not too big, it admits of the introduction/description of every single function used.
+The textual description is not complete but only comprises particularities and features that are considered worth mentionning.
+A Nassi-Schneidermann-Diagram (NSD)~\cite{Nassi???} complements each description and shows the control flow for each function as well as the interdependence of the individual functions.
+For the sake of a clear illustration , the NSD does not display every loop of the program; frequently, loops over all particles and the interaction list are ommitted (the instruction 'calculate ...
+for each particle' for example means the implementation of a loop over all particles i.e.
+all components of the corresponding variable's vector).
+Consulting the comments in the source code is recommended if an even more detailed understanding is necessary or desired.
+
+\paragraph{Explanation of a Nassi-Schneidermann-Diagram}
+A NSD Diagram is employed in this section as it allows for a more compact description of the code structure within limited space than a conventional flow diagram and, in addition, offers a range of further advantages~\cite{Nassi???}.
+It is read from top to bottom, with different box symbols representing different kinds of instructions or control elements.
+The symbols used during the description of the functions below are the following ones:
+
+\subparagraph{The process symbol}
+there has to be some text, otherwise the parcolumns environment will delete the subparagraph heading!?!
+\vspace{5mm}
+\begin{parcolumns} [colwidths={1=60mm,2=35mm}] {2}
+
+\colchunk{this symbol represents simple instructions for which during their execution no analys has to be made. Examples are assignments or inputts/outputs. 
+A variation of the conventional process box is the symbol for the call of an external function.} 
+\colchunk{
+
+\begin{struktogramm}(40,10)
+  \assign[10]{\(Instruction\)}
+\end{struktogramm}
+\vspace{10mm}
+\begin{struktogramm}(30,10)
+  \sub[10]{\texttt{function()}}
+\end{struktogramm}}
+
+\colplacechunks
+\end{parcolumns}
+
+% \begin{multicols} [colwidths={1=0.6\textwidth,2=0.35\textwidth}] {2}  
+%  
+% \colchunk{hhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhhh}
+% \colchunk{gggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggggg}
+% \colplacechunks
+% 
+% \end{multicols}
+
+\subparagraph{The iteration symbol}
+there has to be some text, otherwise the parcolumns environment will delete the subparagraph heading!?!
+\vspace{5mm}
+\begin{parcolumns} [colwidths={1=60mm,2=35mm}] {2}
+
+\colchunk{The shown iteration symbol represents loops, where the condition is tested each time before entering the body. This control struct can be implemented by a while loop or a for loop. } 
+\colchunk{
+
+\begin{struktogramm}(40,10)
+\while[10]{\(while condition true\)}  
+\assign[10]{\(body\)}
+\whileend
+\end{struktogramm}}
+
+\colplacechunks
+\end{parcolumns}
+
+\subparagraph{The decission symbols}
+there has to be some text, otherwise the parcolumns environment will delete the subparagraph heading!?!
+\vspace{5mm}
+\begin{parcolumns} [colwidths={1=60mm,2=50mm}] {2}
+
+\colchunk{Control structures that depending on a condition enter different branches, are represented by the decission symbols.
+A binary desiccion symbol corresponding to an if-else statement in programming languages is shown in (FIGURE...).
+For multi branch control structs, such as if-ifelse-...-else or switch-case, (FIGURE...) provides the corresponding symbol (in the example: 3 branches).
+ } 
+\colchunk{
+\sProofOn
+\begin{struktogramm}(60,25)
+\ifthenelse[10]{6}{6}{condition true?}{Y}{N}
+\assign[10]{\(subblock\ 1\)}
+\change
+\assign[10]{\(subblock\ 2\)}
+\ifend
+\end{struktogramm}
+\sProofOff
+
+\sProofOn
+\begin{struktogramm}(60,15)
+  \case[15]{3}{3}{\(test\ X\ \ \)}{cond. 1}
+        \assign[10]{\(subblock\ 1\)}
+    \switch{~2}
+        \assign[10]{\(subblock\ 2\)}
+    \switch[r]{3~}
+      \assign[10]{\(subblock\ 3\)}
+   \caseend
+\end{struktogramm}
+\sProofOff
+}
+\colplacechunks
+\end{parcolumns}
+\vspace{5mm}
+
+%this does work in principle, but the figures are not placed exactly at the right position
+% \begin{floatingfigure}[v]{50mm}
+% \begin{struktogramm}(20,20)[]
+% \assign{\(Instruction\)}
+% \end{struktogramm}\caption{test}
+% \end{floatingfigure}
+
+Remark: The NSD flowchart language provides the possibility to describe programs at their level of implementation.
+In the following section however, it is used in a more abstract way and instructions or conditions are verbalized.
+
+\paragraph{The Main() function}
+
+As its name suggests, main.cpp(WRITE IN CODE STYLE) is the main function of the program.
+It is entered upon execution of the program, declares and initializes the data structures and calls the functions needed.
+
+\begin{center}
+\sProofOn
+\begin{struktogramm}(76,27)[MAIN]
+  \assign{\(declare \ parameters\ data\ structure\)}
+  \assign{\(declare \leq 4 \ simulation\ data\ structure\)}
+  %\sub{\begin{verb} setupSim(param, sims) \end{verb}}
+  \sub{\texttt{setupSim(param, sims) }}
+  %\sub{\begin{verb} \ marchTime(param, sims)\end{verb}}
+  \sub{\texttt{ marchTime(param, sims)}}
+  \assign{\(return\ 0  \ (program\ successfully\ ended)\)}
+\end{struktogramm}
+\sProofOff
+\end{center}
+
+\paragraph{The setupSim() function}
+
+Implemented in the file setupSim.cpp (with the corresponding header setupSim.h), this function represents the 'initialization module' from/shown in \ref{fig:BasicSphCode}.
+More precisely, it first sets up the initial particle distribution for the sepcified problem (which is the Sod shock tube \cite{Sod1978}).
+Depending on the user's selection made by setting the flag 'constspacing' (member of parameters dara structure), this is done/made?
+in two different ways:
+One possibility is to have an initial particle distribution with the same spacing in the high density area of the shock tube as in the low density area (flag constspacing = true).
+(REM: THE SHOCK TUBE PROBLEM SHOULD BE INTRODUCED BEFORE (AND NOT AS ORIGINALLY INTENDED ONLY IN THE RESULTS SECTION, AS I HAVE ALREADY REFERRED TO IT SEVERAL TIMES BY NOW...) In this case though, the mass of the particles has then to be adapted to be coherent with the spacing and the initial value of the density.
+A second possibility is a particle distribution resulting of a (spatially) constant particle mass (flag constspacing= false).
+According to the initial value of the density, the particles will then be further apart in the low density area than in the high density area.
+For the further course of the program it is essential that each particle has a unique mean of identification.
+For more sophisticated 2D or 3D codes, this issue is resolved by explicitely assigning each particle an identification number.
+For this 1D code however, particle identification is already implicitely given due to the way, the particles are represented/stored: The position (consisting only of an $x$ value) of each particle is stored as one component of a position vector X.
+Therefore the particles can be clearly identified by the number of the vector component they are stored into.
+
+Once the particles are set up, they are assigned their initial values for the shock tube problem as choosen in the parameters.h file.  
+\begin{center}
+\sProofOn
+\begin{struktogramm}(140,115)[SETUPSIM]
+  \assign{\(Calculate\ left\ hand\ particle\ spacing\ (dxl)\ based\ on\ constant\ mass\)}
+  \assign{\(Calculate\ right\ hand\ particle\ spacing\ (dxr)\ based\ on\ constant\ mass\)}
+  \assign{\(Calculate\ particle\ spacing\ (dx)\ for\ constant\ spacing\)}
+  \ifthenelse[10]{6}{6}{\(constspacing\ flag==1?\)}{Y}{N}
+    \assign[15]{\(place\ particles\ on\ left\ hand\ side\ of \)\linebreak \( problem\ domain\ starting\ at\ center\ (x=0)\ (with\ distance\ dx)\)}
+    \assign[15]{\(place\ particles\ on\ right\ hand\ side\ of\)\linebreak \( problem\ domain\ starting\ at\ x=0\ (with\ distance\ dx)\)}
+  \change
+    \assign[15]{\(place\ particles\ on\ left\ hand\ side\ of\ \)\linebreak \(problem\ domain\ starting\ at\ x=0\ (with\ dinstance\ dxl)\)}
+    \assign[15]{\(place\ particles\ on\ right\ hand\ side\ of\ \)\linebreak \(problem\ domain\ starting\ at\ x=0\ (with\ dinstance\ dxr)\)}
+  \ifend
+  \assign{\(merge\ particle\ positions\ for\ both\ sides\ into\ one\ vector\ x\)}
+  \assign{\(create\ vectors\ with\ initial\ values\ for\ u,\ \rho,\ p,\ e,\ m,\ h\ for\ particles\ on\ left\ hand\ side\)}
+  \assign{\(create\ vectors\ with\ initial\ values\ for\ u,\ \rho,\ p,\ e,\ m,\ h\ for\ particles\ on\ right\ hand\ side\)}
+  \assign{\(merge\ l.h.s.\ and\ r.h.s\ vectors\ into\ one\ single\ vector\ for\ each\ variable\)}
+  \ifthenelse[10]{6}{1}{\(constspacing\ flag\ ==\ 1?\)}{Y}{N}
+    \assign{\(calculate\ mass\ for\ particles\ on\ left\ hand\ side\)}
+    \assign{\(calculate\ mass\ for\ particles\ on\ right\ hand\ side\)}
+    \assign{\(merge\ mass\ values\ into\ one\ single\ vector\ \)\linebreak \((overwrite\ mass\ vector\ from\ above)\)}
+  \change
+  \ifend
+  \assign{\(initialize\ vectors\ for\ derivatives\ \ du,\ de,\ d\rho \)}
+\end{struktogramm}
+\sProofOff
+\end{center}
+
+\paragraph{The marchTime() function}
+
+The marchTime function conducts the numerical integration using the leapfrog scheme described in \ref{sec:numIntegr}.
+If the program runs in the continuity density mode (flag sumdensity = false), the density is integrated as well, whereas if the program runs in the summation density mode (flag sumdensity = true) the density is smoothed.
+The latter operation is not performed directly in this function but in one of the (sub)functions that it calls.
+
+\begin{center}
+ \sProofOn
+     \begin{struktogramm}(150,140)[MARCHTIME()]
+  \assign{\(initialize\ vectors\ for\ intermediate\ values\ of\  \rho,\ u,\ e\)}
+  \while[10]{\(while\ current\ time\ step\ \leq \ number\ of\ total\ time\ steps\)}
+    \ifthenelse[10]{6}{1}{\(current\ time\ step\ \neq1\)}{Y}{N}
+      \assign{\(save\ current\ values\ for\ \ u,\ e\ in\ their\ intermediate\ variables\)}
+      \ifthenelse[10]{6}{1}{\(sumdensity\ flag\ \neq1?\)}{Y}{N}
+        \assign{\(save\ current\ rho\ value\)\linebreak \(in\ its\ intermediate\ vector\)}
+        \assign{\(calculate\ new\ rho\ (+0.5dt)\ by\ integration\)}
+      \change
+      \ifend
+      \assign{\(calculate\ new\ u,\ e\ (+0.5dt) \)\linebreak \(\ by\ integration\)}
+    \change
+    \ifend
+    \sub{\texttt{calcDerivatives()}}
+    \ifthenelse[10]{6}{6}{\(current\ time\ step\ ==1?\)}{Y}{N}
+      \ifthenelse{6}{1}{\(sumdensity \neq1?\)}{Y}{N}
+        \assign[10]{\(calculate\ new\ \rho\ (+0.5dt)\ by\ inte-\)\linebreak\(gration\)}
+      \change
+      \ifend
+      \assign[10]{\(calculate\ new\ u,\ e\ (+0.5dt)\ by\ integration\)}
+      \assign[10]{\(calculate\ new\ position\ x\ (+1.0dt)\)\linebreak\((advance\ particles\ one\ full\ time\ step)\)}
+    \change
+      \ifthenelse{6}{1}{\(sumdensity \neq1?\)}{Y}{N}
+        \assign[10]{\(calculate\ new\ \rho\ (intermediate\ value\  \)\linebreak\(+1.0dt)\ by\ integration\)}
+      \change
+      \ifend
+      \assign[10]{\(calculate\ new\ u,\ e\ (intermediate\ vaules\ \)\linebreak\(+1.0dt)\ by\ integration\)}
+      \assign[10]{\(claculate\ new\ position\ x(+1.0dt)\) \linebreak\((advance\ particles\ one\ full\ time\ step)\)}
+    \ifend
+    \ifthenelse[10]{6}{6}{\(current\ timestep\ \%\ printstep\ ==0?\)}{Y}{N}
+      \sub{\texttt{plotShock()}}
+    \change
+    \ifend
+    \assign[10]{\(check\ stability\ criterion\ (max\ velocity\ <\ certain\ limit?)\ and\ if\ necessary:\ exit\ program\)}
+  \whileend
+     \end{struktogramm}
+\sProofOff
+\end{center}
+
+\paragraph{The calcDerivatives() function}
+
+This function performs the calculation of the derivatives (or change rates) for the velocity $v$ (equation \ref{eq:VCR_EulerInclArtVis}), the internal energy $e$ (equation\ref{eq:ECR_EulerInclArtVis}) and, if the continuity density appraoch is selected, the density $\rho$(equation\ref{eq:DCR_Euler}).
+Included in equations \ref{eq:ECR_EulerInclArtVis} and \ref{eq:VCR_EulerInclArtVis} is the artificial viscosity term, which is basically calculated according to equation \ref{eq:MonArtVis}.
+For the specific case of a shock tube problem however, it is usual to apply artificial viscosity only in zones where particles are approaching each other and to set it to zero in zones where particles are receding.
+This ensures that the artificial viscosity is used for shocks and not for rarefactions\cite{Monaghan2005}.
+As the described 1D SPH code is (exclusively) apllied to a shock tube problem, this fact/matter/issue has to be taken into account.
+The criterion for not receding(as there is a $\leq$ in Monaghan05 and not a pure <) particles being 
+\begin{equation}
+ v_{ab}\cdot r_{ab}\leq 0
+\end{equation}
+the final expression for the artificial viscosity in this 1D shock tube program is
+\begin{equation}
+\Pi_{ab}=\begin{cases}
+\text{equation \ref{eq:MonArtVis}}, &  \text{for~} v_{ab}\cdot r_{ab}\leq 0 \\
+0,&  \text{for~} v_{ab}\cdot r_{ab}> 0 
+\end{cases}
+\end{equation}
+
+\begin{center}
+\sProofOn
+\begin{struktogramm}(130,110)[CALCDERIVATIVES()]
+  \assign{\(declare\ and\ initialize\ the\ needed\ variables\)}
+  \assign{\(reset\ the\ vectors\ d\rho,\ de,\ du\ for\ the\ cnage\ rates\ to\ zero\)}
+  \sub{\texttt{calcBuddies()}}
+  \ifthenelse[10]{6}{1}{\(sumdensity==1\ or\ first\ time\ step?\ \)}{Y}{N}
+    \assign{\(calculate\ \rho\ by\ smoothing:\) \\ \(-\ calculate\ self\ contribution\ for\ each\ particle\ \) \\ \( -\ calculate\ pair\ contribution\)}
+  \change
+  \ifend
+  \assign{\(calculate\ p\ and\ c\ for\ each\ particle\)}
+  \while[10]{\(for\ loop\ to\ iterate\ interaction\ list\ for\ calculation\ of\ change\ rates\)}
+    \assign{\(calculate\ values\ needed\ for\ artificial\ viscosity\ and\ change\ rates\)}
+    \ifthenelse[10]{6}{6}{\(interaction\ pair\ in\ compression?\)}{Y}{N}
+      \assign{\(calculate\ artificial\ viscosity\ \Pi_{ab}\)}
+    \change
+      \assign{\(set\ artificial\ viscosity\ \Pi_{ab}\ to\ zero\)}
+    \ifend
+    \assign{\(calculate\ contribution\ of\ current\ interaction\ pair\ to\ change\ rates\ du,\ de\)}
+    \ifthenelse[10]{6}{1}{\(sumdensity\ \neq1?\)}{Y}{N}
+      \assign{\(calculate\ contribution\ of\ interaction\ pair\ to\ change\ rate\ d\rho\)}
+    \change
+    \ifend
+    \assign{\(add\ contributions\ of\ change\ rates\ to\ the\ change\ rate\ variables\ \) \linebreak\((in\ the\ appropriate\ component\ of\ the\ change\ rate\ vectors)\)}
+  \whileend
+\end{struktogramm}
+\sProofOff
+\end{center}
+
+\paragraph{The calcBuddies() function}
+This function conducts the nearest neighboring particle search as described in \ref{sec:NNPS} using the pairwise interaction method.
+If two particles $i$ and $j$ constitute an interaction pair, their unique particle ID (see SETUPSIM) is stored in the same component of the vectors pairi and pairj respectively.
+pairi and pairj belong to the simulation data structure.
+
+\begin{center}
+\sProofOn 
+\begin{struktogramm}(130,90)[CALCBUDDIES()]
+  \assign{\(initialize\ the\ varibales\ to\ zero\ \)\\\((components\ of\ the\ two\ vectors\ pairi,\ pairj\ constituing\ the\ interaction\ list,\)\\ \(\ the\ counter\ for\ the\ total\ number\ if\ interactions,\ \) \\ \(the\ vectors\ containing\ w\ dW\ for\ each\ interaction\ pair,\)\\ \(...)\)}
+  \while[10]{\(loop\ from\ first\ to\ penultimate\ particle\)}
+    \while[10]{\(loop\ from\ second\ to\ last\ particle\)}
+      \ifthenelse[10]{6}{1}{\(are\ particles\ interacting?\)}{Y}{N}
+        \assign{\(increment\ counter\ of\ total\ interactions\ niac\)}
+        \assign{\(save\ the\ particle's\ IDs\ in\ the\ vectors\ pairi\ and\ pairj\)}
+        \assign{\(calculate\ kernel\ value\ W_{ab}\ and\ derivative\ dW_{ab}\)\\\( for\ interaction\ pair\)}
+        \ifthenelse[10]{6}{1}{\(niac\ \geq max.\ admissible?\)}{Y}{N}
+          \assign{\(output\ message\ on\ screen\ and\ exit\ program\)}
+        \change
+        \ifend
+      \change
+      \ifend
+    \whileend
+  \whileend
+\end{struktogramm}
+\sProofOff
+\end{center}
+
+\paragraph{The W() function}
+The W() function implements the smoothing kernel for the SPH method, which in this case is the cubic spline kernel (see \ref{sec:KernelFunction}).
+For implementation purposes the expression of this kernel function (\ref{eq:cubicSpline}) has been expanded resulting in
+
+\begin{equation}
+\label{eq:cubicSplineImplement}
+M_{4}(x)=\begin{cases}
+\frac{2}{3}-q^{2}+0,5q^{3},& \text{for 0 $\leq$ q $\leq$ 1} \\
+\frac{1}{6}(2-q)^{3},&  \text{for 1 $\leq$ q $\leq$ 2} \\
+O,& \text{for q $>$ 2}
+\end{cases}
+\end{equation}
+
+\begin{center}
+\sProofOn
+\begin{struktogramm}(100,31)[W()]
+  \case[15]{3}{3}{\(test\ distance\)}{\(is\ distance\ >2?\)}
+        \assign[10]{\(W\ according\ to \ \)\\(eq:\ref{eq:cubicSplineImplement})}
+    \switch{\(<1?\)}
+        \assign[10]{\(W\ according\ to \ \)\\(eq:\ref{eq:cubicSplineImplement})}
+    \switch[r]{\(else\)}
+      \assign[10]{\(W\ according\ to \ \)\\(eq:\ref{eq:cubicSplineImplement})}
+    \caseend
+  \assign{\(return\ W\)}
+\end{struktogramm}
+\sProofOff
+\end{center}
+
+\paragraph{The dW() function}
+The derivative of the smoothing kernel $\frac{dW}{dx}$ (in 1D) is calculated by this function.
+Based on the definition of the cubic Spline Kernel(\ref{eq:cubicSpline}), this derivative can be determined easily as
+
+\begin{equation}
+\label{eq:cubicSplineDer}
+M_{4}(x)=\begin{cases}
+\-2q+1,5q^2,& \text{for 0 $\leq$ q $\leq$ 1} \\
+-\frac{1}{2}(2-q)^{2},&  \text{for 1 $\leq$ q $\leq$ 2} \\
+O,& \text{for q $>$ 2}
+\end{cases}
+\end{equation}
+
+\begin{center}
+\begin{struktogramm}(100,31)[dW()]
+  \case[15]{3}{3}{\(test\ distance\)}{\(is\ distance\ >2?\)}
+        \assign{\(dW\ according\ to \ \)\\(eq:\ref{eq:cubicSplineImplement})}
+    \switch{\(<1?\)}
+        \assign{\(dW\ according\ to \ \)\\(eq:\ref{eq:cubicSplineImplement})}
+    \switch[r]{\(else\)}
+      \assign{\(dW\ according\ to \ \)\\(eq:\ref{eq:cubicSplineImplement})}
+    \caseend
+  \assign{\(return\ dW\)}
+
+\end{struktogramm}
+\end{center}
+
+\paragraph{The plotShock() function}
+This function corresponds to the output module as shown in \ref{fig:BasicSphCode} and writes the simulation results at a certain time step in a file named 'dataStepxxxxxx.txt, where xxxxx means the corresponding time step.
+The frequency of the output can be choosen by editing the parameter printstep (IN CODE STYLE) of the parameter data structure.
+Each output file has the following format:
+
+$x$ $\rho$ $p$ $u$ $e$
+(one line for each particle)
+(INSERT A TABLE FOR THE FILE STRUCTURE OR DIRECTLY A CAPTION OF THE TXT FILE...)
+\vspace{5mm}
+\sProofOn
+\begin{struktogramm}(127,60)[PLOTSHOCK()]
+  \assign{\(create\ name\ for\ the\ output\ file\ ('dataStepxxxxxx.dat')\)}
+  \assign{\(create\ outputfile\ itself\)}
+  \while[10]{\(loop\ over\ all\ particles\ (i=0\ until\ i<np)\)}
+    \assign{\(output\ component\ i\ of\ the\ position\ vector\ in\ file\)}
+    \assign{\(output\ component\ i\ of\ the\ density\ vector\ in\ file\)}
+    \assign{\(output\ component\ i\ of\ the\ pressure\ vector\ in\ file\)}
+    \assign{\(output\ component\ i\ of\ the\ velocity\ vector\ in\ file\)}
+    \assign{\(output\ component\ i\ of\ the\ internal\ energy\ vector\ in\ file\)}
+    \assign{\(linebreak\ in\ file\)}
+    \assign{\(increment\ i\ (next\ particle\)}
+  \whileend
+\end{struktogramm}
+\sProofOff
+
 \section{2D SPH code}
@@
 \section{1D SPH code}
-...Monaghan05 p.1739... not width important but pre and after shock values...
+...Monaghan05 p.1739... not shock width important but pre and after shock values...
 
@@
 
+\section{2D SPH code}
+
 \chapter{Conclusion}

### 2010-07-10 ms/titelblatt.tex
documentation updated

@@
 \begin{minipage}[c]{.43\textwidth}
-    { ~\\ Lehrstuhl f\"{u}r Aerodynamik \\ Prof.~Dr.-Ing. N.~A.~Adams}%
+    { ~\\ Institute of Aerodynamics \\ Prof.~Dr.-Ing. N.~A.~Adams}%
 \end{minipage}
@@
 {\LARGE\bf 
-A Riemann solver }
+Simuation of a high enthalpy flow through porosities using SPH}
 \end{minipage}
@@
 \vspace*{0.8cm}
-Mark F\"{o}rster\\
+Oliver Oberinger\\
 
@@
 \begin{tabular}{ll}
-Betreuer: &  Dr.-Ing. Christian Stemmer \\
+Betreuer: &  Dipl.-Ing. Sergey Litvinov \\
 \ & \ \\
-Ausgabe: & 1.\ Oktober 2008\\
-Abgabe: & 31.\ M\"{a}rz 2009\\
+Ausgabe: & 15.\ Juni 2010\\
+Abgabe: & 15.\ Dezember 2010\\
 \end{tabular}
@@
 %\large
-Lehrstuhl f\"{u}r Aerodynamik an der Technischen Universit\"{a}t M\"{u}nchen\\
-2009
+Institute of Aerodynamics Technische Universit\"{a}t M\"{u}nchen\\
+Graduate Aerospace Laboratories California Institute of Technology
+2010	
 \end{center}

### 2010-07-13 ms/main.tex
changed mass initiation, litte change in dat2punto.sh

@@
 analysis of the acting phenomena. The simulation method of choice for the first approach
-to this configuration is called Smoothed Particle Hydrodynamics (SPH).Although
+to this configuration is called Smoothed Particle Hydrodynamics (SPH). Although
 there has been no known application of SPH to this precise/concrete case yet/before,
@@
 The initial developement of the method dates back to 1977, where Gingold and
-Monaghan tempted to compute an astrophysical problem with a new, more
+Monaghan tempted to compute an astrophysical gas dynamics problem with a new, more
 efficient method~\cite{Gingold1977}. Independently and simultaneously, work in
@@
 
-INTRODUCE THE TWO CODES AND MENTION THAT THEY ARE WRITTEN IN C/C++...
+INTRODUCE THE TWO CODES AND MENTION THAT THEY ARE CODED IN C/C++...
 
@@
 To illustrate the basic idea of SPH, it is helpful to first have a look at the
-ruling equations of fluid dynamics, here represented by the SPH equations in
-lagrangian form. The use of the lagrangian form seems logical as SPH is a
+ruling equations of fluid dynamics, here represented by the Navier stokes equations in
+lagrangian form (using the substantive derivative). The use of the lagrangian form seems logical as SPH is a
 particle method.
@@
 \end{equation}
+is the substantive derivative.
 
@@
 
-Applying the particle approximation on \ref{eq:int_interpolant} leads with the
-relation between mass, density and volume for each discretized particle
+With the relation between mass, density and volume for each discretized particle
 \begin{equation}
 m_i=\rho_i V_i
-\end{equation}
- to the following expression
+\end{equation},
+applying the particle approximation on \ref{eq:int_interpolant} leads to the following expression
 
@@
 
-In the same way, the derivative of the fieldfunction $frac{dA(x)}{dx}$ can be
+In the same way, the derivative of the field function $frac{dA(x)}{dx}$ can be
 approximated to give\cite{Monaghan2005}or\cite{Liu2003}(in Liu with gradient,
@@
 SPH form  equation \ref{eq:derivativeIdentity} reads as follows:
+
 \begin{equation}
@@
 It can be seen, that the (approximation of the) derivative of the
-field function $A$ is now expressed by a summation over the fieldfunction itself
+field function $A$ is now expressed by a summation over the field function itself
 and the derivative of the kernel function - which can be determined exactly.
@@
 Now the basic formulations are introduced in principle: Both the fieldfunction
-itself and its spacial derivatives can be approximated using only information
-(=the states) of a discrete number of particles. Hence, the change rates of
+itself and its spacial derivatives can be approximated using only information of a discrete number of particles. Hence, the change rates of
 the states described by the equations of fluid dynamics, which have a form
@@
 the field function and its spacial derivatives dependent exclusively on discrete values
-of the fieldfunction itself (and the kernel function, which is known as well as
-its derivatvies).By finally choosing an appropriate kernel function with
+of the fieldfunction itself (and of the kernel function, which is known as well as
+its derivatvies). By finally choosing an appropriate kernel function with
 compact support, the summation over all particles in the domain can be reduced
@@
 internal energy based on the EULER EQUATIONS (i.e. without viscosity) is
-listed\cite{Monaghan2005}\cite{Liu2003} (perhaps also list NSG-form, and
+listed\cite{Monaghan2005,Liu2003} (perhaps also list NSG-form, and
 explain why Euler is of interest as well (for 1DSPH code, perhaps later real
@@
 
-mention somewhere that kernel unity is inverse of volume?!?!?
+...mention somewhere that kernel unity is inverse of volume?!?!?
 
@@
 
-ILLUSTRATION OF VELOCITY ASSIGNMENT FOR VIRTUAL BOUNDARY PARTICLES
+FIGURE: ILLUSTRATION OF VELOCITY ASSIGNMENT FOR VIRTUAL BOUNDARY PARTICLES
 
@@
 
-DIAGRAM WITH CELLS /PARTICLES /DOMAIN!?!
+FIGURE: DIAGRAM WITH CELLS /PARTICLES /DOMAIN!?!
 
@@
 
-...equation of state in the original form...
-
-...
-transformation steps (or at least realations needed)...
+%...equation of state in the original form...
+
+%...
+%transformation steps (or at least realations needed)...
 
@@
 The textual description is not complete but only comprises particularities and features that are considered worth mentionning.
-A Nassi-Schneidermann-Diagram (NSD)~\cite{Nassi???} complements each description and shows the control flow for each function as well as the interdependence of the individual functions.
+A Nassi-Schneidermann-Diagram (NSD)~\cite{Nassi1973} complements each description and shows the control flow for each function as well as the interdependence of the individual functions.
 For the sake of a clear illustration , the NSD does not display every loop of the program; frequently, loops over all particles and the interaction list are ommitted (the instruction 'calculate ...
@@
 \paragraph{Explanation of a Nassi-Schneidermann-Diagram}
-A NSD Diagram is employed in this section as it allows for a more compact description of the code structure within limited space than a conventional flow diagram and, in addition, offers a range of further advantages~\cite{Nassi???}.
+A NSD Diagram is employed in this section as it allows for a more compact description of the code structure within limited space than a conventional flow diagram and, in addition, offers a range of further advantages~\cite{Nassi1973}.
 It is read from top to bottom, with different box symbols representing different kinds of instructions or control elements.

### 2010-07-13 ms/titelblatt.tex
changed mass initiation, litte change in dat2punto.sh

@@
   \begin{flushleft}
-    \includegraphics[width=3cm,clip=]{LOGO/new-aerlogo.eps}%
+    \includegraphics[width=3cm,clip=]{LOGO/caltech_logo.eps}%
   \end{flushleft}
@@
 \begin{minipage}[c]{.43\textwidth}
-    { ~\\ Institute of Aerodynamics \\ Prof.~Dr.-Ing. N.~A.~Adams}%
+\vspace*{1em}
+    {GALCIT (Caltech)\\Prof. Hans G. Hornung \\ \\ Institute of Aerodynamics (TUM) \\ Prof.~Dr.-Ing. N.~A.~Adams}%
 \end{minipage}
@@
 \begin{tabular}{ll}
-Betreuer: &  Dipl.-Ing. Sergey Litvinov \\
-\ & \ \\
+Betreuer: & ~Prof. Hans G. Hornung (Caltech)\\
+\ & \ Dipl.-Ing. Sergey Litvinov (TUM)\\
+ \\
 Ausgabe: & 15.\ Juni 2010\\
@@
 Institute of Aerodynamics Technische Universit\"{a}t M\"{u}nchen\\
-Graduate Aerospace Laboratories California Institute of Technology
+Graduate Aerospace Laboratories California Institute of Technology\\
 2010	

### 2010-07-13 cases/create_IC.cpp

@@ -18,7 +18,7 @@ int main ()
   double delta_l=0.001875;
   double delta_r=0.001875*8;
   int N_r;
-  N_r=domain_size/2/delta_r;
+  N_r=domain_size/2/delta_r+1;
   int  N_l;
   N_l=domain_size/2/delta_l;
   int N;

### 2010-07-13 src/Kernel/cubicspline.cpp

@@ -1,4 +1,4 @@
-///\file quinticspline.cpp
+///\file cubicspline.cpp
 ///\author Xiangyu Hu <Xiangyu.Hu@aer.mw.tum.de>
 ///\author changes by: Martin Bernreuther <Martin.Bernreuther@ipvs.uni-stuttgart.de>, 
 

### 2010-07-22 src/Kernel/cubicspline.cpp
shock tube works, leap frog integrator, summation and continuity density implemented

@@ -30,7 +30,7 @@ const double pi = 3.141592653589793238462643383279502884197;
 /// Cubic spline kernel (see Liu eq. (3.6)
 CubicSpline::CubicSpline(const double supportlength)
   : Kernel(supportlength),
-    norm( 10.0 / (7.0*pi)  / (supportlength*supportlength) ) ,
+    norm( /*10.0 / (7.0*pi)*/1.0/3.0  / (supportlength/**supportlength*/) ) ,
     factorGradW( 2.0*norm /supportlength )
 {
   // initialize the auxiliary factors
@@ -44,7 +44,7 @@ double CubicSpline::w(const double distance) const
   const double R= 2.0 * distance/ supportlength;
   if(R>2.0)
     {
-      //support of 4h, everything beyond is zero
+      //support of 4h (supportlength =2h, h=0.015), everything beyond is zero
       return 0.0;
     }
   else if(R>1.0) {
@@ -79,14 +79,14 @@ double CubicSpline::F(const double distance) const
   }
   else if(R>1.0 ) {
     const double s2 = 2.0 - R;
-    return  factorGradW * ( 3.0 * s2*s2);
+    return/*minus inserted!!! */ - factorGradW * ( 3.0 * s2*s2);
   } else  {
     const double s1 = 1.0 - R;
     const double s2 = 2.0 - R;
-    return  -factorGradW * ( 12.0 * s1*s1 - 3.0 * s2 * s2 );
+    return /* -*/factorGradW * ( 12.0 * s1*s1 - 3.0 * s2 * s2 );
   }
 }
 
 void CubicSpline::show_information() const {
-  std::cerr << "(kernel) QubicSpline\n";
+  std::cerr << "(kernel) CubicSpline\n";
 }

### 2010-07-22 src/TimeSolver/gastimesolver.h

@@ -18,6 +18,10 @@ public:
   void TimeIntegral_summation(Hydrodynamics &hydro, ParticleManager &particles, 
                               Boundary &boundary, double &Time, double D_time, 
                               const Initiation &ini, spKernel weight_function);
+void TimeIntegral(Hydrodynamics &hydro, ParticleManager &particles, 
+                              Boundary &boundary, double &Time, double D_time, 
+                              const Initiation &ini, spKernel weight_function);
+
   void show_information() const;
 };
 #endif //GAS_TIMESOLVER_H

### 2010-07-22 src/TimeSolver/hydrotimesolver.h

@@ -18,6 +18,10 @@ public:
   void TimeIntegral_summation(Hydrodynamics &hydro, ParticleManager &particles, 
                               Boundary &boundary, double &Time, double D_time, 
                               const Initiation &ini, spKernel weight_function);
+/// advance time interval D_time with integration for density (has still to be implemented)
+void TimeIntegral(Hydrodynamics &hydro, ParticleManager &particles, 
+                              Boundary &boundary, double &Time, double D_time, 
+                              const Initiation &ini, spKernel weight_function);
 
   /// show some information about the solver
   void show_information() const;

### 2010-07-22 src/TimeSolver/timesolver.h

@@ -16,6 +16,12 @@ class TimeSolver : boost::noncopyable {
   virtual void TimeIntegral_summation(Hydrodynamics &hydro, ParticleManager &particles, 
                                       Boundary &boundary, double &Time, double D_time, 
                                       const Initiation &ini, spKernel weight_function) = 0;
+
+ /// advance time interval D_time with integration for density
+  virtual void TimeIntegral(Hydrodynamics &hydro, ParticleManager &particles, 
+                                      Boundary &boundary, double &Time, double D_time, 
+                                      const Initiation &ini, spKernel weight_function) = 0;
+
   /// print kernel type
   virtual void show_information() const = 0;
  protected:

### 2010-07-22 src/hydrodynamics.cpp

@@ -110,6 +110,12 @@ void Hydrodynamics::UpdateDensity(ParticleManager &particles, spKernel weight_fu
   ///- iterate the interaction list
   BOOST_FOREACH(spInteraction pair, interaction_list) {
     pair->SummationDensity();	
+  };
+
+  LOG(INFO)<<"density after smoothing";
+
+  BOOST_FOREACH(spParticle prtl, particle_list){
+    LOG(INFO) << setprecision (20)<<::setw( 7 )<<prtl->ID<< ::setw( 25 )<<prtl->rho<<::setw( 7 )<<endl;
   }
 		
   ///- calulate new pressure by calling UpdateState() Method
@@ -127,6 +133,11 @@ void Hydrodynamics::UpdateDensity(const Initiation &ini, spKernel  weight_functi
   BOOST_FOREACH(spInteraction pair, interaction_list) {
     pair->SummationDensity();	
   }
+ // LOG(INFO)<<"density after smoothing";
+
+ //  BOOST_FOREACH(spParticle prtl, particle_list){
+ //    LOG(INFO) << setprecision (9)<<prtl->ID<<"    "<<prtl->rho<<endl;
+ //  }
 
   ///- calulate new pressure by calling UpdateState()
   UpdateState(ini);
@@ -168,10 +179,52 @@ void Hydrodynamics::UpdateChangeRate(const Initiation& ini) {
   BOOST_FOREACH(spParticle prtl, particle_list) {
     LOG_EVERY_N(INFO, 100) <<"dUdt: "<<prtl->dUdt[0] << " dUdt1: "<<prtl->dUdt[1];
   }
+
+
+ofstream tx2tFile("DerivativesDataN1");
+	if (tx2tFile.is_open())
+        {
+        BOOST_FOREACH(spParticle prtl, particle_list) {
+	  
+	  tx2tFile <<setprecision (9)<< ::setw( 5 )<<prtl->ID<< ::setw(20)<<prtl->dUdt[0]<<::setw(20)<<prtl->dUdt[1]<<::setw(20)<<prtl->dedt<<endl;
+	
+	  }
+	tx2tFile.close();
+	}
+		else cout << "Unable to open/create file";
+
+BOOST_FOREACH(spParticle prtl, particle_list) {
+    LOG_EVERY_N(INFO, 100) <<"dUdt: "<<prtl->dUdt[0] << " dUdt1: "<<prtl->dUdt[1];
+  }
+
+
[…]

### 2010-07-22 src/interaction.h

@@ -59,11 +59,13 @@ class Interaction {
 
   ///update forces
   void UpdateForces();
+  void UpdateForcesAndRho();
 
   spParticle  getOrigin() const;
   spParticle  getDest() const;
   double getWij() const;
   Vec2d getGradWij() const;
+  double get_rij() const;
 
   /// destructor 
   ~Interaction();

### 2010-07-22 src/output.cpp

@@ -74,13 +74,13 @@ void Output::OutputParticle(Hydrodynamics &hydro, Boundary &boundary,
 	      << "  " << prtl->rho << '\n';
         }
 	if (ini.simu_mode == 2)
-	  out<<setprecision(6)
-	     << ::setw(16)<<prtl->R[0] 
-	     << ::setw(16)<<prtl->R[1] 
-	     << ::setw(16) <<prtl->rho 
-	     << ::setw(16)<<prtl->p
-	     << ::setw(16)<<prtl->U[0]
-	     << ::setw(16)<<prtl->e
+	  out<<setprecision(9)
+	     << ::setw(19)<<prtl->R[0] 
+	     << ::setw(19)<<prtl->R[1] 
+	     << ::setw(19) <<prtl->rho 
+	     << ::setw(19)<<prtl->p
+	     << ::setw(19)<<prtl->U[0]
+	     << ::setw(19)<<prtl->e
 	     <<"  "<<prtl->ID<<"\n";
       }
     }

### 2010-07-22 src/sph.cpp

@@ -65,12 +65,12 @@ int main(int argc, char *argv[]) {
   std::string aux_string  = std::string(argv[1]);
   ///- global initialization 
   /// (by defining an object of class Initiation (initialization "automatically" done at this moment 
-  /// (from .cfg or .rst file) by constructor method of Initiation class. 
+  /// (from .tcl or .rst file) by constructor method of Initiation class. 
   /// That is by the way the reason why the initiation::initiation method does not figure 
   /// in the call graph of the main function (constructors are not shwon there)
   Initiation ini(aux_string); 
 
-  /// choost a kernel
+  /// choose a kernel
   spKernel weight_function;
   if  (ini.kernel_type == "CubicSpline")   {
       weight_function = boost::make_shared<CubicSpline>(ini.supportlength); 
@@ -81,7 +81,7 @@ int main(int argc, char *argv[]) {
   else if (ini.kernel_type == "QuinticSpline")   {
       weight_function = boost::make_shared<QuinticSpline>(ini.supportlength); 
   } else {
-      std::cerr << __FILE__ << ':' << __LINE__ << " unknown kerenel type (KERNEL_TYPE in configuration file)\n" ;
+      std::cerr << __FILE__ << ':' << __LINE__ << " unknown kernel type (KERNEL_TYPE in configuration file)\n" ;
       std::cerr << __FILE__ << ':' << __LINE__ << " KERNEL_TYPE: " << ini.kernel_type;
       exit(EXIT_FAILURE);
   }
@@ -93,7 +93,7 @@ int main(int argc, char *argv[]) {
   Hydrodynamics hydro(particles, ini); ///- create materials, forces and real particles
   Boundary boundary(ini, hydro, particles); ///- initiate boundary conditions and boundary particles
   
-  /// a smart pinter to timesolver
+  /// a smart pointer to timesolver
   spTimeSolver timesolver;
   switch (ini.simu_mode) {
     case 1: 
@@ -134,13 +134,17 @@ int main(int argc, char *argv[]) {
     srand( static_cast<unsigned int>(time( NULL ) ));
 		
     //control output
-    LOG(INFO)<< "new output intervall beginns:output interval time:" << ini.D_time;
+    LOG(INFO)<< "new output intervall begins:output interval time:" << ini.D_time;
 		  
     ///- call the time slover (who iterates over one output time interval)
-    timesolver->TimeIntegral_summation(hydro, particles, boundary, Time, 
[…]

### 2010-07-28 src/output.cpp
added some missing files for documentation

@@ -51,7 +51,7 @@ void Output::OutputParticle(Hydrodynamics &hydro, Boundary &boundary,
   if( ini.simu_mode==1)
     out<<"variables=x, y, Ux, Uy rho\n";
   if (ini.simu_mode==2)
-    out<<"variables=x, y, rho, p, U, e \n";
+    out<<"variables=x, y, rho, p, U, e, ID, m \n";
   int f=0, g=0, a=0, b=0; 	
   ///<li>output real and soild particles
   for(int i = 0; i < ini.number_of_materials; i++) {

### 2010-08-02 ms/main.tex
shock tube works, leap frog integrator, summation and continuity density implemented

@@
 
-This work aimes at the numerical simluation of high enthalpy flow in
+This work aims at the numerical simulation of high enthalpy flow in
 porosities. The subject is of interest, as CITATION
@@
 dynamics~\cite{Monaghan2005}.
-The initial developement of the method dates back to 1977, where Gingold and
+The initial development of the method dates back to 1977, where Gingold and
 Monaghan tempted to compute an astrophysical gas dynamics problem with a new, more
@@
 approximation consists in transforming the integral over the domain into a
-summation over the discrete elements constituing this domain (the particles). This allows to express both
+summation over the discrete elements constituting this domain (the particles). This allows to express both
 the field function and its spacial derivatives dependent exclusively on discrete values
 of the fieldfunction itself (and of the kernel function, which is known as well as
-its derivatvies). By finally choosing an appropriate kernel function with
+its derivatives). By finally choosing an appropriate kernel function with
 compact support, the summation over all particles in the domain can be reduced
@@
 
-As already mentionned above, the SPH formulation of the equations of fluid
+As already mentioned above, the SPH formulation of the equations of fluid
 dynamics is obtained by applying the above principles and conducting different
@@
 Another point that has to be taken into account for SPH simulations, especially
-such including shock phenomena, is arificial viscosity\cite{Monaghan2005}. It
+such including shock phenomena, is artificial viscosity\cite{Monaghan2005}. It
 prevents particles from penetrating one into an other in zones with high
 compression rates and also generally stabilizes a numerical
-allgorithm.
+algorithm.
 Artificial viscosity for numerical simulation of shock phenomena
@@
 low density respectively low particle presence. 
-Finally, the form of artificial viscosity most commomly used in SPH
+Finally, the form of artificial viscosity most commonly used in SPH
 literature\cite{Liu2003} is the one proposed by Monaghan and
@@
 located in the support domain of a particle $b$ but not vice versa. This would
-lead to an assymetric mutual contribution of forces. To avoid this, using the
+lead to an asymmetric mutual contribution of forces. To avoid this, using the
 averaged smoothing length between two particles is an appropriate remedy\cite{Liu2003}.
@@
 Points of interest are the implementation of different boundary conditions in
-SPH, a closer description of the kernel function, as well as different methods/allgorithms
+SPH, a closer description of the kernel function, as well as different methods/algorithms
 to perform the search for the interacting particles. Furthermore different
@@
 the simple fact that outside the domain there are no
-particles.\cite{Liu2003}(find better citation...) This efect is called the
+particles.\cite{Liu2003}(find better citation...) This effect is called the
 problem of article deficiencythe particle deficiency
@@
 But for other applications the edges play an important role or the domain has
-to be rendered periodocally. So there is a need to define specific boundary
+to be rendered periodically. So there is a need to define specific boundary
 conditions. This can be accomplished by a special boundary treatment, which
@@
 Some properties of Kernel functions (smoothing functions) and notions related
-to them have allready been mentionned in the section
+to them have already been mentioned in the section
 \ref{sec:BasicsSPH}. In principal every function can act as Kernel function
-when it respects a set of criteria complsed by \cite{Liu2003}.
+when it respects a set of criteria composed by \cite{Liu2003}.
 The most important ones are:
@@
 
-In the work of \cite{Fulk1996} a mesure of merit for Kernels is developed and
+In the work of \cite{Fulk1996} a measure of merit for Kernels is developed and
 they came to the result, that in 1D no kernel performed significantly better
@@
 To calculate the change rates in \ref{eq:DCR_Euler}-\ref{eq:ECR_Euler} a
-summation over all paricles has to be performed. However, as we defined kernel
+summation over all particles has to be performed. However, as we defined kernel
 functions with a compact support, only particles within a certain distance from
@@
   \centering
-      \includegraphics[width=1.0\textwidth]{Graphics/general_structure_SPH}
+     % \includegraphics[width=1.0\textwidth]{Graphics/general_structure_SPH}
   \caption{basic structure of an SPH code}

### 2010-09-24 scripts/postProcessingTaylorGreen/VelocDecayAnalysisTG_const_dt.cpp
corrected error norms, all results post-processed with new norms, implemented physical viscosity (constant in first step and only in momentum equation), adapted output to SPLASH visualization program

@@ -1,0 +1,201 @@
+
+
+#include <iostream>
+#include <iomanip>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdlib.h>
+#include <string.h>
+#include <vector>
+#include <math.h>
+
+
+using namespace std;
+
+int main (){
+
+  int n_col=0;// number of columns in inputfile
+
+  cout<<"\n"<<"please enter the number of columns in the input file:  ";
+  cin>>n_col;
+
+  double buffer;
+  double timeInterval;// output time interval for simulation data output files
+  int counter=0;
+  vector<double> row(n_col,0);
+  vector <vector <double> > inputFileData; // stores data read from inputfile
+  vector <vector <double> > MaxVelocAllInstants;// vector for max velocities of all instants and their corresponding time value
+  vector <double>maxVelThisInstAndTime(2,0);
+  int fileCounter=0;
+  
+  cout<<"please enter the output time interval in s (as specified in TaylorGreen.tcl file:"<<endl;
+  cin>>timeInterval;
+  
+  // while loop over all output interval values
+  for(;;) {
+    double maxVelocThisInstant=-10000;// max velocity of current instant(=output time)
+    
+    // assemble input file name
+    stringstream number;// string for number (time stamp)
+    stringstream number2;// string for second time stamp if first one not o.k.
+    // calculate number (time stamp) for file name
+    // needs to be casted to int as otherwise numbers over 1,000,000 
+    // have the format 1e+6 which is not ok for the file name
+    number << setw(8) << setfill('0') <<(int)(fileCounter*timeInterval*1000000);
+    const string inputfile = "../../src/outdata/prtl" + number.str() + ".dat";
+    cout<<endl<<inputfile<<endl;
+
+    // create and open inputfile
+    ifstream fin(inputfile.c_str(), ios::in);
+    // test if inputfile opened, if not try different filename
+    if (!fin) {
+      // this is, as sometimes filenames are...999 instead of ..0000
+      // because time value is truncated for timestamp of file name...
+      number2 << setw(8) << setfill('0') <<(int)(fileCounter*timeInterval*1000000-1);
+      const string inputfile2 = "../../src/outdata/prtl" + number2.str() + ".dat";
+      cout<<endl<<inputfile2<<endl;
+      // assign a new filename to the streaming object
[…]

### 2010-09-24 src/Kernel/cubicspline.cpp

@@ -60,7 +60,7 @@ Vec2d CubicSpline::gradW(const double distance, const Vec2d& distanceVector) con
 //----------------------------------------------------------------------------------------
 double CubicSpline::F(const double distance) const
 {
-  double R= 2.0*distance/ supportlength; // 
+  double R= 2.0*distance/ supportlength; 
   if (R>2.0) {
     //support of 4h, everything beyond is zero    
     return 0.0;

### 2010-09-24 src/TimeSolver/gastimesolverLeapFrog.cpp

@@ -48,13 +48,13 @@ void GasTimeSolverLeapFrog::TimeIntegral_summation(Hydrodynamics &hydro, Particl
   double integeral_time = 0.0;
   /// loop as long as time < output interval
   while(integeral_time < D_time) {
-
-    ///\todo{ move into Initiation?...and/or make time step calculation automatically (constant time step was only for testing purposes)}
-    //const double dt = 0.0025;
     
-    ///<ul><li> call for automatic time step control GasDyn
-     const double dt=hydro.GetTimestepGas(ini);
-    // const double dt=0.000422577127;
+    ///<ul><li> call automatic time step control GasDyn or take manual dt (depending on preference specified in .tcl-file)
+    double dt;//time step
+    if(ini.autom_dt_control==1)
+      dt=hydro.GetTimestepGas(ini);
+    else
+      dt=ini.manually_choosen_dt;
     
     //control output
     LOG(INFO)<<"\n current timestep:"<<dt;
@@ -106,6 +106,9 @@ void GasTimeSolverLeapFrog::TimeIntegral_summation(Hydrodynamics &hydro, Particl
       hydro.AdvanceFirstStep(dt);
     else 
       hydro.AdvanceStandardStep(dt);
+
+    //udate particle volume (this is neccerary each time the particle position has changed)
+    hydro.UpdateVolume(particles, weight_function);
     
     if  (ini.disable_boundary != 1)
       ///run away check before cell link lists are updated (due to index purposes)
@@ -122,10 +125,14 @@ void GasTimeSolverLeapFrog::TimeIntegral(Hydrodynamics &hydro, ParticleManager &
 {
   double integeral_time = 0.0;
   while(integeral_time < D_time) {
-    
-    ///<ul><li> call for automatic time step control GasDyn
-    const double dt=hydro.GetTimestepGas(ini);
-    
+
+    ///<ul><li> call automatic time step control GasDyn or take manual dt (depending on preference specified in .tcl-file)
+    double dt;//time step
+    if(ini.autom_dt_control==1)
+      dt=hydro.GetTimestepGas(ini);
+    else
+      dt=ini.manually_choosen_dt;
+        
     //control output
     LOG(INFO)<<"\n current timestep:"<<dt;
     LOG(INFO)<<"\n current absolute integraltime:"<<Time;
[…]

### 2010-09-24 src/material.h

@@ -24,8 +24,9 @@ public:
 	int material_type;
 
 	double cv;///<heat capacity
-	double eta;///<viscosity
-	double gamma; ///<???
+	double eta;///<(shear) viscosity
+	double zeta;///<bulk viscosity
+	double gamma; ///<ratio of specific heats (adiabatic index)
 
 	double nu; ///<kinetice viscosity
 	double b0;///<reference pressure

### 2010-09-30 scripts/InitCondTaylorGreen/create_ICTaylorGreen.cpp
little modifications during viscosity error search

@@ -17,7 +17,7 @@ int main () {
   double y=0;
   const double domain_size_x=1.0;
   const double domain_size_y=domain_size_x;
-  const int N_x=100;
+  const int N_x=60;
   const int N_y=N_x;
   const int N=N_x*N_y;
   const double dx=domain_size_x/N_x;

### 2010-09-30 src/particle.h

@@ -37,7 +37,7 @@ class Particle {
 	///particle states copier for boundary particles
 	void StatesCopier(spParticle RealParticle , const int type);
 
-	/// \brief boundary particle or not
+	/// \brief boundary particle or not (click for mor info)
 	///
 	///- 0: inside the boundary
 	///- 1: on the boundary
@@ -52,9 +52,12 @@ class Particle {
 	///for ghost particles: pointer to their real particle
 	spParticle rl_prtl;
 
-	///for time step control: max value (over all interaction partners) of
-	///mue_ab (paramter for monaghan art. viscosity,
+	///\brief for time step control (click for more info)
+	///
+	/// max value (over all interaction partners) of
+	/// mue_ab (paramter for monaghan art. viscosity,
 	/// cf. Monaghan 1992 SPH review
+	/// (mue_ab has the units of a dynamic viscosity: [Pa s])
 	double mue_ab_max;
 
 	//Physical data
@@ -87,7 +90,7 @@ class Particle {
 	Vec2d dUdt;///<acceleration change for real particles <b>or is it the other wa round</b>
 
 
-	///\brief ID number
+	///\brief ID number (click for more info)
 	///
 	///- a real particle has a unique positive ID
 	///- a wall particle has zero ID

### 2010-10-17 ms/titelblatthh.tex
added some missing files for documentation
incl. heat conduction and its validation

--- 2010-07-13 ms/titelblatt.tex
@@
   \begin{flushleft}
-    \includegraphics[width=3cm,clip=]{LOGO/caltech_logo.eps}%
+    \includegraphics[width=3cm,clip=]{LOGO/caltech_logo}%
   \end{flushleft}
@@
     \vspace*{1em}
-    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB.eps}%
+    \includegraphics[width=3cm,clip=]{LOGO/TUMLogo_oZ_Vollfl_blau_RGB}%
   \end{flushright}
@@
 {\LARGE\bf 
-Simuation of a high enthalpy flow through porosities using SPH}
+Simuation of high enthalpy flow in porosities using SPH}
 \end{minipage}

### 2010-10-17 gnuplot/PureHeatConduction/EnergyContentEvolution.sh

@@ -1,0 +1,20 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+gnuplot << EOF
+set terminal postscript eps enhanced color  "Helvetica" 26
+
+set output "EnergyContentEvolution.eps"
+
+
+set grid;
+set xlabel "Time"; set ylabel "Energy Content";
+plot [0.0:600][0.0:0.65] 'energyContentEvolution.dat' u 1:2 title 'simu' with line lw 3;
+set terminal png large
+set output "EnergyContentEvolution.png"
+replot
+
+reset
+
+EOF

### 2010-10-17 ms/Graphics/results/PureHeatConduction/EnergyContentEvolution.sh

@@ -1,0 +1,20 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+gnuplot << EOF
+set terminal postscript eps enhanced color  "Helvetica" 26
+
+set output "EnergyContentEvolution.eps"
+
+
+set grid;
+set xlabel "Time"; set ylabel "Energy Content";
+plot [0.0:600][0.0:0.65] 'energyContentEvolution.dat' u 1:2 title 'simu' with line lw 8;
+set terminal png large
+set output "EnergyContentEvolution.png"
+replot
+
+reset
+
+EOF

### 2010-10-17 ms/Graphics/results/PureHeatConduction/ErrorTimestep.sh

@@ -1,0 +1,27 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+gnuplot << EOF
+set terminal postscript eps enhanced color  "Helvetica" 26
+
+set output "ErrorTimestep.eps"
+
+
+set logscale x
+set logscale y
+set format y "10^{%L}"
+
+#set ylabel "Y-AXIS" 2,0 # to move y axis to the left by 2 points
+
+set grid;
+set xlabel "Timestep"; set ylabel "Error";
+plot  'ErrorTimestep.dat' u 1:2 title 'L_{1 } error' with linespoints lw 8, 'ErrorTimestep.dat' u 1:3 title 'L_{2 } error' with linespoints lw 8,'ErrorTimestep.dat' u 1:4 title 'L_{inf} error' with linespoints lw 8;
+
+set terminal png large
+set output "ErrorTimestep.png"
+replot
+
+reset
+
+EOF

### 2010-10-17 ms/Graphics/results/PureHeatConduction/isothermal/simulatedProfileOnly.sh

@@ -1,0 +1,22 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+
+gnuplot << EOF
+set terminal postscript eps enhanced color  "Helvetica" 26
+
+set output "T_profile$1.eps"
+
+
+set grid;
+set xlabel "Length"; set ylabel "Temperature";
+plot [0.0:1.0][-0.15:1.15] 'simuForPlot$1.dat' u 1:2 title 'simu' with points;
+
+set terminal png large
+set output "T_profile$1.png"
+replot
+
+reset
+
+EOF

### 2010-10-17 ms/Graphics/results/PureHeatConduction/simulatedProfileOnly.sh

@@ -1,0 +1,21 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+gnuplot << EOF
+set terminal postscript eps enhanced color  "Helvetica" 26
+
+set output "T_profile$1.eps"
+
+
+set grid;
+set xlabel "Length"; set ylabel "Temperature";
+plot [0.0:1.0][0.49:0.51] 'simuForPlot$1.dat' u 1:2 title 'simu' with points;
+
+set terminal png large
+set output "T_profile$1.png"
+replot
+
+reset
+
+EOF

### 2010-10-17 ms/Graphics/results/PureHeatConduction/tempErrEvolution.sh

@@ -1,0 +1,24 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+gnuplot << EOF
+set terminal postscript eps enhanced color  "Helvetica" 26
+
+set output "temporalErrEvolution.eps"
+
+set format y "10^{%L}"
+set logscale y
+#set ylabel "Y-AXIS" 2,0 # to move y axis to the left by 2 points
+
+set grid;
+set xlabel "Time"; set ylabel "Error";
+plot [0.0:4.2][0.00001:0.08] 'tempErrEvolution.dat' u 1:2 title 'L_{1 } error' with linespoints lw 8, 'tempErrEvolution.dat' u 1:3 title 'L_{2 } error' with linespoints lw 8,'tempErrEvolution.dat' u 1:4 title 'L_{inf} error' with linespoints lw 8;
+
+set terminal png large
+set output "temporalErrEvolution.png"
+replot
+
+reset
+
+EOF

### 2010-10-17 scripts/InitCondPureHeatConduction/createIC_PureHeatConduction.cpp

@@ -1,0 +1,114 @@
+#include <iostream>
+#include <fstream>
+#include <cstring>
+#include <iomanip>
+#include <cstdio>
+#include <cstdlib>
+#include <math.h>
+
+using namespace std;
+
+// creates a slab of size (domain_size_x,domain_size_y) with equal
+// particle spacing in both directions (according to Cleary1999, test-case 5.1)
+
+// the temperature profile is T_l=const. in the left half and T_r=cosnt.
+// in the right half of the slab.
+
+int main () {
+  
+  //
+  const double rho=1000.0;// density 
+  const double domain_size_x=1.0;// domain size x-direction
+  const double domain_size_y=0.05;// domain size y-direction
+  const int N_x=40;// number of particles in x direction
+  const int N_y=2;
+ // const int N_y=N_x*(domain_size_y/domain_size_x);// number of particles in y directon
+  const int N=N_x*N_y;// total number of particles
+  const double dx=domain_size_x/N_x;// distance between two particles
+  const double dy=dx;//particles equispaced in both directions
+  double x=dx/2.0;// initialize x with dx/2 (=x-value of first row of particles)
+  double y=0;// y coordinate of particle
+  const double T_l=0.0;// LHS Temperature
+  const double T_r=1.0;// RHS Temperature
+  //vectors containing all particles' data for output in file 
+  double x_array[N];
+  double y_array[N];
+  double vx_array[N];
+  double vy_array[N];
+  double p_array[N];
+  double rho_array[N];
+  double m_array[N];
+
+  // m is not used in the simulation program
+  // it is written in theinitiation file
+  // only to maintain input-file structure
+  const double m=rho*dx*dy;
+
+  // p is not needed for the simulation either, BUT:
+  // I need p to create the desired Temperature profile because
+  // there is no direct initialiation with T or the internal energy.
+  // The Internal Energy or T are calculated within the simulation program
+  // based on rho, p and gamma (ideal gas equation of state)
+  // therefore I initialize p and rho in a way to obtain the desired 
+  // Temperatures T_l and T_r
[…]

### 2010-10-17 scripts/postProcessingHeatConduction/energyContentPureHeat.cpp

@@ -1,0 +1,173 @@
+
+#include <iostream>
+#include <iomanip>
+#include <fstream>
+#include <string>
+#include <sstream>
+#include <stdlib.h>
+#include <string.h>
+#include <vector>
+#include <math.h>
+
+
+using namespace std;
+
+int main (){
+  
+  const int n_col=11;// number of columns in inputfile (11 for SPLASH optimized output)
+  int fileCounter=0;// to count number of read input-files
+  // 2D vector containing energy_content and respective time for all instants
+  // format: (t, energy)
+  vector < vector < double > > TimeAndEnergyAllInstants;
+
+  // user input: output time interval of simulation:
+  cout<<" please enter output time interval (as specified in .tcl file)"<<endl;
+  double timeInterval;
+  cin>>timeInterval;
+  
+  // while loop over all output intervall values
+  for(;;) {
+    
+    // little passage to find and create good inputfile-name
+    
+    // assemble input file name
+    stringstream number;//string for number (time stamp)
+    stringstream number2;//string for second time stamp if first one not o.k.
+    stringstream number3;//string for second time stamp if second one not o.k.
+    // calculate number (time stamp) for file name
+    // needs to be casted to int as otherwise numbers over1,000,000 
+    // have the format 1e+6 which is not ok for the file name
+    number << setw(12) << setfill('0') <<(int)(fileCounter*timeInterval*1000000);
+    const string inputfile = "../../src/outdata/prtl" + number.str() + ".dat";
+    cout<<endl<<"trying "<<inputfile<<endl;
+    
+    // create and open inputfile
+    ifstream fin(inputfile.c_str(), ios::in);
+    // test if inputfile opened, if not try different filename
+    if (!fin) {
+      // this is as sometimes filenames are...999 instead of ..0000
+      // because time value is truncated (not  for timestamp of file name...
+      number2 << setw(12) << setfill('0') <<(int)(fileCounter*timeInterval*1000000-1);
+      const string inputfile2 = "../../src/outdata/prtl" + number2.str() + ".dat";
+      cout<<endl<<"trying "<<inputfile2<<endl;
+      // assign a new filename to the streaming object
+      fin.open(inputfile2.c_str(), ifstream::in);
+      // test if inputfile opened, if not try different filename
+      if (!fin) {
+	// this is as sometimes, when entering e.g.0.8673, program 
[…]

### 2010-10-17 src/glbfunc.h

@@ -8,4 +8,5 @@ double AMAX1(const double a, const double b);
 ///Get the minimum
 double AMIN1(const double a, const double b);
 double AMIN1(const double a, const double b, const double c);
+double AMIN1(const double a, const double b, const double c, double d);
 #endif

### 2010-10-17 src/initiation.h

@@ -51,9 +51,22 @@ public:
   int initial_condition;
 
   ///\brief disable boundary condition marker:
+  ///
   ///- 0 boundary conditions enabled
   ///- 1 boundary conditions disabled
   int disable_boundary;
+
+  ///\brief isothermal boundaries (for "free-slip" and "wall" only)
+  /// 
+  /// 0 NOT isothermal
+  /// 1 isothermal
+  int isothermal_boundary;
+
+  ///\brief marker for pure heat conduction simulation setup
+  ///
+  ///- 1: pure heat conduction ON (i.e. no change of quantities other than internak energy)
+  ///- 0: pure heat conduction OFF (normal flow simulation taking int account all change rates)
+  int pure_conduction; 
 
   ///simulation mode (1: liquids, 2: gas dynamics)
   int simu_mode;
@@ -97,6 +110,15 @@ public:
   /// 0: used for post-processing of shocktube cases and wave propagation; format: x, y, rho, p, Ux, e, ID, m
   /// 1: used for visualization with SPLASH-program; format x, y, Ux, Uy, rho, e, p, h=supportlength/2, m, V, ID
   int splash_optimized_output;
+
+  ///\brief  marker for 12-digit timestamp in file name (standard: 8 digit)
+  ///
+  /// this is necessary as for some applications (like pure heat conduction)
+  /// the simulation time is so huge that the standard time stamp is
+  /// not sufficient
+  /// 0: standard timestamp (8 digits)
+  /// 1: extra large timestamp (12 digits)
+  int xxl_timestamp_marker;
 
   //timing control
   double Start_time;///<Simulation start time

### 2010-10-17 src/interaction.h

@@ -37,6 +37,11 @@ class Interaction {
   double etaj;///<(shear) viscosity for particle j
   double zetai;///<bulk viscosity for particle i
   double zetaj;///<bulk viscosity for particle j
+  double ki;///<thermal conductivity for particls i
+  double kj;///<thermal conductivity for particle j
+  double Ti;///<Temperature of particle i
+  double Tj;///<Temperature of particle j
+
 
  public:
 
@@ -64,7 +69,9 @@ class Interaction {
   ///update forces
   void UpdateForces();
   void UpdateForcesAndRho();
-
+  ///update internal energy only (taking into account ony change rate due to heat coduction)
+  void UpdateEnergyPureConduction();
+    
   spParticle  getOrigin() const;
   spParticle  getDest() const;
   double getWij() const;

### 2010-10-17 src/material.cpp

@@ -38,6 +38,7 @@ Material::Material(Initiation &ini, const int number)
   eta = ini.interp.eval("[return $material_eta"  + index);
   if (ini.simu_mode == 2) {
    zeta = ini.interp.eval("[return $material_zeta"  + index);
+   k = ini.interp.eval("[return $material_k"  + index);
   }
   LOG(INFO) << "Material object is created";
 }
@@ -53,6 +54,7 @@ void Material::show_properties()
 	LOG(INFO)<<"The heat capacity is  "<<cv<<" J/kg/K\n";
 	LOG(INFO)<<"The (shear) viscosity is "<<eta<<" Pa.s \n";
 	LOG(INFO)<<"The bulk viscosity is "<<zeta<<" Pa.s \n";
+	LOG(INFO)<<"The thermal conductivity is "<<k<<" W/K/m \n";
 	LOG(INFO)<<"The heat ratio is "<<gamma<<"\n";
 	LOG(INFO)<<"The reference pressure b0 is "<<b0<<" Pa\n";
 	LOG(INFO)<<"The reference density is "<<rho0<<" kg/m^3 \n";
@@ -120,6 +122,6 @@ double Material::get_e(const double T) const
 double Material::get_Cs(const double p, const double rho)
 {
   assert(rho>0.0);
-  assert(p>0.0);
+  assert(p>=0.0);
   return sqrt(gamma*p/rho);
 }

### 2010-10-17 src/particle.h

@@ -84,6 +84,8 @@ class Particle {
 
 	double eta; ///<(shear) viscosity of each particle
 	double zeta; ///<bulk viscosity of each particle
+	double k;///< thermal conductivity
+	double cv;///< heat capacity at constant volume 
 	//change rate for real particles
 	double drhodt; ///<density change rate for real particles
         double dedt; ///<internal energy change rate for real particles

### 2010-10-17 ms/titelblattSUPAERO.tex
added report and presentation held for supaero

--- 2010-10-17 ms/titelblatthh.tex
@@
 {\LARGE\bf 
-Simuation of high enthalpy flow in porosities using SPH}
+Simulation of high enthalpy flow in porosities using SPH}
 \end{minipage}
 
-\vspace*{0.8cm}
+\vspace*{1.0cm}
+
 Oliver Oberinger\\
+\vspace*{1.0cm}
+{\bfseries Intermediate version of Master's Thesis}\\
+\vspace*{0.5cm}
+for presentation at \\
+\vspace*{0.3cm}
+Institut Sup\'{e}rieur de l'A\'{e}ronautique et de l'Espace\\
 
-\vspace*{2.8cm}
-{\bfseries Diplomarbeit}
+\begin{minipage}[c]{.25\textwidth}
+	\includegraphics[width=3cm,clip=]{LOGO/LogoISAE}\\
+\end{minipage}
+\\
+\vspace*{0.1cm}
+responsible at ISAE: J\'{e}r\'{e}mie Gressier (Professeur SUPAERO)
 
@@
 \begin{tabular}{ll}
-Betreuer: & ~Prof. Hans G. Hornung (Caltech)\\
+Advisors: & ~Prof. Hans G. Hornung (Caltech)\\
 \ & \ Dipl.-Ing. Sergey Litvinov (TUM)\\
+\ & \ Prof. Dr.-Ing. Nikolaus A. Adams (TUM)\\
  \\
-Ausgabe: & 15.\ Juni 2010\\
-Abgabe: & 15.\ Dezember 2010\\
 \end{tabular}

### 2010-10-21 src/initiation.h
separated all contributions to change rate in interaction.cpp

@@ -77,11 +77,22 @@ public:
   ///- 0: no physical viscosity
   int physical_viscosity_marker; 
 
+  ///\brief marker for temperature dependend viscosity and thermal conduction
+  ///
+  /// 1: variable viscosity/conductivity taken into account (Sutherland law)
+  /// 0: constant viscosity/conductivity (takes values specified in .tcl file)
+  int variableEtaAndK;
+
   ///\brief artificial viscosity marker:
-  ///- 2. art. visc. globally turned on
+  ///- 2: art. visc. globally turned on
   ///- 1: incl. art. visc. for compression only (as needed for shock-tube case)
   ///- 0: no artificial viscosity
   int artificial_viscosity_marker; 
+
+  ///\brief external mass initialization marker
+  ///- 0: mass initialization within simulation program (by smoothing)
+  ///- 1: mass initialized externally (via initialization file)
+  int external_mass_initialization;
 
   ///\brief density mode marker
   ///
@@ -92,17 +103,17 @@ public:
   double supportlength;
   /// parameter n for harmonic kerenel
   double harmonic_n;
-  ///the compuational domain size
+  /// the compuational domain size
   Vec2d box_size;
   ///cell size
   double cell_size;
-  ///the inital particle distance
+  /// the inital particle distance
   double delta;
-  ///the ration between smoothing length and inital particle distance
+  /// the ration between smoothing length and inital particle distance
   int hdelta;
-  ///cells matrix for real particles
+  /// cells matrix for real particles
   int x_cells, y_cells;
-  ///g force on particles
+  /// g force on particles
   Vec2d g_force;
 
   ///\brief marker to choose output format
@@ -128,7 +139,7 @@ public:
   /// 0: autom. time conrtol switched off
   /// 1: autom time control activated!
   double autom_dt_control;
-  double manually_choosen_dt;///<Time-step (specified in .tcl-configuration file) which is applied if autom. dt-control is turned off
+  double manually_choosen_dt;///<Timestep (specified in .tcl-configuration file) which is applied if autom. dt-control is turned off
 
 
   Vec2d U0;///<inital flow speed (if initial condition is defined here)w

### 2010-10-21 src/material.cpp

@@ -27,7 +27,7 @@ Material::Material(Initiation &ini, const int number)
   // to have array in the return string for tcl
   // example [return A(1)]
   const std::string index = boost::str(boost::format("(%i)]") % number);
-
+  // read material properties from .tcl input file
   material_name = std::string(ini.interp.eval("[return $material_name" + index));
   material_type = ini.interp.eval("[return $material_type"  + index);
   cv = ini.interp.eval("[return $material_cv"  + index);
@@ -35,10 +35,26 @@ Material::Material(Initiation &ini, const int number)
   b0 = ini.interp.eval("[return $material_b0"  + index);
   rho0 = ini.interp.eval("[return $material_rho0"  + index);
   a0 = ini.interp.eval("[return $material_a0"  + index);
-  eta = ini.interp.eval("[return $material_eta"  + index);
+  //local copy of variable eta and k flag
+  variableEtaAndK=ini.variableEtaAndK;
   if (ini.simu_mode == 2) {
-   zeta = ini.interp.eval("[return $material_zeta"  + index);
-   k = ini.interp.eval("[return $material_k"  + index);
+    if(variableEtaAndK==0) {
+      //read eta, zeta, k from .tcl file (are considered constant during simulation)
+      eta = ini.interp.eval("[return $material_eta"  + index);
+      zeta = ini.interp.eval("[return $material_zeta"  + index);
+      k = ini.interp.eval("[return $material_k"  + index);
+    }
+    else {
+      // read reference values for sutherland law
+      // for viscosity
+      eta_0=ini.interp.eval("[return $material_eta_0"  + index);
+      T_0_eta=ini.interp.eval("[return $material_T_0_eta"  + index);
+      S_eta=ini.interp.eval("[return $material_S_eta"  + index);
+      // for thermal conductivity
+      k_0=ini.interp.eval("[return $material_k_0"  + index);
+      T_0_k=ini.interp.eval("[return $material_T_0_k"  + index);
+      S_k=ini.interp.eval("[return $material_S_k"  + index);
+    }
   }
   LOG(INFO) << "Material object is created";
 }
@@ -125,3 +141,34 @@ double Material::get_Cs(const double p, const double rho)
   assert(p>=0.0);
   return sqrt(gamma*p/rho);
 }
+//----------------------------------------------------------------------------------------
+//	       	get viscosity (either constant or f(T, depending on user settings)))
[…]

### 2010-10-26 gnuplot/TaylorGreen/AnalyzeVelocDecay.sh
mainly changes in thesis

@@ -18,7 +18,7 @@ set y2tics border
 #set xtics 0.25;
 
 set xlabel "Time"; set ylabel "Maximum Velocity (abs. value)";
-plot [0.0:1.5][0.0:0.04] 'decayAnalysis.dat' u 1:2 title 'exact' with line, 'decayAnalysis.dat' u 1:3 title 'simu' with points,'decayAnalysis.dat' u 1:4 axes x1y2 title 'error' with line;
+plot [0.0:0.000005][0.0:0.04] 'decayAnalysis.dat' u 1:2 title 'exact' with line, 'decayAnalysis.dat' u 1:3 title 'simu' with points,'decayAnalysis.dat' u 1:4 axes x1y2 title 'error' with line;
 
 set terminal png
 set output "Figures/VelocDecay.png"

### 2010-10-26 ms/Graphics/results/ShockTube/1D_CS_LF_SD/dtVariat_dx005_SupLen03_dt03_Oscillations/compareResults.sh

@@ -1,0 +1,86 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+gnuplot << EOF
+set terminal postscript eps enhanced color "Helvetica" 26
+set output "Err_p$1.eps"
+
+
+set grid; set key left top
+set y2label "(absolute) error";
+set y2range [0:1]
+set y2tics border
+set mxtics 0.05;
+set xtics 0.25;
+
+set xlabel "length x"; set ylabel "pressure p";
+plot [1.5:2.5][0.0:1.5] 'prtl$1.dat' u 1:4 title 'simu' with line lw 8, 'relError$1.dat' u 1:4 title 'exact' with line lw 8,  'relError$1.dat' u 1:5 axes x1y2 title 'error'with line lw 8;
+
+
+set terminal png
+set output "Err_p$1.png"
+replot
+
+reset
+
+set terminal postscript eps enhanced color "Helvetica" 26
+set output "Err_rho$1.eps"
+
+set grid; set key left top
+set y2label "(absolute) error";
+set y2range [0:1]
+set y2tics border
+set mxtics 0.05;
+set xtics 0.25;
+
+set xlabel "length x"; set ylabel "density rho";
+ plot [1.5:2.5][0.0:1.3]  'prtl$1.dat' u 1:3 title 'simu' with line lw 8,'relError$1.dat' u 1:2 title 'exact' with line lw 8,'relError$1.dat' u 1:3 axes x1y2 title 'error'with line lw 8;
+
+set terminal png
+set output "Err_rho$1.png"
+replot
+
+reset
+
+
+set terminal postscript eps enhanced color "Helvetica" 26
+set output "Err_u$1.eps"
+
+set grid; set key left top
+set y2label "(absolute) error";
+set y2range [0:1]
+set y2tics border
+set mxtics 0.05;
+set xtics 0.25;
+
+set xlabel "length x"; set ylabel "velocity u";
+ plot [1.5:2.5][0.0:1.1] 'prtl$1.dat' u 1:5 title 'simu' with line lw 8, 'relError$1.dat' u 1:6 title 'exact' with line lw 8 , 'relError$1.dat' u 1:7 axes x1y2 title 'error'with line lw 8;
+
+set terminal png
+set output "Err_u$1.png"
+replot
+ 
+reset
+
+
+set terminal postscript eps enhanced color "Helvetica" 26
[…]

### 2010-10-26 ms/Graphics/results/ShockTube/q1D_CS_LF_SD/supLenVariat_dxdy005/Drifting/suplen015/visualizeScattering.sh

@@ -1,0 +1,21 @@
+#! /bin/bash
+
+#eps solid for solid (not dashed) lines, momochrome (instead of color),... 
+
+
+
+gnuplot << EOF
+set terminal postscript eps enhanced color "Helvetia" 26
+set output "x_y_plane$1.eps"
+
+set grid;
+set xlabel "length x"; set ylabel "length y";
+plot [2.05:2.35][0.0:0.015] 'prtl$1.dat' u 1:2 notitle with points;
+
+set terminal png
+set output "x_y_plane$1.png"
+replot
+
+reset
+
+EOF

### 2010-10-26 src/Interaction/interactioncomp.cpp

@@ -106,8 +106,6 @@ void InteractionComp::UpdateForces() {
   Vec2d  dUdti_visc(0,0);
   Vec2d  dUdtj_visc(0,0);
   // control output for one interaction pair
-  // if(Org->ID==2 && Dest->ID==1)
-  //   LOG(INFO)<<"dUdt_visc before (should always be zero) : ("<<dUdt_visc[0]<<","<<dUdt_visc[1]<<")";
   if (ini.physical_viscosity_marker==1) {
     // physical viscosity implementation according to espanol2003 (eq. 30)
     // where Fij is defined as >= 0 (gradW(r)=-F(r)*r) contrary to Monaghan 
@@ -154,9 +152,12 @@ void InteractionComp::UpdateForces() {
     
   } 
   // again control output for first interaction pair
-  // if(Org->ID==2 && Dest->ID==1)
-  //   LOG(INFO)<<"dUdt_visc after : ("<<dUdt_visc[0]<<","<<dUdt_visc[1]<<")";
-  
+  if(Org->ID==2 && Dest->ID==1) {
+    LOG(INFO)<<"dUdti_visc after : ("<<dUdti_visc[0]<<","<<dUdti_visc[1]<<")";
+    LOG(INFO)<<"dUdtj_visc after : ("<<dUdtj_visc[0]<<","<<dUdtj_visc[1]<<")";
+  }
+
+
   // calculate total velocity change rate (due to pressure, art. visc and physical visc.)
   // const Vec2d dUdti=-mj*(pi/pow(rhoi,2)+pj/pow(rhoj,2)+piij)*gradWij+dUdti_visc;
   // const Vec2d dUdtj=mi*(pi/pow(rhoi,2)+pj/pow(rhoj,2)+piij)*gradWij+dUdtj_visc;
@@ -202,6 +203,9 @@ void InteractionComp::UpdateForces() {
   //energy change rate contribution due to phsyical viscosity
   const double dedti_visc=0.5*dot(dUdti_visc,(Uj-Ui));
   const double dedtj_visc=0.5*dot(dUdtj_visc,(Ui-Uj));
+  if(Org->ID==2 && Dest->ID==1) {
+    LOG(INFO)<<"dedti_visc: "<< dedti_visc<<","<< "dedtj_visc: "<<dedtj_visc;
+  }
   
   //now complete energy change rate
   const double dedti=dedti_p+dedti_artVisc+dedti_visc;
[…]

### 2010-10-29 scripts/InitCondCompressibleCouette/create_ICCompressibleCouette.cpp
added switch to change timestamp units for outputfile

@@ -12,19 +12,19 @@ using namespace std;
 int main () {
   const double rho=1.0;
   const double p=1.0;
-  const double m=0;// m is initialized as zero, will be calculated in simulation
+  const double m=0;// m is initialized to zero, will be calculated in simulation
   double x=0;
   double y=0;
-  const double domain_size_x=1.0;
-  const double domain_size_y=domain_size_x;
-  const int N_x=60;
-  const int N_y=N_x;
+  const double domain_size_x=0.0333333333333333333333;
+  const double domain_size_y=0.5;//domain_size_x/2;
+  const int N_x=2;
+  const int N_y=30;
   const int N=N_x*N_y;
   const double dx=domain_size_x/N_x;
   const double dy=dx;
   cout<<"dx=dy="<<dx<<endl;
   cout<<"N"<<N<<endl;
-  const double gamma=1.4;
+  const double gamma=1.5;
   
   double x_array[N];
   double y_array[N];

### 2010-10-29 src/boundary.cpp

@@ -1,4 +1,4 @@
-// \file boundary.cpp
+/// \file boundary.cpp
 /// \author Xiangyu Hu <Xiangyu.Hu@aer.mw.tum.de>
 /// \author changes by: Martin Bernreuther <Martin.Bernreuther@ipvs.uni-stuttgart.de>
 #include <glog/logging.h>
@@ -1244,7 +1244,7 @@ void Boundary::Boundary_SW(spParticle prtl)
       prtl->U[1] = UxBl[1]*2.0 - prtl->U[1];
       //besides set temperature if isothermal boundary
       if(isothermal_boundary==1)
-	prtl->T=TxBl;
+	prtl->T=TyBd;
       break;
       //perodic
     case 1:
@@ -1282,7 +1282,7 @@ void Boundary::Boundary_NW(spParticle prtl)
       prtl->U[1] = UxBl[1]*2.0 - prtl->U[1];
       //besides set temperature if isothermal boundary
       if(isothermal_boundary==1)
-	prtl->T=TxBl;
+	prtl->T=TyBu;
       break;
       //perodic
     case 1:
@@ -1322,7 +1322,7 @@ void Boundary::Boundary_NE(spParticle prtl)
       prtl->U[1] = UxBr[1]*2.0 - prtl->U[1];
       //besides set temperature if isothermal boundary
       if(isothermal_boundary==1)
-	prtl->T=TxBr;
+	prtl->T=TyBu;
       break;
       //perodic
     case 1:
@@ -1360,7 +1360,8 @@ void Boundary::Boundary_SE(spParticle prtl)
     prtl->U[1] = UxBr[1]*2.0 - prtl->U[1];
     //besides set temperature if isothermal boundary
     if(isothermal_boundary==1)
-      prtl->T=TxBr;
+      ///\TODO{as only either horizontal walls or vertical walls can be isothermal boundary conditions (when at different temperatures) I have to construct a switch which takes into account T=TxBr (if vertical walls isothermal) and T=TyBd (if horizontal wall isothermal!!! and the equivalent for all corners}
+      prtl->T=TyBd;
     break;
     //perodic
   case 1:

### 2010-10-29 src/initiation.h

@@ -131,6 +131,15 @@ public:
   /// 1: extra large timestamp (12 digits)
   int xxl_timestamp_marker;
 
+
+  ///\brief  marker to switch timestamp  unit of outputfiles
+  ///
+  /// becomes necessary for simulations with very small dt,
+  /// for example due to high viscosity values 
+  /// 0: standard (timestamp unit [ms])
+  /// 1: high resolution (timestamp unit [1e-10s])
+  int high_res_timestamp_marker;
+
   //timing control
   double Start_time;///<Simulation start time
   double End_time;///<Simulation end time

### 2010-11-03 src/hydrodynamics.cpp
cavity boundary conditions (first step: v_ghostparticle=0) set up & thesis update

@@ -136,7 +136,7 @@ void Hydrodynamics::UpdateDensity(const Initiation &ini, spKernel  weight_functi
 //				calculate interaction with updating interaction list
 //----------------------------------------------------------------------------------------
 void Hydrodynamics::UpdateChangeRate(ParticleManager &particles, spKernel weight_function, 
-				     const Initiation& ini) {
+				     const Initiation& ini, const double Time) {
   LOG(INFO) << " Hydrodynamics::UpdateChangeRate(particles, weight_function, ini)";
   ///- initiate change rate of each real particle by calling ZerpChangeRate()
   ZeroChangeRate();
@@ -151,12 +151,12 @@ void Hydrodynamics::UpdateChangeRate(ParticleManager &particles, spKernel weight
   }
   
   ///- include the gravity effects by calling AddGravity()
-  AddGravity(ini);
+  AddGravity(ini, Time);
 }
 //----------------------------------------------------------------------------------------
 //				calculate interaction without updating interaction list
 //----------------------------------------------------------------------------------------
-void Hydrodynamics::UpdateChangeRate(const Initiation& ini) {
+void Hydrodynamics::UpdateChangeRate(const Initiation& ini, const double Time) {
   LOG(INFO) << " Hydrodynamics::UpdateChangeRate(ini)";
   ///- initiate the change rate of each real particle by calling ZeroChangeRate()
   ZeroChangeRate();	
@@ -189,10 +189,10 @@ void Hydrodynamics::UpdateChangeRate(const Initiation& ini) {
   
   
   ///- include the gravity effects
-  AddGravity(ini);
+  AddGravity(ini, Time);
 }
 //----------------------------------------------------------------------------------------
-void Hydrodynamics::UpdateChangeRateInclRho(const Initiation& ini) {
+void Hydrodynamics::UpdateChangeRateInclRho(const Initiation& ini, const double Time) {
   LOG(INFO) << " Hydrodynamics::UpdateChangeRateInclRho(ini)";
   ///- initiate the change rate of each real particle by calling ZeroChangeRate()
   ZeroChangeRate();	
@@ -207,7 +207,7 @@ void Hydrodynamics::UpdateChangeRateInclRho(const Initiation& ini) {
   }
 
   ///- include the gravity effects
-  AddGravity(ini);
+  AddGravity(ini, Time);
 }
 //						initiate particle change rate
 //----------------------------------------------------------------------------------------
[…]

### 2010-11-03 src/hydrodynamics.h

@@ -48,14 +48,15 @@ class Hydrodynamics
   ///initiate particle change rate
   void ZeroChangeRate();
   ///add the gravity effects
-  void AddGravity(const Initiation& ini);
+  void AddGravity(const Initiation& ini, const double Time);
   ///calculate interaction with updating interaction list
   void UpdateChangeRate(ParticleManager &particles, 
 			spKernel weight_function,
-			const Initiation& ini);
+			const Initiation& ini,
+			const double Time);
   ///calculate interaction without updating interaction list
-  void UpdateChangeRate(const Initiation& ini);
-  void UpdateChangeRateInclRho(const Initiation& ini);
+  void UpdateChangeRate(const Initiation& ini, const double Time);
+  void UpdateChangeRateInclRho(const Initiation& ini, const double Time);
   ///initiate particle density to zero
   void Zero_density();
   /// initiate particle density to the contributions of the 

### 2010-11-03 src/initiation.cpp

@@ -65,6 +65,8 @@ Initiation::Initiation(const std::string& project_name, const std::string& ivs_f
     //assert(integration_scheme == 1 || integration_scheme == 2);
     splash_optimized_output = interp.eval("[return $SPLASH_OPTIMIZED_OUTPUT]");
     assert(splash_optimized_output==0||splash_optimized_output==1);
+    smoothDensityProfile=interp.eval("[return $SMOOTH_DENSITY_PROFILE]");
+    assert(smoothDensityProfile==0||smoothDensityProfile==1);
     /// read parameters of artificial viscosity 
     alpha_artVis = interp.eval("[return $alpha_artVis]");
     beta_artVis = interp.eval("[return $beta_artVis]");
@@ -110,6 +112,8 @@ Initiation::Initiation(const std::string& project_name, const std::string& ivs_f
   
   g_force[0] = interp.eval ("[return $G_FORCE(0)]");
   g_force[1] = interp.eval ("[return $G_FORCE(1)]");
+  
+  g_force_delay=interp.eval ("[return $g_force_delay]");
   
   number_of_materials = interp.eval("[return $NUMBER_OF_MATERIALS]");
   assert(number_of_materials > 0);
@@ -198,7 +202,8 @@ void Initiation::VolumeMass(Hydrodynamics &hydro, ParticleManager &particles,
   ///The mass for each particle  stays constant during the simulation.
 
   /// <ul><li>iterate particles on the particle list
-  double mass; // local variable to save one particles m for assignment to ghost prtl
+  double mass; // local variable to save one particle's m for assignment to ghost prtl
+  double volume; // local variable to save one particle's V for assignment to ghost prtl
   BOOST_FOREACH(spParticle prtl_org, hydro.particle_list) {
     ///\todo{initialize particle mass via initiation file...}
     //prtl_org->m=0.001875;
@@ -223,8 +228,9 @@ void Initiation::VolumeMass(Hydrodynamics &hydro, ParticleManager &particles,
     prtl_org->V = reciprocV;
     prtl_org->m = prtl_org->rho*reciprocV;
     LOG_EVERY_N(INFO, 1000) <<std::setprecision(10)<< "prtl ID"<<prtl_org->ID<<"prtl m  = " << prtl_org->m;
-    //
+    //save mass and volume for assignment to ghost particles
     mass=prtl_org->m;
+    volume=prtl_org->V;
   }
   
   // in case of SolidObstacles where not the entire obstacle is filled with particles
[…]

### 2010-11-03 src/initiation.h

@@ -77,6 +77,13 @@ public:
   ///simulation mode (1: liquids, 2: gas dynamics)
   int simu_mode;
 
+  ///\brief flag to turn on/off smoothing of initial density profile
+  ///
+  ///(only useful for initially discontinuous density profile like for shock-tube)
+  /// 0: NO smoothing of initial density profile
+  /// 1: smoothing of initial density profile
+  int smoothDensityProfile;
+
   ///\brief physical viscosity marker:
   ///
   ///- 1: including physical viscosity
@@ -121,6 +128,8 @@ public:
   int x_cells, y_cells;
   /// g force on particles
   Vec2d g_force;
+  ///\brief temporal delay for beginning of g-force action
+  double g_force_delay;
 
   ///\brief marker to choose output format
   /// 

### 2010-11-03 src/output.h

@@ -10,7 +10,8 @@ public:
   ///output particle positions respected different materials
   void OutputParticle(const Hydrodynamics &hydro,
 		      const Boundary &boundary, 
-		      const double Time, const Initiation &ini);
+		      const double Time, const Initiation &ini, 
+		      const spSolidObstacles &obstacles);
   ///Output real particle data for restart the computation
   void OutRestart(const Hydrodynamics &hydro, 
 		  const double Time, const Initiation& ini);

### 2010-11-05 scripts/InitCondPorosities/create_ICLinearWall.cpp
docu is updated

@@ -57,7 +57,7 @@ int main () {
   }
   
   ofstream out("../../cases/LinearWall.ivs");
-  // output first line of .ivs file (geometrical data for cavity)
+  // output first line of .ivs file (geometrical data for wall)
   out <<setprecision (6)
       <<"   "<<y_wall
       <<endl;

### 2010-11-10 src/initiation.cpp
fixed issue with Leapfrog-output for small times, updated thesis, started isothermal BC for solid Obstacles

@@ -57,7 +57,11 @@ Initiation::Initiation(const std::string& project_name, const std::string& ivs_f
   }
   SolidObstacles_type = static_cast<std::string>(interp.eval("[return $SOLID_OBSTACLES]"));
   //assertion made in sph.cpp
-  
+
+  solObs_virt_veloc_type=interp.eval("[return $SOLOBS_VIRT_VELOC_TYPE]");
+  assert(solObs_virt_veloc_type==0||solObs_virt_veloc_type==1);
+  d_realPart_solObs_min=interp.eval("[return $d_realPart_solObs_min]");
+  assert(d_realPart_solObs_min>=0);
   /// if gas dynamics
   if (simu_mode == 2) {
     //further markers exclusively applied to gas dynamics

### 2010-11-10 src/output.cpp

@@ -76,10 +76,10 @@ void Output::OutputParticle(const Hydrodynamics &hydro, const Boundary &boundary
 	    out<<setprecision(9)
 	       << ::setw(17)<<prtl->R[0] 
 	       << ::setw(17)<<prtl->R[1] 
-	       << ::setw(17) <<prtl->rho 
-	       << ::setw(17)<<prtl->p
-	       << ::setw(17)<<prtl->U[0]
-	       << ::setw(17)<<prtl->e
+	       << ::setw(17) <<prtl->rho_output 
+	       << ::setw(17)<<prtl->mtl->get_p(prtl->rho_output,prtl->e_output)
+	       << ::setw(17)<<prtl->U_output[0]
+	       << ::setw(17)<<prtl->e_output
 	       <<"  "<<prtl->ID
 	       <<"  "<<prtl->m
 	       <<"\n";
@@ -87,14 +87,14 @@ void Output::OutputParticle(const Hydrodynamics &hydro, const Boundary &boundary
 	    out<<setprecision(9)
 	       << ::setw(17)<<prtl->R[0] 
 	       << ::setw(17)<<prtl->R[1] 
-	       << ::setw(17)<<prtl->U[0]
-	       << ::setw(17)<<prtl->U[1]
-	       << ::setw(17) <<prtl->rho 
-	       << ::setw(17)<<prtl->e
-	       << ::setw(17)<<prtl->p
+	       << ::setw(17)<<prtl->U_output[0]
+	       << ::setw(17)<<prtl->U_output[1]
+	       << ::setw(17) <<prtl->rho_output 
+	       << ::setw(17)<<prtl->e_output
+	       << ::setw(17)<<prtl->mtl->get_p(prtl->rho_output,prtl->e_output)
 	       << ::setw(17)<<ini.supportlength/2
 	       <<"  "<<prtl->m
-	       <<"  "<<prtl->V
+	       <<"  "<<prtl->V// up-to-date as prtl position up-to-date and V only f(R,m)
 	       <<"  "<<prtl->ID
 	       <<"\n";
 	}
@@ -106,48 +106,48 @@ void Output::OutputParticle(const Hydrodynamics &hydro, const Boundary &boundary
     // }
 
     /// <li>iterate the boundary partilce list
-    BOOST_FOREACH(spParticle prtl, boundary.boundary_particle_list) {
-      g++;		
[…]

### 2010-11-10 src/particle.h

@@ -104,6 +104,11 @@ class Particle {
 	double e_I;///<intermediate value of internal enegry (used in the integrator)
         double e_n; //intermediate volume, internal energy used in integrator
 
+	// variables for particle values at full timestep needed for output when
+	// leapfrog integration scheme applied
+	Vec2d U_output;///<U at full timestep for output (needed for leapfrog integration)
+	double e_output;///<e at full timestep for output (needed for leapfrog integration)
+	double rho_output;///<rho at full timestep for output (needed for leapfrog integration)
 
 	double eta; ///<(shear) viscosity of each particle
 	double zeta; ///<bulk viscosity of each particle

### 2010-11-10 src/sph.cpp

@@ -192,8 +192,15 @@ int main(int argc, char *argv[]) {
   //start time
   double Time = ini.Start_time;
 
-  //output initial conditions
+  //output initial particle configuration
   output.OutputParticle(hydro, boundary, Time, ini, obstacles); //particle positions and velocites
+
+  // just to be sure that for the beginning of the actual computation loop 
+  // all change rates are zero (as they were not always explicitely initialized:
+  // they were not always exactly zero. Did only affect determination
+  // of first time step, which is done before any change rates are calculated.
+  // Before actual calculation of change rates they were reset to 0 anyway...)
+  hydro.ZeroChangeRate();
 
   ///\n computation loop starts 
   while(Time < ini.End_time) {
@@ -221,7 +228,9 @@ int main(int argc, char *argv[]) {
     //control output
     LOG(INFO)<<"time is "<<Time<<"\n";
     ///- output results after a time interval\n\n
-
+    ///  if leapfrog intetration: calculate values at full step for output
+    hydro.UpdateValuesForOutput(ini, timesolver->dt);
+    
     output.OutputParticle(hydro, boundary, Time, ini, obstacles); //particle positions and velocites
     output.OutRestart(hydro, Time, ini); //restarting file
   }

### 2010-11-11 ms/Graphics/results/Porosities/LinearWall/Poiseuille_DomainEdgeBC_N4x40_suplen2dx_t3sec/compProfiles.sh
updated docu, continued T boundary condition

@@ -11,7 +11,7 @@ set output "U_profiles$1.eps"
 
 set grid;
 set xlabel "U"; set ylabel "length y";
-plot [0.0:0.014][-0.5:0.5]  'exact$1.dat' u 2:1 title 'exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'simu' lt 1 with points;
+plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'simu' lt 1 with points;
 
 set terminal png large
 set output "U_profiles$1.png"

### 2010-11-11 src/initiation.h

@@ -86,6 +86,17 @@ public:
   /// virtual velocity calculation according to Morris1999
   double d_realPart_solObs_min;
 
+  /// thermal boundary condition type for solid obstacles
+  /// for the moment only isothermal BC implemented for solObs
+  /// 0: isothermal, ghost prtl left at const T as initialized from .ivs file
+  /// 1: isothermal, realized with constant ghost prtl. temperature T_w
+  /// 2: isothermal, realized with linear extrapolation around T_w
+  int solObs_thermal_BC_type;
+
+  /// wall temperature for isothermal solid Obstacles temperature
+  /// boundary condition 
+  double T_w_solObs_isothermal;
+
   ///simulation mode (1: liquids, 2: gas dynamics)
   int simu_mode;
 

### 2010-11-12 src/Interaction/interaction.cpp
thermal BC tesh solid Obstacles continued, thesis update

@@ -27,7 +27,7 @@ Interaction::Interaction(const spParticle prtl_org, const spParticle prtl_dest,
 			 const Initiation& ini, const spSolidObstacles obstacles):
   ini(ini), obstacles (obstacles), Org(prtl_org), Dest(prtl_dest), mi(Org->m), mj(Dest->m), 
   rmi(1.0/mi), rmj(1.0/mj),   etai(Org->eta), etaj(Dest->eta),
-  zetai(Org->zeta), zetaj(Dest->zeta),   rij(dstc) {
+  zetai(Org->zeta), zetaj(Dest->zeta),  ki(Org->k), kj(Dest->k), rij(dstc) {
 
   assert(prtl_dest != NULL);
   assert(prtl_org != NULL);
@@ -83,6 +83,7 @@ void Interaction::RenewInteraction(spKernel weight_function) {
   zetai=Org->zeta;
   etaj=Dest->eta;
   zetaj=Dest->zeta;
+  ki=Org->k, kj=Dest->k,
   assert(rrij>0.0);
   rrij = 1.0/rij;
   Vi=Org->V;
@@ -113,6 +114,12 @@ void Interaction::UpdateForcesAndRho() {
   //define pair values change in sub time steps
   const double rhoi = Org->rho; 
   const double rhoj = Dest->rho;
+
+ //set temperatures to local variables (for destination temperature use solidObstacles
+  // method which assigns temperature according to temperature boundary condition
+  // in case destination particle is ghost particle for solid obstacle)
+  const double Ti=Org->T;
+  const double Tj=obstacles->set_Temperature_SolObs_isothermal(Org,Dest); 
   
   /// make sure density is OK
   assert(rhoi>0.0);
@@ -313,34 +320,39 @@ void Interaction::UpdateForcesAndRho() {
   };
 }
 
-void Interaction::UpdateEnergyPureConduction(){
- LOG_EVERY_N(INFO, 100000) << "Interaction::UpdateEnergyPureConduction()";
- //define pair values change in sub time steps
- const double rhoi = Org->rho; 
- const double rhoj = Dest->rho;
- 
- //energy change rate    
- //(physical viscosity  not (yet) taken into account in energy equation)
- 
- //first energy change rate contribution  due to thermal conduction (Cleary1999)
- const double dedtij_cond=4.0*mj/(rhoi*rhoj)*ki*kj/(ki+kj)*(Ti-Tj)*Fij;
- //now complete energy equation
- const double dedti=+dedtij_cond;
[…]

### 2010-11-12 src/TimeSolver/gastimesolverLeapFrog.cpp

@@ -96,14 +96,21 @@ void GasTimeSolverLeapFrog::TimeIntegral_summation(Hydrodynamics &hydro,
       }
     ///build interactions
     hydro.BuildInteractions(particles, weight_function, ini);
-    ///calculate density (by summation)
+    ///calculate density (by summation) (and included in method: update state afterwards
     hydro.UpdateDensity(ini, weight_function);
 
 
     //renew interaction (so that local copies of particle variables 
     //in interaction are updated everytime a particle variable changes)
-    //hydro.UpdateInteractions(weight_function);
+    hydro.UpdateInteractions(weight_function);
     // not needed because rho is not locally copied into interaction
+    //=> now needed as eta, zeta, k T-dependand and after density update T might change!
+    ///\{todo=> alternative would be to remove update of eta, zeta, k from interaction 
+    // constructor and method renewInteraction and to assign values locally in
+    // the corresponding updateForces method!
+    // this way the iteration over all interactions at this place could be avoided
+    // but as I did not know how this would affect incompressible implementation I 
+    // let it like thos for the moment}
 
     // just before updateing state of boundary particles for force calculation:
     // set tangent plane to solidObstacle surface for each real particle

### 2010-11-12 src/particle.cpp

@@ -43,12 +43,12 @@ Particle::Particle (Vec2d position, Vec2d velocity, double density,
 	
   ///- set states
   rho = density; p = pressure; T = temperature; Cs = mtl->get_Cs(p, rho);
-  U = velocity; U_I = U;
+  U = velocity; U_I = U; U_output=U;
 	
   ///- set conservative values (mass and volume determined lateron) and their  intermediate values
   // m = 0.0; // for 2D shock tube mass is initialized from the external
- V = 0.0; e = mtl->get_e(T); e_I = e;
-  R_I = R; P_I = P; rho_I = rho;
+  V = 0.0; e = mtl->get_e(T); e_I = e; e_output=e;
+  R_I = R; P_I = P; rho_I = rho; rho_output=rho;
   P_n = P; U_n = U; rho_n = rho; e_n = e; 
 
 }
@@ -95,12 +95,12 @@ Particle::Particle (Vec2d position, Vec2d velocity, double density,
   ///
   
   ///- set states
-  rho = density; m=mass; p = pressure; T = temperature; Cs = mtl->get_Cs(p, rho);  U = velocity; U_I = U;
+  rho = density; m=mass; p = pressure; T = temperature; Cs = mtl->get_Cs(p, rho);  U = velocity; U_I = U; U_output=U;
 	
   ///- set conservative values (mass and volume determined lateron) and their  intermediate values
   // m = 0.0; // for 2D shock tube mass is initialized from the external
-  V = 0.0; e = mtl->get_e(T); e_I = e;
-  R_I = R; P_I = P; rho_I = rho;
+  V = 0.0; e = mtl->get_e(T); e_I = e; e_output=e;
+  R_I = R; P_I = P; rho_I = rho; rho_output=rho;
   P_n = P; U_n = U; rho_n = rho; e_n = e; 
 
   // as dUdt was not always properly initialized to zero:

### 2010-11-17 src/Interaction/interaction.cpp
first attempts of cavity simulation with variabel viscosity and heat conduction

@@ -305,8 +305,8 @@ void Interaction::UpdateForcesAndRho() {
     }
     
     // now complete energy change rate
-    const double dedti=dedti_p+dedti_artVisc+dedti_visc;
-    const double dedtj=dedtj_p+dedtj_artVisc+dedtj_visc;
+    const double dedti=dedti_p+dedti_artVisc+dedti_visc+ dedti_cond;
+    const double dedtj=dedtj_p+dedtj_artVisc+dedtj_visc+ dedtj_cond;
   
     // add result to corresponding particle variable 
     // (so, an iteration over the interaction list corresponds

### 2010-11-17 src/SolidObstacles/porosities.cpp

@@ -12,18 +12,18 @@
 
 //local includes
 #include "SolidObstacles/porosities.h"
+#include "vec2d.h"
 
 
 using namespace std;
 
-/// Cubic spline kernel (see Liu eq. (3.6)
 Porosities::Porosities(const Initiation& ini)
   :SolidObstacles(ini)
 {
   // read head of porosities.ivs file, which contains essential data to build domain
   // structure of  .ivs file header:
-  // ->number of zylinders
-  // ->Pos_ci[0] Pos_ci[1] Rad_i (x-center, y-center, radius; one row for each zylinder)
+  // ->number of cylinders
+  // ->Pos_ci[0] Pos_ci[1] Rad_i (x-center, y-center, radius; one row for each cylinder)
   
   const std::string inputfile =std::string(ini.Ivs_file_name);
   //check if the .ivs file exists
@@ -34,20 +34,20 @@ Porosities::Porosities(const Initiation& ini)
   }
   else LOG(INFO)<<"read porosities data from first line in .ivs file "<< inputfile <<" \n"; 
   //read first header of porosities.ivs file to get porosities geometry  
-  fin>>N_zyl;
-  for (int i=0;i<N_zyl;i++) {
-    // intermediate variable to store position of center of zylinder i
+  fin>>N_cyl;
+  for (int i=0;i<N_cyl;i++) {
+    // intermediate variable to store position of center of cylinder i
     Vec2d Pos_ci;
-    // intermediate variable to store radius of center of zylinder i
+    // intermediate variable to store radius of center of cylinder i
     double rad_i;
     fin>>Pos_ci[0];
     fin>>Pos_ci[1];
     fin>>rad_i;
     assert(rad_i>0);
-    //add current zylinder heotery information to vectors containing
-    // all zylinders' geometrical info
-    all_Zyl_centers.push_back(Pos_ci);
-    all_Zyl_radii.push_back(rad_i);      
+    //add current cylinder heotery information to vectors containing
+    // all cylinders' geometrical info
+    all_Cyl_centers.push_back(Pos_ci);
+    all_Cyl_radii.push_back(rad_i);      
   }
   //close inputfile
   fin.close();
@@ -65,21 +65,21 @@ int Porosities::prtl_in_solid(const  Vec2d& coordinates) const
   // all for the simulation: in this case return 2
   // if the particle is not located within the solid return 0 (i.e.
[…]

### 2010-11-17 src/sph.cpp

@@ -28,6 +28,7 @@
 #include "SolidObstacles/noObstacles.h"
 #include "SolidObstacles/cavity.h"
 #include "SolidObstacles/linearWall.h"
+#include "SolidObstacles/porosities.h"
 
 //using namespace std;
 
@@ -119,9 +120,9 @@ int main(int argc, char *argv[]) {
   else if (ini.SolidObstacles_type == "Cavity")   {
     obstacles = boost::make_shared<Cavity>(ini); 
   } 
-  //  else if (ini.SolidObstacles_type == "Porosities")   {
-  //obstacles = boost::make_shared<Porosities>(ini);
-  //  }
+  else if (ini.SolidObstacles_type == "Porosities")   {
+    obstacles = boost::make_shared<Porosities>(ini);
+  }
   else if (ini.SolidObstacles_type == "LinearWall")   {
     obstacles = boost::make_shared<LinearWall>(ini); 
   } 

### 2010-11-17 scripts/InitCondPorosities/create_ICPorosities_uniformSqareLattice.cpp
added files

@@ -1,0 +1,116 @@
+#include <iostream>
+#include <fstream>
+#include <cstring>
+#include <iomanip>
+#include <cstdio>
+#include <cstdlib>
+#include <math.h>
+#include <assert.h>
+
+
+using namespace std;
+
+//this program generates a uniform particle distribution where particles
+// are arranged in a continuous rectangular lattice, no matter if
+// they are located within a cylinder or in the actual calculation domain...
+
+// the porosity is generated here by for cylinders with
+// center point =domain corners and same radius
+int main () {
+  
+  const double rho=1.0;
+  const double p=1.0;
+  const double m=0;// m is initialized to zero, will be calculated in simulation
+  double x=0;
+  double y=0;
+  const double domain_size_x=1.0;
+  const double domain_size_y=domain_size_x;
+  const int N_x=50;
+  const int N_y=N_x;
+  const int N=N_x*N_y;
+  const double dx=domain_size_x/N_x;
+  const double dy=dx;
+  cout<<"dx=dy="<<dx<<endl;
+  cout<<"N"<<N<<endl;
+  
+  //geometrical cylinder data
+  const double N_cyl=4;// number of cylinders;
+  const double rad=0.3; //radius of one cylinder
+  const double Pos_c1[2]={0.0,0.0};
+  const double Pos_c2[2]={0.0,domain_size_y};
+  const double Pos_c3[2]={domain_size_x,0.0};
+  const double Pos_c4[2]={domain_size_x,domain_size_y};
+
+
+  double x_array[N];
+  double y_array[N];
+  double vx_array[N];
+  double vy_array[N];
+  double p_array[N];
+  double rho_array[N];
+  double m_array[N];
+  
+
+  // place particles (one contimuous rectangular lattice no matter
+  // if in zylinder or not
+  for(int j=0;j<N_y;j++) {
+    x=dx/2;
+    
+    for(int i=j*N_x;i<(j+1)*N_x;i++) {
+      x_array[i]=x;
+      y=(j+0.5)*dy;
+      y_array[i]=y;
+      vx_array[i]=0;
+	vy_array[i]=0;
+      x=x+dx;
+      p_array[i]=p;
+      rho_array[i]=rho;
+      m_array[i]=m;
+    };
+  }
+  
[…]

### 2010-11-17 src/SolidObstacles/cavity.h

@@ -1,0 +1,51 @@
+#ifndef CAVITY_H
+#define CAVITY_H
+/// \file cavity.h
+/// \brief  solidObstacles class for cavity
+
+/// Cavity class
+
+#include "SolidObstacles/solidObstacles.h"
+
+class Cavity : public SolidObstacles
+{
+
+public:
+
+  ///constructor to initialize the data members (auxiliary factors for solidObstacles calculation)
+  Cavity(const Initiation& ini);
+
+  
+  /// \brief checks if the particle (given by its coordinates) lies within the solid obstacle
+  ///
+  /// returns the following values:
+  /// 0: if particle is located outslde the wall (i.e real particle)
+  /// 1: if particle located inside the solid wall wih a distance of <=
+  /// one supportlength to the wall surface(i.e particle is ghost particle)
+  /// 2: if particle is located further inside the solid obstacle:
+  /// in this case particle does not need to be taken into account for the simulation
+  int prtl_in_solid(const Vec2d& coordinates) const;
+
+  void cut_ivs_file_header(std::ifstream& inputfile) const;
+
+  void set_solObs_tangentAndDistance(spParticle& prtl) const;
+ 
+  /// show the solidObstacles type
+  void show_information() const;
+
+private:
+    ///depth of the cavity
+    double depth;
+    ///width of the cavity
+    double width;
+    ///y_position of the cavity surface
+    double y_surface;
+    ///y_position of the cavity bottom
+    double y_bottom;
+    ///x-position of RHS wall of cavity
+    double x_wall_left;
+    ///x-position of LHS wall of cavity
+    double x_wall_right;
+};
+
+#endif //CAVITY_H

### 2010-11-17 src/SolidObstacles/linearWall.h

@@ -1,0 +1,48 @@
+#ifndef LINEARWALL_H
+#define LINEARWALL_H
+/// \file linearWall.h
+/// \brief  solidObstacles class for linearWall parallel to x coordinate 
+///
+/// wall position determined by y_wall
+/// purpose of this linear wall: test the boundary conditions for the 
+/// SolidObstacles, as they are not implemented the same way as the boundary
+/// conditions for the domain edges, which are already tested
+
+/// LinearWall class
+
+#include "SolidObstacles/solidObstacles.h"
+
+class LinearWall : public SolidObstacles
+{
+
+public:
+
+  ///constructor to initialize the data members (auxiliary factors for solidObstacles calculation)
+  LinearWall(const Initiation& ini);
+
+  
+  /// \brief checks if the particle (given by its coordinates) lies within the solid obstacle
+  ///
+  /// returns the following values:
+  /// 0: if particle is located outslde the wall (i.e real particle)
+  /// 1: if particle located inside the solid wall wih a distance of <=
+  /// one supportlength to the wall surface(i.e particle is ghost particle)
+  /// 2: if particle is located further inside the solid obstacle:
+  /// in this case particle does not need to be taken into account for the simulation
+  int prtl_in_solid(const Vec2d& coordinates) const;
+
+  void cut_ivs_file_header(std::ifstream& inputfile) const;
+
+  void set_solObs_tangentAndDistance(spParticle& prtl) const;
+ 
+  /// show the solidObstacles type
+  void show_information() const;
+
+private:
+    ///depth of the linearWall(s)
+    double y_wall_1;
+    double y_wall_2;
+    
+};
+
+#endif //LINEARWALL_H

### 2010-11-17 src/SolidObstacles/noObstacles.cpp

@@ -1,0 +1,48 @@
+///\file noObstacles.cpp
+///\author Xiangyu Hu <Xiangyu.Hu@aer.mw.tum.de>
+///\author changes by: Martin Bernreuther <Martin.Bernreuther@ipvs.uni-stuttgart.de>, 
+
+//----------------------------------------------------------------------------------------
+//    a concrete soldi obstacle class: no obstalce      
+//
+//----------------------------------------------------------------------------------------
+
+//local includes
+#include "SolidObstacles/noObstacles.h"
+
+using namespace std;
+
+
+NoObstacles::NoObstacles(const Initiation& ini)
+  :SolidObstacles(ini)
+{
+  // in this case (no obstacles) no need to do anything
+}
+
+//----------------------------------------------------------------------------------------
+// checks if particle is located within solid object
+//----------------------------------------------------------------------------------------
+int NoObstacles::prtl_in_solid(const  Vec2d& coordinates) const
+{
+  // test position of coordinates and return 1 when particle is
+  // located within the solid obstacle  and has a distance of
+  // less than one supportlength to the wall surface.
+  // If it is located further within the solid, the particle is ot needed at
+  // all for the simulation: in this case return 2
+  // if the particle is not located within the solid return 0 (i.e.
+  // particle is a real particle
+  //=> in the case of NO obstacles the method therefore returns always "0"
+      return 0;
+}
+
+void NoObstacles::cut_ivs_file_header(ifstream& inputfile)const {
+  // do nothing as no line needs to be cut off
+}
+
+void NoObstacles::set_solObs_tangentAndDistance(spParticle& prtl)const {
+
+}
+
+void NoObstacles::show_information() const {
+  std::cerr << " NoObstacles\n";
+}

### 2010-11-17 src/SolidObstacles/solidObstacles.cpp

@@ -1,0 +1,167 @@
+/// \file solidObstacles.cpp
+/// \author Xiangyu Hu <Xiangyu.Hu@aer.mw.tum.de>
+/// \author changes by: Martin Bernreuther <Martin.Bernreuther@ipvs.uni-stuttgart.de>
+/// \author changes by: Andreas Mattes
+/// \brief abstract class for solid obstacles within the calculation domain
+///
+
+
+//----------------------------------------------------------------------------------------
+//      abstract class for solid obstacles within the calculation domain
+//----------------------------------------------------------------------------------------
+#include <glog/logging.h>
+#include <boost/foreach.hpp>
+#include "glbfunc.h"
+
+// ***** local includes *****
+#include "SolidObstacles/solidObstacles.h"
+
+//constructor to inizialize the data members
+SolidObstacles::SolidObstacles(const Initiation& ini)
+  : domain_size(ini.box_size), supportlength(ini.supportlength), solObs_virt_veloc_type(ini.solObs_virt_veloc_type),d_realPart_solObs_min(ini.d_realPart_solObs_min), solObs_thermal_BC_type(ini.solObs_thermal_BC_type), T_w_solObs_isothermal(ini.T_w_solObs_isothermal)
+{
+  
+}
+
+
+// sets flag <<solidObstacle_ghostParticle>>, 
+// which is an attribute of each particle object.
+void SolidObstacles::set_ghostPrtlSolidObstacle_flag(spParticle& prtl)
+{
+  prtl->solidObstacle_ghostParticle=1;
+}
+
+//set tangents to solObs surface for all particles 
+void SolidObstacles::set_all_solObs_tangentsAndDistances(Hydrodynamics &hydro) {
+  // iterate particle list
+  BOOST_FOREACH(spParticle prtl, hydro.particle_list) {
+    set_solObs_tangentAndDistance(prtl);
+  } 
+}
+
+
+// set virtual velocity for destination particle if ghost particle 
+// (if no ghost particle set virtual velocity equal to real velocity) 
+Vec2d SolidObstacles::set_virtual_velocity(spParticle& org_prtl,spParticle& dest_prtl) {
+  // first check if destination particle is a ghost particle for solid Obstacle
+  // ad if a virtual velcoity assignment is activated
+  if(dest_prtl->solidObstacle_ghostParticle==1&&solObs_virt_veloc_type==1) {
+    // if this is the case: calculate virtual velocity according to Morris1997
+    
+    // first calculate distance d_ghost_tang from
[…]

### 2010-11-17 src/SolidObstacles/solidObstacles.h

@@ -1,0 +1,103 @@
+#ifndef SOLIDOBSTACLES_H
+#define SOLIDOBSTACLES_H
+
+/// \file solidObstacles.h 
+/// \brief SolidObstacles abstract base
+
+/// SolidObstacles abstract base
+#include <fstream>
+#include <iostream>
+#include <list>
+#include "vec2d.h"
+#include "initiation.h"
+#include "particle.h"
+#include "glbtype.h"
+#include <blitz/array.h>
+#include <glog/logging.h>
+#include "hydrodynamics.h"
+
+class SolidObstacles
+{
+  
+ public:
+
+  ///Constructor
+  SolidObstacles(const Initiation& ini);
+  
+  ///Base classes with virtual member functions should have a virtual destructor
+  virtual ~SolidObstacles();
+  
+  /// \brief checks if the particle (given by its coordinates) lies within the solid obstacle
+  ///
+  /// returns the following values:
+  /// 0: if particle is located outslde the wall (i.e real particle)
+  /// 1: if particle located inside the solid wall wih a distance of <=
+  /// one supportlength to the wall surface(i.e particle is ghost particle)
+  /// 2: if particle is located further inside the solid obstacle:
+  /// in this case particle does not need to be taken into account for the simulation
+  virtual int prtl_in_solid(const Vec2d& coordinates) const = 0;
+
+  ///\brief function to cut off .ivs file header containing geometrical data for SolidObstacles in order for the particlemanager to get a filestream starting at the point where particle information starts!
+  ///
+  /// as required geometrical information depends on SolidObstacles type,
+  /// an individual method has to be implemented for each of them
+  virtual void cut_ivs_file_header(std::ifstream& inputfile) const = 0;
+
+  ///\brief function that calculates tangent plane for one real particle and sets its distance to solidobstacle surface
+  ///
+  /// tangent plane (line) calculated if real particle closer than 
+  /// 1 supportlength to the SolidObstacle
+  /// tangent plane is attribute of each particle object
+  virtual void set_solObs_tangentAndDistance(spParticle& prtl)const=0;
+
+  ///\brief function that sets tangent plane and distance to solid obstacle surface for all real particles
+  ///
+  /// (by iterating particle list and calling set_solObs_tangent for each prtl)
+  void set_all_solObs_tangentsAndDistances(Hydrodynamics &hydro);
+
+  ///\brief sets flag <<solidObstacle_ghostParticle>>, 
+  /// which is an attribute of each particle object.
+  ///
[…]

### 2010-11-19 scripts/InitCondPorosities/create_ICCavity.cpp
intermediate commit

@@ -17,17 +17,17 @@ int main () {
   // in a way that there are particles right at the solid wall surfaces!!!
   
   const double y_surface=1.39;//bottom of cavity will be 0.19
-  const double depth=0.0;
-  const double width=0.0;
+  const double depth=0.6;
+  const double width=0.3;
   //
   const double rho=1.0;
   const double p=1.0;
   const double m=0;// m is initialized to zero, will be calculated in simulation
   double x=0;
   double y=0;
-  const double domain_size_x=0.1;
+  const double domain_size_x=1.0;
   const double domain_size_y=2.0;
-  const int N_x=5;
+  const int N_x=50;
   const int N_y=100;
   const int N=N_x*N_y;
   const double dx=domain_size_x/N_x;

### 2010-11-23 src/initiation.cpp
settings for isothermal BC test

@@ -42,6 +42,8 @@ Initiation::Initiation(const std::string& project_name, const std::string& ivs_f
   interp.eval(tclfilename);
   ///<li>reading key words and configuration data from configuration file and assign them to the appropriate variable
   disable_boundary  = interp.eval("[return $DISABLE_BOUNDARY]");
+  output_boundary_prtl = interp.eval("[return $OUTPUT_BOUNDARY_PRTL]");
+  assert( (output_boundary_prtl == 0) || (output_boundary_prtl== 1));
   initial_condition = interp.eval("[return $INITIAL_CONDITION]");
   assert( (initial_condition == 0) || (initial_condition == 1));
   simu_mode = interp.eval("[return $SIMULATION_MODE]");

### 2010-11-23 src/initiation.h

@@ -61,6 +61,13 @@ public:
   ///- 1 boundary conditions disabled
   int disable_boundary;
 
+  ///\ flag to ozput (or not) boundary particles in the prtlxxx.dat file
+  /// along with real particles
+  ///
+  /// 0: NO outout of boundary particles
+  /// 1: output of boundary particles
+  int output_boundary_prtl;
+
   ///\brief isothermal boundaries (for "free-slip" and "wall" only)
   /// 
   /// 0 NOT isothermal

### 2010-12-07 scripts/InitCondPorosities/create_ICPorosities_SqareLatticeRealPrtl_CircularCyl.cpp
mainly thesis updates

@@ -132,7 +132,7 @@ int main (int argc, char *argv[]) {
     const double l_arc= All_Cyl_rad[i]*2*PI;
     // determine number of particles per layer
     // (remains constant for all layers)
-    const double N_p_layer=round(l_arc/dx_hex);
+    const int N_p_layer=round(l_arc/dx_hex);
     // determine angle (polar coordinates with cylinder center as origin)
     // increment for particle placement (remains constant for all layers
     // as number of particles remains constant)
@@ -162,8 +162,12 @@ int main (int argc, char *argv[]) {
       else
 	phi_start=d_phi/2;
       
+      
       //places all particles in one layer by incrementing angle phi
-      for (double current_phi=phi_start;current_phi<2*PI+phi_start; current_phi+=d_phi) {
+      // "-d_phi*1e-5" is needed due to accuracy problems of double:
+      // to ensure particles are not placed twice at the same spot
+      // (once for phi=0 and once for phi~=2*PI...)
+      for (double current_phi=phi_start;current_phi<2*PI+phi_start-d_phi*1e-5; current_phi+=d_phi) {
 	//place current particle if position within calculation domain
 	const double x=All_Cyl_Pos_c[i][0]+current_rad*cos(current_phi);
 	const double y=All_Cyl_Pos_c[i][1]+current_rad*sin(current_phi);

### 2010-12-07 src/SolidObstacles/solidObstacles.cpp

@@ -52,7 +52,7 @@ Vec2d SolidObstacles::set_virtual_velocity(spParticle& org_prtl,spParticle& dest
     // ghost particle to boundary tangent 
     
     // first step for this:
-    // from straight line equation: x=origin_point+lambda*direction-vector
+    // from line equation: x=origin_point+lambda*direction-vector
     // calculate lambda which leads to the point C on the line closest to ghost
     // particle
     // ATTENTION: the origin is here origin of the line and NOT
@@ -71,7 +71,7 @@ Vec2d SolidObstacles::set_virtual_velocity(spParticle& org_prtl,spParticle& dest
     // LOG(INFO)<<"lambda"<<lambda;
     
     // second step: with this lambda value and the equation for the
-    // straight one obtais point C, the vector D connecting particle position
+    // line one obtais point C, the vector D connecting particle position
     // and point_c has the desired length
     
     const Vec2d vector_D=P_ghost-(origin_point+lambda*direction_vector);
@@ -80,7 +80,7 @@ Vec2d SolidObstacles::set_virtual_velocity(spParticle& org_prtl,spParticle& dest
     // LOG(INFO)<<"distance ghost tang"<<d_ghost_tang;
     
     const double d_realPart_solObs=AMAX1(org_prtl->d_realPart_solObs,d_realPart_solObs_min);
-    // LOG(INFO)<<"final distance real part <-> tangent"<<d_realPart_solObs;
+    // LOG(INFO)<<"final distance real prtl. <-> tangent"<<d_realPart_solObs;
 
     //finally return the virtual velocity 
     const Vec2d U_virt= -1*d_ghost_tang/d_realPart_solObs*org_prtl->U;

### 2010-12-07 src/material.h

@@ -67,6 +67,12 @@ public:
 	double get_rho(const double p, const double e) const;//equation of state for gasdynamics
 	///get interal energy
 	double get_e(const double T) const;
+
+	/* ///updates internal energy of a particle to be coherent */
+	/* /// with its temperature  */
+	/* ///(used for ghost particles for solid obstcales) */
+	/* void update_e(const spParticle& prtl); */
+
 	///get temperature 
 	double get_T(const double e) const;//(function is defined nowhere)
 

### 2010-12-15 gnuplot/TaylorGreen/AnalyzeVelocDecay.sh
docu updated

@@ -1,7 +1,7 @@
 #! /bin/bash
 
 #eps solid for solid (not dashed) lines, momochrome (instead of color),... 
-#cp ../../src/outdata/prtl$1.dat prtl$1.dat
+
 mkdir Figures
 
 gnuplot << EOF
@@ -12,13 +12,13 @@ set output "Figures/VelocDecay.eps"
 
 set grid;
 set y2label "(relative) error";
-set y2range [0:1]
+
 set y2tics border
 #set mxtics 0.05;
 #set xtics 0.25;
 
 set xlabel "Time"; set ylabel "Maximum Velocity (abs. value)";
-plot [0.0:0.000005][0.0:0.04] 'decayAnalysis.dat' u 1:2 title 'exact' with line, 'decayAnalysis.dat' u 1:3 title 'simu' with points,'decayAnalysis.dat' u 1:4 axes x1y2 title 'error' with line;
+plot [0.0:][0.0:] 'decayAnalysis.dat' u 1:3 title 'Simulation' with points, 'decayAnalysis.dat' u 1:2 title 'Exact' with line, 'decayAnalysis.dat' u 1:4 axes x1y2 title 'Error' with line;
 
 set terminal png
 set output "Figures/VelocDecay.png"

### 2010-12-15 src/TimeSolver/gastimesolverLeapFrog.cpp

@@ -68,25 +68,27 @@ void GasTimeSolverLeapFrog::TimeIntegral_summation(Hydrodynamics &hydro,
     // integeral_time =integeral_time+ dt;
     
     // Time += dt;
-
+     
     //=>dt assignment moved just after update change rate so that change rates
     // from current step are taken into account
-
-    // try oscillating wall
-
-    // //generate first wave at instant t=0
-    // if(Time<0.422577127)
-    //   boundary.UxBl[0]=0.05916*sin(14.86873023*Time);
-    // if(Time>=0.422577127-1e-7)
-    //   boundary.UxBl[0]=0;
-    
-    // // generate second wave as soon as first wave hits RHS wall
-    // if(Time>1.690308509 && Time<2.112885637)
-    //   boundary.UxBl[0]=0.05916*sin(14.86873023*Time);
-    // if(Time>=2.112885637-1e-7)
-    //   boundary.UxBl[0]=0;
-    LOG(INFO)<<"ite is "<<ite;
-    if(ite!=1)
+     
+    // BEGIN OSCILLATING WALL PASSAGE (please uncomment)
+     
+    //generate first wave at instant t=0
+    if(Time<0.422577127)
+      boundary.UxBl[0]=0.05916*sin(14.86873023*Time);
+    if(Time>=0.422577127-1e-7)
+      boundary.UxBl[0]=0;
+     
+    // generate second wave as soon as first wave hits RHS wall
+    if(Time>1.690308509 && Time<2.112885637)
+      boundary.UxBl[0]=0.05916*sin(14.86873023*Time);
+    if(Time>=2.112885637-1e-7)
+      boundary.UxBl[0]=0;
+     
+     // END OSCILLATING WALL PASSAGE
+     LOG(INFO)<<"ite is "<<ite;
+     if(ite!=1)
       {
 	hydro.UpdateUe2FullStep(dt);
 	

### 2010-12-15 src/sph.cpp

@@ -184,9 +184,21 @@ int main(int argc, char *argv[]) {
     boundary.BuildBoundaryParticle(particles, hydro, Time);
   
   Output output; ///- initialize output class (should be the last to be initialized)
-  //predict particle volume and mass (if mass not initialized externally)
-  if(ini.external_mass_initialization==0)
-    ini.VolumeMass(hydro, particles, weight_function, obstacles); //predict particle volume and mass
+  //predict particle volume and mass (if mass not initialized externally
+  // AND for gas dynamicy: if not started from restart file, as restart file)
+  if(ini.external_mass_initialization==0) {
+    //if new simulation
+    if(ini.initial_condition==0)
+      //predict particle volume and mass
+      ini.VolumeMass(hydro, particles, weight_function, obstacles);
+    // if started from restart file, caluclate mass only for liquids mode
+    // as it would overwrite the inital mass values for gases
+    else if (ini.simu_mode==1)
+      ini.VolumeMass(hydro, particles, weight_function, obstacles);
+    //if restart for gasdynamics: only calculate volume
+    else
+      hydro.UpdateVolume(particles, weight_function);
+  }
   
   //for 2D particle distribution BC is needed
   ///\todo{define a variable which controls the use of boundary conditions and solve it smarter than just testing  if  (ini.kernel_type != "CubicSpline1D")! done: disable_boundary marker! }

### 2010-12-23 ms/Graphics/results/1DCode/compareResults.sh
thesis update

@@ -9,13 +9,14 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 set output "pressure.eps"
 
 
-set border lw 3;
-set grid lw 3;
+#set border lw 3;
+#set grid lw 3;
+set grid
 set mxtics;
 set xtics;
 #lw sets line width (1= normal)
-set xlabel "length x"; set ylabel "pressure p";
-plot [-0.5:0.5][0.0:1.1] 'dataStep$1.txt' u 1:4 title 'Simulation' with line lw 8,"compData/ExactResultsN80.txt" using 1:3 title 'Exact' with line lw 8;
+set xlabel "Position x"; set ylabel "Pressure p";
+plot [-0.5:0.5][0.0:1.1] "compData/ExactResultsN80.txt" using 1:3 title 'Exact' with line lt 2 lw 8, 'dataStep$1.txt' u 1:4 title 'Simulation' with line lt 1 lw 8;
 
 #### large for large fonts, options: tiny , small , medium,large, giant (does not work for postscript)
 
@@ -29,13 +30,14 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 26
 set output "velocity.eps"
 
-set border lw 3;
-set grid;
+#set border lw 3;
+#set grid lw 3;
+set grid
 set mxtics 0.05;
 set xtics 0.25;
 
-set xlabel "length x"; set ylabel "velocity u"; 
-plot [-0.5:0.5][0.0:1.15] 'dataStep$1.txt' u 1:5 title'Simulation' with line lw 8,"compData/ExactResultsN80.txt" using 1:4 title 'Exact' with line lw 8;
+set xlabel "Position x"; set ylabel "Velocity u"; 
+plot [-0.5:0.5][0.0:1.15] "compData/ExactResultsN80.txt" using 1:4 title 'Exact' with line lt 2 lw 8, 'dataStep$1.txt' u 1:5 title'Simulation' with line lt 1 lw 8;
 
 set terminal png  large 
 set output "velocity.png"
@@ -47,13 +49,15 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 26
 set output "density.eps"
 
-set border lw 3;
-set grid;
+
+#set border lw 3;
+#set grid lw 3;
+set grid
 set mxtics 0.05;
 set xtics 0.25;
 
-set xlabel "length x"; set ylabel "density rho";
[…]

### 2010-12-23 ms/Graphics/results/CompressibleCouette/N2x40_supLen_dx4_compressible/showUTProfiles.sh

@@ -10,8 +10,8 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 set output "U_profile$1.eps"
 set key top left
 set grid;
-set xlabel "U"; set ylabel "length y";
-plot [0.0:][0.0:1.0] 'U_line.dat' u 2:1 notitle with line lt -1 lw 0.1, 'prtl$1.dat' u 3:2 title 'simu' lt 1 with points;
+set xlabel "Velocity u"; set ylabel "Position y";
+plot [0.0:][0.0:1.0] 'U_line.dat' u 2:1 notitle with line lt -1 lw 0.1, 'prtl$1.dat' u 3:2 notitle lt 1 with points;
 
 set terminal png large
 set output "U_profile$1.png"
@@ -24,8 +24,8 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 set output "T_profile$1.eps"
 set key top left
 set grid;
-set xlabel "T"; set ylabel "length y";
-plot [:][0.0:1.0] 'prtl$1.dat' u 6:2 title 'simu' lt 1 with points;
+set xlabel "Temperature T"; set ylabel "Position y";
+plot [:][0.0:1.0] 'prtl$1.dat' u 6:2 notitle lt 1 with points;
 
 set terminal png large
 set output "T_profile$1.png"

### 2010-12-23 ms/Graphics/results/Porosities/LinearWall/Poiseuille_DomainEdgeBC_N4x40_suplen4dx_t3sec/compProfiles.sh

@@ -8,10 +8,11 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 
 set output "U_profiles$1.eps"
 
-
+set key 0.005,0.07
 set grid;
-set xlabel "U"; set ylabel "length y";
-plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'simu' lt 1 with points;
+set xtics 0.002
+set xlabel "Velocity u"; set ylabel "Position y";
+plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'Exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'Simulation' lt 1 lw 8 with points;
 
 set terminal png large
 set output "U_profiles$1.png"

### 2010-12-23 ms/Graphics/results/Porosities/LinearWall/Poiseuille_SolObsBC1_N4x40_suplen2dx_t3sec_ghost_prtl_on_surface/compProfiles.sh

@@ -8,10 +8,10 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 
 set output "U_profiles$1.eps"
 
-
+set key 0.006,0.07 
 set grid;
-set xlabel "U"; set ylabel "length y";
-plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'simu' lt 1 with points;
+set xlabel "Velocity u"; set ylabel "Position y";
+plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'Exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'Simulation' lt 1 lw 8 with points;
 
 set terminal png large
 set output "U_profiles$1.png"

### 2010-12-23 ms/Graphics/results/Porosities/LinearWall/Poiseuille_SolObsBC2_N4x40_suplen2dx_t3sec_ghost_prtl_dx2_from_surface/compProfiles.sh

@@ -8,10 +8,10 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 
 set output "U_profiles$1.eps"
 
-
+#set key 0.006,0.07 
 set grid;
-set xlabel "U"; set ylabel "length y";
-plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'simu' lt 1 with points;
+set xlabel "Velocity u"; set ylabel "Position y";
+plot [0.0:][-0.5:0.5]  'exact$1.dat' u 2:1 title 'Exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 2:1 title 'Simulation' lt 1 lw 8 with points;
 
 set terminal png large
 set output "U_profiles$1.png"

### 2010-12-23 ms/Graphics/results/Porosities/LinearWall/ThermalBC1_N2x39_suplen2dx/compProfiles.sh

@@ -1,7 +1,7 @@
 #! /bin/bash
 
 #eps solid for solid (not dashed) lines, momochrome (instead of color),... 
-cp ../../src/outdata/prtl$1.dat prtl$1.dat
+#cp ../../src/outdata/prtl$1.dat prtl$1.dat
 
 gnuplot << EOF
 set terminal postscript eps enhanced color  "Helvetica" 26
@@ -10,8 +10,8 @@ set output "T_profiles$1.eps"
 
 
 set grid;
-set xlabel "length y"; set ylabel "T";
-plot [0.0:0.5][0.0:1.0]  'exact$1.dat' u 1:2 title 'exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 1:2 title 'simu' lt 1 with points;
+set xlabel "Position y"; set ylabel "Temperature T";
+plot [0.0:0.5][0.0:1.0]  'exact$1.dat' u 1:2 title 'Exact' with line lt 2 lw 8,'simuForPlot$1.dat' u 1:2 title 'Simulation' lt 1 lw 8 with points;
 
 set terminal png large
 set output "T_profiles$1.png"

### 2010-12-23 ms/Graphics/results/PureHeatConduction/ErrorTimestep.sh

@@ -7,7 +7,7 @@ set terminal postscript eps enhanced color  "Helvetica" 26
 
 set output "ErrorTimestep.eps"
 
-
+set key top left
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -15,7 +15,7 @@ set format y "10^{%L}"
 #set ylabel "Y-AXIS" 2,0 # to move y axis to the left by 2 points
 
 set grid;
-set xlabel "Timestep"; set ylabel "Error";
+set xlabel "Time step dt"; set ylabel "Error";
 plot  'ErrorTimestep.dat' u 1:2 title 'L_{1 } error' with linespoints lw 8, 'ErrorTimestep.dat' u 1:3 title 'L_{2 } error' with linespoints lw 8,'ErrorTimestep.dat' u 1:4 title 'L_{inf} error' with linespoints lw 8;
 
 set terminal png large

### 2010-12-23 ms/Graphics/results/ShockTube/1D_CM_LF_SD/ratio_supLen_m_const16/ErrorDataSeparated.sh

@@ -8,7 +8,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainRho.eps"
 
 set grid; set key 0.11, 0.0048
-set xlabel "Supportlength"; set ylabel "Error rho";
+set xlabel "Support length l_s"; set ylabel "Error rho";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -23,7 +23,7 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainU.eps"
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error U";
+set xlabel "Support length l_s"; set ylabel "Error u";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -39,7 +39,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainE.eps"
 
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error e";
+set xlabel "Support length l_s"; set ylabel "Error e";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -55,7 +55,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3Rho.eps"
 
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error rho";
+set xlabel "Support length l_s"; set ylabel "Error rho";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -70,7 +70,7 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3U.eps"
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error U";
+set xlabel "Support length l_s"; set ylabel "Error u";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -85,7 +85,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3E.eps"
 
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error e";
+set xlabel "Support length l_s"; set ylabel "Error e";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -100,7 +100,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area2Rho.eps"
 
 set grid; set nokey
[…]

### 2010-12-23 ms/Graphics/results/ShockTube/1D_CM_LF_SD/supLenVariat_m001875/ErrorDataSeparated.sh

@@ -8,7 +8,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainRho.eps"
 
 set grid; set key 0.105, 0.0098
-set xlabel "Supportlength"; set ylabel "Error rho";
+set xlabel "Support length l_s"; set ylabel "Error rho";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -23,7 +23,7 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainU.eps"
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error U";
+set xlabel "Support length l_s"; set ylabel "Error u";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -39,7 +39,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainE.eps"
 
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error e";
+set xlabel "Support length l_s"; set ylabel "Error e";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -55,7 +55,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3Rho.eps"
 
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error rho";
+set xlabel "Support length l_s"; set ylabel "Error rho";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -70,7 +70,7 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3U.eps"
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error U";
+set xlabel "Support length l_s"; set ylabel "Error u";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -85,7 +85,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3E.eps"
 
 set grid; set nokey
-set xlabel "Supportlength"; set ylabel "Error e";
+set xlabel "Support length l_s"; set ylabel "Error e";
 set logscale x
 set logscale y
 set format y "10^{%L}"
@@ -100,7 +100,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area2Rho.eps"
 
 set grid; set nokey
[…]

### 2010-12-23 ms/Graphics/results/ShockTube/1D_CS_LF_SD/dtVariat_dx005_SupLen03/ErrorDataSeparated.sh

@@ -8,10 +8,10 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainRho.eps"
 
 set grid; set key 0.11, 0.0048
-set xlabel "Timestep"; set ylabel "Error rho";
+set xlabel "Time step dt"; set ylabel "Error rho";
 set logscale x
 set logscale y
-set format y "10^{%L}"
+set format y "10^{%L}"; set format x "10^{%L}"
 
 plot [:][:] 'ErrorData.dat' u 1:2 title 'L_1' with linespoints lw 8, 'ErrorData.dat' u 1:5 title 'L_2' with linespoints lw 8, 'ErrorData.dat' u 1:8 title 'L_{inf}' with linespoints lw 8;
 
@@ -23,10 +23,10 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainU.eps"
 set grid; set nokey
-set xlabel "Timestep"; set ylabel "Error U";
+set xlabel "Time step dt"; set ylabel "Error u";
 set logscale x
 set logscale y
-set format y "10^{%L}"
+set format y "10^{%L}"; set format x "10^{%L}"
 
 plot [:][:] 'ErrorData.dat' u 1:3 title 'L_1' with linespoints lw 8, 'ErrorData.dat' u 1:6 title 'L_2' with linespoints lw 8, 'ErrorData.dat' u 1:9 title 'L_{inf}' with linespoints lw 8;
 
@@ -39,10 +39,10 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainE.eps"
 
 set grid; set nokey
-set xlabel "Timestep"; set ylabel "Error e";
+set xlabel "Time step dt"; set ylabel "Error e";
 set logscale x
 set logscale y
-set format y "10^{%L}"
+set format y "10^{%L}"; set format x "10^{%L}"
 
 plot [:][:] 'ErrorData.dat' u 1:4 title 'L_1' with linespoints lw 8, 'ErrorData.dat' u 1:7 title 'L_2' with linespoints lw 8, 'ErrorData.dat' u 1:10 title 'L_{inf}' with linespoints lw 8;
 
@@ -55,10 +55,10 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3Rho.eps"
 
 set grid; set nokey
-set xlabel "Timestep"; set ylabel "Error rho";
[…]

### 2010-12-23 ms/Graphics/results/ShockTube/1D_CS_LF_SD/dtVariat_dx005_SupLen03_dt03_Oscillations/compareResults.sh

@@ -14,8 +14,8 @@ set y2tics border
 set mxtics 0.05;
 set xtics 0.25;
 
-set xlabel "length x"; set ylabel "pressure p";
-plot [1.5:2.5][0.0:1.5] 'prtl$1.dat' u 1:4 title 'simu' with line lw 8, 'relError$1.dat' u 1:4 title 'exact' with line lw 8,  'relError$1.dat' u 1:5 axes x1y2 title 'error'with line lw 8;
+set xlabel "Position x"; set ylabel "Pressure p";
+plot [1.5:2.5][0.0:1.5] 'prtl$1.dat' u 1:4 title 'Simulation' with line lw 8, 'relError$1.dat' u 1:4 title 'Exact' with line lw 8,  'relError$1.dat' u 1:5 axes x1y2 title 'error'with line lw 8;
 
 
 set terminal png
@@ -34,8 +34,8 @@ set y2tics border
 set mxtics 0.05;
 set xtics 0.25;
 
-set xlabel "length x"; set ylabel "density rho";
- plot [1.5:2.5][0.0:1.3]  'prtl$1.dat' u 1:3 title 'simu' with line lw 8,'relError$1.dat' u 1:2 title 'exact' with line lw 8,'relError$1.dat' u 1:3 axes x1y2 title 'error'with line lw 8;
+set xlabel "Position x"; set ylabel "Density rho";
+ plot [1.5:2.5][0.0:1.3]  'prtl$1.dat' u 1:3 title 'Simulation' with line lw 8,'relError$1.dat' u 1:2 title 'Exact' with line lw 8,'relError$1.dat' u 1:3 axes x1y2 title 'error'with line lw 8;
 
 set terminal png
 set output "Err_rho$1.png"
@@ -47,15 +47,15 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 26
 set output "Err_u$1.eps"
 
-set grid; set key left top
-set y2label "(absolute) error";
-set y2range [0:1]
-set y2tics border
+set grid; set key 1.95,1.08
+#set y2label "(absolute) error";
+#set y2range [0:1]
+#set y2tics border
 set mxtics 0.05;
 set xtics 0.25;
 
-set xlabel "length x"; set ylabel "velocity u";
[…]

### 2010-12-23 ms/Graphics/results/ShockTube/PertStudy/basedOn1DconstSpace/ErrorDataSeparated.sh

@@ -7,8 +7,8 @@ gnuplot << EOF
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainRho.eps"
 
-set grid; set key 0.11, 0.0048
-set xlabel "Perturbation"; set ylabel "Error rho";
+set grid; set key 0.29, 0.06
+set xlabel "Perturbation factor"; set ylabel "Error rho";
 
 
 plot [:][:] 'ErrorData.dat' u 1:2 title 'L_1' with linespoints lw 8, 'ErrorData.dat' u 1:5 title 'L_2' with linespoints lw 8, 'ErrorData.dat' u 1:8 title 'L_{inf}' with linespoints lw 8;
@@ -21,7 +21,7 @@ reset
 set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainU.eps"
 set grid; set nokey
-set xlabel "Perturbation"; set ylabel "Error U";
+set xlabel "Perturbation factor"; set ylabel "Error u";
  
 
 plot [:][:] 'ErrorData.dat' u 1:3 title 'L_1' with linespoints lw 8, 'ErrorData.dat' u 1:6 title 'L_2' with linespoints lw 8, 'ErrorData.dat' u 1:9 title 'L_{inf}' with linespoints lw 8;
@@ -35,7 +35,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "WholeDomainE.eps"
 
 set grid; set nokey
-set xlabel "Perturbation"; set ylabel "Error e";
+set xlabel "Perturbation factor"; set ylabel "Error e";
 
 
 plot [:][:] 'ErrorData.dat' u 1:4 title 'L_1' with linespoints lw 8, 'ErrorData.dat' u 1:7 title 'L_2' with linespoints lw 8, 'ErrorData.dat' u 1:10 title 'L_{inf}' with linespoints lw 8;
@@ -49,7 +49,7 @@ set terminal postscript eps enhanced color "Helvetica" 36
 set output "Area3Rho.eps"
 
 set grid; set nokey
-set xlabel "Perturbation"; set ylabel "Error rho";
+set xlabel "Perturbation factor"; set ylabel "Error rho";
 
 
[…]

### 2010-12-23 ms/Graphics/results/ShockTube/q1D_CS_LF_SD/supLenVariat_dxdy005/Variance/VarianceVersusSupLen.sh

@@ -12,8 +12,8 @@ set grid;
 set key top right;
 set format y "10^{%L}"
 set logscale y;
-set xlabel "Supportlength"; set ylabel "Variance";
-plot [0.015:0.045][:] 'VarianceVersusSuplen.dat' u 1:2 title 'x-position' with linespoints lw 8, 'VarianceVersusSuplen.dat' u 1:3 title 'density' with linespoints lw 8, 'VarianceVersusSuplen.dat' u 1:5 title 'velocity' with linespoints lw 8;
+set xlabel "Support length l_s"; set ylabel "Variance";
+plot [0.015:0.045][:] 'VarianceVersusSuplen.dat' u 1:2 title 'x-position' with linespoints lw 8, 'VarianceVersusSuplen.dat' u 1:3 title 'Density' with linespoints lw 8, 'VarianceVersusSuplen.dat' u 1:5 title 'Velocity' with linespoints lw 8;
 
 
 set terminal png
@@ -29,8 +29,8 @@ set grid;
 set key top right;
 set format y "10^{%L}"
 set logscale y;
-set xlabel "Supportlength"; set ylabel "Variance";
-plot [0.015:0.045][:] 'VarianceVersusSuplen.dat' u 1:4 title 'pressure' with linespoints lw 8, 'VarianceVersusSuplen.dat' u 1:6 title 'energy' with linespoints lw 8;
+set xlabel "Support length l_s"; set ylabel "Variance";
+plot [0.015:0.045][:] 'VarianceVersusSuplen.dat' u 1:4 title 'Pressure' with linespoints lw 8, 'VarianceVersusSuplen.dat' u 1:6 title 'Energy' with linespoints lw 8;
 
 set terminal png
 set output "VariancePart2.png"

### 2010-12-23 ms/Graphics/results/ShockTube/q1D_CS_LF_SD/supLenVariat_dxdy005/Variance/suplen02/VarianceVersusPositionPlot.sh

@@ -12,8 +12,8 @@ set grid;
 set key top left;
 set format y "10^{%L}"
 set logscale y;
-set xlabel "length x"; set ylabel "variance";
-plot [1.5:2.5][1e-15:] 'variance$1.dat' u 1:4 title 'density' with line lw 8, 'variance$1.dat' u 1:6 title 'velocity' with line lw 8;
+set xlabel "Position x"; set ylabel "Variance";
+plot [1.5:2.5][1e-15:] 'variance$1.dat' u 1:4 title 'Density' with line lw 8, 'variance$1.dat' u 1:6 title 'Velocity' with line lw 8;
 
 set terminal png
 set output "Variance$1.png"

### 2010-12-23 scripts/postProcessingShockTube/exactResAndErr1DST.cpp

@@ -100,8 +100,8 @@ int main () {
   // for simulation) as for changed conditions, p_2 has to be calculated
   // manually anyway (see below)
   const double gamma=1.4;
-  const double rho_1=0.125; 
-  // const double rho_1=0.1111111111111111;//for 2D const Mass particle distribution
+  //const double rho_1=0.125; 
+  const double rho_1=0.1111111111111111;//for 2D const Mass particle distribution
   const double p_1=0.1;
   const double u_1=0.0;
   const double e_1=p_1/((gamma-1)*rho_1);
@@ -126,8 +126,8 @@ int main () {
   // case with density ratio 9 (rho_4=1, rho_1=0.11111111111) all the other values
   // remain unchanged
   
-  const double p_2=0.303130178;//for rho_4=1, rho_1=0.125
-  // const double p_2=0.293309753;//for rho_4=1, rho_1=0.111111111
+  // const double p_2=0.303130178;//for rho_4=1, rho_1=0.125
+  const double p_2=0.293309753;//for rho_4=1, rho_1=0.111111111
   const double p_3=p_2; // pressure the same over contact discontinuity
   
   // rho_2 with shock relation from state 1
